### 2019-06-28 paper.tex
Skelection version

\documentclass[ALICE,manyauthors]{cernphprep}

\usepackage[comma,square,numbers,sort&compress]{natbib}
\usepackage{hyperref}
\usepackage{lineno}
\usepackage{subcaption}
\usepackage[section]{placeins}
\usepackage {multicol}% Multi column in the table
\usepackage {multirow}% Multi row in the table
\usepackage {units}

\linenumbers

\input{commands.tex}
\begin{document}%

%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
\begin{titlepage}

\PHyear{}
\PHnumber{2019-xxx}      % required, will be obtained from PH
%\PHdate{Day Month}  % required, will be obtained from PH
\PHdate{\today}
%

%%% Put your own title + short title here:
\title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV}}
\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers

%%% Do not change the next lines
%\Collaboration{ALICE Collaboration\thanks{See Appendix~\ref{app:collab} for the list of collaboration members}}
\ShortAuthor{ALICE Collaboration} % appears on left page headers, do not change

\begin{abstract}

\end{abstract}
\end{titlepage}
\setcounter{page}{2}

\section{Introduction}

\section{Experimental setup}

\section {Data sample and analysis}

\section {Results}

\section{Conclusions}

%%%%% acknowledgements
\newenvironment{acknowledgement}{\relax}{\relax}
%\begin{acknowledgement}
%\section*{Acknowledgements}
%\input{acknowledgements.tex}    %%%%%%% done by webmaster team
%\end{acknowledgement}

%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
%\bibliographystyle{utphys}   % Remember we use title in the biblio
%\bibliography{biblio}
%\input {bibliography.tex}

%%%%%%%%% appendix with author list
\newpage
\appendix
%
%\input{}               %%%%%%%%%%% put your appendices here
%

%\section{The ALICE Collaboration}
%\label{app:collab}
%\input{authorlist-preprint.tex}  %%%%%%% done by webmaster team

\clearpage
\bibliography{reference}
\bibliographystyle{utphys}

\end{document}

### 2019-07-08 paper.tex
intro

@@
 
+%Studies of particle correlations in high-energy hadronhadron collisions provide valuable information on the underlying quantum chromodynamics processes leading to particle production.
+Measurements of two-particle angular correlations are typically performed in terms of twodimensional Δη-Δϕ correlation functions, where η is the pseudorapidity and ϕ is the azimuthal angle.
+Of particular interest in studies of possible novel partonic collective effects is the long-range (e.g., jΔηj > 2.0) structure of twoparticle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
+In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side (Δϕ ≈ π) jet correlations.
+Measurements in high-energy nucleusnucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed [1].
+Several novel features were observed in azimuthal correlations over large Δη for intermediate particle transverse momenta, pT ≈ 1–5 GeV=c [2,3].
+These correlations are thought to arise from the response of a hydrodynamically expanding partonic medium to fluctuations of the initial collision geometry [4–9].
+Measurements in pp collisions at a center-of-mass energy of ffiffi s p ¼ 7 TeV have also revealed the presence of long-range, near-side (Δϕ ≈ 0) correlations in events with very large final-state particle multiplicity [10].
+Similar phenomena have also been observed in high-multiplicity proton-lead (pPb) collisions [11–13], where they have been studied extensively [14–21].
+A wide range of models have been suggested to explain the emergence of these correlations in pp [22] and pPb [23–27] collisions.
+While models based on a hydrodynamic approach can describe many aspects of the observed correlations [23,24], it has been proposed that initial-state correlations of gluon fields could also lead to similar effects [25–27].
+
+%Two-particle correlations are a powerful tool to explore the mechanism of particle production in collisions of hadrons and nu-clei at high energy.
+Such studies involve measuring the distribu-tions of relative anglesφandηbetween pairs of particles: a“trigger” particle in a certain transverse momentumpT,trigintervaland an “associated” particle in apT,associnterval, whereφandηare the differences in azimuthal angleφand pseudorapidityηbetween the two particles.In proton–proton (pp) collisions, the correlation at (φ≈0,η≈0) forpT,trig>2GeV/cis dominated by the “near-side” jetpeak, where trigger and associated particles originate from a frag-menting parton, and atφ≈πby the recoil or “away-side” jet[1].The away-side structure is elongated alongηdue to the longitu-dinal momentum distribution of partons in the colliding protons.In nucleus–nucleus collisions, the jet-related correlations are mod-ified and additional structures emerge, which persist over a longrange inηon the near side and on the away side[2–14].Theshape of these distributions when decomposed into a Fourier se-ries defined byvncoefficients[15]is found to be dominated bycontributions from terms withn=2 andn=3 [6,7,9–14].Thevncoefficients are sensitive to the geometry of the initial stateof the colliding nuclei[16,17]and can be related to the transport properties of the strongly-interacting de-confined matter via hy-drodynamic models[18–20].Recently, measurements in pp collisions at a centre-of-massenergy√s=7TeV[21]and in proton–lead (p–Pb) collisions ata nucleon–nucleon centre-of-mass energy√sNN=5.02 TeV[22]have revealed long-range (2<|η|<4) near-side (φ≈0) cor-relations in events with significantly higher-than-average particlemultiplicity.
+Various mechanisms have been proposed to explainthe origin of these ridge-like correlations in high-multiplicity ppand p–Pb events.
+These mechanisms include colour connectionsforming along the longitudinal direction[23–26], jet-medium[27]and multi-parton induced[28,29]interactions, and collective ef-fects arising in the high-density system possibly formed in thesecollisions[30–35].Results from two-particle correlations in√sNN=0.2TeVd–Aucollisions[36,37]show a strong suppression of the away-side yieldat forward rapidity in central collisions.
+This modification has beeninterpreted in the framework of “Colour Glass Condensate” mod-els [38]as a saturation effect caused by nonlinear gluon inter-actions in the high-density regime at small longitudinal partonmomentum fractionx.
+Similar effects may arise at midrapidity inp–Pb collisions at√sNN=5.02 TeV, where the parton distributionsare probed down tox<10−3, which is comparable to the relevantrange ofxat forward rapidity (y∼3) at√sNN=0.2TeV.This Letter presents results extracted from two-particle cor-relation measurements in p–Pb collisions at√sNN=5.02 TeV,recorded with the ALICE detector[39]at the Large Hadron Col-lider (LHC).
+The correlations are measured over two units of pseudorapidity and full azimuthal angle as a function of charged-particle multiplicity, and expressed as associated yield per triggerparticle.
+Sections2 and 3describe the experimental setup, andthe event and track selection, respectively.
+Details on the defini-tion of the correlation and the per-trigger-particle associated yieldare given in Section4.
+The results of the analysis are discussed inSection5 and a summary is given in Section
+
+Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
+The enhancement in the production of two-particle correlations at small relative azimuthal angle($\Delta\varphi$) that extends over a long-range of relative pseudorapidity($\Delta\eta$) is often referred to as the “ridge”, which is one observable of the collective effect.
+In recent years, many results of unexpected observation of ridge in small systems, like proton-proton collisions and proton-nucleus collisions, has been reported, showing similar features to those in heavy ion collisions, where the volume and lifetime of the medium produced are expected to be to small to form Quark Gluon Plasma(QGP) thought to play a important and dominant role in formation of the ridge in heavy ion collisions.
+There are many theoretical trials to interpret the ridge considering hydrodynamics, saturation or other mechanisms, not demonstrating measured data fully, because the sources of the ridge is not understood quantitatively.
+The understanding of possible origins of the ridge in small systems may provide a hint to distinguish the mechanism of formation of ridges in large systems and small systems.
+
+%Measurements of two-particle angular correlations in high-multiplicity proton-proton (pp) collisions at a centerof-mass energy ffiffi s p ¼ 7 TeV at the LHC showed an enhancement in the production of pairs at small azimuthal-angle separation, Δϕ, that extends over a wide range of pseudorapidity differences, Δη, and which is often referred to as the “ridge” [1].
+The ridge has also been observed in proton-lead (p þ Pb) collisions [2–7], where it is found to result from a global sinusoidal modulation of the per-event single-particle azimuthal angle distributions [3–6].
+While many theoretical interpretations of the ridge, including those based on hydrodynamics [8–12], saturation [13–23], or other mechanisms [24–30], have been, or could be applied to both pp and p þ Pb collisions, it has not yet been demonstrated that the ridge in pp collisions results from single-particle azimuthal anisotropies.
+Testing whether the ridges in pp and p þ Pb collisions arise from the same underlying features of the single-particle distributions may provide insight into the physics responsible for the phenomena.
+Separately, a study of the ffiffi s p dependence
+%Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
+One novel tool for studying the collective effect is two-particle angular correlations as function of relative pseudo-rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$) between the trigger particle and the associated particle.
+The main source of collective
+
+%QCD has been studied through particles produced in heavy ion collisions.
+Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions.
+One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle.
+Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.
 \section{Experimental setup}

### 2019-07-10 paper.tex
experimental setup

@@
 \title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV}}
-\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
+\ShortTitle{Long-range correlations in \pp collisions}   % appears on right page headers
 
@@
 Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
-The enhancement in the production of two-particle correlations at small relative azimuthal angle($\Delta\varphi$) that extends over a long-range of relative pseudorapidity($\Delta\eta$) is often referred to as the “ridge”, which is one observable of the collective effect.
-In recent years, many results of unexpected observation of ridge in small systems, like proton-proton collisions and proton-nucleus collisions, has been reported, showing similar features to those in heavy ion collisions, where the volume and lifetime of the medium produced are expected to be to small to form Quark Gluon Plasma(QGP) thought to play a important and dominant role in formation of the ridge in heavy ion collisions.
+The enhancement in the production of two-particle correlations at small relative azimuthal angle($\Delta\varphi$) that extends over a long-range of relative pseudorapidity($\Delta\eta$) is often referred to as the “ridge”, which is one crucial observables of the collective effect.
+In recent years, many results of unexpected observation of ridge in small systems, like proton-proton(pp) collisions and proton-nucleus(pA) collisions, has been reported, showing similar features to those in heavy ion collisions, where the volume and lifetime of the medium produced are expected to be to small to form Quark Gluon Plasma(QGP) thought to play a important and dominant role in formation of the ridge in heavy ion collisions.
 There are many theoretical trials to interpret the ridge considering hydrodynamics, saturation or other mechanisms, not demonstrating measured data fully, because the sources of the ridge is not understood quantitatively.
@@
 \section{Experimental setup}
+Collisions of proton and proton were provided by the LHC for a few years from 2015 to 2018 with various energy during Run2 period.
+The used beam energies were \unit[6.5]{TeV} for both protons so that center-of-mass energy is \unit[13]{TeV}.
+Among data from pp collisions at \unit[13]{TeV}, This paper shows the results with 2016 to 2017 data set whose total cross section corresponds to xxx.
+Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref(?).
+The VZERO is separated into two plates, VZERO-A and VZERO-C, consisting of two arrays of 32 scintillator tiles each, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively.
+The VZERO provides trigger and event characterization with respect to particle-multiplicity.
+The ITS is composed of three subsystem, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD).
+Each subsystem consists of two layers with an acceptance of $|\eta|<$1.95, $|\eta|<$1.xx and $|\eta|<$1.xx.
+The TPC, which is operated inside a solenoidal magnetic field of 0.5 T, have an acceptance of $|\eta|<$0.9 for tracks reaching the outer radius of the TPC.
+In pp collisions, trigger requirement is fulfilled by the combination of SPD, VZERO-A or VZERO-C.
 

### 2019-07-13 paper.tex
Test

@@
 Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.
+
 \section{Experimental setup}
@@
 
-\section {Data sample and analysis}
+\section {Event and track selection}
+Several event selections have been applied to the data set to reject bad signals.
+Multiple collisions in the same time(<100 ns) is tagged as "Pileup", which is detected by SPD.
+The Pileup events have been rejected from the present analysis.
+Primary vertex range has been chosen as $|z_{\rm{vtx}}|<$8 cm to keep higher tracking efficiency  in large $\eta$ region.
+The event classes are separated through charged particle-multiplicity using VZERO.
+The analysis uses ITS and TPC to reconstruct the track of the charged particle.
+The reconstructed tracks have been selected with $|\eta|<$0.9 and $\it{p}_{\rm{T}}>$0.2 GeV/\it{c}\rm{}.
+The efficiency of track reconstructed has been estimated from a Monte Carlo(MC) simulation using PYTHIA event generator.
+
+\section {Analysis}
+The two-particle angular correlation between trigger particle and associated particle has been measured as function of relative pseudo-rapidity versus relative azimuthal angle.
+Two particles constructing the correlation are defined as the trigger particle and the associated particle by considering magnitude of transverse momentum of two particles to be $\it{p}_{\rm{T}}^{\rm{trig}}>\it{p}_{\rm{T}}^{\rm{assoc}}$.
+The correlation takes the number of the trigger particles into its denominator to make the correlation present the associated yield.
 

### 2019-10-14 paper.tex
Some updates by following the proceeding

--- 2019-07-08 paper.tex
@@
 %%% Put your own title + short title here:
-\title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV}}
-\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
+\title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV} with ALICE at the LHC}
+\ShortTitle{Long-range correlations in \pp collisions}   % appears on right page headers
 
@@
 \begin{abstract}
+
+The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
+Many theoretical approaches to interpreting this effect have been developed.
+However, it is still unclear whether these long-range correlations are due to final or initial state effects.
+To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during 2016 and 2017 with ALICE.
+In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
+The results will be compared to previous measurements from CMS and ATLAS experiments.
+In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
 
@@
 
-Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
-The enhancement in the production of two-particle correlations at small relative azimuthal angle($\Delta\varphi$) that extends over a long-range of relative pseudorapidity($\Delta\eta$) is often referred to as the “ridge”, which is one observable of the collective effect.
-In recent years, many results of unexpected observation of ridge in small systems, like proton-proton collisions and proton-nucleus collisions, has been reported, showing similar features to those in heavy ion collisions, where the volume and lifetime of the medium produced are expected to be to small to form Quark Gluon Plasma(QGP) thought to play a important and dominant role in formation of the ridge in heavy ion collisions.
-There are many theoretical trials to interpret the ridge considering hydrodynamics, saturation or other mechanisms, not demonstrating measured data fully, because the sources of the ridge is not understood quantitatively.
-The understanding of possible origins of the ridge in small systems may provide a hint to distinguish the mechanism of formation of ridges in large systems and small systems.
+Collective effect is one of key probes to study evolution of the hot and dense matter created in heavy-ion collisions at unltra-relativistic energy.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle($\Delta\varphi$) that extends over a long-range of relative pseudorapidity($\Delta\eta$) is often referred to as the “ridge”, which is one of the crucial observables of the result from the collective effect\cite{ridge_aa_1, ridge_aa_2}.
+In recent years, many results of unexpected observation of ridge in small systems, like proton-proton(pp) collisions and proton-nucleus(pA) collisions, has been reported(\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}), showing similar features to those in heavy-ion collisions, where the volume and lifetime of the medium produced are expected to be small.
+There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms.
+Those attempts are not demonstrating measured data fully because the sources of the ridge is not understood quantitatively in small systems.
+The understanding of possible origins of the ridge in small systems may provide a hint to distinguish the mechanism of formation of ridges.
 
@@
 Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.
+
 \section{Experimental setup}
 
-\section {Data sample and analysis}
+Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
+Recent center-of-mass energy of colliding two protons is increased up to \unit[13]{TeV} during LHC Run2 period.
+Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2017 data sets.
+
+Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref.
+\cite{ALICEdet}.
+The VZERO is separated into two plates, VZERO-A and VZERO-C, consisting of two arrays of 32 scintillator tiles each, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively.
+The VZERO provides trigger and event characterization with respect to particle abundance.
+With higher threshold, High Multiplicity Trigger can be implemented by VZERO to acquire very high multiplicity events exclusively.
+
+The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD).
+ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
+The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
+The tracking of charged-particles is done with the combination of ITS and TPC, which also enable to reconstruct low transverse momentum tracks down to 0.15 GeV/\it{c}\rm{} with $\sim$70\% efficiency.
+
+\section{Analysis}
+
+The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure from the following results(\cite{ridge_pp_1}).
+The present analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
+The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo(M.C.) simulation with PYTHIA8 event generator with particle transport through the detector using GEANT simulation.
+The efficiency and the contamination are dependent on particle multiplicity, where the tendencies of the changes are opposite each other up to $\sim$10\%, making total correction invariant.
+
+The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$).
+The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
+\begin{eqnarray}
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{assoc}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
+\end{eqnarray}
+Where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
+The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event.
+The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having same primary vertex and multiplicity class as in the events.
+
+The quantitative study of ridge is done with $\Delta\varphi$ distribution in the large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
+The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
+The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum(ZYAM) procedure.
+The minimum yield($C_{\rm{ZYAM}}$) is obtained by fitting the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
+By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution.
+The margin of the integration(near-side) is determined as the minimum point from ZYAM procedure.
+
+The ridge yield is further studied with various hard fragment event selections in pp collisions.
+The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold.
+The leading track is defined as a charged track having the largest transverse momentum in a given event.
+Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge in hard events.
 
 \section {Results}
+The ridge yield as function of transverse momentum of trigger particle and associated particle has been measured with ALICE. The measured spectrum shows ....
 
@@
 \clearpage
-\bibliography{reference}
-\bibliographystyle{utphys}
+
+\begin{thebibliography}{99}
+
+\bibitem{ridge_aa_1}
+CMS Collaboration, "Centrality dependence of dihadron correlations and azimuthal anisotropy harmonics in PbPb collisions at  $\sqrt{\it{s_{\rm{NN}}}} = $2.76 TeV",   Eur. Phys J. C72 (2012)
+\bibitem{ridge_aa_2}
+ALICE Collaboration, "Anisotropic Flow of Charged Particles in Pb-Pb Collisions at $\sqrt{\it{s_{\rm{NN}}}} = $5.02 TeV",  Phys. Rev. Lett. 116, 132302 (2016)
+\bibitem{ridge_pp_1}
+CMS Collaboration, Measurement of Long-Range Near-Side Two-Particle Angular Correlations in pp Collisions at $\sqrt{\it{s}} = $13 TeV", Phys. Rev. Lett. 116, 172302 (2016)
+\bibitem{ridge_pp_2}
+CMS Collaboration, "Evidence for collectivity in pp collisions at the LHC", Phys. Lett. B765 (2017) 193
+\bibitem{ridge_pp_3}
+ALICE Collaboration, "Investigations of anisotropic flow using multi-particle azimuthal correlations in pp, p-Pb, Xe-Xe, and Pb-Pb collisions at the LHC", arXiv:1903.01790 [nucl-ex]
+\bibitem{ridge_pp_4}
+PHENIX Collaboration, "Creation of quark–gluon plasma droplets with three distinct geometries", Nature Phys. 15, 214 (2019)
+, Nature Phys. 13, 535
+\bibitem{ridge_theory_1}
+H. Mäntysaari, B. Schenke, C. Shen and P. Tribedy, "Imprints of fluctuating proton shapes on flow in proton-lead collisions at the LHC", Phys. Lett. B772 (2017) 681
+\bibitem{ridge_theory_2}
+W. Zhao, Y. Zhou, H. Xu, W. Deng, and H. Song, “Hydrodynamic collectivity in proton?proton collisions at 13 TeV,” Phys. Lett. B780 (2018) 495
+\bibitem{ridge_theory_3}
+K. Welsh, J. Singer, and U. W. Heinz, “Initial state fluctuations in collisions between light and heavy ions,” Phys. Rev. C94 no. 2, (2016) 024919
+\bibitem{ridge_theory_4}
+M. Greif, C. Greiner, B. Schenke, S. Schlichting, and Z. Xu, “Importance of initial and final state effects for azimuthal correlations in p+Pb collisions,” Phys. Rev. D96 no. 9, (2017) 091504
+\bibitem{ALICEdet}
+ALICE Collaboration, “The ALICE experiment at the CERN LHC,” JINST 3 (2008) S08002.
+\bibitem{ITSpaper}
+ALICE Collaboration, "Performance of the present ALICE Inner Tracking System and studies for the upgrade",  Journal of Instrumentation, 7, June (2012) C06007
+\bibitem{VZEROpaper}
+ALICE Collaboration, "Performance of the ALICE VZERO system", JINST 8 (2013) P10016
+\bibitem{TPCpaper}
+ALICE Collaboration, "Performance of the ALICE Time Projection Chamber", Physics Procedia 37, (2012) 434
+
+\end{thebibliography}
 

### 2019-11-12 paper.tex
Updates on ALICE Experiments
Figure added

@@
 \usepackage{lineno}
-\usepackage{subcaption}
+%\usepackage{subcaption}
+\usepackage{subfigure}
 \usepackage[section]{placeins}
@@
 \input{commands.tex}
-\begin{document}%
+\begin{document}
 
@@
 \title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV} with ALICE at the LHC}
-\ShortTitle{Long-range correlations in \pp collisions}   % appears on right page headers
+\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
 
@@
 In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
-The results will be compared to previous measurements from CMS and ATLAS experiments.
+The results are compared to previous measurements from CMS and ATLAS experiments.
 In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
@@
 
-Collective effect is one of key probes to study evolution of the hot and dense matter created in heavy-ion collisions at unltra-relativistic energy.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle($\Delta\varphi$) that extends over a long-range of relative pseudorapidity($\Delta\eta$) is often referred to as the “ridge”, which is one of the crucial observables of the result from the collective effect\cite{ridge_aa_1, ridge_aa_2}.
-In recent years, many results of unexpected observation of ridge in small systems, like proton-proton(pp) collisions and proton-nucleus(pA) collisions, has been reported(\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}), showing similar features to those in heavy-ion collisions, where the volume and lifetime of the medium produced are expected to be small.
-There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms.
-Those attempts are not demonstrating measured data fully because the sources of the ridge is not understood quantitatively in small systems.
-The understanding of possible origins of the ridge in small systems may provide a hint to distinguish the mechanism of formation of ridges.
+Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{ridge_aa_1, ridge_aa_2}.
+In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}.
+There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
 
@@
 
+The full description of ALICE detector in the LHC Run 2 can be found in Ref.
+\cite{ALICEdet}.
+The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
+The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively.
+The V0 provides trigger and estimation of event multiplicity.
+A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.
+The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
+ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
+The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
+The tracking of charged-particles is done with the combination of ITS and TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
+
 Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref.
@@
 
+The responsibility of reconstruction of charged track is up to the ITS and the TPC.
 The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD).
@@
 
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure from the following results(\cite{ridge_pp_1}).
-The present analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
-The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo(M.C.) simulation with PYTHIA8 event generator with particle transport through the detector using GEANT simulation.
-The efficiency and the contamination are dependent on particle multiplicity, where the tendencies of the changes are opposite each other up to $\sim$10\%, making total correction invariant.
+The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure.
+This analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
+The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
 
-The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$).
-The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
+The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity and azimuthal angle.
+The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$
 \begin{eqnarray}
@@
 \end{eqnarray}
-Where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
+where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
 The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event.
-The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having same primary vertex and multiplicity class as in the events.
+The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having the same primary vertex and belonging to the same multiplicity class.
 
-The quantitative study of ridge is done with $\Delta\varphi$ distribution in the large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
+The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
 The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
-The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum(ZYAM) procedure.
-The minimum yield($C_{\rm{ZYAM}}$) is obtained by fitting the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
+The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
+The minimum yield ($C_{\rm{ZYAM}}$) is defined as minimum value of the function, which consists of Fourier series up to the third harmonic and is determined by fitting the $\Delta\varphi$ distribution.
 By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution.
-The margin of the integration(near-side) is determined as the minimum point from ZYAM procedure.
+The range of integration is enclosed by the points having the minimum yield, which is obtained from ZYAM procedure.
 
-The ridge yield is further studied with various hard fragment event selections in pp collisions.
+The ridge yield is further studied with various event selections regarding hard processes.
 The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold.
 The leading track is defined as a charged track having the largest transverse momentum in a given event.
-Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge in hard events.
+Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.
 
 \section {Results}
-The ridge yield as function of transverse momentum of trigger particle and associated particle has been measured with ALICE. The measured spectrum shows ....
+
+The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
+The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.
+
+\begin{figure}
+	\centering
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
+	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class.
+The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
+}
+
+\end{figure}
+
+The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
+The associated yield per trigger particle is compared with CMS results.
+The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.
+
+The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results.
+The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
+Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
+Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
+
+\begin{figure}
+	\centering
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
+	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
+Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
+}
+
+\end{figure}
+
+\begin{figure}
+	\centering
+	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/y.pdf} }
+	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
+	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
+	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class.
+The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots.
+Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively.
+}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy1.pdf} }
+	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy2.pdf} }
+	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
+Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
+Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.
+}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/yl.pdf} }
+	\caption{ The ridge yield spectrum with respect to the leading trac∂çk selection. The ridge yields are identical within uncertainties.}
+\end{figure}
+
+To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
+The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
+
+The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Figure 5.
+The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
+
+The ridge yield is inspected as a function of the leading track selection in Figure 6.
+As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
+
+\section{Model Comparison}
 
 \section{Conclusions}
+
+Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE.
+The measured associated yield is found to be consistent with the previous results from CMS experiment.
+The ridge yield, for the first time, has been observed in events including hard processes.
+Furthermore, it is found to be independent of the hardness of the events.
+This observation is important for the study of the origins of the ridge in small collision systems.
 
@@
 \bibitem{ridge_aa_1}
-CMS Collaboration, "Centrality dependence of dihadron correlations and azimuthal anisotropy harmonics in PbPb collisions at  $\sqrt{\it{s_{\rm{NN}}}} = $2.76 TeV",   Eur. Phys J. C72 (2012)
+CMS Collaboration, "Centrality dependence of dihadron correlations and azimuthal anisotropy harmonics in PbPb collisions at  $\sqrt{\it{s_{\rm{NN}}}} = $2.76 TeV",   Eur. Phys J. C72 (2012).
 \bibitem{ridge_aa_2}
-ALICE Collaboration, "Anisotropic Flow of Charged Particles in Pb-Pb Collisions at $\sqrt{\it{s_{\rm{NN}}}} = $5.02 TeV",  Phys. Rev. Lett. 116, 132302 (2016)
+ALICE Collaboration, "Anisotropic Flow of Charged Particles in Pb-Pb Collisions at $\sqrt{\it{s_{\rm{NN}}}} = $5.02 TeV",  Phys. Rev. Lett. 116, 132302 (2016).
 \bibitem{ridge_pp_1}
-CMS Collaboration, Measurement of Long-Range Near-Side Two-Particle Angular Correlations in pp Collisions at $\sqrt{\it{s}} = $13 TeV", Phys. Rev. Lett. 116, 172302 (2016)
+CMS Collaboration, Measurement of Long-Range Near-Side Two-Particle Angular Correlations in pp Collisions at $\sqrt{\it{s}} = $13 TeV", Phys. Rev. Lett. 116, 172302 (2016).
 \bibitem{ridge_pp_2}
-CMS Collaboration, "Evidence for collectivity in pp collisions at the LHC", Phys. Lett. B765 (2017) 193
+CMS Collaboration, "Evidence for collectivity in pp collisions at the LHC", Phys. Lett. B765 (2017) 193.
 \bibitem{ridge_pp_3}
-ALICE Collaboration, "Investigations of anisotropic flow using multi-particle azimuthal correlations in pp, p-Pb, Xe-Xe, and Pb-Pb collisions at the LHC", arXiv:1903.01790 [nucl-ex]
+ALICE Collaboration, "Investigations of anisotropic flow using multi-particle azimuthal correlations in pp, p-Pb, Xe-Xe, and Pb-Pb collisions at the LHC", arXiv:1903.01790 [nucl-ex].
 \bibitem{ridge_pp_4}
-PHENIX Collaboration, "Creation of quark–gluon plasma droplets with three distinct geometries", Nature Phys. 15, 214 (2019)
-, Nature Phys. 13, 535
+PHENIX Collaboration, "Creation of quark–gluon plasma droplets with three distinct geometries", Nature Phys. 15, 214 (2019), Nature Phys. 13, 535.
 \bibitem{ridge_theory_1}
-H. Mäntysaari, B. Schenke, C. Shen and P. Tribedy, "Imprints of fluctuating proton shapes on flow in proton-lead collisions at the LHC", Phys. Lett. B772 (2017) 681
+H. Mäntysaari, B. Schenke, C. Shen and P. Tribedy, "Imprints of fluctuating proton shapes on flow in proton-lead collisions at the LHC", Phys. Lett. B772 (2017) 681.
 \bibitem{ridge_theory_2}
-W. Zhao, Y. Zhou, H. Xu, W. Deng, and H. Song, “Hydrodynamic collectivity in proton?proton collisions at 13 TeV,” Phys. Lett. B780 (2018) 495
+W. Zhao, Y. Zhou, H. Xu, W. Deng, and H. Song, “Hydrodynamic collectivity in proton?proton collisions at 13 TeV,” Phys. Lett. B780 (2018) 495.
 \bibitem{ridge_theory_3}
-K. Welsh, J. Singer, and U. W. Heinz, “Initial state fluctuations in collisions between light and heavy ions,” Phys. Rev. C94 no. 2, (2016) 024919
+K. Welsh, J. Singer, and U. W. Heinz, “Initial state fluctuations in collisions between light and heavy ions,” Phys. Rev. C94 no. 2, (2016) 024919.
 \bibitem{ridge_theory_4}
-M. Greif, C. Greiner, B. Schenke, S. Schlichting, and Z. Xu, “Importance of initial and final state effects for azimuthal correlations in p+Pb collisions,” Phys. Rev. D96 no. 9, (2017) 091504
+M. Greif, C. Greiner, B. Schenke, S. Schlichting, and Z. Xu, “Importance of initial and final state effects for azimuthal correlations in p+Pb collisions,” Phys. Rev. D96 no. 9, (2017) 091504.
 \bibitem{ALICEdet}
@@
 \bibitem{ITSpaper}
-ALICE Collaboration, "Performance of the present ALICE Inner Tracking System and studies for the upgrade",  Journal of Instrumentation, 7, June (2012) C06007
+ALICE Collaboration, "Performance of the present ALICE Inner Tracking System and studies for the upgrade",  Journal of Instrumentation, 7, June (2012) C06007.
 \bibitem{VZEROpaper}
-ALICE Collaboration, "Performance of the ALICE VZERO system", JINST 8 (2013) P10016
+ALICE Collaboration, "Performance of the ALICE VZERO system", JINST 8 (2013) P10016.
 \bibitem{TPCpaper}
-ALICE Collaboration, "Performance of the ALICE Time Projection Chamber", Physics Procedia 37, (2012) 434
+ALICE Collaboration, "Performance of the ALICE Time Projection Chamber", Physics Procedia 37, (2012) 434.
 

### 2019-11-19 paper.tex
updates

@@
 Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to \unit[13]{TeV} during LHC Run2 period.
-Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2017 data sets.
+Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period.
+Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
 
@@
 The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively.
+The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively.
 The V0 provides trigger and estimation of event multiplicity.
 A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.
-The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
-The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
-The tracking of charged-particles is done with the combination of ITS and TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
-
-Subsystems mainly used in the present analysis, VZERO detector, Inner Tracking System(ITS) and Time Projection Chamber(TPC), are mainly discussed in the paper while the whole ALICE detector is well described in Ref.
-\cite{ALICEdet}.
-The VZERO is separated into two plates, VZERO-A and VZERO-C, consisting of two arrays of 32 scintillator tiles each, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7 respectively.
-The VZERO provides trigger and event characterization with respect to particle abundance.
-With higher threshold, High Multiplicity Trigger can be implemented by VZERO to acquire very high multiplicity events exclusively.
 
 The responsibility of reconstruction of charged track is up to the ITS and the TPC.
-The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon DriftDetector (SDD) and Silicon Strip Detector(SSD).
-ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
+The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
+The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
 The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
-The tracking of charged-particles is done with the combination of ITS and TPC, which also enable to reconstruct low transverse momentum tracks down to 0.15 GeV/\it{c}\rm{} with $\sim$70\% efficiency.
+The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
 

### 2020-01-22 paper.tex
Add Systematics

@@
 In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
-The results are compared to previous measurements from CMS and ATLAS experiments.
+The results are compared to previous measurements from CMS experiments.
 In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
@@
 Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-
 The full description of ALICE detector in the LHC Run 2 can be found in Ref.
@@
 The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
+
 The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively.
 The V0 provides trigger and estimation of event multiplicity.
-A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.
+A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring higher amplitude of V0 Detector.
 
@@
 
-\section{Analysis}
+\section{Analysis Procedure}
 
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure.
-This analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
-The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
+The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events including  $\sim$31 charged particles in the mid-rapidity region, to observe the clear ridge structure.
+This analysis uses charged particles, whose reconstructed transverse momenta are larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
+The efficiency and contamination from non-primary particles are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
 
@@
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{assoc}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
 \end{eqnarray}
@@
 The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
+\begin{eqnarray}
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.5} \rm{d} \Delta \eta \frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi}
+\end{eqnarray}
 The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
@@
 Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.
+
+\section{Systematic Uncertainty}
+The background distribution is constructed using several events having same primary vertex.
+The effect of construction of background distribution is estimated by varying the primary vertex interval from 2 cm to 1 cm.
+The estimated effect is 6-10\%.
+
+The $\Delta\eta$ projection range for construction of long-range $\Delta\varphi$ is sensitive to contamination of non-flow effect.
+The effect of  $\Delta\eta$ projection range is estimated by varying the projection range.
+The estimated effect is 10-15\% for $\it{p}_{\rm{T}}>$1.0 GeV/\it{c}\rm{} and 20\% for 0.5$<\it{p}_{\rm{T}}<$1.0 GeV/\it{c}\rm{}.
+
+The M.C. closure test for efficiency correction results in $\sim$4\% discrepancy. The discrepancy is considered into systematic uncertainty.
+
+The effect of primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm.
+The estimated effect is $\sim$4\%.
+The effect of rejection of pile-up events.
+is estimated by varying the methodology of pile-up rejection.
+The estimated effect is $\sim$4\%.
+The effect of track selection is estimated by varying a few selection criteria included in track selection.The estimated effect is $\sim$5\%.
+
+\begin{table}[!h]
+\centering
+\caption{ Summary of the systematic uncertainties. See text for details.}
+\begin{tabular}{ c|c }
+%\begin{tabular}{c || c}
+\hline
+Source &  Uncertainty \\ \hline
+Event mixing & 6-10\% \\  \hline
+$\Delta\eta$ projection range & 10-15\% \\ \hline
+M.C. closure & 4\% \\ \hline
+Primary vertex & 4\% \\ \hline
+Pileup Cut & 4\% \\ \hline
+Track selection & 5\% \\ \hline
+Total & 14-20\% \\
+\hline
+\end{tabular}
+%\caption{ Definition of multiplicity class in this analysis.
+Reference definition of multiplicity coud be found in the following link; \url{https://twiki.cern.ch/twiki/bin/viewauth/ALICE/ReferenceMult}  }
+\end{table}
 

### 2020-04-23 abstract.tex
split sections and bib etc

--- 2019-11-19 paper.tex
@@
-\documentclass[ALICE,manyauthors]{cernphprep}
-
-\usepackage[comma,square,numbers,sort&compress]{natbib}
-\usepackage{hyperref}
-\usepackage{lineno}
-%\usepackage{subcaption}
-\usepackage{subfigure}
-\usepackage[section]{placeins}
-\usepackage {multicol}% Multi column in the table
-\usepackage {multirow}% Multi row in the table
-\usepackage {units}
-
-\linenumbers
-
-\input{commands.tex}
-\begin{document}
-
-%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
-\begin{titlepage}
-
-\PHyear{}
-\PHnumber{2019-xxx}      % required, will be obtained from PH
-%\PHdate{Day Month}  % required, will be obtained from PH
-\PHdate{\today}
-%
-
-%%% Put your own title + short title here:
-\title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV} with ALICE at the LHC}
-\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
-
-%%% Do not change the next lines
-%\Collaboration{ALICE Collaboration\thanks{See Appendix~\ref{app:collab} for the list of collaboration members}}
-\ShortAuthor{ALICE Collaboration} % appears on left page headers, do not change
-
-\begin{abstract}
-
 The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
@@
 In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
-The results are compared to previous measurements from CMS and ATLAS experiments.
+The results are compared to previous measurements from CMS experiments.
 In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
-
-\end{abstract}
-\end{titlepage}
-\setcounter{page}{2}
-
-\section{Introduction}
-
-%Studies of particle correlations in high-energy hadronhadron collisions provide valuable information on the underlying quantum chromodynamics processes leading to particle production.
-Measurements of two-particle angular correlations are typically performed in terms of twodimensional Δη-Δϕ correlation functions, where η is the pseudorapidity and ϕ is the azimuthal angle.
-Of particular interest in studies of possible novel partonic collective effects is the long-range (e.g., jΔηj > 2.0) structure of twoparticle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side (Δϕ ≈ π) jet correlations.
-Measurements in high-energy nucleusnucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed [1].
-Several novel features were observed in azimuthal correlations over large Δη for intermediate particle transverse momenta, pT ≈ 1–5 GeV=c [2,3].
-These correlations are thought to arise from the response of a hydrodynamically expanding partonic medium to fluctuations of the initial collision geometry [4–9].
-Measurements in pp collisions at a center-of-mass energy of ffiffi s p ¼ 7 TeV have also revealed the presence of long-range, near-side (Δϕ ≈ 0) correlations in events with very large final-state particle multiplicity [10].
-Similar phenomena have also been observed in high-multiplicity proton-lead (pPb) collisions [11–13], where they have been studied extensively [14–21].
-A wide range of models have been suggested to explain the emergence of these correlations in pp [22] and pPb [23–27] collisions.
-While models based on a hydrodynamic approach can describe many aspects of the observed correlations [23,24], it has been proposed that initial-state correlations of gluon fields could also lead to similar effects [25–27].
-
-%Two-particle correlations are a powerful tool to explore the mechanism of particle production in collisions of hadrons and nu-clei at high energy.
-Such studies involve measuring the distribu-tions of relative anglesφandηbetween pairs of particles: a“trigger” particle in a certain transverse momentumpT,trigintervaland an “associated” particle in apT,associnterval, whereφandηare the differences in azimuthal angleφand pseudorapidityηbetween the two particles.In proton–proton (pp) collisions, the correlation at (φ≈0,η≈0) forpT,trig>2GeV/cis dominated by the “near-side” jetpeak, where trigger and associated particles originate from a frag-menting parton, and atφ≈πby the recoil or “away-side” jet[1].The away-side structure is elongated alongηdue to the longitu-dinal momentum distribution of partons in the colliding protons.In nucleus–nucleus collisions, the jet-related correlations are mod-ified and additional structures emerge, which persist over a longrange inηon the near side and on the away side[2–14].Theshape of these distributions when decomposed into a Fourier se-ries defined byvncoefficients[15]is found to be dominated bycontributions from terms withn=2 andn=3 [6,7,9–14].Thevncoefficients are sensitive to the geometry of the initial stateof the colliding nuclei[16,17]and can be related to the transport properties of the strongly-interacting de-confined matter via hy-drodynamic models[18–20].Recently, measurements in pp collisions at a centre-of-massenergy√s=7TeV[21]and in proton–lead (p–Pb) collisions ata nucleon–nucleon centre-of-mass energy√sNN=5.02 TeV[22]have revealed long-range (2<|η|<4) near-side (φ≈0) cor-relations in events with significantly higher-than-average particlemultiplicity.
-Various mechanisms have been proposed to explainthe origin of these ridge-like correlations in high-multiplicity ppand p–Pb events.
-These mechanisms include colour connectionsforming along the longitudinal direction[23–26], jet-medium[27]and multi-parton induced[28,29]interactions, and collective ef-fects arising in the high-density system possibly formed in thesecollisions[30–35].Results from two-particle correlations in√sNN=0.2TeVd–Aucollisions[36,37]show a strong suppression of the away-side yieldat forward rapidity in central collisions.
-This modification has beeninterpreted in the framework of “Colour Glass Condensate” mod-els [38]as a saturation effect caused by nonlinear gluon inter-actions in the high-density regime at small longitudinal partonmomentum fractionx.
-Similar effects may arise at midrapidity inp–Pb collisions at√sNN=5.02 TeV, where the parton distributionsare probed down tox<10−3, which is comparable to the relevantrange ofxat forward rapidity (y∼3) at√sNN=0.2TeV.This Letter presents results extracted from two-particle cor-relation measurements in p–Pb collisions at√sNN=5.02 TeV,recorded with the ALICE detector[39]at the Large Hadron Col-lider (LHC).
-The correlations are measured over two units of pseudorapidity and full azimuthal angle as a function of charged-particle multiplicity, and expressed as associated yield per triggerparticle.
-Sections2 and 3describe the experimental setup, andthe event and track selection, respectively.
-Details on the defini-tion of the correlation and the per-trigger-particle associated yieldare given in Section4.
-The results of the analysis are discussed inSection5 and a summary is given in Section
-
-Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{ridge_aa_1, ridge_aa_2}.
-In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}.
-There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
-
-%Measurements of two-particle angular correlations in high-multiplicity proton-proton (pp) collisions at a centerof-mass energy ffiffi s p ¼ 7 TeV at the LHC showed an enhancement in the production of pairs at small azimuthal-angle separation, Δϕ, that extends over a wide range of pseudorapidity differences, Δη, and which is often referred to as the “ridge” [1].
-The ridge has also been observed in proton-lead (p þ Pb) collisions [2–7], where it is found to result from a global sinusoidal modulation of the per-event single-particle azimuthal angle distributions [3–6].
-While many theoretical interpretations of the ridge, including those based on hydrodynamics [8–12], saturation [13–23], or other mechanisms [24–30], have been, or could be applied to both pp and p þ Pb collisions, it has not yet been demonstrated that the ridge in pp collisions results from single-particle azimuthal anisotropies.
-Testing whether the ridges in pp and p þ Pb collisions arise from the same underlying features of the single-particle distributions may provide insight into the physics responsible for the phenomena.
-Separately, a study of the ffiffi s p dependence
-%Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
-One novel tool for studying the collective effect is two-particle angular correlations as function of relative pseudo-rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$) between the trigger particle and the associated particle.
-The main source of collective
-
-%QCD has been studied through particles produced in heavy ion collisions.
-Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions.
-One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle.
-Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.
-
-\section{Experimental setup}
-
-Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period.
-Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-
-The full description of ALICE detector in the LHC Run 2 can be found in Ref.
-\cite{ALICEdet}.
-The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively.
-The V0 provides trigger and estimation of event multiplicity.
-A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.
-
-The responsibility of reconstruction of charged track is up to the ITS and the TPC.
-The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
-The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
-The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
-
-\section{Analysis}
-
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure.
-This analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
-The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
-
-The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity and azimuthal angle.
-The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$
-\begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{assoc}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
-\end{eqnarray}
-where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event.
-The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having the same primary vertex and belonging to the same multiplicity class.
-
-The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
-The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
-The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
-The minimum yield ($C_{\rm{ZYAM}}$) is defined as minimum value of the function, which consists of Fourier series up to the third harmonic and is determined by fitting the $\Delta\varphi$ distribution.
-By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution.
-The range of integration is enclosed by the points having the minimum yield, which is obtained from ZYAM procedure.
-
-The ridge yield is further studied with various event selections regarding hard processes.
-The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold.
-The leading track is defined as a charged track having the largest transverse momentum in a given event.
-Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.
-
-\section {Results}
-
-The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
-The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-}
-
-\end{figure}
-
-The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
-The associated yield per trigger particle is compared with CMS results.
-The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.
-
-The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results.
-The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
-Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
-}
-
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/y.pdf} }
-	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively.
-}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy2.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.
-}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/yl.pdf} }
-	\caption{ The ridge yield spectrum with respect to the leading trac∂çk selection. The ridge yields are identical within uncertainties.}
-\end{figure}
-
-To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
-The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
-
-The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Figure 5.
-The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
-
-The ridge yield is inspected as a function of the leading track selection in Figure 6.
-As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
-
-\section{Model Comparison}
-
-\section{Conclusions}
-
-Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE.
-The measured associated yield is found to be consistent with the previous results from CMS experiment.
-The ridge yield, for the first time, has been observed in events including hard processes.
-Furthermore, it is found to be independent of the hardness of the events.
-This observation is important for the study of the origins of the ridge in small collision systems.
-
-%%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax}
-%\begin{acknowledgement}
-%\section*{Acknowledgements}
-%\input{acknowledgements.tex}    %%%%%%% done by webmaster team
-%\end{acknowledgement}
-
-%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
-%\bibliographystyle{utphys}   % Remember we use title in the biblio
-%\bibliography{biblio}
-%\input {bibliography.tex}
-
-%%%%%%%%% appendix with author list
-\newpage
-\appendix
-%
-%\input{}               %%%%%%%%%%% put your appendices here
-%
-
-%\section{The ALICE Collaboration}
-%\label{app:collab}
-%\input{authorlist-preprint.tex}  %%%%%%% done by webmaster team
-
-\clearpage
-
-\begin{thebibliography}{99}
-
-\bibitem{ridge_aa_1}
-CMS Collaboration, "Centrality dependence of dihadron correlations and azimuthal anisotropy harmonics in PbPb collisions at  $\sqrt{\it{s_{\rm{NN}}}} = $2.76 TeV",   Eur. Phys J. C72 (2012).
-\bibitem{ridge_aa_2}
-ALICE Collaboration, "Anisotropic Flow of Charged Particles in Pb-Pb Collisions at $\sqrt{\it{s_{\rm{NN}}}} = $5.02 TeV",  Phys. Rev. Lett. 116, 132302 (2016).
-\bibitem{ridge_pp_1}
-CMS Collaboration, Measurement of Long-Range Near-Side Two-Particle Angular Correlations in pp Collisions at $\sqrt{\it{s}} = $13 TeV", Phys. Rev. Lett. 116, 172302 (2016).
-\bibitem{ridge_pp_2}
-CMS Collaboration, "Evidence for collectivity in pp collisions at the LHC", Phys. Lett. B765 (2017) 193.
-\bibitem{ridge_pp_3}
-ALICE Collaboration, "Investigations of anisotropic flow using multi-particle azimuthal correlations in pp, p-Pb, Xe-Xe, and Pb-Pb collisions at the LHC", arXiv:1903.01790 [nucl-ex].
-\bibitem{ridge_pp_4}
-PHENIX Collaboration, "Creation of quark–gluon plasma droplets with three distinct geometries", Nature Phys. 15, 214 (2019), Nature Phys. 13, 535.
-\bibitem{ridge_theory_1}
-H. Mäntysaari, B. Schenke, C. Shen and P. Tribedy, "Imprints of fluctuating proton shapes on flow in proton-lead collisions at the LHC", Phys. Lett. B772 (2017) 681.
-\bibitem{ridge_theory_2}
-W. Zhao, Y. Zhou, H. Xu, W. Deng, and H. Song, “Hydrodynamic collectivity in proton?proton collisions at 13 TeV,” Phys. Lett. B780 (2018) 495.
-\bibitem{ridge_theory_3}
-K. Welsh, J. Singer, and U. W. Heinz, “Initial state fluctuations in collisions between light and heavy ions,” Phys. Rev. C94 no. 2, (2016) 024919.
-\bibitem{ridge_theory_4}
-M. Greif, C. Greiner, B. Schenke, S. Schlichting, and Z. Xu, “Importance of initial and final state effects for azimuthal correlations in p+Pb collisions,” Phys. Rev. D96 no. 9, (2017) 091504.
-\bibitem{ALICEdet}
-ALICE Collaboration, “The ALICE experiment at the CERN LHC,” JINST 3 (2008) S08002.
-\bibitem{ITSpaper}
-ALICE Collaboration, "Performance of the present ALICE Inner Tracking System and studies for the upgrade",  Journal of Instrumentation, 7, June (2012) C06007.
-\bibitem{VZEROpaper}
-ALICE Collaboration, "Performance of the ALICE VZERO system", JINST 8 (2013) P10016.
-\bibitem{TPCpaper}
-ALICE Collaboration, "Performance of the ALICE Time Projection Chamber", Physics Procedia 37, (2012) 434.
-
-\end{thebibliography}
-
-\end{document}

### 2020-04-23 bibold.tex
split sections and bib etc

--- 2019-11-19 paper.tex
@@
-\documentclass[ALICE,manyauthors]{cernphprep}
-
-\usepackage[comma,square,numbers,sort&compress]{natbib}
-\usepackage{hyperref}
-\usepackage{lineno}
-%\usepackage{subcaption}
-\usepackage{subfigure}
-\usepackage[section]{placeins}
-\usepackage {multicol}% Multi column in the table
-\usepackage {multirow}% Multi row in the table
-\usepackage {units}
-
-\linenumbers
-
-\input{commands.tex}
-\begin{document}
-
-%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
-\begin{titlepage}
-
-\PHyear{}
-\PHnumber{2019-xxx}      % required, will be obtained from PH
-%\PHdate{Day Month}  % required, will be obtained from PH
-\PHdate{\today}
 %
-
-%%% Put your own title + short title here:
-\title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV} with ALICE at the LHC}
-\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
-
-%%% Do not change the next lines
-%\Collaboration{ALICE Collaboration\thanks{See Appendix~\ref{app:collab} for the list of collaboration members}}
-\ShortAuthor{ALICE Collaboration} % appears on left page headers, do not change
-
-\begin{abstract}
-
-The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
-Many theoretical approaches to interpreting this effect have been developed.
-However, it is still unclear whether these long-range correlations are due to final or initial state effects.
-To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during 2016 and 2017 with ALICE.
-In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
-The results are compared to previous measurements from CMS and ATLAS experiments.
-In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
-
-\end{abstract}
-\end{titlepage}
-\setcounter{page}{2}
-
-\section{Introduction}
-
-%Studies of particle correlations in high-energy hadronhadron collisions provide valuable information on the underlying quantum chromodynamics processes leading to particle production.
-Measurements of two-particle angular correlations are typically performed in terms of twodimensional Δη-Δϕ correlation functions, where η is the pseudorapidity and ϕ is the azimuthal angle.
-Of particular interest in studies of possible novel partonic collective effects is the long-range (e.g., jΔηj > 2.0) structure of twoparticle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side (Δϕ ≈ π) jet correlations.
-Measurements in high-energy nucleusnucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed [1].
-Several novel features were observed in azimuthal correlations over large Δη for intermediate particle transverse momenta, pT ≈ 1–5 GeV=c [2,3].
-These correlations are thought to arise from the response of a hydrodynamically expanding partonic medium to fluctuations of the initial collision geometry [4–9].
-Measurements in pp collisions at a center-of-mass energy of ffiffi s p ¼ 7 TeV have also revealed the presence of long-range, near-side (Δϕ ≈ 0) correlations in events with very large final-state particle multiplicity [10].
-Similar phenomena have also been observed in high-multiplicity proton-lead (pPb) collisions [11–13], where they have been studied extensively [14–21].
-A wide range of models have been suggested to explain the emergence of these correlations in pp [22] and pPb [23–27] collisions.
-While models based on a hydrodynamic approach can describe many aspects of the observed correlations [23,24], it has been proposed that initial-state correlations of gluon fields could also lead to similar effects [25–27].
-
-%Two-particle correlations are a powerful tool to explore the mechanism of particle production in collisions of hadrons and nu-clei at high energy.
-Such studies involve measuring the distribu-tions of relative anglesφandηbetween pairs of particles: a“trigger” particle in a certain transverse momentumpT,trigintervaland an “associated” particle in apT,associnterval, whereφandηare the differences in azimuthal angleφand pseudorapidityηbetween the two particles.In proton–proton (pp) collisions, the correlation at (φ≈0,η≈0) forpT,trig>2GeV/cis dominated by the “near-side” jetpeak, where trigger and associated particles originate from a frag-menting parton, and atφ≈πby the recoil or “away-side” jet[1].The away-side structure is elongated alongηdue to the longitu-dinal momentum distribution of partons in the colliding protons.In nucleus–nucleus collisions, the jet-related correlations are mod-ified and additional structures emerge, which persist over a longrange inηon the near side and on the away side[2–14].Theshape of these distributions when decomposed into a Fourier se-ries defined byvncoefficients[15]is found to be dominated bycontributions from terms withn=2 andn=3 [6,7,9–14].Thevncoefficients are sensitive to the geometry of the initial stateof the colliding nuclei[16,17]and can be related to the transport properties of the strongly-interacting de-confined matter via hy-drodynamic models[18–20].Recently, measurements in pp collisions at a centre-of-massenergy√s=7TeV[21]and in proton–lead (p–Pb) collisions ata nucleon–nucleon centre-of-mass energy√sNN=5.02 TeV[22]have revealed long-range (2<|η|<4) near-side (φ≈0) cor-relations in events with significantly higher-than-average particlemultiplicity.
-Various mechanisms have been proposed to explainthe origin of these ridge-like correlations in high-multiplicity ppand p–Pb events.
-These mechanisms include colour connectionsforming along the longitudinal direction[23–26], jet-medium[27]and multi-parton induced[28,29]interactions, and collective ef-fects arising in the high-density system possibly formed in thesecollisions[30–35].Results from two-particle correlations in√sNN=0.2TeVd–Aucollisions[36,37]show a strong suppression of the away-side yieldat forward rapidity in central collisions.
-This modification has beeninterpreted in the framework of “Colour Glass Condensate” mod-els [38]as a saturation effect caused by nonlinear gluon inter-actions in the high-density regime at small longitudinal partonmomentum fractionx.
-Similar effects may arise at midrapidity inp–Pb collisions at√sNN=5.02 TeV, where the parton distributionsare probed down tox<10−3, which is comparable to the relevantrange ofxat forward rapidity (y∼3) at√sNN=0.2TeV.This Letter presents results extracted from two-particle cor-relation measurements in p–Pb collisions at√sNN=5.02 TeV,recorded with the ALICE detector[39]at the Large Hadron Col-lider (LHC).
-The correlations are measured over two units of pseudorapidity and full azimuthal angle as a function of charged-particle multiplicity, and expressed as associated yield per triggerparticle.
-Sections2 and 3describe the experimental setup, andthe event and track selection, respectively.
-Details on the defini-tion of the correlation and the per-trigger-particle associated yieldare given in Section4.
-The results of the analysis are discussed inSection5 and a summary is given in Section
-
-Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{ridge_aa_1, ridge_aa_2}.
-In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}.
-There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
-
-%Measurements of two-particle angular correlations in high-multiplicity proton-proton (pp) collisions at a centerof-mass energy ffiffi s p ¼ 7 TeV at the LHC showed an enhancement in the production of pairs at small azimuthal-angle separation, Δϕ, that extends over a wide range of pseudorapidity differences, Δη, and which is often referred to as the “ridge” [1].
-The ridge has also been observed in proton-lead (p þ Pb) collisions [2–7], where it is found to result from a global sinusoidal modulation of the per-event single-particle azimuthal angle distributions [3–6].
-While many theoretical interpretations of the ridge, including those based on hydrodynamics [8–12], saturation [13–23], or other mechanisms [24–30], have been, or could be applied to both pp and p þ Pb collisions, it has not yet been demonstrated that the ridge in pp collisions results from single-particle azimuthal anisotropies.
-Testing whether the ridges in pp and p þ Pb collisions arise from the same underlying features of the single-particle distributions may provide insight into the physics responsible for the phenomena.
-Separately, a study of the ffiffi s p dependence
-%Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
-One novel tool for studying the collective effect is two-particle angular correlations as function of relative pseudo-rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$) between the trigger particle and the associated particle.
-The main source of collective
-
-%QCD has been studied through particles produced in heavy ion collisions.
-Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions.
-One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle.
-Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.
-
-\section{Experimental setup}
-
-Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period.
-Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-
-The full description of ALICE detector in the LHC Run 2 can be found in Ref.
-\cite{ALICEdet}.
-The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively.
-The V0 provides trigger and estimation of event multiplicity.
-A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.
-
-The responsibility of reconstruction of charged track is up to the ITS and the TPC.
-The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
-The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
-The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
-
-\section{Analysis}
-
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure.
-This analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
-The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
-
-The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity and azimuthal angle.
-The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$
-\begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{assoc}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
-\end{eqnarray}
-where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event.
-The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having the same primary vertex and belonging to the same multiplicity class.
-
-The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
-The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
-The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
-The minimum yield ($C_{\rm{ZYAM}}$) is defined as minimum value of the function, which consists of Fourier series up to the third harmonic and is determined by fitting the $\Delta\varphi$ distribution.
-By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution.
-The range of integration is enclosed by the points having the minimum yield, which is obtained from ZYAM procedure.
-
-The ridge yield is further studied with various event selections regarding hard processes.
-The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold.
-The leading track is defined as a charged track having the largest transverse momentum in a given event.
-Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.
-
-\section {Results}
-
-The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
-The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-}
-
-\end{figure}
-
-The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
-The associated yield per trigger particle is compared with CMS results.
-The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.
-
-The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results.
-The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
-Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
-}
-
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/y.pdf} }
-	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively.
-}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy2.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.
-}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/yl.pdf} }
-	\caption{ The ridge yield spectrum with respect to the leading trac∂çk selection. The ridge yields are identical within uncertainties.}
-\end{figure}
-
-To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
-The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
-
-The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Figure 5.
-The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
-
-The ridge yield is inspected as a function of the leading track selection in Figure 6.
-As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
-
-\section{Model Comparison}
-
-\section{Conclusions}
-
-Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE.
-The measured associated yield is found to be consistent with the previous results from CMS experiment.
-The ridge yield, for the first time, has been observed in events including hard processes.
-Furthermore, it is found to be independent of the hardness of the events.
-This observation is important for the study of the origins of the ridge in small collision systems.
-
-%%%%% acknowledgements
-\newenvironment{acknowledgement}{\relax}{\relax}
-%\begin{acknowledgement}
-%\section*{Acknowledgements}
-%\input{acknowledgements.tex}    %%%%%%% done by webmaster team
-%\end{acknowledgement}
-
-%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
-%\bibliographystyle{utphys}   % Remember we use title in the biblio
-%\bibliography{biblio}
-%\input {bibliography.tex}
-
-%%%%%%%%% appendix with author list
-\newpage
-\appendix
-%
-%\input{}               %%%%%%%%%%% put your appendices here
-%
-
-%\section{The ALICE Collaboration}
-%\label{app:collab}
-%\input{authorlist-preprint.tex}  %%%%%%% done by webmaster team
-
-\clearpage
-
-\begin{thebibliography}{99}
-
 \bibitem{ridge_aa_1}
@@
 ALICE Collaboration, "Performance of the ALICE Time Projection Chamber", Physics Procedia 37, (2012) 434.
-
-\end{thebibliography}
-
-\end{document}

### 2020-04-23 paper.tex
split sections and bib etc

--- 2019-11-19 paper.tex
@@
 %%% Put your own title + short title here:
-\title{Long-range correlations  in high-multiplicity  proton--proton collisions  at \s~=~\unit[13]{TeV} with ALICE at the LHC}
+\title{Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV}
 \ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
@@
 \begin{abstract}
-
-The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
-Many theoretical approaches to interpreting this effect have been developed.
-However, it is still unclear whether these long-range correlations are due to final or initial state effects.
-To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during 2016 and 2017 with ALICE.
-In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
-The results are compared to previous measurements from CMS and ATLAS experiments.
-In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
-
+\input{abstract.tex}
 \end{abstract}
@@
 
-\section{Introduction}
-
-%Studies of particle correlations in high-energy hadronhadron collisions provide valuable information on the underlying quantum chromodynamics processes leading to particle production.
-Measurements of two-particle angular correlations are typically performed in terms of twodimensional Δη-Δϕ correlation functions, where η is the pseudorapidity and ϕ is the azimuthal angle.
-Of particular interest in studies of possible novel partonic collective effects is the long-range (e.g., jΔηj > 2.0) structure of twoparticle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side (Δϕ ≈ π) jet correlations.
-Measurements in high-energy nucleusnucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed [1].
-Several novel features were observed in azimuthal correlations over large Δη for intermediate particle transverse momenta, pT ≈ 1–5 GeV=c [2,3].
-These correlations are thought to arise from the response of a hydrodynamically expanding partonic medium to fluctuations of the initial collision geometry [4–9].
-Measurements in pp collisions at a center-of-mass energy of ffiffi s p ¼ 7 TeV have also revealed the presence of long-range, near-side (Δϕ ≈ 0) correlations in events with very large final-state particle multiplicity [10].
-Similar phenomena have also been observed in high-multiplicity proton-lead (pPb) collisions [11–13], where they have been studied extensively [14–21].
-A wide range of models have been suggested to explain the emergence of these correlations in pp [22] and pPb [23–27] collisions.
-While models based on a hydrodynamic approach can describe many aspects of the observed correlations [23,24], it has been proposed that initial-state correlations of gluon fields could also lead to similar effects [25–27].
-
-%Two-particle correlations are a powerful tool to explore the mechanism of particle production in collisions of hadrons and nu-clei at high energy.
-Such studies involve measuring the distribu-tions of relative anglesφandηbetween pairs of particles: a“trigger” particle in a certain transverse momentumpT,trigintervaland an “associated” particle in apT,associnterval, whereφandηare the differences in azimuthal angleφand pseudorapidityηbetween the two particles.In proton–proton (pp) collisions, the correlation at (φ≈0,η≈0) forpT,trig>2GeV/cis dominated by the “near-side” jetpeak, where trigger and associated particles originate from a frag-menting parton, and atφ≈πby the recoil or “away-side” jet[1].The away-side structure is elongated alongηdue to the longitu-dinal momentum distribution of partons in the colliding protons.In nucleus–nucleus collisions, the jet-related correlations are mod-ified and additional structures emerge, which persist over a longrange inηon the near side and on the away side[2–14].Theshape of these distributions when decomposed into a Fourier se-ries defined byvncoefficients[15]is found to be dominated bycontributions from terms withn=2 andn=3 [6,7,9–14].Thevncoefficients are sensitive to the geometry of the initial stateof the colliding nuclei[16,17]and can be related to the transport properties of the strongly-interacting de-confined matter via hy-drodynamic models[18–20].Recently, measurements in pp collisions at a centre-of-massenergy√s=7TeV[21]and in proton–lead (p–Pb) collisions ata nucleon–nucleon centre-of-mass energy√sNN=5.02 TeV[22]have revealed long-range (2<|η|<4) near-side (φ≈0) cor-relations in events with significantly higher-than-average particlemultiplicity.
-Various mechanisms have been proposed to explainthe origin of these ridge-like correlations in high-multiplicity ppand p–Pb events.
-These mechanisms include colour connectionsforming along the longitudinal direction[23–26], jet-medium[27]and multi-parton induced[28,29]interactions, and collective ef-fects arising in the high-density system possibly formed in thesecollisions[30–35].Results from two-particle correlations in√sNN=0.2TeVd–Aucollisions[36,37]show a strong suppression of the away-side yieldat forward rapidity in central collisions.
-This modification has beeninterpreted in the framework of “Colour Glass Condensate” mod-els [38]as a saturation effect caused by nonlinear gluon inter-actions in the high-density regime at small longitudinal partonmomentum fractionx.
-Similar effects may arise at midrapidity inp–Pb collisions at√sNN=5.02 TeV, where the parton distributionsare probed down tox<10−3, which is comparable to the relevantrange ofxat forward rapidity (y∼3) at√sNN=0.2TeV.This Letter presents results extracted from two-particle cor-relation measurements in p–Pb collisions at√sNN=5.02 TeV,recorded with the ALICE detector[39]at the Large Hadron Col-lider (LHC).
-The correlations are measured over two units of pseudorapidity and full azimuthal angle as a function of charged-particle multiplicity, and expressed as associated yield per triggerparticle.
-Sections2 and 3describe the experimental setup, andthe event and track selection, respectively.
-Details on the defini-tion of the correlation and the per-trigger-particle associated yieldare given in Section4.
-The results of the analysis are discussed inSection5 and a summary is given in Section
-
-Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{ridge_aa_1, ridge_aa_2}.
-In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}.
-There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
-
-%Measurements of two-particle angular correlations in high-multiplicity proton-proton (pp) collisions at a centerof-mass energy ffiffi s p ¼ 7 TeV at the LHC showed an enhancement in the production of pairs at small azimuthal-angle separation, Δϕ, that extends over a wide range of pseudorapidity differences, Δη, and which is often referred to as the “ridge” [1].
-The ridge has also been observed in proton-lead (p þ Pb) collisions [2–7], where it is found to result from a global sinusoidal modulation of the per-event single-particle azimuthal angle distributions [3–6].
-While many theoretical interpretations of the ridge, including those based on hydrodynamics [8–12], saturation [13–23], or other mechanisms [24–30], have been, or could be applied to both pp and p þ Pb collisions, it has not yet been demonstrated that the ridge in pp collisions results from single-particle azimuthal anisotropies.
-Testing whether the ridges in pp and p þ Pb collisions arise from the same underlying features of the single-particle distributions may provide insight into the physics responsible for the phenomena.
-Separately, a study of the ffiffi s p dependence
-%Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
-One novel tool for studying the collective effect is two-particle angular correlations as function of relative pseudo-rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$) between the trigger particle and the associated particle.
-The main source of collective
-
-%QCD has been studied through particles produced in heavy ion collisions.
-Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions.
-One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle.
-Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.
-
-\section{Experimental setup}
-
-Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period.
-Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-
-The full description of ALICE detector in the LHC Run 2 can be found in Ref.
-\cite{ALICEdet}.
-The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively.
-The V0 provides trigger and estimation of event multiplicity.
-A sample of events with high numbers of produced particles is obtained with a high multiplicity trigger in the V0 detector.
-
-The responsibility of reconstruction of charged track is up to the ITS and the TPC.
-The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
-The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
-The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
-
-\section{Analysis}
-
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events, to study high multiplicity events and to observe the ridge structure.
-This analysis uses charged tracks, whose reconstructed transverse momentum is larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
-The efficiency and contamination from non-primary tracks are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
-
-The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity and azimuthal angle.
-The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$
-\begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{assoc}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
-\end{eqnarray}
-where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event.
-The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having the same primary vertex and belonging to the same multiplicity class.
-
-The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
-The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
-The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
-The minimum yield ($C_{\rm{ZYAM}}$) is defined as minimum value of the function, which consists of Fourier series up to the third harmonic and is determined by fitting the $\Delta\varphi$ distribution.
-By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution.
-The range of integration is enclosed by the points having the minimum yield, which is obtained from ZYAM procedure.
-
-The ridge yield is further studied with various event selections regarding hard processes.
-The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold.
-The leading track is defined as a charged track having the largest transverse momentum in a given event.
-Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.
-
-\section {Results}
-
-The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
-The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-}
-
-\end{figure}
-
-The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
-The associated yield per trigger particle is compared with CMS results.
-The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.
-
-The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results.
-The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
-Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
-}
-
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/y.pdf} }
-	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively.
-}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy2.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.
-}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/yl.pdf} }
-	\caption{ The ridge yield spectrum with respect to the leading trac∂çk selection. The ridge yields are identical within uncertainties.}
-\end{figure}
-
-To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
-The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
-
-The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Figure 5.
-The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
-
-The ridge yield is inspected as a function of the leading track selection in Figure 6.
-As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
-
-\section{Model Comparison}
-
-\section{Conclusions}
-
-Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE.
-The measured associated yield is found to be consistent with the previous results from CMS experiment.
-The ridge yield, for the first time, has been observed in events including hard processes.
-Furthermore, it is found to be independent of the hardness of the events.
-This observation is important for the study of the origins of the ridge in small collision systems.
+\input{sec_intro.tex}
+\input{sec_ana.tex}
+\input{sec_results.tex}
+\input{sec_summary.tex}
 
@@
 
-\begin{thebibliography}{99}
+\bibliographystyle{utphys}
+\bibliography{paper.bib}
 
-\bibitem{ridge_aa_1}
-CMS Collaboration, "Centrality dependence of dihadron correlations and azimuthal anisotropy harmonics in PbPb collisions at  $\sqrt{\it{s_{\rm{NN}}}} = $2.76 TeV",   Eur. Phys J. C72 (2012).
-\bibitem{ridge_aa_2}
-ALICE Collaboration, "Anisotropic Flow of Charged Particles in Pb-Pb Collisions at $\sqrt{\it{s_{\rm{NN}}}} = $5.02 TeV",  Phys. Rev. Lett. 116, 132302 (2016).
-\bibitem{ridge_pp_1}
-CMS Collaboration, Measurement of Long-Range Near-Side Two-Particle Angular Correlations in pp Collisions at $\sqrt{\it{s}} = $13 TeV", Phys. Rev. Lett. 116, 172302 (2016).
-\bibitem{ridge_pp_2}
-CMS Collaboration, "Evidence for collectivity in pp collisions at the LHC", Phys. Lett. B765 (2017) 193.
-\bibitem{ridge_pp_3}
-ALICE Collaboration, "Investigations of anisotropic flow using multi-particle azimuthal correlations in pp, p-Pb, Xe-Xe, and Pb-Pb collisions at the LHC", arXiv:1903.01790 [nucl-ex].
-\bibitem{ridge_pp_4}
-PHENIX Collaboration, "Creation of quark–gluon plasma droplets with three distinct geometries", Nature Phys. 15, 214 (2019), Nature Phys. 13, 535.
-\bibitem{ridge_theory_1}
-H. Mäntysaari, B. Schenke, C. Shen and P. Tribedy, "Imprints of fluctuating proton shapes on flow in proton-lead collisions at the LHC", Phys. Lett. B772 (2017) 681.
-\bibitem{ridge_theory_2}
-W. Zhao, Y. Zhou, H. Xu, W. Deng, and H. Song, “Hydrodynamic collectivity in proton?proton collisions at 13 TeV,” Phys. Lett. B780 (2018) 495.
-\bibitem{ridge_theory_3}
-K. Welsh, J. Singer, and U. W. Heinz, “Initial state fluctuations in collisions between light and heavy ions,” Phys. Rev. C94 no. 2, (2016) 024919.
-\bibitem{ridge_theory_4}
-M. Greif, C. Greiner, B. Schenke, S. Schlichting, and Z. Xu, “Importance of initial and final state effects for azimuthal correlations in p+Pb collisions,” Phys. Rev. D96 no. 9, (2017) 091504.
-\bibitem{ALICEdet}
-ALICE Collaboration, “The ALICE experiment at the CERN LHC,” JINST 3 (2008) S08002.
-\bibitem{ITSpaper}
-ALICE Collaboration, "Performance of the present ALICE Inner Tracking System and studies for the upgrade",  Journal of Instrumentation, 7, June (2012) C06007.
-\bibitem{VZEROpaper}
-ALICE Collaboration, "Performance of the ALICE VZERO system", JINST 8 (2013) P10016.
-\bibitem{TPCpaper}
-ALICE Collaboration, "Performance of the ALICE Time Projection Chamber", Physics Procedia 37, (2012) 434.
-
-\end{thebibliography}
+%%%%%%%%% appendix with author list
+%\section{The ALICE Collaboration}
+%\label{app:collab}
+%\input{Alice_Authorlist_2017-Aug-21.tex}  %%%%%%% done by webmaster team
+%\input{}
 

### 2020-04-23 sec_ana.tex
split sections and bib etc

\section{Experimental setup}

Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions. Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period. Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets. The full description of ALICE detector in the LHC Run 2 can be found in Ref. \cite{ALICEdet}. The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.

The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively. The V0 provides trigger and estimation of event multiplicity. A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring higher amplitude of V0 Detector.

The responsibility of reconstruction of charged track is up to the ITS and the TPC. The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD). The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction. The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC. The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.

\section{Analysis Procedure}

The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events including  $\sim$31 charged particles in the mid-rapidity region, to observe the clear ridge structure. This analysis uses charged particles, whose reconstructed transverse momenta are larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9. The efficiency and contamination from non-primary particles are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.

The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity and azimuthal angle. The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$
\begin{eqnarray}
\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
\end{eqnarray}
where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class. The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event. The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having the same primary vertex and belonging to the same multiplicity class.

The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals. The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
\begin{eqnarray}
\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.5} \rm{d} \Delta \eta \frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi}
\end{eqnarray}
The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure. The minimum yield ($C_{\rm{ZYAM}}$) is defined as minimum value of the function, which consists of Fourier series up to the third harmonic and is determined by fitting the $\Delta\varphi$ distribution. By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution. The range of integration is enclosed by the points having the minimum yield, which is obtained from ZYAM procedure.

The ridge yield is further studied with various event selections regarding hard processes. The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold. The leading track is defined as a charged track having the largest transverse momentum in a given event. Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.

\section{Systematic Uncertainty}
The background distribution is constructed using several events having same primary vertex. The effect of construction of background distribution is estimated by varying the primary vertex interval from 2 cm to 1 cm. The estimated effect is 6-10\%.

The $\Delta\eta$ projection range for construction of long-range $\Delta\varphi$ is sensitive to contamination of non-flow effect. The effect of  $\Delta\eta$ projection range is estimated by varying the projection range. The estimated effect is 10-15\% for $\it{p}_{\rm{T}}>$1.0 GeV/\it{c}\rm{} and 20\% for 0.5$<\it{p}_{\rm{T}}<$1.0 GeV/\it{c}\rm{}.

The M.C. closure test for efficiency correction results in $\sim$4\% discrepancy. The discrepancy is considered into systematic uncertainty.

The effect of primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm. The estimated effect is $\sim$4\%. The effect of rejection of pile-up events. is estimated by varying the methodology of pile-up rejection. The estimated effect is $\sim$4\%. The effect of track selection is estimated by varying a few selection criteria included in track selection.The estimated effect is $\sim$5\%.

\begin{table}[!h]
\centering
\caption{ Summary of the systematic uncertainties. See text for details.}
\begin{tabular}{ c|c }
%\begin{tabular}{c || c}
\hline
Source &  Uncertainty \\ \hline
Event mixing & 6-10\% \\  \hline
$\Delta\eta$ projection range & 10-15\% \\ \hline
M.C. closure & 4\% \\ \hline
Primary vertex & 4\% \\ \hline
Pileup Cut & 4\% \\ \hline
Track selection & 5\% \\ \hline
Total & 14-20\% \\
\hline
\end{tabular}
%\caption{ Definition of multiplicity class in this analysis. Reference definition of multiplicity coud be found in the following link; \url{https://twiki.cern.ch/twiki/bin/viewauth/ALICE/ReferenceMult}  }
\end{table}

### 2020-04-23 sec_intro.tex
split sections and bib etc

\section{Introduction}

%Studies of particle correlations in high-energy hadronhadron collisions provide valuable information on the underlying quantum chromodynamics processes leading to particle production. Measurements of two-particle angular correlations are typically performed in terms of twodimensional Δη-Δϕ correlation functions, where η is the pseudorapidity and ϕ is the azimuthal angle. Of particular interest in studies of possible novel partonic collective effects is the long-range (e.g., jΔηj > 2.0) structure of twoparticle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small. In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side (Δϕ ≈ π) jet correlations. Measurements in high-energy nucleusnucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed [1]. Several novel features were observed in azimuthal correlations over large Δη for intermediate particle transverse momenta, pT ≈ 1–5 GeV=c [2,3]. These correlations are thought to arise from the response of a hydrodynamically expanding partonic medium to fluctuations of the initial collision geometry [4–9]. Measurements in pp collisions at a center-of-mass energy of ffiffi s p ¼ 7 TeV have also revealed the presence of long-range, near-side (Δϕ ≈ 0) correlations in events with very large final-state particle multiplicity [10]. Similar phenomena have also been observed in high-multiplicity proton-lead (pPb) collisions [11–13], where they have been studied extensively [14–21]. A wide range of models have been suggested to explain the emergence of these correlations in pp [22] and pPb [23–27] collisions. While models based on a hydrodynamic approach can describe many aspects of the observed correlations [23,24], it has been proposed that initial-state correlations of gluon fields could also lead to similar effects [25–27].

%Two-particle correlations are a powerful tool to explore the mechanism of particle production in collisions of hadrons and nu-clei at high energy. Such studies involve measuring the distribu-tions of relative anglesφandηbetween pairs of particles: a“trigger” particle in a certain transverse momentumpT,trigintervaland an “associated” particle in apT,associnterval, whereφandηare the differences in azimuthal angleφand pseudorapidityηbetween the two particles.In proton–proton (pp) collisions, the correlation at (φ≈0,η≈0) forpT,trig>2GeV/cis dominated by the “near-side” jetpeak, where trigger and associated particles originate from a frag-menting parton, and atφ≈πby the recoil or “away-side” jet[1].The away-side structure is elongated alongηdue to the longitu-dinal momentum distribution of partons in the colliding protons.In nucleus–nucleus collisions, the jet-related correlations are mod-ified and additional structures emerge, which persist over a longrange inηon the near side and on the away side[2–14].Theshape of these distributions when decomposed into a Fourier se-ries defined byvncoefficients[15]is found to be dominated bycontributions from terms withn=2 andn=3 [6,7,9–14].Thevncoefficients are sensitive to the geometry of the initial stateof the colliding nuclei[16,17]and can be related to the transport properties of the strongly-interacting de-confined matter via hy-drodynamic models[18–20].Recently, measurements in pp collisions at a centre-of-massenergy√s=7TeV[21]and in proton–lead (p–Pb) collisions ata nucleon–nucleon centre-of-mass energy√sNN=5.02 TeV[22]have revealed long-range (2<|η|<4) near-side (φ≈0) cor-relations in events with significantly higher-than-average particlemultiplicity. Various mechanisms have been proposed to explainthe origin of these ridge-like correlations in high-multiplicity ppand p–Pb events. These mechanisms include colour connectionsforming along the longitudinal direction[23–26], jet-medium[27]and multi-parton induced[28,29]interactions, and collective ef-fects arising in the high-density system possibly formed in thesecollisions[30–35].Results from two-particle correlations in√sNN=0.2TeVd–Aucollisions[36,37]show a strong suppression of the away-side yieldat forward rapidity in central collisions. This modification has beeninterpreted in the framework of “Colour Glass Condensate” mod-els [38]as a saturation effect caused by nonlinear gluon inter-actions in the high-density regime at small longitudinal partonmomentum fractionx. Similar effects may arise at midrapidity inp–Pb collisions at√sNN=5.02 TeV, where the parton distributionsare probed down tox<10−3, which is comparable to the relevantrange ofxat forward rapidity (y∼3) at√sNN=0.2TeV.This Letter presents results extracted from two-particle cor-relation measurements in p–Pb collisions at√sNN=5.02 TeV,recorded with the ALICE detector[39]at the Large Hadron Col-lider (LHC). The correlations are measured over two units of pseudorapidity and full azimuthal angle as a function of charged-particle multiplicity, and expressed as associated yield per triggerparticle. Sections2 and 3describe the experimental setup, andthe event and track selection, respectively. Details on the defini-tion of the correlation and the per-trigger-particle associated yieldare given in Section4. The results of the analysis are discussed inSection5 and a summary is given in Section

Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions. The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{ridge_aa_1, ridge_aa_2}. In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}. There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.

%Measurements of two-particle angular correlations in high-multiplicity proton-proton (pp) collisions at a centerof-mass energy ffiffi s p ¼ 7 TeV at the LHC showed an enhancement in the production of pairs at small azimuthal-angle separation, Δϕ, that extends over a wide range of pseudorapidity differences, Δη, and which is often referred to as the “ridge” [1]. The ridge has also been observed in proton-lead (p þ Pb) collisions [2–7], where it is found to result from a global sinusoidal modulation of the per-event single-particle azimuthal angle distributions [3–6]. While many theoretical interpretations of the ridge, including those based on hydrodynamics [8–12], saturation [13–23], or other mechanisms [24–30], have been, or could be applied to both pp and p þ Pb collisions, it has not yet been demonstrated that the ridge in pp collisions results from single-particle azimuthal anisotropies. Testing whether the ridges in pp and p þ Pb collisions arise from the same underlying features of the single-particle distributions may provide insight into the physics responsible for the phenomena. Separately, a study of the ffiffi s p dependence
%Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy. One novel tool for studying the collective effect is two-particle angular correlations as function of relative pseudo-rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$) between the trigger particle and the associated particle. The main source of collective

%QCD has been studied through particles produced in heavy ion collisions. Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions. One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle. Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.

### 2020-04-23 sec_results.tex
split sections and bib etc

% !TEX root = paper.tex

\section {Results}

The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region. The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. }

\end{figure}

The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class. The associated yield per trigger particle is compared with CMS results. The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.

The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results. The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}. Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%. Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively. }

\end{figure}

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/Fig1_RidgeYield.pdf} }
	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
\end{figure}

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots. Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively. }
\end{figure}

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy1.pdf} }
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy2.pdf} }
	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds. Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}. Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively. }
\end{figure}

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.8\textwidth]{./figures/Fig2_RidgeYield_Esel_py.pdf}}
	\caption{ The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
\end{figure}

To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4. The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.

The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Figure 5. The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.

The ridge yield is inspected as a function of the leading track selection in Figure 6. As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.

\section{Model Comparison}

### 2020-04-23 sec_summary.tex
split sections and bib etc

\section{Conclusions}

Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE. The measured associated yield is found to be consistent with the previous results from CMS experiment. The ridge yield, for the first time, has been observed in events including hard processes. Furthermore, it is found to be independent of the hardness of the events. This observation is important for the study of the origins of the ridge in small collision systems.

### 2020-04-23 sec_intro.tex
clean up bib

@@
+% !TEX root = paper.tex
+
 \section{Introduction}
@@
 Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{ridge_aa_1, ridge_aa_2}.
-In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{ridge_pp_1, ridge_pp_2, ridge_pp_3, ridge_pp_4}.
-There are many theoretical attempts\cite{ridge_theory_1, ridge_theory_2, ridge_theory_3, ridge_theory_4} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{Chatrchyan:2012wg, Adam:2016izf}.
+In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{Khachatryan:2015lva, Khachatryan:2016txc, Acharya:2019vdf, phenixnature}.
+There are many theoretical attempts\cite{Mantysaari:2017cni, Zhao:2017rgg, Welsh:2016siu, Greif:2017bnr} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
 

### 2020-04-23 makeunusedbib.sh

@@ -1,0 +1,3 @@
+cat paper.aux | grep '\\citation' | sed -e 's/\\citation{\(.*\)}/\1/g' -e 's/ *\(.*\) */\1/g' | tr ',' '\012' | sort -u > paper.keys
+cat paper.bib | grep "@.*{.*," | sed -e 's/.*{\(.*\),/\1/' | sort -u > bib.keys
+grep -v -f paper.keys bib.keys

### 2020-04-24 sec_intro.tex
cleanup bibtex, first draft of intro

@@
 
-%Studies of particle correlations in high-energy hadronhadron collisions provide valuable information on the underlying quantum chromodynamics processes leading to particle production.
-Measurements of two-particle angular correlations are typically performed in terms of twodimensional Δη-Δϕ correlation functions, where η is the pseudorapidity and ϕ is the azimuthal angle.
-Of particular interest in studies of possible novel partonic collective effects is the long-range (e.g., jΔηj > 2.0) structure of twoparticle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side (Δϕ ≈ π) jet correlations.
-Measurements in high-energy nucleusnucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed [1].
-Several novel features were observed in azimuthal correlations over large Δη for intermediate particle transverse momenta, pT ≈ 1–5 GeV=c [2,3].
-These correlations are thought to arise from the response of a hydrodynamically expanding partonic medium to fluctuations of the initial collision geometry [4–9].
-Measurements in pp collisions at a center-of-mass energy of ffiffi s p ¼ 7 TeV have also revealed the presence of long-range, near-side (Δϕ ≈ 0) correlations in events with very large final-state particle multiplicity [10].
-Similar phenomena have also been observed in high-multiplicity proton-lead (pPb) collisions [11–13], where they have been studied extensively [14–21].
-A wide range of models have been suggested to explain the emergence of these correlations in pp [22] and pPb [23–27] collisions.
-While models based on a hydrodynamic approach can describe many aspects of the observed correlations [23,24], it has been proposed that initial-state correlations of gluon fields could also lead to similar effects [25–27].
-
-%Two-particle correlations are a powerful tool to explore the mechanism of particle production in collisions of hadrons and nu-clei at high energy.
-Such studies involve measuring the distribu-tions of relative anglesφandηbetween pairs of particles: a“trigger” particle in a certain transverse momentumpT,trigintervaland an “associated” particle in apT,associnterval, whereφandηare the differences in azimuthal angleφand pseudorapidityηbetween the two particles.In proton–proton (pp) collisions, the correlation at (φ≈0,η≈0) forpT,trig>2GeV/cis dominated by the “near-side” jetpeak, where trigger and associated particles originate from a frag-menting parton, and atφ≈πby the recoil or “away-side” jet[1].The away-side structure is elongated alongηdue to the longitu-dinal momentum distribution of partons in the colliding protons.In nucleus–nucleus collisions, the jet-related correlations are mod-ified and additional structures emerge, which persist over a longrange inηon the near side and on the away side[2–14].Theshape of these distributions when decomposed into a Fourier se-ries defined byvncoefficients[15]is found to be dominated bycontributions from terms withn=2 andn=3 [6,7,9–14].Thevncoefficients are sensitive to the geometry of the initial stateof the colliding nuclei[16,17]and can be related to the transport properties of the strongly-interacting de-confined matter via hy-drodynamic models[18–20].Recently, measurements in pp collisions at a centre-of-massenergy√s=7TeV[21]and in proton–lead (p–Pb) collisions ata nucleon–nucleon centre-of-mass energy√sNN=5.02 TeV[22]have revealed long-range (2<|η|<4) near-side (φ≈0) cor-relations in events with significantly higher-than-average particlemultiplicity.
-Various mechanisms have been proposed to explainthe origin of these ridge-like correlations in high-multiplicity ppand p–Pb events.
-These mechanisms include colour connectionsforming along the longitudinal direction[23–26], jet-medium[27]and multi-parton induced[28,29]interactions, and collective ef-fects arising in the high-density system possibly formed in thesecollisions[30–35].Results from two-particle correlations in√sNN=0.2TeVd–Aucollisions[36,37]show a strong suppression of the away-side yieldat forward rapidity in central collisions.
-This modification has beeninterpreted in the framework of “Colour Glass Condensate” mod-els [38]as a saturation effect caused by nonlinear gluon inter-actions in the high-density regime at small longitudinal partonmomentum fractionx.
-Similar effects may arise at midrapidity inp–Pb collisions at√sNN=5.02 TeV, where the parton distributionsare probed down tox<10−3, which is comparable to the relevantrange ofxat forward rapidity (y∼3) at√sNN=0.2TeV.This Letter presents results extracted from two-particle cor-relation measurements in p–Pb collisions at√sNN=5.02 TeV,recorded with the ALICE detector[39]at the Large Hadron Col-lider (LHC).
-The correlations are measured over two units of pseudorapidity and full azimuthal angle as a function of charged-particle multiplicity, and expressed as associated yield per triggerparticle.
-Sections2 and 3describe the experimental setup, andthe event and track selection, respectively.
-Details on the defini-tion of the correlation and the per-trigger-particle associated yieldare given in Section4.
-The results of the analysis are discussed inSection5 and a summary is given in Section
+Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\phi$ correlation functions, where $\eta$ is the pseudorapidity and $\phi$ is the azimuthal angle.
+Of particular interest in studies of possible novel  collective effects is the long-range (e.g., $|\Delta\eta| > 2.0$) structure of two-particle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
+In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\phi$ $\approx$ $\pi$ ) jet correlations.
+Measurements in high-energy nucleus nucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed~\cite{Romatschke:2007mq,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je}.
 
 Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often referred to as the “ridge”,  is one of the crucial observables of collectivity \cite{Chatrchyan:2012wg, Adam:2016izf}.
-In recent years, measurements of the ridge in small systems, such as proton-proton (pp) collisions and proton-nucleus (pA) collisions, where the volume and lifetime of the medium produced are expected to be small, have been reported\cite{Khachatryan:2015lva, Khachatryan:2016txc, Acharya:2019vdf, phenixnature}.
+Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus (AA) collisions at the BNL RHIC~\cite{Alver:2006wh} and the CERN LHC~\cite{AAbelev:2014pua,ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior~\cite{}.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often so-called $\it{ridge}$,  is one of the crucial observables to study the collectivity~\cite{Chatrchyan:2012wg, Adam:2016izf}.
+In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Khachatryan:2015lva, Khachatryan:2016txc, Acharya:2019vdf} proton-nucleus (pA)~\cite{}, and lighter nucleus-nucleus systems~\cite{phenixnature}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, even though the volume and lifetime of the medium produced are expected to be small.
 There are many theoretical attempts\cite{Mantysaari:2017cni, Zhao:2017rgg, Welsh:2016siu, Greif:2017bnr} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
-
-%Measurements of two-particle angular correlations in high-multiplicity proton-proton (pp) collisions at a centerof-mass energy ffiffi s p ¼ 7 TeV at the LHC showed an enhancement in the production of pairs at small azimuthal-angle separation, Δϕ, that extends over a wide range of pseudorapidity differences, Δη, and which is often referred to as the “ridge” [1].
-The ridge has also been observed in proton-lead (p þ Pb) collisions [2–7], where it is found to result from a global sinusoidal modulation of the per-event single-particle azimuthal angle distributions [3–6].
-While many theoretical interpretations of the ridge, including those based on hydrodynamics [8–12], saturation [13–23], or other mechanisms [24–30], have been, or could be applied to both pp and p þ Pb collisions, it has not yet been demonstrated that the ridge in pp collisions results from single-particle azimuthal anisotropies.
-Testing whether the ridges in pp and p þ Pb collisions arise from the same underlying features of the single-particle distributions may provide insight into the physics responsible for the phenomena.
-Separately, a study of the ffiffi s p dependence
-%Collective effect is one of key probes to explore evolution of the hot and dense matter as consequence of heavy ion collisions at high energy.
-One novel tool for studying the collective effect is two-particle angular correlations as function of relative pseudo-rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$) between the trigger particle and the associated particle.
-The main source of collective
-
-%QCD has been studied through particles produced in heavy ion collisions.
-Among many observables, collective effect is one of key probes to explore evolution of the hot and dense matter as results of heavy ion collisions.
-One novel tool to study the initial conditions and their evolution is angular correlations of two-particle with respect to two-dimensional $\Delta\eta-\Delta\varphi$ distribution, Where $\eta$ denotes pseudorapidity and $\varphi$ denotes azimuthal angle.
-Especially, much interest.in the distribution is with long-range $\Delta\eta$, where the collective effect thought to be dominant.

### 2020-04-27 sec_intro.tex
first intro
I think it contains all we want to say and i need fine tuning on the pythia and recent work from christian tomorrow.

@@
 \section{Introduction}
+\label{sec:intro}
 
 Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\phi$ correlation functions, where $\eta$ is the pseudorapidity and $\phi$ is the azimuthal angle.
-Of particular interest in studies of possible novel  collective effects is the long-range (e.g., $|\Delta\eta| > 2.0$) structure of two-particle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
+Of particular interest in studies of possible novel  collective effects is the long-range structure of two-particle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
 In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\phi$ $\approx$ $\pi$ ) jet correlations.
-Measurements in high-energy nucleus nucleus collisions have shown a long-range structure in the two-particle angular correlations functions, which has been attributed to the presence of the hot and dense matter formed~\cite{Romatschke:2007mq,Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je}.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in $\Delta\eta-\Delta\phi$ plot.
+The shape of these $\Delta\phi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
+The second and third order terms are the dominant harmonic coefficients $v_n$.
+The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in hydrodynamic models~\cite{Bernhard:2016tnd,Bernhard2019}.
 
-Collective effects are one of the key probes to study evolution of the hot and dense matter created in ultra-relativistic heavy-ion collisions.
-Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus (AA) collisions at the BNL RHIC~\cite{Alver:2006wh} and the CERN LHC~\cite{AAbelev:2014pua,ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior~\cite{}.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), often so-called $\it{ridge}$,  is one of the crucial observables to study the collectivity~\cite{Chatrchyan:2012wg, Adam:2016izf}.
-In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Khachatryan:2015lva, Khachatryan:2016txc, Acharya:2019vdf} proton-nucleus (pA)~\cite{}, and lighter nucleus-nucleus systems~\cite{phenixnature}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, even though the volume and lifetime of the medium produced are expected to be small.
-There are many theoretical attempts\cite{Mantysaari:2017cni, Zhao:2017rgg, Welsh:2016siu, Greif:2017bnr} to interpret the ridge considering hydrodynamics, saturation or other mechanisms, but a quantitative description of the full set of experimental data has not yet been achieved.
+Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior~\cite{Romatschke:2007mq}.
+The recent efforts are nowadays focused on constrainig the transport properties of the QGP in hydrodynamic models~\cite{Bernhard:2016tnd,Bernhard2019} along with few advanced experimental works~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
+In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf} proton-nucleus (pA)~\cite{Abelev:2012ola}, and lighter nucleus-nucleus systems~\cite{phenixnature}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, even though the volume and lifetime of the medium produced are expected to be small.
+
+% TODO more pA measurements
+The ridge structures in high-multiplicity pp and pPb events have been attributed to mechanisms that involve initial-state effects, such as gluon saturation~\cite{Dusling:2012cg} and colour connections~\cite{Sarma:2019teo} forming along the longitudinal direction and final-state effects, such as parton-induced interactions~\cite{Arbuzov:2011yr}, and collective effects arising in a high-density system possibly formed in these collisions~\cite{Zhao:2017rgg}.
+As a natural choice, hybrid models which implement both effects are geneally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
+% IS only
+% FS only
+% IS + FS ::
+The importance of the proton shape and its fluctuations to model the small system was recongnized in \cite{Mantysaari:2017cni}.
+The hydrodynamics itself might not be the only mechanism of the observed collectivity was acknowledged in ~\cite{Zhao:2020pty}. 
+The influence and interplay of initial state and final state effects are recently studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for the quantitative description of observables in small systems~\cite{Schenke:2019pmk}.
+The attempts to describe the collective effects systematically from the small to large systems are being made both for experiments~\cite{Acharya:2019vdf} and theory side~\cite{Greif:2019ygb}.
+However, a quantitative description of the full set of experimental data has not yet been achieved.
+The summary of various explanations for the observed correlations in these small systems are summarized in ~\cite{Strickland:2018exs}.
+
+Furthermore, if collectivity in small systems is due to final state interactions, it should be possible to measure its effect on jets.
+Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high multiplicity pp collisions.
+The most of observables for the jet quenching in pp and pPb collisions didn't show any evidences so far~\cite{}.
+The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity in the event~\cite{}.
+
+%Small system studies: A theory overview 1807.07191 Strickland:2018exs
+%find one more one this regard.
+The ATLAS experiment has recently shown that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
+The impact paramenter dependence on di-jet or multi-jet production in pp collisons was studied in \cite{Frankfurt:2003td}. $v_2$ will be different.
+The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 Monte Carlo event generator so called ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc} and ATLAS Z-tagged ridge.
+This challenges the hydrodymic picture and predicts modifications to jet fragmentation
+properties~\cite{Bierlich:2019ixq}.
+
+% Bierlich:2017vhg (Shoving) Bierlich:2019ixq  
+% add vn extractio??
+% flow vn extraction : awayside ??
+% 
+% AA geometry dominant for v2 and what about in pp, b vs v2 or ridge..
+% Frankfurt:2003td
+% Aaboud:2019mcw Z-tagged ridge ATLAS
+
+To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during 2016 and 2017 with ALICE.
+In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.
+The results are compared to previous measurements from CMS experiments.
+In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
+The experimental setup and measurements are described in Sec.~\ref{sec:experiment}.
+In Sec.~\ref{sec:ana} we present the analysis methods.
+The sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
+The results of the measurements are presented in Sec.~\ref{sec:results}.
+In Sec.~\ref{sec:theory} we present comparisons to model calculations.
+Finally, Sec.~\ref{sec:summary} summarizes our new results.

### 2020-04-27 sec_intro.tex
finalizing the references

@@
 The second and third order terms are the dominant harmonic coefficients $v_n$.
-The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in hydrodynamic models~\cite{Bernhard:2016tnd,Bernhard2019}.
+The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
 
-Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior~\cite{Romatschke:2007mq}.
-The recent efforts are nowadays focused on constrainig the transport properties of the QGP in hydrodynamic models~\cite{Bernhard:2016tnd,Bernhard2019} along with few advanced experimental works~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
-In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf} proton-nucleus (pA)~\cite{Abelev:2012ola}, and lighter nucleus-nucleus systems~\cite{phenixnature}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, even though the volume and lifetime of the medium produced are expected to be small.
+Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
+The recent efforts are nowadays focused on constrainig the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
+In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf} proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced are expected to be small.
 
 % TODO more pA measurements
-The ridge structures in high-multiplicity pp and pPb events have been attributed to mechanisms that involve initial-state effects, such as gluon saturation~\cite{Dusling:2012cg} and colour connections~\cite{Sarma:2019teo} forming along the longitudinal direction and final-state effects, such as parton-induced interactions~\cite{Arbuzov:2011yr}, and collective effects arising in a high-density system possibly formed in these collisions~\cite{Zhao:2017rgg}.
-As a natural choice, hybrid models which implement both effects are geneally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
-% IS only
-% FS only
-% IS + FS ::
+The ridge structures in high-multiplicity pp and pPb events have been attributed to mechanisms that involve initial-state effects, such as gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and colour connections~\cite{Ortiz:2013yxa,Sarma:2019teo} forming along the longitudinal direction and final-state effects, such as parton-induced interactions~\cite{Arbuzov:2011yr}, and collective effects due to a hydrodynamic behaviour of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+Hybrid models which implement both effects are geneally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
 The importance of the proton shape and its fluctuations to model the small system was recongnized in \cite{Mantysaari:2017cni}.
@@
 However, a quantitative description of the full set of experimental data has not yet been achieved.
-The summary of various explanations for the observed correlations in these small systems are summarized in ~\cite{Strickland:2018exs}.
+The summary of various explanations for the observed correlations in these small systems are summarized in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
 
@@
 Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high multiplicity pp collisions.
-The most of observables for the jet quenching in pp and pPb collisions didn't show any evidences so far~\cite{}.
-The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity in the event~\cite{}.
+The most of observables for the jet quenching in pp and pPb collisions didn't show any clear evidences so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
+The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity in the event~\cite{Adam:2016jfp,Acharya:2018egz}.
 
@@
 The ATLAS experiment has recently shown that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
-The impact paramenter dependence on di-jet or multi-jet production in pp collisons was studied in \cite{Frankfurt:2003td}. $v_2$ will be different.
+The impact paramenter dependence on di-jet or multi-jet production in pp collisons was studied in \cite{Frankfurt:2003td}.
 The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 Monte Carlo event generator so called ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc} and ATLAS Z-tagged ridge.
@@
 
+% check this paper https://arxiv.org/abs/1910.13978 ATLAS pt cut...
 % Bierlich:2017vhg (Shoving) Bierlich:2019ixq  

### 2020-04-28 sec_intro.tex
ok until we finalize the results and other sections

@@
 
+Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
+The recent efforts are nowadays focused on constrainig the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
+In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf} proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced are expected to be small.
+
 Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\phi$ correlation functions, where $\eta$ is the pseudorapidity and $\phi$ is the azimuthal angle.
-Of particular interest in studies of possible novel  collective effects is the long-range structure of two-particle correlation functions, in which the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
+Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
 In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\phi$ $\approx$ $\pi$ ) jet correlations.
@@
 The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
-
-Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
-The recent efforts are nowadays focused on constrainig the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
-In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf} proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced are expected to be small.
 

### 2020-05-04 sec_ana.tex
first intro
I think it contains all we want to say and i need fine tuning on the pythia and recent work from christian tomorrow.
experimental citation updated

@@
+% !TEX root = paper.tex
+
 \section{Experimental setup}
+\label{sec:experiment}
 
 Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period.
+Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}}$~=~\unit[13]{TeV} during LHC Run2 period.
 Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-The full description of ALICE detector in the LHC Run 2 can be found in Ref.
-\cite{ALICEdet}.
-The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
+The full description of ALICE detector in the LHC Run 2 can be found in Refs.
+\cite{Aamodt:2008zz,Abelev:2014ffa}.
+The present analysis mainly uses V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
 
@@
 \section{Analysis Procedure}
+\label{sec:ana}
 
@@
 \section{Systematic Uncertainty}
+\label{sec:uncertainties}
 The background distribution is constructed using several events having same primary vertex.

### 2020-05-06 sec_ana.tex
update on chap 3

--- 2020-04-23 sec_ana.tex
@@
+% !TEX root = paper.tex
+
 \section{Experimental setup}
+\label{sec:experiment}
 
@@
 
+The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events including  $\sim$31 charged particles in the mid-rapidity region($|\eta|<$0.5).
+This analysis uses charged particles, whose reconstructed transverse momenta are larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
+
 \section{Analysis Procedure}
+\label{sec:na}
 
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events including  $\sim$31 charged particles in the mid-rapidity region, to observe the clear ridge structure.
-This analysis uses charged particles, whose reconstructed transverse momenta are larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
-The efficiency and contamination from non-primary particles are estimated from a Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation.
-
-The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudorapidity and azimuthal angle.
-The following equation expresses the correlation as associated yield per trigger particle as function of transverse momentum( $\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the condition of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$
+The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudo rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$).
+The following equation expresses the correlation as associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ with a given transverse momentum($\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the notation of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
 \begin{eqnarray}
@@
 where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event.
-The background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed several events having the same primary vertex and belonging to the same multiplicity class.
+The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event and the background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed 10 events having the same primary vertex and belonging to the same multiplicity class.
 
-The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to allow direct comparison of ridges between different $\it{p}_{\rm{T}}$ intervals.
-The large $\Delta\eta$ range is defined as 1.5$<|\Delta\eta|<$1.8 considering the limited detector acceptance.
+The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to achieve direct comparison of ridges between different event classes and transverse momentum intervals.
+The large $\Delta\eta$ range is defined as 1.6$<|\Delta\eta|<$1.8, which allows non-flow effects, mainly coming from the jet, not to contribute to the $\Delta\varphi$ distribution.
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.5} \rm{d} \Delta \eta \frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi}
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.6} \rm{d} \Delta \eta \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi}
 \end{eqnarray}
 The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
-The minimum yield ($C_{\rm{ZYAM}}$) is defined as minimum value of the function, which consists of Fourier series up to the third harmonic and is determined by fitting the $\Delta\varphi$ distribution.
-By subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution, the magnitude of long-range near-side yield is obtained and can be quantified by integrating the near-side peak of the $\Delta\varphi$ distribution.
-The range of integration is enclosed by the points having the minimum yield, which is obtained from ZYAM procedure.
+The minimum yield ($C_{\rm{ZYAM}}$) at the minimum $\Delta\varphi$($\Delta\varphi_{\rm{min}}$) of the $\Delta\varphi$ distribution are obtained from the function, which fits the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
+Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to take into consideration the major combinatorial correlations to be rejected.
+The associated yield of the ridge($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after ZYAM.
+\begin{eqnarray}
+Y^{\rm{assoc}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \rm{d} \Delta\varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } 
+\end{eqnarray}
 
 The ridge yield is further studied with various event selections regarding hard processes.
-The event selection is implemented by requiring that transverse momentum of leading track is larger than specific threshold.
-The leading track is defined as a charged track having the largest transverse momentum in a given event.
-Because the high transverse momentum track mainly comes from hard scattering, the requirement of the leading track can control the hardness of events, which allow one to study the ridge with events containing hard scatterings.
+The event selection is applied by requiring minimum transverse momentum of leading track or jet reconstructed in the mid-rapidity, where the leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{T}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$.
+The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer.
+
+Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation has been used to estimate the charged single particle efficiency and the contamination from the non-primary particle.
+The corrections have been tested by comparing the distributions, which are constructed with generated true particles and reconstructed particles with detector responses.
+The several percentage of non-closure has been considered into systematic uncertainty.
 
 \section{Systematic Uncertainty}
+\label{sec:uncertainties}
 The background distribution is constructed using several events having same primary vertex.

### 2020-05-06 sec_ana.tex

@@
 Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}} =$ \unit[13]{TeV} during LHC Run2 period.
+Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}}$~=~\unit[13]{TeV} during LHC Run2 period.
 Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-The full description of ALICE detector in the LHC Run 2 can be found in Ref.
-\cite{ALICEdet}.
-The present analysis mainly uses V0(\cite{VZEROpaper}), ITS (Inner Tracking System, \cite{ITSpaper}) and TPC (Time Projection Chamber, \cite{TPCpaper}) detectors.
+The full description of ALICE detector in the LHC Run 2 can be found in Refs.
+\cite{Aamodt:2008zz,Abelev:2014ffa}.
+The present analysis mainly uses V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
 

### 2020-05-18 sec_ana.tex
Update on Sec3

@@
 The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudo rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$).
-The following equation expresses the correlation as associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ with a given transverse momentum($\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particle and associated particle with the notation of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
+The following equation expresses the angular correlation function as associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ with a given transverse momentum($\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particles and associated particles.
+%with the notation of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
 \begin{eqnarray}
@@
 where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event and the background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed 10 events having the same primary vertex and belonging to the same multiplicity class.
+The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event and the background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed events having the same primary vertex and belonging to the same multiplicity class.
 
@@
 The minimum yield ($C_{\rm{ZYAM}}$) at the minimum $\Delta\varphi$($\Delta\varphi_{\rm{min}}$) of the $\Delta\varphi$ distribution are obtained from the function, which fits the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
-Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to take into consideration the major combinatorial correlations to be rejected.
+Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to describe the shape to find the minimum to be used for integral of the yield.
 The associated yield of the ridge($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after ZYAM.
@@
 The ridge yield is further studied with various event selections regarding hard processes.
-The event selection is applied by requiring minimum transverse momentum of leading track or jet reconstructed in the mid-rapidity, where the leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{T}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$.
-The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer.
+The event selection is applied by requiring minimum transverse momentum of leading track or jet reconstructed in the mid-rapidity.
+The leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{\rm{T}}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$.
+The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer from the collisions to the initial partons.
 
@@
 \label{sec:uncertainties}
+
 The background distribution is constructed using several events having same primary vertex.

### 2020-05-18 sec_intro.tex
Comments by BK for the introduction

@@
 
-Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, has indicated the formation of a strongly interacting quark gluon plasma (QGP) matter, which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
-The recent efforts are nowadays focused on constrainig the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
-In recent years similar long-range collective azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf} proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced are expected to be small.
+Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, indicates the formation of a strongly interacting matter called the quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
+The recent efforts are focused on constraining the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
+In recent years similar collective behaviors via long-range azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced by such a system are expected to be small.
 
-Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\phi$ correlation functions, where $\eta$ is the pseudorapidity and $\phi$ is the azimuthal angle.
+Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\varphi$ correlation functions, where $\eta$ is the pseudorapidity and $\varphi$ is the azimuthal angle.
 Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-In most Monte Carlo (MC) event generators for proton-proton (pp) collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\phi$ $\approx$ $\pi$ ) jet correlations.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in $\Delta\eta-\Delta\phi$ plot.
-The shape of these $\Delta\phi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
+For most Monte Carlo (MC) event generators in pp collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\varphi$ $\approx$ $\pi$ ) jet correlations.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in the $\Delta\eta-\Delta\varphi$ plane.
+The shape of these $\Delta\varphi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
 The second and third order terms are the dominant harmonic coefficients $v_n$.
@@
 % TODO more pA measurements
-The ridge structures in high-multiplicity pp and pPb events have been attributed to mechanisms that involve initial-state effects, such as gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and colour connections~\cite{Ortiz:2013yxa,Sarma:2019teo} forming along the longitudinal direction and final-state effects, such as parton-induced interactions~\cite{Arbuzov:2011yr}, and collective effects due to a hydrodynamic behaviour of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
-Hybrid models which implement both effects are geneally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
-The importance of the proton shape and its fluctuations to model the small system was recongnized in \cite{Mantysaari:2017cni}.
-The hydrodynamics itself might not be the only mechanism of the observed collectivity was acknowledged in ~\cite{Zhao:2020pty}. 
+The ridge structures in high-multiplicity pp and p--Pb events have been attributed to mechanisms like initial-state effects, such as gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo} forming along the longitudinal direction and final-state effects, such as parton-induced interactions~\cite{Arbuzov:2011yr}, and collective effects due to a hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+Hybrid models implementing both effects are generally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
+The proton shape and its fluctuations are also important to model the small systems \cite{Mantysaari:2017cni}.
+The hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty}. 
 The influence and interplay of initial state and final state effects are recently studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for the quantitative description of observables in small systems~\cite{Schenke:2019pmk}.
-The attempts to describe the collective effects systematically from the small to large systems are being made both for experiments~\cite{Acharya:2019vdf} and theory side~\cite{Greif:2019ygb}.
-However, a quantitative description of the full set of experimental data has not yet been achieved.
+The attempts to describe the collective effects systematically from the small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoritically~\cite{Greif:2019ygb}.
+However, a quantitative description of the full set of experimental data has not been achieved yet.
 The summary of various explanations for the observed correlations in these small systems are summarized in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
 
-Furthermore, if collectivity in small systems is due to final state interactions, it should be possible to measure its effect on jets.
-Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high multiplicity pp collisions.
-The most of observables for the jet quenching in pp and pPb collisions didn't show any clear evidences so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
+Furthermore, if collectivity in small systems is due to final state interactions, it is expected to measure its effect on jets.
+Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high-multiplicity pp collisions.
+The most of observables for the jet quenching in pp and p--Pb collisions do not show any clear evidences so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
 The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity in the event~\cite{Adam:2016jfp,Acharya:2018egz}.
@@
 %find one more one this regard.
-The ATLAS experiment has recently shown that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
-The impact paramenter dependence on di-jet or multi-jet production in pp collisons was studied in \cite{Frankfurt:2003td}.
-The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 Monte Carlo event generator so called ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc} and ATLAS Z-tagged ridge.
-This challenges the hydrodymic picture and predicts modifications to jet fragmentation
+The ATLAS experiment recently showed that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
+The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in \cite{Frankfurt:2003td}.
+The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 event generator so called the ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc} and ATLAS Z-tagged ridge.
+This challenges the hydrodynamic picture and predicts modifications to jet fragmentation
 properties~\cite{Bierlich:2019ixq}.
@@
 The results are compared to previous measurements from CMS experiments.
-In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
-The experimental setup and measurements are described in Sec.~\ref{sec:experiment}.
-In Sec.~\ref{sec:ana} we present the analysis methods.
-The sources of systematic uncertainties are explained in Sec.~\ref{sec:uncertainties}.
-The results of the measurements are presented in Sec.~\ref{sec:results}.
-In Sec.~\ref{sec:theory} we present comparisons to model calculations.
+In addition, we report the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
+
+The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, sequentially.
+The sources of systematic uncertainties are represented in Sec.~\ref{sec:uncertainties}.
+The results of the measurements are interpreted in Sec.~\ref{sec:results}.
+In Sec.~\ref{sec:theory} we report comparisons to model calculations.
 Finally, Sec.~\ref{sec:summary} summarizes our new results.
+
+ %h has indicated the formation of a strongly interacting quark-gluon plasma (QGP) matteras indicated the formation of a strongly interacting quark-gluon plasma (QGP) matter

### 2020-05-19 sec_ana.tex
Comments by BK for the introduction
Update on sec3 and sec4

@@
 \section{Analysis Procedure}
-\label{sec:na}
+\label{sec:an}
 
@@
 The leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{\rm{T}}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$.
+The transverse momentum of jet is also corrected with underlying event density($\rho \cdot A$).
 The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer from the collisions to the initial partons.
@@
 Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation has been used to estimate the charged single particle efficiency and the contamination from the non-primary particle.
-The corrections have been tested by comparing the distributions, which are constructed with generated true particles and reconstructed particles with detector responses.
+
+%The corrections have been tested by comparing the distributions, which are constructed with generated true particles and reconstructed particles with detector responses.
 The several percentage of non-closure has been considered into systematic uncertainty.
@@
 \label{sec:uncertainties}
+The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and efficiency correction.
+Each source is separated into individual parts.
+The uncertainty from the event selection can be divided into Pile-up rejection and primary vertex selection.
+The uncertainty from the track selection is estimated by changing the selection criteria.
+The uncertainty from the yield extraction procedures can be divided into long-range definition and ZYAM procedure.
+The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to acceptance correction.
+Finally, The uncertainty from the application of track efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed by true particles.
+
+\begin{table}[!h]
+\caption{ The relative systematic uncertainty(\%) of the associated yield spectrum as function of $(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$(second), $\it{p}_{\rm{T,Lead}}$(thrid) or $\it{p}_{\rm{T,jet}}$(fourth) selection in high multiplicity(0-0.1\%) }
+\centering
+\begin{tabular}{|c|<{\centering}m{8em}|<{\centering}m{6em}|<{\centering}m{6em}|}
+\hline 
+Sources & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
+Mixing			& $\sim$4.4	&2-8		&1-16	\\ \hline
+Pileup			& $\sim$0.8	&0-4		&0-4		\\ \hline
+Tracking			& $\sim$4.0 	&2		&2		\\ \hline
+Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline
+ZYAM			& $\sim$5.1	&2		&2		\\ \hline
+$\Delta\eta$ range	& $\sim$4.5	&3-7		&3-9		\\ \hline
+M.C. non-closure	& $\sim$2.5 	&1		&1		\\ \hline
+Total 			& $\sim$9.7	&4-16	&4-22	\\ 
+\hline 
+\end{tabular}
+
+\end{table}
 
@@
 The effect of track selection is estimated by varying a few selection criteria included in track selection.The estimated effect is $\sim$5\%.
+
+\iffalse
 
@@
 \end{table}
+\fi

### 2020-05-22 sec_ana.tex
update on sec4

@@
 The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudo rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$).
-The following equation expresses the angular correlation function as associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ with a given transverse momentum($\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particles and associated particles.
+The following equation expresses the correlation function as associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ with a given transverse momentum($\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particles and associated particles.
 %with the notation of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
@@
 \end{eqnarray}
-where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding event class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event and the background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed events having the same primary vertex and belonging to the same multiplicity class.
+where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding multiplicity class.
+The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event and the background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed events having the same primary vertex and belonging to the same multiplicity class considering the change of acceptance effect with respect to the multiplicity class and primary vertex.
 
@@
 Finally, The uncertainty from the application of track efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed by true particles.
-
+The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}}$.
+The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ or $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
 \begin{table}[!h]
@@
 Sources & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
-Mixing			& $\sim$4.4	&2-8		&1-16	\\ \hline
-Pileup			& $\sim$0.8	&0-4		&0-4		\\ \hline
+Pileup cut			& $\sim$0.8	&0-4		&0-4		\\ \hline
+Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline
+
 Tracking			& $\sim$4.0 	&2		&2		\\ \hline
-Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline
+
 ZYAM			& $\sim$5.1	&2		&2		\\ \hline
 $\Delta\eta$ range	& $\sim$4.5	&3-7		&3-9		\\ \hline
-M.C. non-closure	& $\sim$2.5 	&1		&1		\\ \hline
+
+Mixing			& $\sim$4.4	&2-8		&1-16	\\ \hline
+
+M.C. non-closure*	& $\sim$2.5 	&1		&1		\\ \hline
 Total 			& $\sim$9.7	&4-16	&4-22	\\ 
@@
 
-The background distribution is constructed using several events having same primary vertex.
-The effect of construction of background distribution is estimated by varying the primary vertex interval from 2 cm to 1 cm.
-The estimated effect is 6-10\%.
+The uncertainty from the pileup rejection is estimated by inspecting the changes of results with different rejection methodologies from the default one.
+The estimated uncertainty is 1\% without $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
+The uncertainty is increased up to 4\% with $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
 
-The $\Delta\eta$ projection range for construction of long-range $\Delta\varphi$ is sensitive to contamination of non-flow effect.
-The effect of  $\Delta\eta$ projection range is estimated by varying the projection range.
-The estimated effect is 10-15\% for $\it{p}_{\rm{T}}>$1.0 GeV/\it{c}\rm{} and 20\% for 0.5$<\it{p}_{\rm{T}}<$1.0 GeV/\it{c}\rm{}.
+The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm.
+The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select long-range side.
+The estimated uncertainty is increased up to 12\% from 1\%, which is obtained without the event scale selection.
 
-The M.C. closure test for efficiency correction results in $\sim$4\% discrepancy. The discrepancy is considered into systematic uncertainty.
+The uncertainty from the track selection is estimated by varying the track selection methodologies from the one optimized for refining the angular track distribution to the other optimized for particle identification.
+The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks.
 
-The effect of primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm.
-The estimated effect is $\sim$4\%.
-The effect of rejection of pile-up events.
-is estimated by varying the methodology of pile-up rejection.
-The estimated effect is $\sim$4\%.
-The effect of track selection is estimated by varying a few selection criteria included in track selection.The estimated effect is $\sim$5\%.
+The uncertainty from the ZYAM procedure is estimated by varying the finding-scope for minimum position.
+The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks, which is not largely affected by the event scale selection.
+
+The uncertainty from the long $\Delta\eta$ range is estimated by varying the $\Delta\eta$ range.
+The uncertainty might include effects from the longitudinal de-correlations and possible non-flow contamination, which is thought be small.
+The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.
+
+The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2.0 cm to 1.0 cm. The estimated uncertainty is 1-16\%
+
+*The M.C. closure test for efficiency correction results in $\sim$2.5\% discrepancy. The discrepancy is considered into systematic uncertainty.
 

### 2020-05-26 paper.tex
Update on sec3 and sec4
abstract updated

@@
 \usepackage {units}
-
+\usepackage {array}
 \linenumbers
@@
 \begin{abstract}
-\input{abstract.tex}
-\end{abstract}
+%\input{abstract.tex}
+
+In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons.
+Many theoretical approaches have been applied to interpret the similarities.
+However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision.
+To further investigate these effects on the ridge effect, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at a center-of-mass energy $\sqrt{s} = 13$~TeV.
+A dedicated high-multiplicity trigger implemented in ALICE since 2016 is beneficial for the study because of increased statistics for high-multiplicity pp collisions.
+The results are compared to previous measurements by other LHC experiments.
+In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
 \end{titlepage}

### 2020-05-26 paper.tex
abstract updated2

@@
 In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons.
-Many theoretical approaches have been applied to interpret the similarities.
+Many theoretical approaches have been applied to interpret the similarity.
 However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision.
-To further investigate these effects on the ridge effect, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at a center-of-mass energy $\sqrt{s} = 13$~TeV.
-A dedicated high-multiplicity trigger implemented in ALICE since 2016 is beneficial for the study because of increased statistics for high-multiplicity pp collisions.
+To further investigate these effects on the ridge effect, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV.
+The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016 because of increased statistics for high-multiplicity pp collisions.
 The results are compared to previous measurements by other LHC experiments.

### 2020-05-26 sec_intro.tex
adopting JL's comments

@@
 The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in \cite{Frankfurt:2003td}.
-The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 event generator so called the ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc} and ATLAS Z-tagged ridge.
+The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 event generator so called the ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
 This challenges the hydrodynamic picture and predicts modifications to jet fragmentation
@@
 
-To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during 2016 and 2017 with ALICE.
+To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during the LHC Run 2 data taking period.
 In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.

### 2020-05-26 sec_ana.tex
partly analysis section updated

@@
 
-Delivery of protons with world-highest energy by LHC at CERN makes it possible to generate various phenomena from their collisions.
-Recent center-of-mass energy of colliding two protons is increased up to $\sqrt{\it{s}}$~=~\unit[13]{TeV} during LHC Run2 period.
-Among data from proton-proton collisions at \unit[13]{TeV}, This paper describes analysis results obtained by using 2016 to 2018 data sets.
-The full description of ALICE detector in the LHC Run 2 can be found in Refs.
-\cite{Aamodt:2008zz,Abelev:2014ffa}.
-The present analysis mainly uses V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
+%LHC at CERN produces various interesting phenomena including the ridge effect that is the main topic of the document in pp collisions with the highest center-of-mass energy in the world.
+%Recent center-of-mass energy in pp collisions reaches up to $\sqrt{s} = 13$~TeV during the last LHC Run 2 period. 
+The analysis is based on the data sets in pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 in the LHC Run 2 period.
+The full description of ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
+The present analysis mainly utilizes V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
 

### 2020-05-26 sec_ana.tex
update of ana on ITS and TPC

@@
 The V0 provides trigger and estimation of event multiplicity.
-A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring higher amplitude of V0 Detector.
+A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring some thresholds on signal amplitudes of energy deposit by charged particles in the V0 detector.
 
-The responsibility of reconstruction of charged track is up to the ITS and the TPC.
-The ITS is composed of three subsystems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS has an acceptance up to $|\eta|<$1.95 for single charged track reconstruction.
-The TPC, which is working inside solenoidal magnetic field of 0.5 T, has an acceptance up to $|\eta|<$0.9 for charged tracks reaching the outer radius of the TPC.
-The tracking of charged-particles is done with the combination of the ITS and the TPC, which enable the reconstruction of tracks down to 0.2 GeV/\it{c}\rm{} with $\sim$75\% efficiency.
+Charged particles are reconstructed by the ITS and TPC, which are working in a constant solenoidal magnetic field of 0.5~T.
+The ITS is composed of three sub-systems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
+The ITS and TPC have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm.
+The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.2~GeV/$c$ with a $\sim $75\% efficiency.
 
@@
 \section{Analysis Procedure}
-\label{sec:an}
+\label{sec:ana}
 

### 2020-05-26 sec_ana.tex
finish of the section 2

@@
 The ITS is composed of three sub-systems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS and TPC have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm.
+The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.2~GeV/$c$ with a $\sim $75\% efficiency.
 
-The multiplicity class used in the present analysis is top 0-0.1\%, which denotes the most particle-abundant events including  $\sim$31 charged particles in the mid-rapidity region($|\eta|<$0.5).
-This analysis uses charged particles, whose reconstructed transverse momenta are larger than 0.2 GeV/\it{c}\rm{} in a fiducial region as $|\eta|<$0.9.
+%The multiplicity class is classified by the signal amplitude of the V0 detector.
+The multiplicity class used in the present analysis is the top 0.1\% signal amplitude events by the V0 detector for the set of minimum bias events at ALICE.
+Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
+Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
 

### 2020-05-26 sec_ana.tex
correlation function definition updated

@@
 Charged particles are reconstructed by the ITS and TPC, which are working in a constant solenoidal magnetic field of 0.5~T.
-The ITS is composed of three sub-systems, Silicon Pixel Detector(SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
+The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
 The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm.
@@
 %The multiplicity class is classified by the signal amplitude of the V0 detector.
-The multiplicity class used in the present analysis is the top 0.1\% signal amplitude events by the V0 detector for the set of minimum bias events at ALICE.
+The high multiplicity events used in the present analysis have the top 0.1\% signal amplitude by the V0 detector with respect to the set of minimum bias events at ALICE.
 Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
@@
 
-The two-particle correlation between trigger particle and associated particle is measured as function of relative pseudo rapidity($\Delta\eta$) and azimuthal angle($\Delta\varphi$).
-The following equation expresses the correlation function as associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ with a given transverse momentum($\it{p}_{\rm{T, trig}}$, $\it{p}_{\rm{T, assoc}}$) of trigger particles and associated particles.
-%with the notation of $\it{p}_{\rm{T, trig}} > \it{p}_{\rm{T, assoc}}$.
+The yield of two-particle correlations between the trigger and associated particles are measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle ($\Delta\varphi$) differences
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)},
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}\quad,
 \end{eqnarray}
-where the $N_{\rm{trig}}$ is the number of trigger particles in the corresponding multiplicity class.
-The signal distribution $S(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in the same event and the background distribution $B(\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlation in mixed events having the same primary vertex and belonging to the same multiplicity class considering the change of acceptance effect with respect to the multiplicity class and primary vertex.
+where  $p_{\mathrm{T, trig}}$ and $p_{\mathrm{T, assoc}}$ are the transverse momenta of  trigger particles and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, and $N_\mathrm{pair}$ is the number of pairs between the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
+$S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is the yield of two-particle correlations in mixed events.
+In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
 

### 2020-05-26 sec_ana.tex
section 3 updated

@@
 
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within 2.8$<\eta<$5.1 and -3.7$<\eta<$-1.7, respectively.
+The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
 The V0 provides trigger and estimation of event multiplicity.
@@
 The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}|<10$~cm.
+The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}| < 10$~cm.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.2~GeV/$c$ with a $\sim $75\% efficiency.
@@
 \end{eqnarray}
-where  $p_{\mathrm{T, trig}}$ and $p_{\mathrm{T, assoc}}$ are the transverse momenta of  trigger particles and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, and $N_\mathrm{pair}$ is the number of pairs between the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
+where  $p_{\mathrm{T, trig}}$ and $p_{\mathrm{T, assoc}}$ are the transverse momenta of  trigger particles and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, and $N_\mathrm{pair}$ is the number of pairs of the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
 $S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is the yield of two-particle correlations in mixed events.
+The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$ $B (0,0)$.
 In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
 
-The quantitative study of ridge is done with $\Delta\varphi$ distribution at large $\Delta\eta$ to achieve direct comparison of ridges between different event classes and transverse momentum intervals.
-The large $\Delta\eta$ range is defined as 1.6$<|\Delta\eta|<$1.8, which allows non-flow effects, mainly coming from the jet, not to contribute to the $\Delta\varphi$ distribution.
+ The quantitative study of ridge is done with $\Delta\varphi$ distribution at a large $\Delta\eta$ to achieve direct comparison of ridges between different event classes and transverse momentum intervals.
+The large $\Delta\eta$ range can be selected as $1.6<|\Delta\eta|<1.8$ where non-flow effects (mainly coming from jets) are rarely accepted.
+In this region, jets are not supposed to contribute to the $\Delta\varphi$ distribution that is expressed as
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.6} \rm{d} \Delta \eta \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta \rm{d}\Delta\varphi}
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.6} \rm{d} \Delta \eta \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \quad.
 \end{eqnarray}
+
 The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
@@
 Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to describe the shape to find the minimum to be used for integral of the yield.
-The associated yield of the ridge($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after ZYAM.
+The associated yield of the ridge $Y^{\rm{assoc}}$ is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
 \begin{eqnarray}
-Y^{\rm{assoc}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \rm{d} \Delta\varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } 
+Y^{\rm{assoc}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \rm{d} \Delta\varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } \quad.
 \end{eqnarray}
 
-The ridge yield is further studied with various event selections regarding hard processes.
-The event selection is applied by requiring minimum transverse momentum of leading track or jet reconstructed in the mid-rapidity.
-The leading track is accepted within $|\Delta\eta|<0.9$ and reconstructed jet, which are made with anti-$k_{\rm{T}}$ algorithm with cone radius as 0.4, is accepted within $|\Delta\eta|<0.4$.
-The transverse momentum of jet is also corrected with underlying event density($\rho \cdot A$).
-The high $\it{p}_{\rm{T}}$ track and jet mostly generated from the hard scatterings in the initial collisions of hadrons so that tagging of events with transverse momentum of leading track or jet allows us to access to the high momentum transfer from the collisions to the initial partons.
+The ridge yield is further studied with respect to the magnitude of the hard process.
+Events with the hard process are selected by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the deep inelastic scattering of the initial partons.
+The leading track is selected within $|\Delta\eta|<0.9$.
+Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$.
+Jets are selected within $|\eta_\mathrm{jet}|<0.4$.
+The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density $rho$.
 
-Monte Carlo simulation with PYTHIA8 event generator and with particle transport through the detector using GEANT simulation has been used to estimate the charged single particle efficiency and the contamination from the non-primary particle.
+Monte Carlo simulation with PYTHIA 8 event generator and particle transport inside ALICE using GEANT 3 is used to correct the acceptance and the efficiency of ALICE detectors.
 
@@
 \label{sec:uncertainties}
-The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and efficiency correction.
-Each source is separated into individual parts.
+The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction.
+Each source is assumed uncorrelated.
 The uncertainty from the event selection can be divided into Pile-up rejection and primary vertex selection.
@@
 \begin{table}[!h]
-\caption{ The relative systematic uncertainty(\%) of the associated yield spectrum as function of $(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$(second), $\it{p}_{\rm{T,Lead}}$(thrid) or $\it{p}_{\rm{T,jet}}$(fourth) selection in high multiplicity(0-0.1\%) }
+\caption{ The relative systematic uncertainty of the associated yield spectrum as function of 
+$(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ (second), $\it{p}_{\rm{T,Lead}}$ (thrid) or $\it{p}_{\rm{T,jet}}$ (fourth) selection in high multiplicity (0--0.1\%) }
 \centering

### 2020-05-26 paper.tex
section 3 updated
section 3 and 4 updated

--- 2020-04-23 paper.tex
@@
 \begin{abstract}
-\input{abstract.tex}
+%\input{abstract.tex}
+
+%In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons.
+Many theoretical approaches have been applied to interpret the similarity.
+However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision.
+
+To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV.
+The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016 because of increased statistics for high-multiplicity pp collisions.
+The results are compared to previous measurements by other LHC experiments.
+In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
 \end{abstract}
+
 \end{titlepage}
+
 \setcounter{page}{2}

### 2020-05-26 sec_ana.tex
section 3 and 4 updated

@@
 Each source is assumed uncorrelated.
-The uncertainty from the event selection can be divided into Pile-up rejection and primary vertex selection.
+The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection.
 The uncertainty from the track selection is estimated by changing the selection criteria.
-The uncertainty from the yield extraction procedures can be divided into long-range definition and ZYAM procedure.
-The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to acceptance correction.
-Finally, The uncertainty from the application of track efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed by true particles.
-The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}}$.
-The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ or $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
+The uncertainty from the yield extraction procedures can be categorized into long-range definition and ZYAM procedure.
+The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction.
+Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed.
+The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging each uncertainty for given $\it{p}_{\rm{T, trig}}$ and $\it{p}_{\rm{T, assoc}}$.
+The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ and $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, Lead}}$ and $\it{p}_{\rm{T, Jet}}$ selection, respectively.
 \begin{table}[!h]
@@
 
-The uncertainty from the pileup rejection is estimated by inspecting the changes of results with different rejection methodologies from the default one.
+The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
 The estimated uncertainty is 1\% without $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
 The uncertainty is increased up to 4\% with $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
-
 The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm.
@@
 The estimated uncertainty is increased up to 12\% from 1\%, which is obtained without the event scale selection.
-
-The uncertainty from the track selection is estimated by varying the track selection methodologies from the one optimized for refining the angular track distribution to the other optimized for particle identification.
+The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
 The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks.
@@
 The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks, which is not largely affected by the event scale selection.
-
 The uncertainty from the long $\Delta\eta$ range is estimated by varying the $\Delta\eta$ range.
@@
 The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.
-
 The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2.0 cm to 1.0 cm. The estimated uncertainty is 1-16\%
 
-*The M.C. closure test for efficiency correction results in $\sim$2.5\% discrepancy. The discrepancy is considered into systematic uncertainty.
+%*The M.C. closure test for efficiency correction results in $\sim$2.5\% discrepancy. The discrepancy is considered into systematic uncertainty.
 

### 2020-05-27 sec_ana.tex
table error fixed

@@
-% !TEX root = paper.tex
-
 \section{Experimental setup}
@@
 \centering
-\begin{tabular}{|c|<{\centering}m{8em}|<{\centering}m{6em}|<{\centering}m{6em}|}
+\begin{tabular}{|c|c|c|c|}
 \hline 
-Sources & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & Uncertainty $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
+\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty error (\%)} \\\cline{2-4}
+         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
 Pileup cut			& $\sim$0.8	&0-4		&0-4		\\ \hline
@@
 The uncertainty is increased up to 4\% with $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
-The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_{vtx}|<$ 8 cm to $|z_{vtx}|<$ 6 cm.
+The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 cm to $|z_\mathrm{vtx}|<$ 6 cm.
 The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select long-range side.
@@
 The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
-The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks.
+The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks.
 

### 2020-05-27 sec_results.tex
first intro
I think it contains all we want to say and i need fine tuning on the pythia and recent work from christian tomorrow.
table error fixed

@@
 \section {Results}
+\label{sec:results}
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/dpy2.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
+	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
 Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.
-}
+Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.}
+	\label{fig:PlotDeltaPhiESE}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
-	\subfigure{ \includegraphics[width=0.8\textwidth]{./figures/Fig2_RidgeYield_Esel_py.pdf}}
-	\caption{ The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
+	\includegraphics[width=0.99\linewidth]{./figures/Fig2_RidgeYield_Esel_py.pdf}
+	\caption{The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
+	\label{fig:RidgeYield_ESE}
 \end{figure}
@@
 
-The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Figure 5.
+The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
 The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
 
-The ridge yield is inspected as a function of the leading track selection in Figure 6.
+The ridge yield is inspected as a function of the leading track selection in Fig.~\ref{fig:RidgeYield_ESE}.
 As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
@@
 \section{Model Comparison}
+\label{sec:theory}

### 2020-05-27 paper.tex
table error fixed
abstract redefined

@@
 %%% Put your own title + short title here:
-\title{Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s}$ =13 TeV}
+\title{Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
 \ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
@@
 
-To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV.
-The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016 because of increased statistics for high-multiplicity pp collisions.
-The results are compared to previous measurements by other LHC experiments.
-In addition, we explore possible physical origins of the ridge effects in small systems by studying the results as a function of the energy scale of the hard fragmentation process and comparing the various theoretical models tuned for the initial and final state effect.
+To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE.
+The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016.
+Jet events are selected by two methods.
+The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$.
+The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$.
+The measured ridge yield is consistent with the previous results from other LHC experiments.
+Furthermore, the ridge yield is found to be independent of the energy scale of the hard scattering process.
+This observation can help identify the origins of the ridge in small systems.
+
 \end{abstract}
@@
 
-%%%%%%%% Bibliography (In case of using bibtex generate the bbl requested by arXiv)
-%\bibliographystyle{utphys}   % Remember we use title in the biblio
-%\bibliography{biblio}
-%\input {bibliography.tex}
-
-%%%%%%%%% appendix with author list
 \newpage
 \appendix
-%
-%\input{}               %%%%%%%%%%% put your appendices here
-%
-
-%\section{The ALICE Collaboration}
-%\label{app:collab}
-%\input{authorlist-preprint.tex}  %%%%%%% done by webmaster team
 

### 2020-05-28 paper.tex
abstract improved

@@
 
-To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE.
-The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016.
+To further investigate the ridge effect in small systems, we present new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE.
+The ridge yield is investigated in the pseudorapidity difference range $1.6<|\Delta \eta|<1.8$ of two-particle correlations.
 Jet events are selected by two methods.
 The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$.
-The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$.
+The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in the pseudorapidity range of jets $|\eta_\mathrm{jet}|<0.4$.
+The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016.
 The measured ridge yield is consistent with the previous results from other LHC experiments.

### 2020-05-28 paper.tex
abstract improved
abstract
need to do a final touch once we have all the models in

--- 2020-05-27 paper.tex
@@
 
-%In recent years, similar features between small systems like proton-proton (pp) collisions and large systems like lead-lead collisions have been observed via long-range correlations in pseudorapidity (so-called the ridge) for pairs of charged hadrons.
-Many theoretical approaches have been applied to interpret the similarity.
-However, it is still controversial whether the ridge in small systems is originated from initial or final-state effects of the collision.
-
-To further investigate the ridge effect in small systems, we present the new results of long-range correlations as a function of transverse momentum of jets in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV with ALICE.
-The study benefit from a dedicated high-multiplicity trigger implemented in ALICE since 2016.
-Jet events are selected by two methods.
-The first one is done by seeing the transverse momentum of  leading particle in the pseudorapidity range $|\eta|<0.9$.
-The second method is done by reconstruction of charged jets using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$.
-The measured ridge yield is consistent with the previous results from other LHC experiments.
-Furthermore, the ridge yield is found to be independent of the energy scale of the hard scattering process.
-This observation can help identify the origins of the ridge in small systems.
+Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by the ALICE experiment at the Large Hadron Collider. 
+These results are obtained in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
+In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with harder fragmentations is to be present.
+The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
+The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
+These correlations also persists in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $p_{\mathrm T, jet} > 10$~GeV/$c$.
+The results are compared to PYTHIA8 string shoving, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  
+PYTHIA8 string shoving model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of  $p_{\mathrm T}$ dependence both for the unbiased and jet events.
+The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
 

### 2020-05-29 sec_results.tex
adding fig5
adding Fig2
adding new figure

@@
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/dp3.pdf} }
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
+	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
 Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
 }
-
+	\label{fig:PlotDeltaPhi}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig2_RidgeYield_Esel_py.pdf}
+	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
 	\caption{The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
@@
 As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
-
-\section{Model Comparison}
-\label{sec:theory}

### 2020-06-01 sec_ana.tex
update on sec 4

@@
 $S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is the yield of two-particle correlations in mixed events.
-The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$ $B (0,0)$.
+The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$ .
 In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
@@
 The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction.
-Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed.
+%Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. 
+Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlations function constructed by generated particles from the event generator.
 The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging each uncertainty for given $\it{p}_{\rm{T, trig}}$ and $\it{p}_{\rm{T, assoc}}$.
@@
 The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
+The pileup rejection is achieved by reconstructing the multiple vertex in the individual event.
+The multiplicity of the reconstructed vertices determines whether the event is contaminated by pileup or not.
+The variation is set by the minimum multiplicity of reconstructed vertices from 5 to 3.
+%Pileup cut (multbins) -> (default pileup from the physics selection)
+%Pileup cut (multbins) -> PileupMV (?)
 The estimated uncertainty is 1\% without $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
@@
 The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
+The variation is achieved by changing the mendatory SPD requirement and the maximal threshold for chi-square of the track fit.
+%https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
 The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks.

### 2020-06-01 sec_results.tex
update on results

@@
 
-The two-dimensional associated yield per trigger particle is shown in Figure 1 for pairs of trigger particle and associated particle with 1.0$<\it{p}_{\rm{T, assoc}}<\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
+\subsection{Ridge yield}
+
+Measurement of the correlations function is shown in Fig.~\ref{fig:PlotCorrMBHMT} for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), and 0-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
 The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
 	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr2.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr3.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left), 5-20\% (middle) and 20-100\% (right) multiplicity class.
+	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corrmb.pdf} }
+	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left) and 0-100\% (right) multiplicity class.
 The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
 }
-
+	\label{fig:PlotCorrMBHMT}
 \end{figure}
 
-The one-dimensional $\Delta\varphi$ distribution is shown in Figure 2 for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
+The one-dimensional $\Delta\varphi$ distribution is shown in Fig.~\ref{fig:PlotDeltaPhi} for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
 The associated yield per trigger particle is compared with CMS results.
 The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.
-
-The spectra of the ridge yield is shown in Figure 3 in very high multiplicity class and compared with CMS results.
-The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
-Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals.
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class.
+The distributions in upper panels are measured with 0-100\% multiplicity class.
+The distribution in lower panels are measured with 0-0.1\% multiplicity class.
 Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
@@
 
-\begin{figure}
+The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in very high multiplicity class and compared with CMS results.
+The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
+Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
+Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
+The spectrum is also compared with model predictions.
+The PYTHIA8 default and PYTHIA8 + String Shoving are used for the prediction.
+The PYTHIA8 default is shown as black line and predicts no ridge in pp collisions, which is expected and indicates ignorable jet contamination.
+The PYTHIA8 + String Shoving is shown as red line and predicts existence of ridge yield in pp collisions, which decreases more rapidly than measurement as transverse momentum increases.
+
+\begin{figure}[h!]
 	\centering
 	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/Fig1_RidgeYield.pdf} }
-	\caption{(color online) The spectra of ridge yield as function of transverse momentum. The spectrum is compared with CMS result \cite{ridge_pp_1}.}
+	\caption{ The spectra of ridge yield as function of transverse momentum.
+The filled circles denote the measurement with ALICE and compared with CMS measurement \cite{ridge_pp_1}, which is represented as open box.
+The two lines show model predictions from PYTHIA8 default(black line) and PYTHIA8 + String Shoving(red line).
+}
+	\label{fig:PlotYSpect}
 \end{figure}
+
+\subsection{Event scale dependent ridge yield}
+
+To further observe the behavior of the ridge yield in events including hard processes,
+
+the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
+The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
+
+The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
+The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
+
+The ridge yield is inspected as a function of the leading track selection in Fig.~\ref{fig:RidgeYield_ESE}.
+As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
 
@@
 \end{figure}
-
-To further understand the behavior of the ridge in events including hard processes, the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
-The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
-
-The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
-
-The ridge yield is inspected as a function of the leading track selection in Fig.~\ref{fig:RidgeYield_ESE}.
-As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.

### 2020-06-01 sec_results.tex
update on results

@@
 
-To further observe the behavior of the ridge yield in events including hard processes,
-
-the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4.
-The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.
+To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with minimum $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the ridge yield is maximum.
 
@@
 
-\begin{figure}
+\begin{figure}[h!]
 	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
+	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrlh.pdf} }
+	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrjet.pdf} }
 	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class.

### 2020-06-01 sec_results.tex
update on sec5

@@
 	\centering
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.31\textwidth]{./figures/corrmb.pdf} }
+	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corr1.pdf} }
+	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrmb.pdf} }
 	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left) and 0-100\% (right) multiplicity class.
@@
 
-To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with minimum $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the ridge yield is maximum.
-
-The one-dimensional $\Delta\varphi$ distribution with the leading track selection is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield doesn't change with respect to the leading track requirements within the uncertainties, whereas the away-side peak increases as the leading track requirement gets stronger, presumably because of the increase of the recoil jet yield.
-
-The ridge yield is inspected as a function of the leading track selection in Fig.~\ref{fig:RidgeYield_ESE}.
-As seen in the previous plots, the ridge yield does not depend on the selection, which indicates that the ridge is not affected significantly by the hardness of the events.
+To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}.
+The ridge structures are still seen with the event scale selection.
+With the minimum $\it{p}_{\rm{T, Jet}}$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrlh.pdf} }
-	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrjet.pdf} }
-	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively.
+	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrlh.pdf} }
+	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrjet.pdf} }
+	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) selection.
+The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
+The minimum requirement for $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ is 9 GeV/\it{c}\rm{} or 10 GeV/\it{c}\rm{}, respectively.
 }
+	\label{fig:PlotCorrHMTSel}
 \end{figure}
+
+The one-dimensional $\Delta\varphi$ distribution with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
+The near-side yield increases as the event scale increases by requiring higher $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$.
+The model comparisons are seen as blue line for PYTHIA8 + String Shoving and apricot line for PYTHIA8 default, respectively.
+The PYTHIA8 + String Shoving describes ridge yield with the selection.
+The PYTHIA8 default predict the ridge yield to be zero with the selection, which also tell there is little ignorable jet contamination.
+Both models well describe the away-side yield with the $\it{p}_{\rm{T, Jet}}$ selection and overestimates away-side yield with the $\it{p}_{\rm{T, Lead}}$ selection.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various leading track selection thresholds.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right) respectively.}
+	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\it{p}_{\rm{T, Lead}}$(lower) or $\it{p}_{\rm{T, Jet}}$(upper) selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in 0-0.1\% multiplicity class.
+The filled circles show measurement with ALICE.
+Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
 	\label{fig:PlotDeltaPhiESE}
 \end{figure}
+
+The spectra of the ridge yield as function of the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The spectra are compared with model predictions.
+The increases of ridge yield with the selections are observed and the model with PYTHIA8 + String Shoving underestimates the ridge yield.
+with the $\it{p}_{\rm{T, Jet}}$ selection.
+the model prediction with PYTHIA8 default still assures ignorable jet contamination.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
-	\caption{The ridge yield spectrum with respect to the leading particle and jet selections. The ridge yields are identical within uncertainties.}
+	\caption{The ridge yield spectra with respect to the leading particle and jet selections.
+The filled circles show measurement with ALICE.
+Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
 	\label{fig:RidgeYield_ESE}

### 2020-06-08 sec_summary.tex
first intro
I think it contains all we want to say and i need fine tuning on the pythia and recent work from christian tomorrow.
update on sec6

@@
+% !TEX root = paper.tex
+
 \section{Conclusions}
+\label{sec:summary}
 
-Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE.
-The measured associated yield is found to be consistent with the previous results from CMS experiment.
-The ridge yield, for the first time, has been observed in events including hard processes.
-Furthermore, it is found to be independent of the hardness of the events.
-This observation is important for the study of the origins of the ridge in small collision systems.
+ALICE has measured the $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider.
+The spectrum of the ridge yield has been measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
+The result has been compared with CMS measurement and shown that the results are compatible.
+Further understandings of the correlations in small system have been tried by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
+The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) shows enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
+The results have been compared with PYTHIA8 string shoving calculation, showing comparable enhancement as data.

### 2020-06-09 sec_summary.tex
update on sec6

@@
 The result has been compared with CMS measurement and shown that the results are compatible.
-Further understandings of the correlations in small system have been tried by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
-The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) shows enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
-The results have been compared with PYTHIA8 string shoving calculation, showing comparable enhancement as data.
+The PYTHIA8 string shoving has quantitatively estimated the spectrum while PYTHIA8 default shows zero yield.
+Further understandings of the correlations in small system have been attempted by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
+The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
+The results have been compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.

### 2020-06-09 sec_summary.tex
update on sec6

--- 2020-04-23 sec_summary.tex
@@
+% !TEX root = paper.tex
+
 \section{Conclusions}
+\label{sec:summary}
 
-Two-particle angular correlations in large $|\Delta\eta|$ has been measured in very high multiplicity events in pp collsions at $\sqrt{\it{s}}=13$ TeV with ALICE.
-The measured associated yield is found to be consistent with the previous results from CMS experiment.
-The ridge yield, for the first time, has been observed in events including hard processes.
-Furthermore, it is found to be independent of the hardness of the events.
-This observation is important for the study of the origins of the ridge in small collision systems.
+The $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider.
+The spectrum of the ridge yield is measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
+The result is compared with CMS measurement and shown that the results are compatible.
+The PYTHIA8 string shoving quantitatively estimates the spectrum while PYTHIA8 default shows zero yield.
+Further understandings of the correlations in small system are attempted by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
+The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
+The results have been compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.

### 2020-06-12 paper.tex
JL and BK lastet

@@
 
-Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by the ALICE experiment at the Large Hadron Collider. 
-These results are obtained in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
-In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with harder fragmentations is to be present.
+Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
+These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ for the trigger and associated particles.
+In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with a harder fragmentation are present.
 The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
 The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
-These correlations also persists in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $p_{\mathrm T, jet} > 10$~GeV/$c$.
-The results are compared to PYTHIA8 string shoving, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  
-PYTHIA8 string shoving model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of  $p_{\mathrm T}$ dependence both for the unbiased and jet events.
+These correlations also persists in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
+The results are compared to $\pythiashoving$, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  
+$\pythiashoving$ model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of  $p_{\mathrm T}$ dependence both for the unbiased and jet events.
 The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-06-12 sec_ana.tex
JL and BK lastet

@@
 %The multiplicity class is classified by the signal amplitude of the V0 detector.
-The high multiplicity events used in the present analysis have the top 0.1\% signal amplitude by the V0 detector with respect to the set of minimum bias events at ALICE.
+The high multiplicity events used in the present analysis have the top 0.1\%  signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
 Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
@@
 
-The yield of two-particle correlations between the trigger and associated particles are measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle ($\Delta\varphi$) differences
+The yield of two-particle correlations between the trigger and associated particles are measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle ($\Delta\varphi$) differences
 \begin{eqnarray}
 \frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}\quad,
+\label{eq:corrfunction}
 \end{eqnarray}
-where  $p_{\mathrm{T, trig}}$ and $p_{\mathrm{T, assoc}}$ are the transverse momenta of  trigger particles and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, and $N_\mathrm{pair}$ is the number of pairs of the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
+where  $\pttrig$ and $\ptassoc$ are the transverse momenta of  the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, $N_\mathrm{pair}$ is the number of pairs of the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
 $S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is the yield of two-particle correlations in mixed events.
-The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$ .
+The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
 In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
 
- The quantitative study of ridge is done with $\Delta\varphi$ distribution at a large $\Delta\eta$ to achieve direct comparison of ridges between different event classes and transverse momentum intervals.
+ The quantitative study of the ridge is done with $\Delta\varphi$ distribution at a large $\Delta\eta$ to achieve direct comparison of ridges between different event classes and transverse momentum intervals.
 The large $\Delta\eta$ range can be selected as $1.6<|\Delta\eta|<1.8$ where non-flow effects (mainly coming from jets) are rarely accepted.
-In this region, jets are not supposed to contribute to the $\Delta\varphi$ distribution that is expressed as
+In this region, jets are supposed not to contribute to the $\Delta\varphi$ distribution that is expressed as
 \begin{eqnarray}
@@
 
-The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure.
-The minimum yield ($C_{\rm{ZYAM}}$) at the minimum $\Delta\varphi$($\Delta\varphi_{\rm{min}}$) of the $\Delta\varphi$ distribution are obtained from the function, which fits the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
+The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
+The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi$ ($\Delta\varphi_{\rm{min}}$) in the $\Delta\varphi$ distribution is obtained from the function, which fits the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
 Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to describe the shape to find the minimum to be used for integral of the yield.
@@
 
+The ridge yield is measured with respect to the multiplicity classes.
+Multiplicity classes are defined by a probability range with respect to the minimum bias events, constituting 100\%.
+Percentile values are close to 0  for higher multiplicity while close to 100 for lower multiplicity collisions like the centrality classification in heavy-ion collisions~\cite{Abelev:2013qoq,ALICE-PUBLIC-2018-003}.
+Multiplicity classes are estimated by the V0 detector.The high multiplicity pp collisions in this analysis is defined as the top 0.1\% signal amplitude events measured by the V0 detector.
+The corresponding multiplicity class is called the 0--0.1\%.
+
 The ridge yield is further studied with respect to the magnitude of the hard process.
 Events with the hard process are selected by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the deep inelastic scattering of the initial partons.
-The leading track is selected within $|\Delta\eta|<0.9$.
+The leading track is selected within $|\Delta\eta|<0.9$ and the full azimuthal angle.
 Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$.
-Jets are selected within $|\eta_\mathrm{jet}|<0.4$.
-The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density $rho$.
+Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
+The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured for the $k_{\rm{T}}$ algorithm with $R = 0.2$.
 
-Monte Carlo simulation with PYTHIA 8 event generator and particle transport inside ALICE using GEANT 3 is used to correct the acceptance and the efficiency of ALICE detectors.
+Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT 3 is used to correct the acceptance and the efficiency of the ALICE detectors.
 
@@
 Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlations function constructed by generated particles from the event generator.
-The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ is summarized by averaging each uncertainty for given $\it{p}_{\rm{T, trig}}$ and $\it{p}_{\rm{T, assoc}}$.
-The uncertainty of $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ and $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ is summarized by averaging the each uncertainty for a given $\it{p}_{\rm{T, Lead}}$ and $\it{p}_{\rm{T, Jet}}$ selection, respectively.
+The uncertainty of $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$ is summarized by averaging each uncertainty for given $\pttrig$ and $\ptassoc$.
+The uncertainty of $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$ is summarized by averaging the each uncertainty for a given $\ptlead$ and $\ptjet$ selection, respectively.
 \begin{table}[!h]
-\caption{ The relative systematic uncertainty of the associated yield spectrum as function of 
-$(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ (second), $\it{p}_{\rm{T,Lead}}$ (thrid) or $\it{p}_{\rm{T,jet}}$ (fourth) selection in high multiplicity (0--0.1\%) }
+\caption{ The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.
+}
 \centering
@@
 \hline 
-\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty error (\%)} \\\cline{2-4}
+\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty (\%)} \\\cline{2-4}
          & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
-Pileup cut			& $\sim$0.8	&0-4		&0-4		\\ \hline
-Primary Vertex		& $\sim$2.4	&1-12	&1-8		\\ \hline
+Pileup cut			& $\sim$0.8	&0--4		&0--4		\\ \hline
+Primary Vertex		& $\sim$2.4	&1--12	&1-8		\\ \hline
 
@@
 ZYAM			& $\sim$5.1	&2		&2		\\ \hline
-$\Delta\eta$ range	& $\sim$4.5	&3-7		&3-9		\\ \hline
+$\Delta\eta$ range	& $\sim$4.5	&3-7		&3--9		\\ \hline
 
-Mixing			& $\sim$4.4	&2-8		&1-16	\\ \hline
+Mixing			& $\sim$4.4	&2--8		&1--16	\\ \hline
 
 M.C. non-closure*	& $\sim$2.5 	&1		&1		\\ \hline
-Total 			& $\sim$9.7	&4-16	&4-22	\\ 
+Total 			& $\sim$9.7	&4--16	&4--22	\\ 
 \hline 
@@
 %Pileup cut (multbins) -> PileupMV (?)
-The estimated uncertainty is 1\% without $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
-The uncertainty is increased up to 4\% with $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection.
-The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 cm to $|z_\mathrm{vtx}|<$ 6 cm.
-The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select long-range side.
+The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection.
+The uncertainty is increased up to 4\% with $\ptlead$ or $\ptjet$ selection.
+The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
+The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select the long-range side.
 The estimated uncertainty is increased up to 12\% from 1\%, which is obtained without the event scale selection.
 The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
-The variation is achieved by changing the mendatory SPD requirement and the maximal threshold for chi-square of the track fit.
+The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
@@
 The uncertainty from the ZYAM procedure is estimated by varying the finding-scope for minimum position.
-The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/\it{c}\rm{} tracks, which is not largely affected by the event scale selection.
+The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks, which is not largely affected by the event scale selection.
 The uncertainty from the long $\Delta\eta$ range is estimated by varying the $\Delta\eta$ range.
@@
 The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.
-The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2.0 cm to 1.0 cm. The estimated uncertainty is 1-16\%
+The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2 to 1 cm. The estimated uncertainty is 1--16\%
 

### 2020-06-12 sec_results.tex
JL and BK lastet

@@
 
-Measurement of the correlations function is shown in Fig.~\ref{fig:PlotCorrMBHMT} for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} in the 0-0.1\% (left), and 0-100\% (right) multiplicity class estimated by V0 detector, which covers forward rapidity region.
-The ridge is clearly seen in high multiplicity class unlike in lower multiplicity classes.
+Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the relative pseudorapidity ($\Delta \eta$) and azimuthal angle ($\Delta \varphi$) differences between the trigger and associated particles.
+The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm{and}~\ptassoc < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
+The left figure shows the function for the 0--0.1\% multiplicity class.
+The right one shows the function for the minimum bias events (the 0--100\% multiplicity class).
+The ridge behaviour is clearly observed in the high multiplicity class compared to the function for the minimum-bias events.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrmb.pdf} }
-	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in 0-0.1\% (left) and 0-100\% (right) multiplicity class.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.pdf} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
+	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right).
+The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < 2$ GeV/$c$.
 }
@@
 
-The one-dimensional $\Delta\varphi$ distribution is shown in Fig.~\ref{fig:PlotDeltaPhi} for pairs of particles with various $\it{p}_{\rm{T}}$ intervals in very high multiplicity class.
-The associated yield per trigger particle is compared with CMS results.
-The near-side peak is highest in the 1.0$<\it{p}_{\rm{T}}<$2.0 interval and gradually decreases with increasing $\it{p}_{\rm{T}}$.
+ Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the high multiplicity class (0--0.1\%).
+The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$.
+ %The associated yield per trigger particle is compared with the CMS results.
 
@@
 	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class.
-The distributions in upper panels are measured with 0-100\% multiplicity class.
+The distributions in upper panels are measured with 0--100\% multiplicity class.
 The distribution in lower panels are measured with 0-0.1\% multiplicity class.
-Interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} (left), 2.0$<\it{p}_{\rm{T}}<$3.0 GeV/\it{c}\rm{} (middle) and 3.0$<\it{p}_{\rm{T}}<$4.0 GeV/\it{c}\rm{} (right), respectively.
+Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
 }
@@
 
-The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in very high multiplicity class and compared with CMS results.
-The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\it{p}_{\rm{T}}>$0.4 GeV/\it{c}\rm{}.
+The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared with the CMS result~\cite{}.
+The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
 Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity,, the measurements are can be considered comparable with each other.
+Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity, the measurements are can be considered comparable with each other.
 The spectrum is also compared with model predictions.
-The PYTHIA8 default and PYTHIA8 + String Shoving are used for the prediction.
-The PYTHIA8 default is shown as black line and predicts no ridge in pp collisions, which is expected and indicates ignorable jet contamination.
-The PYTHIA8 + String Shoving is shown as red line and predicts existence of ridge yield in pp collisions, which decreases more rapidly than measurement as transverse momentum increases.
+$\pythiam$ and $\pythiashoving$ are used for the prediction.
+$\pythiam$ is shown with a black line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect.
+$\pythoashoving$ shown with a red line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.7\textwidth]{./figures/Fig1_RidgeYield.pdf} }
+	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig1_RidgeYield.pdf} }
 	\caption{ The spectra of ridge yield as function of transverse momentum.
 The filled circles denote the measurement with ALICE and compared with CMS measurement \cite{ridge_pp_1}, which is represented as open box.
-The two lines show model predictions from PYTHIA8 default(black line) and PYTHIA8 + String Shoving(red line).
+The two lines show model predictions from $\pythiam$ (black line) and $\pythiashoving$ (red line).
 }
@@
 
-To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}.
+To further observe the behavior of the ridge yield with respect to the hard process, the correlation function is measured with the minimum $\ptlead$ (left) or $\ptjet$ (right) thresholds for $1<\pttrigassoc<2$ GeV/$c$, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}.
 The ridge structures are still seen with the event scale selection.
-With the minimum $\it{p}_{\rm{T, Jet}}$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.
+With the minimum $\ptjet$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrlh.pdf} }
-	\subfigure{ \includegraphics[width=0.4 \textwidth]{./figures/corrjet.pdf} }
-	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) selection.
-The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{}.
-The minimum requirement for $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ is 9 GeV/\it{c}\rm{} or 10 GeV/\it{c}\rm{}, respectively.
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.pdf} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
+	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection.
+The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$.
+The minimum requirement for $\ptlead$ or $\ptjet$ is 9 and 10 GeV/$c$, respectively.
 }
@@
 
-The one-dimensional $\Delta\varphi$ distribution with the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield increases as the event scale increases by requiring higher $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$.
-The model comparisons are seen as blue line for PYTHIA8 + String Shoving and apricot line for PYTHIA8 default, respectively.
-The PYTHIA8 + String Shoving describes ridge yield with the selection.
-The PYTHIA8 default predict the ridge yield to be zero with the selection, which also tell there is little ignorable jet contamination.
-Both models well describe the away-side yield with the $\it{p}_{\rm{T, Jet}}$ selection and overestimates away-side yield with the $\it{p}_{\rm{T, Lead}}$ selection.
+The one-dimensional $\Delta\varphi$ distribution with the minimum $\ptlead$ (left) or $\ptjet$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
+The near-side yield increases as the event scale increases by requiring higher $\ptlead$ (left) or $\ptjet$.
+The model comparisons are are shown for $\pythiashoving$ with a blue and $\pythiam$ with a red line.
+The $\pythiashoving$ describes ridge yield with the selection.
+$\pythiam$ predicts non ridge yield with the selection, which also tell there is little ignore-able jet contamination.
+Both models well describe the away-side yield with the $\ptjet$ selection and overestimates away-side yield with the $\ptlead$ selection.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\it{p}_{\rm{T, Lead}}$(lower) or $\it{p}_{\rm{T, Jet}}$(upper) selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{} in 0-0.1\% multiplicity class.
+	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1<\pttrigassoc<2$ GeV/\it{c}\rm{} in the 0--0.1\% multiplicity class.
 The filled circles show measurement with ALICE.
-Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
+Model predictions are compared with measurement with a blue line for $\pythiashoving$  and a orange line for $\pythiam$.}
 	\label{fig:PlotDeltaPhiESE}

### 2020-06-12 sec_summary.tex
JL and BK lastet

--- 2020-06-08 sec_summary.tex
@@
 
-ALICE has measured the $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider.
-The spectrum of the ridge yield has been measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
-The result has been compared with CMS measurement and shown that the results are compatible.
-Further understandings of the correlations in small system have been tried by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
-The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) shows enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
-The results have been compared with PYTHIA8 string shoving calculation, showing comparable enhancement as data.
+%Two-particle angular correlations in a large pseudorapidity difference of $1.6<|\Delta\eta|<1.8$ are measured in very high-multiplicity pp collisions at $\sqrt{\it{s}}=13$ TeV with ALICE.
+The measured associated yield is found to be consistent with the previous results from CMS experiment.
+The ridge yield, for the first time, is observed with respect to the hard process.
+Furthermore, it is found to be independent of the hardness of events.
+This observation is important for the study of the origins of the ridge in small collision systems.
+
+Ridge yields via long-range azimuthal correlations are measured with respect to the hard process in pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV.
+The hard process is selected respectively by the transverse momenta of the leading track $p_\mathrm{T,\,Lead}$ and leading jet $p_\mathrm{T,\,Jet}$ for each event.
+$\p_\mathrm{T,\,Lead}$ is measured in a pseudorapidity region of $|\eta|<0.9$ for the full azimuthal angle.
+Jets are reconstructed with charged particles using the anti-$k_\mathrm{T}$ algorithm for a resolution parameter $R=0.4$ in a pseudorapidity region of $|\eta_\mathrm{jet}|<0.4$ for the full azimuthal angle.
+The ridge yield is measured in the relative pseudorapidity range $1.6 < |\Delta\eta| < 1.8$ for the transverse momentum range $1 < p_\mathrm{T} < 5$ GeV/$c$.
+The high multiplicity pp collisions are selected in terms of the energy deposit in the V0 detector of ALICE sensitive to charged-particle multiplicity in the forward region.
+
+The ridge behaviour is clearly appeared in high-multiplicity pp collisions that are relevant to the top 0.1\% events for the energy deposit in the V0.
+The result is compared to the CMS result and it is found to be compatible.
+The PYTHIA 8 String Shoving estimates the ridge yield quantitatively while PYTHIA 8 does not describe the ridge effect at all.
+Further study of the ridge behaviors in small system is done by measuring a ridge yield in events, where jets accompanying with the hard scattering process present by requiring thresholds for $p_\mathrm{T,\,Lead}$ and $p_\mathrm{T,\,Jet}$.
+The ridge yield for events with $p_\mathrm{T,\,jet} > 10$ GeV/$c$ is increased as $p_\mathrm{T,\,Lead}$ and $p_\mathrm{T,\,Jet}$ increase.
+The results are compared with PYTHIA 8 String Shoving model.
+The model describes the enhancement the ridge yield, however, underestimating the absolute ridge yield than data.
+This observation is important for the study of the origins of the ridge in small systems.

### 2020-06-12 sec_intro.tex
commit to github

@@
 
-Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta-\Delta\varphi$ correlation functions, where $\eta$ is the pseudorapidity and $\varphi$ is the azimuthal angle.
+Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta$--\Delta\varphi$ correlation functions, where $\eta$ is the pseudorapidity and $\varphi$ is the azimuthal angle.
 Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
 For most Monte Carlo (MC) event generators in pp collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\varphi$ $\approx$ $\pi$ ) jet correlations.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in the $\Delta\eta-\Delta\varphi$ plane.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in the $\Delta\eta$--$\Delta\varphi$ plane.
 The shape of these $\Delta\varphi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
@@
 The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in \cite{Frankfurt:2003td}.
-The microscopic model for collectivity, based on interacting string implemented in the PYTHIA8 event generator so called the ``shoving model''~\cite{Bierlich:2017vhg} , can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
+The microscopic model for collectivity, based on interacting string implemented in $\pythiae$ event generator so called the ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
 This challenges the hydrodynamic picture and predicts modifications to jet fragmentation

### 2020-06-17 paper.tex
updates

@@
 Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
-These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ for the trigger and associated particles.
+These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles.
 In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with a harder fragmentation are present.
@@
 The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
-These correlations also persists in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
+These correlations also persist in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
 The results are compared to $\pythiashoving$, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  

### 2020-06-17 sec_ana.tex
updates

@@
 The high multiplicity events used in the present analysis have the top 0.1\%  signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
-Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
+Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events~\cite{}.
 Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
@@
 
-The yield of two-particle correlations between the trigger and associated particles are measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle ($\Delta\varphi$) differences
+The yield of two-particle correlations between the trigger and associated particles are measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$)
 \begin{eqnarray}
@@
 
- The quantitative study of the ridge is done with $\Delta\varphi$ distribution at a large $\Delta\eta$ to achieve direct comparison of ridges between different event classes and transverse momentum intervals.
-The large $\Delta\eta$ range can be selected as $1.6<|\Delta\eta|<1.8$ where non-flow effects (mainly coming from jets) are rarely accepted.
-In this region, jets are supposed not to contribute to the $\Delta\varphi$ distribution that is expressed as
+The ridge yields at large $\Delta\eta$ are extracted in different multiplicity classes and transverse momentum intervals.
+The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$ where non-flow effects (mainly coming from jets) are negligible.
+In this region, the per trigger yield is expressed as
 \begin{eqnarray}
@@
 Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to describe the shape to find the minimum to be used for integral of the yield.
-The associated yield of the ridge $Y^{\rm{assoc}}$ is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
+The associated yield $Y^{\rm{assoc}}$ (ridge yield is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
 \begin{eqnarray}
@@
 
-The ridge yield is measured with respect to the multiplicity classes.
-Multiplicity classes are defined by a probability range with respect to the minimum bias events, constituting 100\%.
-Percentile values are close to 0  for higher multiplicity while close to 100 for lower multiplicity collisions like the centrality classification in heavy-ion collisions~\cite{Abelev:2013qoq,ALICE-PUBLIC-2018-003}.
-Multiplicity classes are estimated by the V0 detector.The high multiplicity pp collisions in this analysis is defined as the top 0.1\% signal amplitude events measured by the V0 detector.
-The corresponding multiplicity class is called the 0--0.1\%.
-
-The ridge yield is further studied with respect to the magnitude of the hard process.
-Events with the hard process are selected by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the deep inelastic scattering of the initial partons.
-The leading track is selected within $|\Delta\eta|<0.9$ and the full azimuthal angle.
+The ridge yield is further studied with respect to, so called event scale.
+Usually event scale the momentum of the hard process.
+Events with the hard process are selected by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering.
+The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.
 Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$.
@@
 %Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. 
-Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlations function constructed by generated particles from the event generator.
+Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlation function constructed by generated particles from the event generator.
 The uncertainty of $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$ is summarized by averaging each uncertainty for given $\pttrig$ and $\ptassoc$.
@@
 The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
-The narrower primary vertex selection allows one to accept more forward tracks, which could be very sensitive to select the long-range side.
-The estimated uncertainty is increased up to 12\% from 1\%, which is obtained without the event scale selection.
+The narrower primary vertex selection allows one to test the acceptance effect on the measurement.
+The estimated uncertainty is increased up to 12\% from 1\%.
 The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
@@
 The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks, which is not largely affected by the event scale selection.
-The uncertainty from the long $\Delta\eta$ range is estimated by varying the $\Delta\eta$ range.
+The uncertainty from the $\Delta\eta$ projection range is estimated by varying the $\Delta\eta$ range.
 The uncertainty might include effects from the longitudinal de-correlations and possible non-flow contamination, which is thought be small.
 The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.
-The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2 to 1 cm. The estimated uncertainty is 1--16\%
+The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2 to 1 cm.
 

### 2020-06-17 sec_intro.tex
updates

@@
 
-Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta$--\Delta\varphi$ correlation functions, where $\eta$ is the pseudorapidity and $\varphi$ is the azimuthal angle.
+Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta$--$\Delta\varphi$ correlation functions, where $\eta$ is the pseudorapidity and $\varphi$ is the azimuthal angle.
 Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
@@
 In addition, we report the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
-
 The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, sequentially.
 The sources of systematic uncertainties are represented in Sec.~\ref{sec:uncertainties}.
-The results of the measurements are interpreted in Sec.~\ref{sec:results}.
-In Sec.~\ref{sec:theory} we report comparisons to model calculations.
+The results of the measurements and comparisons to model calculations are interpreted in Sec.~\ref{sec:results}.
 Finally, Sec.~\ref{sec:summary} summarizes our new results.

### 2020-06-17 sec_results.tex
updates

@@
 The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm{and}~\ptassoc < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
-The left figure shows the function for the 0--0.1\% multiplicity class.
-The right one shows the function for the minimum bias events (the 0--100\% multiplicity class).
-The ridge behaviour is clearly observed in the high multiplicity class compared to the function for the minimum-bias events.
+The left figure is for the 0--0.1\% multiplicity class.
+The right one is from the minimum bias events (0--100\% multiplicity class).
+The ridge structure is clearly observed in the high multiplicity class compared to the minimum-bias events while no observation of the ridge in the minimum bias events.
+The away side is dominantly constructed by correlation of back to back jet.
 
@@
 
-The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared with the CMS result~\cite{}.
+The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared with the CMS results~\cite{Khachatryan:2015lva}.
 The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
 Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity, the measurements are can be considered comparable with each other.
+Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity, the measurements are can be considered comparable with each other, which insists that measurements of azimuthal correlations can be achieved with ALICE.
 The spectrum is also compared with model predictions.
@@
 $\pythiam$ is shown with a black line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect.
-$\pythoashoving$ shown with a red line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
+$\pythiashoving$ shown with a red line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
 
@@
 	\caption{ The spectra of ridge yield as function of transverse momentum.
-The filled circles denote the measurement with ALICE and compared with CMS measurement \cite{ridge_pp_1}, which is represented as open box.
+The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open box.
 The two lines show model predictions from $\pythiam$ (black line) and $\pythiashoving$ (red line).

### 2020-06-17 sec_summary.tex
updates

--- 2020-06-09 sec_summary.tex
@@
 The spectrum of the ridge yield is measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
-The result is compared with CMS measurement and shown that the results are compatible.
+The results are compatible to the measurements from CMS experiment.
+One has to add more later about the different models.
 The PYTHIA8 string shoving quantitatively estimates the spectrum while PYTHIA8 default shows zero yield.
@@
 The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
-The results have been compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.
+The results are compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.

### 2020-06-18 sec_ana.tex
add refereces and update on ana

@@
 
-The ridge yield is further studied with respect to, so called event scale.
-Usually event scale the momentum of the hard process.
-Events with the hard process are selected by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering.
+The ridge yield is further studied by exploiting the momentum transfer between the interacting partons, so called, event scale.
+On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two protons~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+In this article, the event scales are set by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.

### 2020-06-18 sec_ana.tex
Updates from Overleaf

@@
 The uncertainty of $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$ is summarized by averaging the each uncertainty for a given $\ptlead$ and $\ptjet$ selection, respectively.
-\begin{table}[!h]
-\caption{ The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.
-}
+\begin{table}[h!]
 \centering
@@
 \end{tabular}
-
+\label{tab:syst}
+\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
 \end{table}

### 2020-06-19 sec_results.tex
Updates from Overleaf
updates

@@
 
- Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the high multiplicity class (0--0.1\%).
-The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$.
+ Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class(0--100\%) and the high multiplicity class (0--0.1\%).
+The near-side($\Delta\varphi\sim 0$) peak in the minimum bias class is rarely seen in the various transverse momentum range.
+The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class.
+The measurements in the high multiplicity class are compared with the CMS results.
+The near-side peak measured with CMS shows agreement with ALICE measurement, while showing higher yield in the away-side($\Delta\varphi\sim\pi$) peak.
+The model predictions are represented for the measurements in the high multiplicity class.
+The $\pythiashoving$ nicely estimates the near-side peak and overestimates the away-side yield fir the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$.
+The $\pythiashoving$ does not reproduce the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
+$\pythiam$ does not show any peaks in the near-side, which is expected.
+While not reproducing the near-side peak, $\pythiam$ estimates the away-side peak, which mainly come from the jet--balancing jet correlations.
+
  %The associated yield per trigger particle is compared with the CMS results.
@@
 Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
-}
+The model predictions are presented as colored lines.
+Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
 	\label{fig:PlotDeltaPhi}
@@
 $\pythiam$ and $\pythiashoving$ are used for the prediction.
-$\pythiam$ is shown with a black line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect.
-$\pythiashoving$ shown with a red line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
+$\pythiam$ is shown with a orange line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect.
+$\pythiashoving$ shown with a blue line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig1_RidgeYield.pdf} }
+	\subfigure{ \includegraphics[width=0.89\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
 	\caption{ The spectra of ridge yield as function of transverse momentum.
-The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open box.
-The two lines show model predictions from $\pythiam$ (black line) and $\pythiashoving$ (red line).
+The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
+The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line).
 }

### 2020-06-20 sec_results.tex
update on sec 5.2

@@
 
-To further observe the behavior of the ridge yield with respect to the hard process, the correlation function is measured with the minimum $\ptlead$ (left) or $\ptjet$ (right) thresholds for $1<\pttrigassoc<2$ GeV/$c$, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}.
-The ridge structures are still seen with the event scale selection.
-With the minimum $\ptjet$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.
+To further observe the behavior of the event scale dependent ridge yield, the correlation function is measured with the minimum $\ptlead$ (left) or $\ptjet$ (right) thresholds for $1<\pttrigassoc<2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection.
+In Fig.~\ref{fig:PlotCorrHMTSel}, The ridge structures are still seen with the event scale selection.
+With the minimum $\ptjet$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which come from the limited jet acceptance.
 
@@
 
-The one-dimensional $\Delta\varphi$ distribution with the minimum $\ptlead$ (left) or $\ptjet$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield increases as the event scale increases by requiring higher $\ptlead$ (left) or $\ptjet$.
-The model comparisons are are shown for $\pythiashoving$ with a blue and $\pythiam$ with a red line.
-The $\pythiashoving$ describes ridge yield with the selection.
-$\pythiam$ predicts non ridge yield with the selection, which also tell there is little ignore-able jet contamination.
+The one-dimensional $\Delta\varphi$ distribution with the minimum $\ptlead$(lower) or $\ptjet$(upper) is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
+The near-side yield increases as the event scale increases by requiring higher $\ptlead$ or $\ptjet$ from the unbiased events, which corresponds to the plot in the most left upper panel.
+The model comparisons are shown for $\pythiashoving$ with a blue and $\pythiam$ with a orange line.
+The $\pythiashoving$ qualitatively describes the near-side peak with the event scale selection.
+On the other hand, $\pythiam$ does not predicts the near-side peak with the event scale selection, which also tell there is ignorable jet contamination.
 Both models well describe the away-side yield with the $\ptjet$ selection and overestimates away-side yield with the $\ptlead$ selection.
@@
 
-The spectra of the ridge yield as function of the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-The spectra are compared with model predictions.
-The increases of ridge yield with the selections are observed and the model with PYTHIA8 + String Shoving underestimates the ridge yield.
-with the $\it{p}_{\rm{T, Jet}}$ selection.
-the model prediction with PYTHIA8 default still assures ignorable jet contamination.
+The spectra of the ridge yield as function of the minimum $\ptlead$(left) or$\ptjet$(right) selection are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The measured spectra show that the ridge yield increases with the increasing selection requirement.
+The spectra are compared with the model predictions.
+$\pythiashoving$ predict the ridge yield with the event scale selection.
+$\pythiashoving$ underestimates the ridge yield with the increasing event scale selection.
+$\pythiam$ does not predict the ridge yield estimating zero yield, which also imply the ignorable jet contamination into the ridge yield.
 
@@
 The filled circles show measurement with ALICE.
-Model predictions are compared with measurement as blue line for PYTHIA8 + String Shoving  and apricot line for PYTHIA8 default.}
+Model predictions are compared with measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
 	\label{fig:RidgeYield_ESE}

### 2020-06-22 sec_results.tex
sec5.2

--- 2020-06-19 sec_results.tex
@@
 Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the relative pseudorapidity ($\Delta \eta$) and azimuthal angle ($\Delta \varphi$) differences between the trigger and associated particles.
-The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm{and}~\ptassoc < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
-The left figure is for the 0--0.1\% multiplicity class.
+The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
+The left panel is for the 0--0.1\% multiplicity class.
 The right one is from the minimum bias events (0--100\% multiplicity class).
-The ridge structure is clearly observed in the high multiplicity class compared to the minimum-bias events while no observation of the ridge in the minimum bias events.
-The away side is dominantly constructed by correlation of back to back jet.
+The ridge structure is clearly observed in the high multiplicity class compared to the minimum-bias events while it is not seen in the minimum bias events.
+The away side is dominant from the correlation of back to back jet.
 
@@
  Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class(0--100\%) and the high multiplicity class (0--0.1\%).
-The near-side($\Delta\varphi\sim 0$) peak in the minimum bias class is rarely seen in the various transverse momentum range.
+The near-side($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all the transverse momentum ranges studied while there is no hint of signal in the minimum bias class.
 The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class.
-The measurements in the high multiplicity class are compared with the CMS results.
-The near-side peak measured with CMS shows agreement with ALICE measurement, while showing higher yield in the away-side($\Delta\varphi\sim\pi$) peak.
-The model predictions are represented for the measurements in the high multiplicity class.
-The $\pythiashoving$ nicely estimates the near-side peak and overestimates the away-side yield fir the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$.
-The $\pythiashoving$ does not reproduce the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
-$\pythiam$ does not show any peaks in the near-side, which is expected.
-While not reproducing the near-side peak, $\pythiam$ estimates the away-side peak, which mainly come from the jet--balancing jet correlations.
+The measurements in the high multiplicity class are compared with the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
+The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties.
+The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances.
+The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity.
+The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$.
+However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
+$\pythiam$ does not show any peaks in the near-side as expected and slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, which mainly come from the back to back jet correlations.
 
@@
 
-The spectra of the ridge yield are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared with the CMS results~\cite{Khachatryan:2015lva}.
-The estimator of particle multiplicity of ALICE is done with forward subsystem(V0), whereas that of CMS is done by mid-rapidity particles meeting with the condition of $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
-Dedicated comparison is conducted and the difference of particle multiplicity is estimated to be about 20\%.
-Taking into account the difference in acceptance of charged tracks and comparable definition of multiplicity, the measurements are can be considered comparable with each other, which insists that measurements of azimuthal correlations can be achieved with ALICE.
-The spectrum is also compared with model predictions.
-$\pythiam$ and $\pythiashoving$ are used for the prediction.
-$\pythiam$ is shown with a orange line and predicts no ridge effect in pp collisions, which is expected because the model does not implement any constraint to describe the ridge effect.
-$\pythiashoving$ shown with a blue line describes the effect better than $\pythiam$, however, its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
+The ridge yields as a function of  the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}.
+The particle multiplicity in this analysis is estimated with the forward subsystem(V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
+By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
+Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other.
+The spectrum is also compared with model calculations.
+$\pythiam$ gives zero yields since it does not contain the ridge effect.
+$\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
 
@@
 \subsection{Event scale dependent ridge yield}
-
-To further observe the behavior of the ridge yield with respect to the hard process, the correlation function is measured with the minimum $\ptlead$ (left) or $\ptjet$ (right) thresholds for $1<\pttrigassoc<2$ GeV/$c$, where the measured ridge yield is maximum in Fig.~\ref{fig:PlotCorrHMTSel}.
-The ridge structures are still seen with the event scale selection.
-With the minimum $\ptjet$ selection, the correlations function has a bump on the $\Delta\eta = 0$ and $\Delta\varphi = \pi$, which occurs due to the limited jet acceptance.
+The event scale dependent ridge yields are measured with the minimum $\ptlead=9.0$ (left) or $\ptjet=10.0$~ GeV/$c$ (right) thresholds for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection.
+In Fig.~\ref{fig:PlotCorrHMTSel}, The ridge structure still persist even with both selections.
+With the minimum $\ptjet$ selection, the correlations function has double peaks on the $\Delta\eta$ at $\Delta\varphi = \pi$ due to the requirement of the limited jet acceptance.
 
@@
 
-The one-dimensional $\Delta\varphi$ distribution with the minimum $\ptlead$ (left) or $\ptjet$ is shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield increases as the event scale increases by requiring higher $\ptlead$ (left) or $\ptjet$.
-The model comparisons are are shown for $\pythiashoving$ with a blue and $\pythiam$ with a red line.
-The $\pythiashoving$ describes ridge yield with the selection.
-$\pythiam$ predicts non ridge yield with the selection, which also tell there is little ignore-able jet contamination.
-Both models well describe the away-side yield with the $\ptjet$ selection and overestimates away-side yield with the $\ptlead$ selection.
+Projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$(lower) and $\ptjet$(upper) are shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
+The near-side yield increases as requiring higher $\ptlead$ or $\ptjet$ from the yield in unbiased events, which is shown in the upper left panel.
+The Model calculations by $\pythiashoving$ and $\pythiam$ are shown with a blue and a orange line, respectively.
+The $\pythiashoving$ gives qualitative agreement of the near-side peak with the event scale selections.
+On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections.
+Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1<\pttrigassoc<2$ GeV/\it{c}\rm{} in the 0--0.1\% multiplicity class.
+	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$ in the 0--0.1\% multiplicity class.
 The filled circles show measurement with ALICE.
@@
 
-The spectra of the ridge yield as function of the minimum $\it{p}_{\rm{T, Lead}}$(left) or $\it{p}_{\rm{T, Jet}}$(right) are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-The spectra are compared with model predictions.
-The increases of ridge yield with the selections are observed and the model with PYTHIA8 + String Shoving underestimates the ridge yield.
-with the $\it{p}_{\rm{T, Jet}}$ selection.
-the model prediction with PYTHIA8 default still assures ignorable jet contamination.
+The ridge yields as functions of the minimum $\ptlead$(left) and $\ptjet$(right) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The ridge yield increases with the increasing selection requirement.$\pythiashoving$ underestimates the ridge yield with the increasing event scale selection.
+$\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.
 

### 2020-06-23 sec_ana.tex
update on sec 5.2
adopted jasper's comment to Sec3

@@
 The V0 provides trigger and estimation of event multiplicity.
-A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring some thresholds on signal amplitudes of energy deposit by charged particles in the V0 detector.
+A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring 5 times of mean signal amplitudes of energy deposit by charged particles in the V0 detector.
 
@@
 The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
-The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}| < 10$~cm.
-The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.2~GeV/$c$ with a $\sim $75\% efficiency.
+The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}| < 8$~cm.
+The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with a $\sim $65\% efficiency.
+%https://arxiv.org/pdf/1910.14400.pdf
 
@@
 
-The yield of two-particle correlations between the trigger and associated particles are measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$)
+The two-particle correlations function between the trigger and associated particles are measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$)
 \begin{eqnarray}
@@
 where  $\pttrig$ and $\ptassoc$ are the transverse momenta of  the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, $N_\mathrm{pair}$ is the number of pairs of the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
-$S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is the yield of two-particle correlations in mixed events.
+$S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is in mixed events.
 The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
@@
 The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$ where non-flow effects (mainly coming from jets) are negligible.
-In this region, the per trigger yield is expressed as
+In this region, the $\Delta\varphi$ distribution, or the so called per-trigger yield is expressed as
 \begin{eqnarray}
@@
 Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to describe the shape to find the minimum to be used for integral of the yield.
-The associated yield $Y^{\rm{assoc}}$ (ridge yield is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
+The ridge yield ($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
 \begin{eqnarray}
@@
 On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two protons~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
-In this article, the event scales are set by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering.
+In this article, the event scales are set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.
@@
 
-Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT 3 is used to correct the acceptance and the efficiency of the ALICE detectors.
+Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT3~\cite{Brun:1994aa} is used to correct the acceptance and the efficiency of the ALICE detectors.
 
@@
 The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction.
-Each source is assumed uncorrelated.
+Each source is assumed to be uncorrelated.
 The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection.
@@
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks.
+The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ particles.
 
@@
 The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2 to 1 cm.
+The estimated uncertainty is increased up to 8-16\% from 1-2\%.
 

### 2020-06-23 sec_intro.tex
add refereces and update on ana
adopted jasper's comment to Sec3

@@
 Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-For most Monte Carlo (MC) event generators in pp collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\varphi$ $\approx$ $\pi$ ) jet correlations.
+For most Monte Carlo (MC) event generators in pp collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\varphi$ $\approx$ $\pi$) jet correlations.
 The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in the $\Delta\eta$--$\Delta\varphi$ plane.
@@
 % TODO more pA measurements
-The ridge structures in high-multiplicity pp and p--Pb events have been attributed to mechanisms like initial-state effects, such as gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo} forming along the longitudinal direction and final-state effects, such as parton-induced interactions~\cite{Arbuzov:2011yr}, and collective effects due to a hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+The ridge structures in high-multiplicity pp and p--Pb events have been attributed to mechanisms from initial-state effects or final-state effects.
+The initial-state effects are usually referred to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo} forming along the longitudinal direction.
+The final-state effects are explained by such as parton-induced interactions~\cite{Arbuzov:2011yr} or collective effects due to a hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
 Hybrid models implementing both effects are generally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
-The proton shape and its fluctuations are also important to model the small systems \cite{Mantysaari:2017cni}.
+The proton shape and its fluctuations are also important to model the small systems~\cite{Mantysaari:2017cni}.
 The hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty}. 
-The influence and interplay of initial state and final state effects are recently studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for the quantitative description of observables in small systems~\cite{Schenke:2019pmk}.
-The attempts to describe the collective effects systematically from the small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoritically~\cite{Greif:2019ygb}.
+The influence and interplay of the initial state and final state effects have recently been studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for the quantitative description of observables in small systems~\cite{Schenke:2019pmk}.
+The attempts to describe the collective effects systematically from small to large systems are being experimentally~\cite{Acharya:2019vdf} and theoritically~\cite{Greif:2019ygb} made.
 However, a quantitative description of the full set of experimental data has not been achieved yet.
-The summary of various explanations for the observed correlations in these small systems are summarized in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
+A summary of various explanations for the observed correlations in these small systems is given in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
 
-Furthermore, if collectivity in small systems is due to final state interactions, it is expected to measure its effect on jets.
+Furthermore, if collectivity in small systems is due to final state interactions, it is expected to have an effect on jets.
 Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high-multiplicity pp collisions.
-The most of observables for the jet quenching in pp and p--Pb collisions do not show any clear evidences so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
-The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity in the event~\cite{Adam:2016jfp,Acharya:2018egz}.
-
+Most of the observables for the jet quenching in pp and p--Pb collisions do not show any clear evidence so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
+The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}.
 %Small system studies: A theory overview 1807.07191 Strickland:2018exs
@@
 The ATLAS experiment recently showed that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
-The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in \cite{Frankfurt:2003td}.
-The microscopic model for collectivity, based on interacting string implemented in $\pythiae$ event generator so called the ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
+The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in~\cite{Frankfurt:2003td,Frankfurt:2010ea}.
+The microscopic model for collectivity, based on interacting string implemented in $\pythiae$ event generator as the so called the ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
 This challenges the hydrodynamic picture and predicts modifications to jet fragmentation
@@
 In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.
-The results are compared to previous measurements from CMS experiments.
-In addition, we report the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
+The results are compared to previous measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+In addition, we report the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of the long-range correlations.
 The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, sequentially.
-The sources of systematic uncertainties are represented in Sec.~\ref{sec:uncertainties}.
-The results of the measurements and comparisons to model calculations are interpreted in Sec.~\ref{sec:results}.
+The sources of systematic uncertainties are presented in Sec.~\ref{sec:uncertainties}.
+The results of the measurements and comparisons to model calculations are given in Sec.~\ref{sec:results}.
 Finally, Sec.~\ref{sec:summary} summarizes our new results.

### 2020-06-23 sec_results.tex
adopted jasper's comment to Sec3

@@
 \subsection{Ridge yield}
-
-Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the relative pseudorapidity ($\Delta \eta$) and azimuthal angle ($\Delta \varphi$) differences between the trigger and associated particles.
-The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
-The left panel is for the 0--0.1\% multiplicity class.
-The right one is from the minimum bias events (0--100\% multiplicity class).
-The ridge structure is clearly observed in the high multiplicity class compared to the minimum-bias events while it is not seen in the minimum bias events.
-The away side is dominant from the correlation of back to back jet.
 
@@
 
- Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class(0--100\%) and the high multiplicity class (0--0.1\%).
-The near-side($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all the transverse momentum ranges studied while there is no hint of signal in the minimum bias class.
+Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the $\Delta \eta$ and $\Delta \varphi$ between the trigger and associated particles.
+The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
+The left panel is for the 0--0.1\% multiplicity class.
+The right one is from the minimum bias events (0--100\% multiplicity class).
+The ridge structure is clearly observed in the high multiplicity class while it is not seen in the minimum bias events.
+The away side is dominant from the correlation of back to back jet.
+
+ %The associated yield per trigger particle is compared with the CMS results.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class.
+The distributions in upper panels are measured with 0--100\% multiplicity class.
+The distribution in lower panels are measured with 0-0.1\% multiplicity class.
+Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
+The model predictions are presented as colored lines.
+Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
+	\label{fig:PlotDeltaPhi}
+\end{figure}
+
+Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high multiplicity class (0--0.1\%).
+The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of signal in the minimum bias class.
 The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class.
@@
 
- %The associated yield per trigger particle is compared with the CMS results.
-
 \begin{figure}[h!]
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class.
-The distributions in upper panels are measured with 0--100\% multiplicity class.
-The distribution in lower panels are measured with 0-0.1\% multiplicity class.
-Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
-The model predictions are presented as colored lines.
-Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
-	\label{fig:PlotDeltaPhi}
+	\subfigure{ \includegraphics[width=0.90\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
+	\caption{ The spectra of ridge yield as function of transverse momentum.
+The filled circles denote the measurement with ALICE and compared with the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
+The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line).
+}
+	\label{fig:PlotYSpect}
 \end{figure}
@@
 The ridge yields as a function of  the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}.
-The particle multiplicity in this analysis is estimated with the forward subsystem(V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
+The particle multiplicity in this analysis is estimated with the forward subsystem (V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
 By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
@@
 
-\begin{figure}[h!]
-	\centering
-	\subfigure{ \includegraphics[width=0.89\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
-	\caption{ The spectra of ridge yield as function of transverse momentum.
-The filled circles denote the measurement with ALICE and compared with CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
-The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line).
-}
-	\label{fig:PlotYSpect}
-\end{figure}
-
 \subsection{Event scale dependent ridge yield}
-The event scale dependent ridge yields are measured with the minimum $\ptlead=9.0$ (left) or $\ptjet=10.0$~ GeV/$c$ (right) thresholds for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection.
-In Fig.~\ref{fig:PlotCorrHMTSel}, The ridge structure still persist even with both selections.
-With the minimum $\ptjet$ selection, the correlations function has double peaks on the $\Delta\eta$ at $\Delta\varphi = \pi$ due to the requirement of the limited jet acceptance.
-
 \begin{figure}[h!]
@@
 
-Projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$(lower) and $\ptjet$(upper) are shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield increases as requiring higher $\ptlead$ or $\ptjet$ from the yield in unbiased events, which is shown in the upper left panel.
-The Model calculations by $\pythiashoving$ and $\pythiam$ are shown with a blue and a orange line, respectively.
-The $\pythiashoving$ gives qualitative agreement of the near-side peak with the event scale selections.
-On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections.
-Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
+Two-particle correlation functions as functions of the $\Delta \eta$ and $\Delta \varphi$ is also studied with two different event selections.
+As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure still persist with the minimum $\ptlead=9.0$ (left) or $\ptjet=10.0$~ GeV/$c$ (right) thresholds for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection.
+With the minimum $\ptjet$ selection, the correlations function has double peaks on the $\Delta\eta$ at $\Delta\varphi = \pi$ due to the requirement of the limited jet acceptance.
 
@@
 
-The ridge yields as functions of the minimum $\ptlead$(left) and $\ptjet$(right) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-The ridge yield increases with the increasing selection requirement.$\pythiashoving$ underestimates the ridge yield with the increasing event scale selection.
-$\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.
+Projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) are shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
+The near-side yield increases for higher $\ptlead$ or $\ptjet$ requirement compared to the yield in unbiased events.
+The results are compared to
+$\pythiashoving$ and $\pythiam$ calculations.
+The $\pythiashoving$ gives qualitative agreement of the near-side peak with the event scale selections.
+On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections.
+Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
 
@@
 \end{figure}
+
+Finally, the ridge yields as functions of the minimum $\ptlead$ (left) and $\ptjet$ (right) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The ridge yield increases with increasing selection requirement.
+$\pythiashoving$ underestimates the ridge yield with the increasing event scale selection.
+$\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.

### 2020-06-23 sec_summary.tex
adopted jasper's comment to Sec3

--- 2020-06-09 sec_summary.tex
@@
 \label{sec:summary}
-
-The $p_{\mathrm T}$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV at the Large Hadron Collider.
-The spectrum of the ridge yield is measured in the relative pseudorapidity range $1.6 < |\eta| < 1.8$ for the transverse momentum range $1.0 < p_{\mathrm T} < 5.0$~GeV/$c$ and 0--0.1\% multiplicity event class.
-The result is compared with CMS measurement and shown that the results are compatible.
-The PYTHIA8 string shoving quantitatively estimates the spectrum while PYTHIA8 default shows zero yield.
-Further understandings of the correlations in small system are attempted by studying the ridge yield in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
-The ridge yield spectrum with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$.) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
-The results have been compared with PYTHIA8 string shoving calculation, showing the enhancement while underestimating the absolute ridge yield.
+Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV at the Large Hadron Collider.
+These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class.
+The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+%In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
+PYTHIA8 string shoving quantitatively estimates the spectrum while $\pythiam$ shows zero yield.
+Further the ridge yields are studied in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
+The ridge structure still persist with both selections.
+The ridge yield with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
+The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.

### 2020-06-23 sec_summary.tex
Updates from Overleaf

@@
 \label{sec:summary}
-Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV at the Large Hadron Collider.
+Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV .
 These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class.
@@
 %In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
-PYTHIA8 string shoving quantitatively estimates the spectrum while $\pythiam$ shows zero yield.
-Further the ridge yields are studied in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
+$\pythiashoving$ describes the yield qualitatively but its yield gets decreased more rapidly than the data as $\pttrigassoc$ increases.
+Furthermore the ridge yields are studied in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
 The ridge structure still persist with both selections.
-The ridge yield with hard fragmentations($p_{\mathrm T, jet} > 10$~GeV/$c$) has shown the enhancement as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
+The ridge yield for the events for $\it{p}_{\rm{T,jet}} > 10$~GeV/$c$ and $\it{p}_{\rm{T,Lead}} > 9$~GeV/$c$ is enhanced as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
+The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-06-24 sec_ana.tex
for PC meeting, ready for IRC

@@
 The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}| < 8$~cm.
-The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with a $\sim $65\% efficiency.
+The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
 %https://arxiv.org/pdf/1910.14400.pdf
@@
 
-The ridge yield is further studied by exploiting the momentum transfer between the interacting partons, so called, event scale.
-On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two protons~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
-In this article, the event scales are set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering.
+The ridge yield is further studied by exploiting the largest momentum transfer between the initial partons in a given event, which results from the hard scattering.
+In this article, larger momentum transfer denotes harder event scale.
+The larger momentum transfer is also expected to be connected with the shorter impact parameters in pp collisions in average~\cite{Sjostrand:1986ep,Frankfurt:2010ea} so that the event scale can be indirectly connected with the impact parameters.
+% The ridge yield is further studied by exploiting the momentum transfer between the interacting partons,so called, event scale.
+On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
+The event scales are set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since hard scattering produces leading tracks with a high $p_\mathrm{T}$ or jets.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.

### 2020-06-24 sec_intro.tex
for PC meeting, ready for IRC

@@
 The influence and interplay of the initial state and final state effects have recently been studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for the quantitative description of observables in small systems~\cite{Schenke:2019pmk}.
-The attempts to describe the collective effects systematically from small to large systems are being experimentally~\cite{Acharya:2019vdf} and theoritically~\cite{Greif:2019ygb} made.
+The attempts to describe the collective effects systematically from small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Greif:2019ygb}.
 However, a quantitative description of the full set of experimental data has not been achieved yet.
@@
 
-Furthermore, if collectivity in small systems is due to final state interactions, it is expected to have an effect on jets.
+Furthermore, if collectivity in small systems is due to final-state interactions, it is expected to have an effect on jets.
 Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high-multiplicity pp collisions.
@@
 The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in~\cite{Frankfurt:2003td,Frankfurt:2010ea}.
-The microscopic model for collectivity, based on interacting string implemented in $\pythiae$ event generator as the so called the ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
+The microscopic model for collectivity, based on interacting string implemented in $\pythiae$ event generator as so-called the ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
 This challenges the hydrodynamic picture and predicts modifications to jet fragmentation

### 2020-06-24 sec_results.tex
Updates from Overleaf
for PC meeting, ready for IRC

@@
 
-\subsection{Event scale dependent ridge yield}
+\subsection{Event-scale dependence of the ridge yield}
 \begin{figure}[h!]
@@
 The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$.
-The minimum requirement for $\ptlead$ or $\ptjet$ is 9 and 10 GeV/$c$, respectively.
+The minimum requirement for $\ptlead$ or $\ptjet$ is 9 or 10 GeV/$c$, respectively.
 }
@@
 
-Two-particle correlation functions as functions of the $\Delta \eta$ and $\Delta \varphi$ is also studied with two different event selections.
-As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure still persist with the minimum $\ptlead=9.0$ (left) or $\ptjet=10.0$~ GeV/$c$ (right) thresholds for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$, where the measured ridge yield is maximum without event scale selection.
-With the minimum $\ptjet$ selection, the correlations function has double peaks on the $\Delta\eta$ at $\Delta\varphi = \pi$ due to the requirement of the limited jet acceptance.
+The ridge yield is also studied with respect to two different event scales of the hard processes.
+Event-scale measurement by the largest $\pt$ of particles in each event that is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$.
+As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high multiplicity pp collisions with $\ptlead>9$ (left) or $\ptjet>10$~GeV/$c$ (right) .
+%The interval is the same to the measured ridge yield is maximum without the event-scale selection.
+It is worth noting that the correlation function with the minimum $\ptjet$ selection has double peaks along the $\Delta\eta$ axis at $\Delta\varphi = \pi$ due to the limited jet acceptance by requiring a minimum $\ptjet$.
 
@@
 
-Projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) are shown in Fig.~\ref{fig:PlotDeltaPhiESE}.
-The near-side yield increases for higher $\ptlead$ or $\ptjet$ requirement compared to the yield in unbiased events.
+Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper).
+The near-side yield increases as the threshold of $\ptjet$ increases compared to one in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
+The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum.
+In contrast, soft jets are favored for reconstructed jets.
 The results are compared to
 $\pythiashoving$ and $\pythiam$ calculations.
-The $\pythiashoving$ gives qualitative agreement of the near-side peak with the event scale selections.
+$\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event scale selections.
 On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections.
@@
 
-Finally, the ridge yields as functions of the minimum $\ptlead$ (left) and $\ptjet$ (right) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-The ridge yield increases with increasing selection requirement.
-$\pythiashoving$ underestimates the ridge yield with the increasing event scale selection.
+Finally, the ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{Lead}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The ridge yield increases with increasing $\it{p}^{\rm{Lead}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$.
+$\pythiashoving$ underestimates the ridge yield with the increasing $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$, still holding presence of the ridge.
 $\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.

### 2020-06-24 sec_summary.tex
for PC meeting, ready for IRC

@@
 Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV .
-These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class.
+These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class.
 The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
@@
 $\pythiashoving$ describes the yield qualitatively but its yield gets decreased more rapidly than the data as $\pttrigassoc$ increases.
-Furthermore the ridge yields are studied in events, where jets with harder fragmentations is to be present by requiring the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$.
+Furthermore the ridge yields are studied in events, where jets with a harder fragmentation is preferred by requiring the minimum value of  the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
 The ridge structure still persist with both selections.
-The ridge yield for the events for $\it{p}_{\rm{T,jet}} > 10$~GeV/$c$ and $\it{p}_{\rm{T,Lead}} > 9$~GeV/$c$ is enhanced as the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ increases.
+The ridge yields increase as $\ptlead$ and $\ptjet$ increase, respectively.
+The latter, however, is significant than the former selection.
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.

### 2020-06-26 paper.tex
adopted jasper's comment to Sec3
final version to IRC first round

@@
 
-Long-range azimuthal correlations are measured in very high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
+Long-range azimuthal correlations are measured in high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
 These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles.
@@
 These correlations also persist in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
-The results are compared to $\pythiashoving$, EPOS and A Multi-Phase Transport ({AMPT}) model calculations.  
+The results are compared to $\pythiashoving$ calculations.  
 $\pythiashoving$ model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of $p_{\mathrm T}$ dependence both for the unbiased and jet events.

### 2020-06-26 sec_ana.tex
final version to IRC first round

@@
 The full description of ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
-The present analysis mainly utilizes V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
+The present analysis mainly utilizes the V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
 
@@
 The high multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
-Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events~\cite{}.
+Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
 Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
@@
 
-The ridge yield is further studied by exploiting the largest momentum transfer between the initial partons in a given event, which results from the hard scattering.
+The ridge yield is further studied by exploiting the largest momentum transfer among the initial partons in a given event, which results from the hard scattering.
 In this article, larger momentum transfer denotes harder event scale.
@@
 \begin{table}[h!]
+\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
 \centering
@@
          & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
-Pileup cut			& $\sim$0.8	&0--4		&0--4		\\ \hline
+Pileup rejection		& $\sim$0.8	&0--4		&0--4		\\ \hline
 Primary Vertex		& $\sim$2.4	&1--12	&1-8		\\ \hline
@@
 \label{tab:syst}
-\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
 \end{table}

### 2020-06-26 sec_results.tex
final version to IRC first round

@@
 
- %The associated yield per trigger particle is compared with the CMS results.
-
 \begin{figure}[h!]
@@
 The distributions in upper panels are measured with 0--100\% multiplicity class.
-The distribution in lower panels are measured with 0-0.1\% multiplicity class.
+The distribution in lower panels are measured with 0--0.1\% multiplicity class.
 Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
 The model predictions are presented as colored lines.
-Blue line corresponds to the $\pythiashoving$ and orange line corresponds to the $\pythiam$}
+Blue line corresponds to $\pythiashoving$ and orange line corresponds to $\pythiam$}
 	\label{fig:PlotDeltaPhi}
@@
 The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class.
-The measurements in the high multiplicity class are compared with the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
+The measurements in the high multiplicity class are compared to the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
 The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties.
@@
 The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity.
+The high multiplicity class for each model is determined by requiring the minimum number of charged particles are larger than 105, which is corresponding to the top 0--0.1\% multiplicity class based on $\pythiam$.
 The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$.
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.90\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
+	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
 	\caption{ The spectra of ridge yield as function of transverse momentum.
-The filled circles denote the measurement with ALICE and compared with the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
+The filled circles denote the measurement with ALICE and compared to the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
 The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line).
@@
 $\pythiam$ gives zero yields since it does not contain the ridge effect.
-$\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the data as $\pttrigassoc$ increases.
+$\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the experimental measurement as $\pttrigassoc$ increases.
 
@@
 
-The ridge yield is also studied with respect to two different event scales of the hard processes.
+The ridge yield is further studied with respect to two different event scales of the hard processes.
 Event-scale measurement by the largest $\pt$ of particles in each event that is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$.
@@
 Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper).
+Even with the event scale selection, the ridge is still visible in near-side.
 The near-side yield increases as the threshold of $\ptjet$ increases compared to one in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
@@
 In contrast, soft jets are favored for reconstructed jets.
-The results are compared to
-$\pythiashoving$ and $\pythiam$ calculations.
+The results are compared with $\pythiashoving$ and $\pythiam$ calculations.
 $\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event scale selections.
@@
 The filled circles show measurement with ALICE.
-Model predictions are compared with measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
+Model predictions are compared to measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
 	\label{fig:RidgeYield_ESE}
@@
 
-Finally, the ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{Lead}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-The ridge yield increases with increasing $\it{p}^{\rm{Lead}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$.
-$\pythiashoving$ underestimates the ridge yield with the increasing $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$, still holding presence of the ridge.
+Finally, the ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The ridge yields are increased for $\it{p}^{\rm{LP}}_{\rm{T,min}} >$ 7 and $\it{p}^{\rm{Jet}}_{\rm{T,min}} \ge$ 10~GeV/$c$ compared to one from the unbiased events.
+A moderate increase of the ridge yields toward higher $\ptlead$ or $\ptjet$ is observed and there is no difference between two event selections within the uncertainties.
+The results are compared with $\pythiashoving$ and $\pythiam$.
+$\pythiashoving$ doesn't show a clear $\it{p}^{\rm{LP}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$ dependence within the errors and underestimates the yields especially for the jet tagged events.
 $\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.
+The origin of the enhanced ridge yields for higher momentum jet tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.

### 2020-06-26 sec_summary.tex
final version to IRC first round

@@
 \label{sec:summary}
-Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV .
-These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles and 0--0.1\% multiplicity event class.
+Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV.
+These results are obtained in a relative pseudorapidity range $1.6 < |\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles.
 The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
 %In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
-$\pythiashoving$ describes the yield qualitatively but its yield gets decreased more rapidly than the data as $\pttrigassoc$ increases.
+$\pythiashoving$ describes the yield qualitatively but its yield is decreased more rapidly than the data as $\pttrigassoc$ increases.
+On the other hand, $\pythiam$ does not describe ridge in the long-range as expected.
+The results from $\pythiam$ also assure that the measured ridge yield is not contaminated by non-flow effects.
 Furthermore the ridge yields are studied in events, where jets with a harder fragmentation is preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
 The ridge structure still persist with both selections.
-The ridge yields increase as $\ptlead$ and $\ptjet$ increase, respectively.
-The latter, however, is significant than the former selection.
+The ridge yields increase as $\ptlead$ and $\ptjet$ increase.
+The latter, however, is more significant than the former selection.
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
-The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
+The results might open new way of studying impact parameter dependence of the small systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-06-27 sec_intro.tex
Updates from Overleaf

@@
 The recent efforts are focused on constraining the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
-In recent years similar collective behaviors via long-range azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced by such a system are expected to be small.
+In recent years similar collective behaviors via long-range azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
 

### 2020-08-10 paper.tex
First actions after IRC's comments

@@
 %%% Put your own title + short title here:
-\title{Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
+\title{Long-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
 \ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
@@
 
-Long-range azimuthal correlations are measured in high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at LHC. 
-These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of $1 < p_{\mathrm T} < 5$~GeV/$c$ for the trigger and associated particles.
-In addition to the conventional long-range correlation studies, the results are further investigated in events, where jets with a harder fragmentation are present.
+Long-range azimuthal correlations are measured in high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at the LHC.
+The measurement was carried out for trigger and associated particles having transverse momenta in the range $1 < p_{\mathrm T} < 5$~GeV/$c$.
+Trigger and associated particles were separated by a large pseudorapidity interval $1.6 < |\Delta \eta |<1.8$.
+%These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of  for the trigger and associated particles.
+In addition to the conventional long-range correlation studies, the results are further investigated in events with a high-pT leading track or jet.
+%where jets with a harder fragmentation are present.
 The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
-The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events. 
-These correlations also persist in the events containing jets. Furthermore data show that the ridge yields tend to increase in events holding $\ptjet > 10$~GeV/$c$.
+%The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events.
+Measured ridge yield is consistent with the results from the CMS experiments for unbiased high-multiplicity events.
+These long-range correlations are also seen in the events containing jets.
+Furthermore, data show that the ridge yields tend to grow with transverse momentum of the jet or leading track.
+%increase in events holding $\ptjet > 10$~GeV/$c$.
 The results are compared to $\pythiashoving$ calculations.  
-$\pythiashoving$ model can describe low $p_{\mathrm T}$  ridge yields but can't give good description of $p_{\mathrm T}$ dependence both for the unbiased and jet events.
+$\pythiashoving$ model can describe low $p_{\mathrm T}$ ridge yields up to 1.5 GeV/$c$ but can not give good description of $p_{\mathrm T}$ dependence both for the unbiased and jet-tagged events.
 The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-08-10 sec_ana.tex
First actions after IRC's comments

@@
 %Recent center-of-mass energy in pp collisions reaches up to $\sqrt{s} = 13$~TeV during the last LHC Run 2 period. 
-The analysis is based on the data sets in pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 in the LHC Run 2 period.
-The full description of ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
-The present analysis mainly utilizes the V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS} and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
+The analysis is based on the data sets of pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 during the LHC Run 2 period.
+The full description of the ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
+The present analysis mainly utilizes the V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS}, and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
 
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
+The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
 The V0 provides trigger and estimation of event multiplicity.
-A sample of events including higher numbers of produced particles is obtained with a high multiplicity trigger, which is achieved by requiring 5 times of mean signal amplitudes of energy deposit by charged particles in the V0 detector.
+A sample of events including higher numbers of produced particles is obtained with a high-multiplicity trigger, which is achieved by requiring 5 times of mean signal amplitudes of energy deposit by charged particles in the V0 detector.
 
@@
 %The multiplicity class is classified by the signal amplitude of the V0 detector.
-The high multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
+The high-multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
 Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
-Statistics of the high multiplicity event benefits from a dedicated high multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
+Statistics of the high-multiplicity event benefits from a dedicated high-multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
 
@@
 
-The two-particle correlations function between the trigger and associated particles are measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$)
+The two-particle correlations function is measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$) between the trigger and associated particles.
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}\quad,
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)} \lvert_{\pttrig,\ptassoc}  ,
 \label{eq:corrfunction}
 \end{eqnarray}
-where  $\pttrig$ and $\ptassoc$ are the transverse momenta of  the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, $N_\mathrm{pair}$ is the number of pairs of the trigger and associated particles, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
+where  $\pttrig$ and $\ptassoc$ are transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, $N_\mathrm{pair}$ is the number of trigger-associated particle pairs, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
 $S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is in mixed events.
@@
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{|\Delta \eta|>1.6} \rm{d} \Delta \eta \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \rm{d} \Delta \eta \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \quad.
 \end{eqnarray}
@@
 The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
-The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi$ ($\Delta\varphi_{\rm{min}}$) in the $\Delta\varphi$ distribution is obtained from the function, which fits the $\Delta\varphi$ distribution with Fourier series up to the third harmonic.
-Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero in order to describe the shape to find the minimum to be used for integral of the yield.
+The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi$=$\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ distribution is obtained from the function, which fits the $\Delta\varphi$ distribution with a Fourier series up to the third harmonic.
+Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero.
 The ridge yield ($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
@@
 
-The ridge yield is further studied by exploiting the largest momentum transfer among the initial partons in a given event, which results from the hard scattering.
-In this article, larger momentum transfer denotes harder event scale.
-The larger momentum transfer is also expected to be connected with the shorter impact parameters in pp collisions in average~\cite{Sjostrand:1986ep,Frankfurt:2010ea} so that the event scale can be indirectly connected with the impact parameters.
+The ridge yield is further studied in events having a hard jet or a high-pT leading particle in the ALICE central barrel.
+Such requirement is expected to bias impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+%The ridge yield is further studied by exploiting the largest momentum transfer among the initial partons in a given event, which results from the hard scattering.
+In this article, larger momentum transfer denotes harder event-scale.
+The larger momentum transfer is also expected to be connected with the shorter impact parameters in pp collisions in average~\cite{Sjostrand:1986ep,Frankfurt:2010ea} so that the event-scale can be indirectly connected with the impact parameters.
 % The ridge yield is further studied by exploiting the momentum transfer between the interacting partons,so called, event scale.
 On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
-The event scales are set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since hard scattering produces leading tracks with a high $p_\mathrm{T}$ or jets.
+The event-scale is set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since hard scattering produces leading tracks with a high $p_\mathrm{T}$ or jets.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.
-Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$.
+Jets are reconstructed with charged particles only (charged jets) with the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$.
 Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
@@
 
-\section{Systematic Uncertainty}
+\section{Systematic Uncertainties of the Measured Yields}
 \label{sec:uncertainties}
-The systematic uncertainty is evaluated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction.
+Systematic uncertainties were estimated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction.
 Each source is assumed to be uncorrelated.
@@
 The uncertainty from the ZYAM procedure is estimated by varying the finding-scope for minimum position.
-The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks, which is not largely affected by the event scale selection.
+The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks, which is not largely affected by the event-scale selection.
 The uncertainty from the $\Delta\eta$ projection range is estimated by varying the $\Delta\eta$ range.

### 2020-08-10 sec_intro.tex
First actions after IRC's comments

--- 2020-06-24 sec_intro.tex
@@
 The recent efforts are focused on constraining the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
-In recent years similar collective behaviors via long-range azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, revealing strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced by such a system are expected to be small.
+In recent years similar collective behaviors via long-range azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, % strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
+The observed long-range azimuthal correlations suggest flow with hydrodynamic characteristics even in these small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
 
-Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta$--$\Delta\varphi$ correlation functions, where $\eta$ is the pseudorapidity and $\varphi$ is the azimuthal angle.
+Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta$--$\Delta\varphi$ correlation functions, where $\Delta\eta$ is the relative pseudorapidity and $\Delta\varphi$ is the azimuthal angle separation between both particles.
 Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-For most Monte Carlo (MC) event generators in pp collisions, the typical sources of such long-range correlations are momentum conservation and away-side ($\Delta\varphi$ $\approx$ $\pi$) jet correlations.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its shape in the $\Delta\eta$--$\Delta\varphi$ plane.
+For most pp Monte Carlo (MC) event generators, the typical sources of such long-range correlations are momentum conservation.
+%and away-side ($\Delta\varphi$ $\approx$ $\pi$) jet correlations.
+The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its characteristic shape in the $\Delta\eta$--$\Delta\varphi$ plane.
 The shape of these $\Delta\varphi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
-The second and third order terms are the dominant harmonic coefficients $v_n$.
-The $v_n$ coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to the transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
+The second and third order terms are the dominant harmonic coefficients.
+In heavy-ion collisions harmonic coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
 
 % TODO more pA measurements
-The ridge structures in high-multiplicity pp and p--Pb events have been attributed to mechanisms from initial-state effects or final-state effects.
-The initial-state effects are usually referred to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo} forming along the longitudinal direction.
-The final-state effects are explained by such as parton-induced interactions~\cite{Arbuzov:2011yr} or collective effects due to a hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+The ridge structures in high-multiplicity pp and p--Pb events have been attributed to initial-state effects or final-state effects.
+The initial-state effects are usually referred to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo}, which are formed along the longitudinal direction.
+The final-state effects may contribute via parton-induced interactions~\cite{Arbuzov:2011yr} or collective effects due to a hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
 Hybrid models implementing both effects are generally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
 The proton shape and its fluctuations are also important to model the small systems~\cite{Mantysaari:2017cni}.
-The hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty}. 
-The influence and interplay of the initial state and final state effects have recently been studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for the quantitative description of observables in small systems~\cite{Schenke:2019pmk}.
-The attempts to describe the collective effects systematically from small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Greif:2019ygb}.
+Nevertheless, the hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty}. 
+The influence and interplay of the initial state and final state effects have recently been studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for quantitative description of measurements in small systems~\cite{Schenke:2019pmk}.
+Attempts to describe the collective effects systematically from small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Greif:2019ygb}.
 However, a quantitative description of the full set of experimental data has not been achieved yet.
@@
 Furthermore, if collectivity in small systems is due to final-state interactions, it is expected to have an effect on jets.
-Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the final-state effect in high-multiplicity pp collisions.
+Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the QGP in high-multiplicity pp collisions.
 Most of the observables for the jet quenching in pp and p--Pb collisions do not show any clear evidence so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
-The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}.
+The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high-multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}.
 %Small system studies: A theory overview 1807.07191 Strickland:2018exs
@@
 
-To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during the LHC Run 2 data taking period.
+To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high-multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high-multiplicity event trigger during the LHC Run 2 data taking period.
 In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.
 The results are compared to previous measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
-In addition, we report the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of the long-range correlations.
-The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, sequentially.
+In addition, we report the ridge yield in events, where a hard scattering took place, to explore possible physical origins of the long-range correlations.
+The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, respectively.
 The sources of systematic uncertainties are presented in Sec.~\ref{sec:uncertainties}.
 The results of the measurements and comparisons to model calculations are given in Sec.~\ref{sec:results}.
-Finally, Sec.~\ref{sec:summary} summarizes our new results.
+Finally, Sec.~\ref{sec:summary} summarizes the obtained results.
 

### 2020-08-10 sec_results.tex
Updates from Overleaf
First actions after IRC's comments

@@
 	\centering
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
-	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right).
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.eps} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.eps} }
+	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high-multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right).
 The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < 2$ GeV/$c$.
@@
 
-Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as functions of the $\Delta \eta$ and $\Delta \varphi$ between the trigger and associated particles.
-The functions are measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
+Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as a function of the $\Delta \eta$ and $\Delta \varphi$ separation of trigger and associated particles.
+The per trigger yield iss measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
 The left panel is for the 0--0.1\% multiplicity class.
 The right one is from the minimum bias events (0--100\% multiplicity class).
-The ridge structure is clearly observed in the high multiplicity class while it is not seen in the minimum bias events.
-The away side is dominant from the correlation of back to back jet.
+The ridge structure is clearly observed in the high-multiplicity class while it is not seen in the minimum bias events.
+The away-side yield is populated mostly by correlation of jets which are back-to-back.
 
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with various transverse momentum intervals in each multiplicity class.
+	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.eps}
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for various transverse momentum intervals in each multiplicity class.
 The distributions in upper panels are measured with 0--100\% multiplicity class.
 The distribution in lower panels are measured with 0--0.1\% multiplicity class.
-Interval of transverse momentum of trigger particle and associated particle is $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
+Transverse momentum ranges of trigger particle and associated particle are $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
 The model predictions are presented as colored lines.
@@
 
-Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high multiplicity class (0--0.1\%).
-The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of signal in the minimum bias class.
-The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high multiplicity class.
-The measurements in the high multiplicity class are compared to the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
-The near-side peaks in all transverse momentum ranges are comparable each other within the uncertainties.
+Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high-multiplicity class (0--0.1\%).
+The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
+The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high-multiplicity class.
+The measurements in the high-multiplicity class are compared to the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
+The near-side peaks in all transverse momentum ranges are comparable to each other within the uncertainties.
 The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances.
-The model predictions are presented for the measurements in the high multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity.
-The high multiplicity class for each model is determined by requiring the minimum number of charged particles are larger than 105, which is corresponding to the top 0--0.1\% multiplicity class based on $\pythiam$.
+The model predictions are presented for the measurements in the high-multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity.
+The high-multiplicity class for each model is determined by requiring the minimum number of charged particles larger than 105, which corresponds to the top 0--0.1\% multiplicity class based on $\pythiam$.
 The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$.
 However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
-$\pythiam$ does not show any peaks in the near-side as expected and slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, which mainly come from the back to back jet correlations.
+$\pythiam$ does not show any peaks in the near-side as expected.
+It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.pdf} }
+	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.eps} }
 	\caption{ The spectra of ridge yield as function of transverse momentum.
@@
 
-The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high multiplicity class and compared to \cite{Khachatryan:2015lva}.
-The particle multiplicity in this analysis is estimated with the forward subsystem (V0), whereas that in \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
+Fig.~\ref{fig:PlotYSpect} shows the near-side ridge yield measured in high-multiplicity events as a function of transverse momentum. The ALICE data are compared to \cite{Khachatryan:2015lva}.
+%The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high-multiplicity class and compared to \cite{Khachatryan:2015lva}.
+The particle multiplicity in our analysis is estimated with the forward V0 subsystem, whereas whereas the analysis \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
 By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
@@
 $\pythiam$ gives zero yields since it does not contain the ridge effect.
-$\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the experimental measurement as $\pttrigassoc$ increases.
+$\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the measured data as $\pttrigassoc$ increases.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.pdf} }
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
-	\caption{ Two-dimensional correlations function as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection.
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.eps} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.eps} }
+	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection.
 The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$.
@@
 
-The ridge yield is further studied with respect to two different event scales of the hard processes.
-Event-scale measurement by the largest $\pt$ of particles in each event that is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$.
-As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high multiplicity pp collisions with $\ptlead>9$ (left) or $\ptjet>10$~GeV/$c$ (right) .
+The ridge yield is further studied with respect to two different event-scales of the hard processes.
+Event-scale measurement by the largest $\pt$ of charged particles in each event is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$.
+As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$ (left) or $\ptjet>10$~GeV/$c$ (right) .
 %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
+	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.eps}
 	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$ in the 0--0.1\% multiplicity class.
-The filled circles show measurement with ALICE.
-Model predictions are compared with measurement with a blue line for $\pythiashoving$  and a orange line for $\pythiam$.}
+The filled circles show the ALICE measurement.
+Model predictions are presented with a blue line for $\pythiashoving$  and an orange line for $\pythiam$.}
 	\label{fig:PlotDeltaPhiESE}
@@
 
-Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper).
-Even with the event scale selection, the ridge is still visible in near-side.
-The near-side yield increases as the threshold of $\ptjet$ increases compared to one in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
+Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ for the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement.
+Even with the event-scale selection, the ridge is still visible at the near-side.
+The near-side yield increases as the threshold of $\ptjet$ increases compared to one measured in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
 The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum.
@@
 The results are compared with $\pythiashoving$ and $\pythiam$ calculations.
-$\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event scale selections.
-On the other hand, $\pythiam$ does not show the near-side peak with the event scale selections.
+$\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event-scale selections.
+On the other hand, $\pythiam$ does not show the near-side peak with the event-scale selections.
 Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
+	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.eps}
 	\caption{The ridge yield spectra with respect to the leading particle and jet selections.
@@
 $\pythiashoving$ doesn't show a clear $\it{p}^{\rm{LP}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$ dependence within the errors and underestimates the yields especially for the jet tagged events.
-$\pythiam$ does not produce the ridge yield, estimating zero yield, which imply the negligible jet contamination in the measurements.
-The origin of the enhanced ridge yields for higher momentum jet tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
+$\pythiam$ does not produce the ridge yield, estimating zero yield, which implies negligible jet contamination in the measurements.
+The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.

### 2020-08-10 sec_summary.tex
First actions after IRC's comments

@@
 Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV.
-These results are obtained in a relative pseudorapidity range $1.6 < |\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles.
+These results are obtained in the relative pseudorapidity range $1.6 < |\Delta\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles.
 The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
@@
 $\pythiashoving$ describes the yield qualitatively but its yield is decreased more rapidly than the data as $\pttrigassoc$ increases.
-On the other hand, $\pythiam$ does not describe ridge in the long-range as expected.
+On the other hand, $\pythiam$ does not describe the ridge in the long-range as expected.
 The results from $\pythiam$ also assure that the measured ridge yield is not contaminated by non-flow effects.
-Furthermore the ridge yields are studied in events, where jets with a harder fragmentation is preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
+Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
 The ridge structure still persist with both selections.

### 2020-08-24 sec_results.tex
figure update

@@
 The model predictions are presented as colored lines.
-Blue line corresponds to $\pythiashoving$ and orange line corresponds to $\pythiam$}
+Blue line corresponds to $\pythiashoving$, orange line corresponds to $\pythiam$ and green line corresponds to $\epos$.}
 	\label{fig:PlotDeltaPhi}
@@
 It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
+On the other hand, $\epos$ describes $\pt$ dependence quantitatively for the $1<\it{p}_{\rm{T}}<4$ GeV/$c$ range., while overestimating the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
 
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.eps} }
+	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.eps}}
 	\caption{ The spectra of ridge yield as function of transverse momentum.
 The filled circles denote the measurement with ALICE and compared to the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
-The two lines show model predictions from $\pythiam$ (orange line) and $\pythiashoving$ (blue line).
-}
+The three lines show model predictions from $\pythiam$ (blue line), $\pythiashoving$ (orange line) and $\epos$ (green line).}
 	\label{fig:PlotYSpect}
@@
 $\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the measured data as $\pttrigassoc$ increases.
+$\epos$, unlike $\pythiashoving$, gives estimates for the $\pt$ dependence showing the ridge yield for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, while estimating larger yield for the $\it{p}_{\rm{T}}<2$ GeV/$c$.
 
@@
 The filled circles show the ALICE measurement.
-Model predictions are presented with a blue line for $\pythiashoving$  and an orange line for $\pythiam$.}
+Model predictions are presented with a blue line for $\pythiam$, an orange line for $\pythiashoving$ and a green line for $\epos$.}
 	\label{fig:PlotDeltaPhiESE}
@@
 The filled circles show measurement with ALICE.
-Model predictions are compared to measurement as blue line for $\pythiashoving$ and orange line for $\pythiam$.}
+Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$.
+Ratios of measured data to models are prepared for $\pythiashoving$ and $\epos$.}
 	\label{fig:RidgeYield_ESE}

### 2020-08-27 sec_ana.tex
updates

@@
 \end{eqnarray}
-where  $\pttrig$ and $\ptassoc$ are transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, $N_\mathrm{pair}$ is the number of trigger-associated particle pairs, and $S (\Delta\eta, \Delta\varphi)$ and $B (\Delta\eta, \Delta\varphi)$ are the signal and background distributions, respectively.
+where  $\pttrig$ and $\ptassoc$ are transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles and $N_\mathrm{pair}$ is the number of trigger-associated particle pairs.
 $S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is in mixed events.
-The background distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
+The mixed events distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
 In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
+The interval of primary vertex is 2 cm.
+The final per-trigger yield is constructed by averaging correlations function over the primary vertex intervals.
 
@@
 Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero.
-The ridge yield ($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure
+The ridge yield ($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure.
 \begin{eqnarray}
@@
 \label{sec:uncertainties}
-Systematic uncertainties were estimated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction.
-Each source is assumed to be uncorrelated.
-The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection.
-The uncertainty from the track selection is estimated by changing the selection criteria.
-The uncertainty from the yield extraction procedures can be categorized into long-range definition and ZYAM procedure.
-The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction.
-%Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. 
-Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlation function constructed by generated particles from the event generator.
-The uncertainty of $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$ is summarized by averaging each uncertainty for given $\pttrig$ and $\ptassoc$.
-The uncertainty of $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$ is summarized by averaging the each uncertainty for a given $\ptlead$ and $\ptjet$ selection, respectively.
+
+Systematic uncertainties on $Y^{\rm{assoc}}$ were estimated by varying the analysis selection criteria and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}.
+The uncertainty on $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, which denotes the ridge yield as a function of $\pttrig$($\ptassoc$), was evaluated without any biases from even-scale selection.
+The uncertainties on $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$, which denote the ridge yield as functions of $\ptlead$ and $\ptjet$, were evaluated only for the 1$<\pttrig, \ptassoc<$2 GeV/$c$ range.
+
 \begin{table}[h!]
@@
          & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
-Pileup rejection		& $\sim$0.8	&0--4		&0--4		\\ \hline
-Primary Vertex		& $\sim$2.4	&1--12	&1-8		\\ \hline
+Pileup rejection		& 0.8	&0--4		&0--4		\\ \hline
+Primary Vertex		& 2.4	&1--12	&1--8		\\ \hline
 
-Tracking			& $\sim$4.0 	&2		&2		\\ \hline
+Tracking			& 4.0 	&2		&2		\\ \hline
 
-ZYAM			& $\sim$5.1	&2		&2		\\ \hline
-$\Delta\eta$ range	& $\sim$4.5	&3-7		&3--9		\\ \hline
+ZYAM			& 5.1	&2		&2		\\ \hline
+$\Delta\eta$ range	& 4.5	&3--7		&3--9		\\ \hline
 
-Mixing			& $\sim$4.4	&2--8		&1--16	\\ \hline
+Event mixing			& 4.4	&2--8		&1--16	\\ \hline
 
-M.C. non-closure*	& $\sim$2.5 	&1		&1		\\ \hline
-Total 			& $\sim$9.7	&4--16	&4--22	\\ 
+Efficiency correction	& 2.5 	&1		&1		\\ \hline \hline
+Total(in quadrature)			& 9.7	&4--16	&4--22	\\ 
 \hline 
@@
 The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection.
-The uncertainty is increased up to 4\% with $\ptlead$ or $\ptjet$ selection.
+The uncertainty is increased up to 4\% for event with the $\ptlead$ or $\ptjet$ selection.
 The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
@@
 The estimated uncertainty is increased up to 12\% from 1\%.
+
 The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
@@
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ particles.
+The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ particles.
 
-The uncertainty from the ZYAM procedure is estimated by varying the finding-scope for minimum position.
-The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ tracks, which is not largely affected by the event-scale selection.
+The ZYAM procedure is implemented by finding a minimum yield in a given finding range.
+The uncertainty from the ZYAM procedure is estimated by varying the range from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$.
+The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ tracks, which is not largely affected by the event-scale selection.
 The uncertainty from the $\Delta\eta$ projection range is estimated by varying the $\Delta\eta$ range.
-The uncertainty might include effects from the longitudinal de-correlations and possible non-flow contamination, which is thought be small.
-The estimated uncertainty is increased up to 9\% from 3\%, which is obtained by averaging the whole transverse momentum range.
-The uncertainty from the mixing pool bin size of primary vertex is estimated by varying the bin size from 2 to 1 cm.
-The estimated uncertainty is increased up to 8-16\% from 1-2\%.
+The uncertainty reflects effects from longitudinal de-correlations and possible non-flow contamination, which is thought be small.
+The estimated uncertainty is 3--9\% with the varying event-scale selection, which is obtained by averaging the whole transverse momentum range.
+
+The uncertainty from the event mixing intervals of primary vertex is estimated by varying the bin size from 2 to 1 cm.
+The estimated uncertainty is 1--16\% with the varying event-scale selection.
+The estimated uncertainty is largely varied from the fact that the event mixing distribution is constructed without the event-scale selection.
+The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
+
+%Systematic uncertainties were estimated by varying the event selection, track selection, yield extraction procedures and detector efficiency correction.
+Each source is assumed to be uncorrelated.
+The uncertainty from the event selection can be divided into pile-up rejection and primary vertex selection.
+The uncertainty from the track selection is estimated by changing the selection criteria.
+The uncertainty from the yield extraction procedures can be categorized into long-range definition and ZYAM procedure.
+The uncertainty from the efficiency correction is estimated by enlarging the event mixing bins, which is relevant to the acceptance correction.
+%Finally, The uncertainty from the application of the detector efficiency correction is estimated comparing the results constructed by efficiency corrected tracks with the results constructed. 
+%Finally, the uncertainty from the efficiency correction for charged tracks is estimated by comparing the correlations function constructed by reconstructed tracks from the detector responses with the correlation function constructed by generated particles from the event generator.
+%The uncertainty of $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$ is summarized by averaging each uncertainty for given $\pttrig$ and $\ptassoc$.
+The uncertainty of $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$ is summarized by averaging the each uncertainty for a given $\ptlead$ and $\ptjet$ selection, respectively.
 

### 2020-10-24 paper.tex
updates

@@
 %increase in events holding $\ptjet > 10$~GeV/$c$.
-The results are compared to $\pythiashoving$ calculations.  
+The results are compared to $\pythiashoving$ and $\epos$ calculations.  
 $\pythiashoving$ model can describe low $p_{\mathrm T}$ ridge yields up to 1.5 GeV/$c$ but can not give good description of $p_{\mathrm T}$ dependence both for the unbiased and jet-tagged events.
+$\epos$ model can describe $\pt$ dependence of ridge yield while overestimating the yield at the low $\pt<$ 2 GeV/$c$.
 The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
@@
 \newenvironment{acknowledgement}{\relax}{\relax}
-%\begin{acknowledgement}
-%\section*{Acknowledgements}
+\begin{acknowledgement}
+\section*{Acknowledgements}
+\noindent The ALICE Collaboration would like to thank Christian Bierlich for providing the PYTHIA8 string shoving calculations.
+%{\it (TBI: The default acknowledgments will be done by EB centrally.)}
 %\input{acknowledgements.tex}    %%%%%%% done by webmaster team
-%\end{acknowledgement}
+\end{acknowledgement}
 

### 2020-10-24 sec_ana.tex
updates

@@
 
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
-The V0 provides trigger and estimation of event multiplicity.
-A sample of events including higher numbers of produced particles is obtained with a high-multiplicity trigger, which is achieved by requiring 5 times of mean signal amplitudes of energy deposit by charged particles in the V0 detector.
-
 Charged particles are reconstructed by the ITS and TPC, which are working in a constant solenoidal magnetic field of 0.5~T.
@@
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
+The efficiency goes up to 80\% for intermediate transverse momentum(1--5~GeV/$c$).
+The transverse momentum resolution is better than 3\% for primary tracks with low $\pt<$1~GeV/$c$, and linearly degrades up to 6\% at $\pt \sim$ 40~GeV/$c$.
 %https://arxiv.org/pdf/1910.14400.pdf
+%https://arxiv.org/abs/1402.4476
+
+The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
+The V0 is used to assess event activity and it provides minimum bias (MB) and high-multiplicity (HM) trigger.
+The minimum bias trigger is obtained by a time coincidence of V0A and V0C signals.
+The high multiplicity trigger requires that amplitude of the combined V0A and V0C signal exceeds 5 times the mean value measured in minimum bias collisions.
+%The high-multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
+Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
+
+%The V0 provides trigger and estimation of event multiplicity.
+A sample of events including higher numbers of produced particles is obtained with a high-multiplicity trigger, which is achieved by requiring 5 times of mean signal amplitudes of energy deposit by charged particles in the V0 detector.
 
 %The multiplicity class is classified by the signal amplitude of the V0 detector.
-The high-multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
-Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
-Statistics of the high-multiplicity event benefits from a dedicated high-multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
 
@@
 
-The two-particle correlations function is measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$) between the trigger and associated particles.
+The minimum-bias pp data sample at $\sqrt{s}$ = 13 TeV were collected as 19.0 nb$^{-1}$.
+The high-multiplicity pp data sample were collected as 11.4 $\mu$b$^{-1}$ with higher threshold of V0 detector~\cite{ALICE-PUBLIC-2016-002}.
+
+The primary vertex position is reconstructed by combining observed signal clusters in the SPD.
+Events including a reconstructed vertex along beam axis($z_{\rm{vtx}}$) within 8 cm are only selected among events having proper primary vertex.
+A few events have multiple reconstructed primary vertice, which are thought to be results from multiple collisions, known as Pileup.
+Such Pileup events are rejected with the number of reconstructed vertice with respect to multiplicity class.
+The probability of Pileup is estimated to be 0.6\%.
+
+Requirements for reconstruction of charged particles are optimized to have the flat angular distribution of charged particles that is called hybrid tracks to minimize the effect of inactive regions of the ITS and TPC detectors~\cite{hybridExplanation}.
+The hybrid tracks combine two different classes of tracks.
+The first class consists of tracks that have at least one hit in the SPD.
+The tracks from the second class do not have any SPD associated hit and mainly rely on the position information of the primary vertex when reconstructing the tracks.
+
+The two-particle correlations function is measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences ($\Delta\varphi$) between the trigger and associated particles.
 \begin{eqnarray}
@@
 $S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is in mixed events.
-The mixed events distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
-In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
+$B(\Delta\eta, \Delta\varphi)$ is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
+The primary vertice of mixed events are required to be in the same range to avoid the acceptance effect.
 The interval of primary vertex is 2 cm.
@@
 
-The ridge yield is further studied in events having a hard jet or a high-pT leading particle in the ALICE central barrel.
+The ridge yield is further studied in events having a hard jet or a high-$\pt$ leading particle in the mid rapidity.
 Such requirement is expected to bias impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
@@
 
-Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT3~\cite{Brun:1994aa} is used to correct the acceptance and the efficiency of the ALICE detectors.
+To quantify variation of jet yield with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $p_\mathrm{T,\,jet}$, jet yield is extracted from near-side $\Delta\eta$ correlations.
+The near-side is defined as $|\Delta\varphi|<$7$\pi$/16, where the correlations function is projected along to $\Delta\varphi$ direction for 1$<\pttrig$, $\ptassoc<$2 GeV/$c$ in high-multiplicity events.
+The near-side $\Delta\eta$ correlations are constructed as
+\begin{eqnarray}
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } = \int_{|\Delta \varphi|<7\pi/16} \rm{d} \Delta \varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \quad.
+\end{eqnarray}
+
+The baseline of the $\Delta\eta$ correlations is also subtracted by implementing ZYAM procedure.
+The minimum yield $(C_{\rm{ZYAM}})$ of $\Delta\eta$ correlations is found within $|\Delta\eta|<$1.8 and used for subtraction from  $\Delta\eta$ correlations, which results in zero-yield at minimum.
+The jet yield ($Y^{\mathrm{jet}}$) is measured by integrating the $\Delta\eta$ correlations over $|\Delta\eta|<$1.6 after applying ZYAM procedure for $\Delta\eta$ correlations.
+\begin{eqnarray}
+Y^{\rm{jet}} = \int_{|\Delta \eta|<1.6} \rm{d} \Delta\eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } - C_{\rm{ZYAM}} \right)\quad.
+\end{eqnarray}
+
+%Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT3~\cite{Brun:1994aa} is used to correct the acceptance and the efficiency of the ALICE detectors.
 
@@
 \begin{table}[h!]
-\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
+\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
 \centering
@@
 Pileup rejection		& 0.8	&0--4		&0--4		\\ \hline
-Primary Vertex		& 2.4	&1--12	&1--8		\\ \hline
+Primary vertex		& 2.4	&1--12	&1--8		\\ \hline
 
@@
 ZYAM			& 5.1	&2		&2		\\ \hline
-$\Delta\eta$ range	& 4.5	&3--7		&3--9		\\ \hline
+Jet contamination	& 4.5	&3--7		&3--9		\\ \hline
 
@@
 The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
-The pileup rejection is achieved by reconstructing the multiple vertex in the individual event.
-The multiplicity of the reconstructed vertices determines whether the event is contaminated by pileup or not.
+The pileup rejection is achieved by reconstructing the multiple vertice in the individual event.
+The multiplicity of the reconstructed vertice determines whether the event is contaminated by pileup or not.
 The variation is set by the minimum multiplicity of reconstructed vertices from 5 to 3.
@@
 The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection.
-The uncertainty is increased up to 4\% for event with the $\ptlead$ or $\ptjet$ selection.
+The uncertainty varies up to 4\% for event with the $\ptlead$ or $\ptjet$ selection.
 The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
 The narrower primary vertex selection allows one to test the acceptance effect on the measurement.
-The estimated uncertainty is increased up to 12\% from 1\%.
+The estimated uncertainty is 1--12\% with the varying event-scale selections.
 
-The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
-The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
+The uncertainty from the track selection is estimated by varying from the hybrid tracks to the other one optimized for particle identification that is called the global tracks.
+The selection criteria of the global tracks are almost identical to the hybrid tracks except for the requirement of at least one hit on the SPD.
+Due to the requirement, the quality of the global tracks is sensitive to the condition of the SPD, finally resulting a non-flat azimuthal distribution of charged particles with the selection.
+%The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ particles.
+The uncertainty origination from the variation of the track selections is estimated as 4\%.
+The uncertainty is measured by averaging for various transverse momentum ranges regardless of event-scale selections.
 
@@
 The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ tracks, which is not largely affected by the event-scale selection.
-The uncertainty from the $\Delta\eta$ projection range is estimated by varying the $\Delta\eta$ range.
-The uncertainty reflects effects from longitudinal de-correlations and possible non-flow contamination, which is thought be small.
-The estimated uncertainty is 3--9\% with the varying event-scale selection, which is obtained by averaging the whole transverse momentum range.
+The uncertainty from the jet contamination is estimated by varying the $\Delta\eta$ projection range to see how much the jet contamination varies, which is thought be small.
+The estimated uncertainty is 3--9\% with the varying event-scale selection.
 
-The uncertainty from the event mixing intervals of primary vertex is estimated by varying the bin size from 2 to 1 cm.
+The uncertainty from the event mixing intervals of primary vertex is estimated by varying the interval size from 2 to 1 cm.
 The estimated uncertainty is 1--16\% with the varying event-scale selection.
-The estimated uncertainty is largely varied from the fact that the event mixing distribution is constructed without the event-scale selection.
 The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
+The estimated uncertainty is 1-2.5\% regardless of the event-scale selection.
 

### 2020-10-24 sec_intro.tex
updates

@@
 A summary of various explanations for the observed correlations in these small systems is given in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
+
+Besides the hybrid models mentioned above, alternative approaches have been developed to describe collectivity in small systems.
+String shoving implemented in PYTHIA 8 describes long-range correlations by generating string fields and interacting fields in transverse direction, which results in a microscopic transverse pressure~\cite{Bierlich:2017vhg}.
+EPOS LHC describes collectivity in small systems with the parameterized hydrodynamic evolution of the dense area, so called "core", consisting of many string fields~\cite{Pierog:2013ria}.
 

### 2020-10-24 sec_results.tex
updates

@@
 The per trigger yield iss measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
-The left panel is for the 0--0.1\% multiplicity class.
-The right one is from the minimum bias events (0--100\% multiplicity class).
+The left panel is for the high-multiplicity class.
+The right one is from the minimum bias events.
 The ridge structure is clearly observed in the high-multiplicity class while it is not seen in the minimum bias events.
@@
 
-Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (0--100\%) and the high-multiplicity class (0--0.1\%).
-The near-side ($\Delta\varphi\sim 0$) peak in 0--0.1\% multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
+Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class and the high-multiplicity class.
+The near-side ($\Delta\varphi\sim 0$) peak in high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
 The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high-multiplicity class.
 The measurements in the high-multiplicity class are compared to the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
+The particle multiplicity in the present analysis is estimated with the forward V0 subsystem, whereas whereas the analysis \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
+By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
 The near-side peaks in all transverse momentum ranges are comparable to each other within the uncertainties.
 The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances.
-The model predictions are presented for the measurements in the high-multiplicity class with the same acceptances used in this article both for $\eta$ and event multiplicity.
+The model predictions are presented for the measurements in high-multiplicity class with the identical charged track acceptance and the $\Delta\eta$ projection range to those used in this article.
 The high-multiplicity class for each model is determined by requiring the minimum number of charged particles larger than 105, which corresponds to the top 0--0.1\% multiplicity class based on $\pythiam$.
-The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$.
-However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
+The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of 1$<\it{p}_{\rm{T}}<$2 GeV/$c$.
+However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
 $\pythiam$ does not show any peaks in the near-side as expected.
-It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
-On the other hand, $\epos$ describes $\pt$ dependence quantitatively for the $1<\it{p}_{\rm{T}}<4$ GeV/$c$ range., while overestimating the near-side peak for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range.
+It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<$2 GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
+On the other hand, $\epos$ describes better $\pt$ dependence quantitatively for the 1$<\it{p}_{\rm{T}}<$4 GeV/$c$ range, while overestimating the near-side peak for the $\it{p}_{\rm{T}}<$2 GeV/$c$ range.
 
@@
 	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.eps}}
-	\caption{ The spectra of ridge yield as function of transverse momentum.
-The filled circles denote the measurement with ALICE and compared to the CMS measurement~\cite{Khachatryan:2015lva}, which is represented as open blue box.
+	\caption{ Fully corrected near-side ridge yield as a function transverse momentum.
+The filled circles denote the measurement with ALICE.
+The CMS measurement~\cite{Khachatryan:2015lva} is represented by open blue box markers.
 The three lines show model predictions from $\pythiam$ (blue line), $\pythiashoving$ (orange line) and $\epos$ (green line).}
@@
 %The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high-multiplicity class and compared to \cite{Khachatryan:2015lva}.
-The particle multiplicity in our analysis is estimated with the forward V0 subsystem, whereas whereas the analysis \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
-By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
 Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other.
@@
 Event-scale measurement by the largest $\pt$ of charged particles in each event is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$.
-As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$ (left) or $\ptjet>10$~GeV/$c$ (right) .
+As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) or $\ptjet>10$~GeV/$c$ (right) .
 %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
-It is worth noting that the correlation function with the minimum $\ptjet$ selection has double peaks along the $\Delta\eta$ axis at $\Delta\varphi = \pi$ due to the limited jet acceptance by requiring a minimum $\ptjet$.
+It is worth noting that the correlation function with the minimum $\ptjet$ selection has double peaks along the $\Delta\eta$ axis at $\Delta\varphi = \pi$ due to the jet tagging with the limited jet acceptance in the mid-rapidity as described in this article.
 
@@
 
-Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ for the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement.
+Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement.
 Even with the event-scale selection, the ridge is still visible at the near-side.
 The near-side yield increases as the threshold of $\ptjet$ increases compared to one measured in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
-The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum.
+\iffalse The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum.
 In contrast, soft jets are favored for reconstructed jets.
-The results are compared with $\pythiashoving$ and $\pythiam$ calculations.
-$\pythiashoving$ can still reproduce the near-side peak, while underestimating the yield with the event-scale selections.
-On the other hand, $\pythiam$ does not show the near-side peak with the event-scale selections.
-Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
+\fi The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations.
+The near-side peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$, while underestimated by $\pythiashoving$ and overestimated by $\epos$.
+On the other hand, $\pythiam$ does not show the near-side peak with the event-scale selections, while giving similar estimates for away-side yield as $\pythiashoving$.
+%Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
 
@@
 A moderate increase of the ridge yields toward higher $\ptlead$ or $\ptjet$ is observed and there is no difference between two event selections within the uncertainties.
-The results are compared with $\pythiashoving$ and $\pythiam$.
-$\pythiashoving$ doesn't show a clear $\it{p}^{\rm{LP}}_{\rm{T,min}}$ or $\it{p}^{\rm{Jet}}_{\rm{T,min}}$ dependence within the errors and underestimates the yields especially for the jet tagged events.
-$\pythiam$ does not produce the ridge yield, estimating zero yield, which implies negligible jet contamination in the measurements.
+The results are compared with $\pythiashoving$, $\pythiam$ and $\epos$.
+$\pythiashoving$ describes comparable trend with data, underestimating the ridge yield.
+On the other hand, $\epos$ also describes comparable trend with data, overestimating the ridge yield.
 The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.

### 2020-10-24 sec_summary.tex
updates

@@
 $\pythiashoving$ describes the yield qualitatively but its yield is decreased more rapidly than the data as $\pttrigassoc$ increases.
-On the other hand, $\pythiam$ does not describe the ridge in the long-range as expected.
-The results from $\pythiam$ also assure that the measured ridge yield is not contaminated by non-flow effects.
-Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
+On the other hand, $\epos$ gives better description for $\pt$ dependence while overestimating the ridge yield in the low $\pt<$2 GeV/$c$.
+$\pythiam$ does not describe the ridge in the long-range, which gives closure of the results against non-flow contamination.
+%Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
 The ridge structure still persist with both selections.
@@
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
+Furthermore the ridge yields are studied with the event-scale selections through the minimum transverse momentum of jet or leading particle requirement, which are more prone of requiring harder processes in pp collisions.
+The ridge structure still persists with both selections.
+The ridge yields increase as $\ptlead$ and $\ptjet$ increase.
+The latter, however, is more significant than the former selection.
+The results are compared with $\pythiashoving$, $\epos$ and $\pythiam$ calculations, where $\pythiam$ also provides closure against non-flow contamination by estimate ridge yield to be zero with event-scale selections.
+$\pythiashoving$ and $\epos$ estimate qualitative trends for event-scale selection.
+The former underestimates the ridge yield, unlike the latter overestimating the ridge yield.
 The results might open new way of studying impact parameter dependence of the small systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-10-26 sec_ana.tex
updates

@@
 
-Systematic uncertainties on $Y^{\rm{assoc}}$ were estimated by varying the analysis selection criteria and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}.
+Systematic uncertainties on $Y^{\rm{assoc}}$ and $Y^{\rm{jet}}$ were estimated by varying the analysis selection criteria and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}.
 The uncertainty on $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, which denotes the ridge yield as a function of $\pttrig$($\ptassoc$), was evaluated without any biases from even-scale selection.
-The uncertainties on $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$, which denote the ridge yield as functions of $\ptlead$ and $\ptjet$, were evaluated only for the 1$<\pttrig, \ptassoc<$2 GeV/$c$ range.
+The uncertainties on $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$, which denote the ridge yield as functions of $\ptlead$ and $\ptjet$, were evaluated for the 1$<\pttrig, \ptassoc<$2 GeV/$c$ range with event-scale selections using $\ptlead$ or $\ptjet$.
+The uncertainties on $Y^{\rm{jet}}(\ptlead)$ and $Y^{\rm{jet}}(\ptjet)$ were evaluated and described together because the measured uncertainties are comparable each other.
 
 \begin{table}[h!]
-\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
+\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, $Y^{\rm{assoc}}(\ptjet)$, and $Y^{\rm{jet}}$ respectively.}
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline 
-\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty (\%)} \\\cline{2-4}
-         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
-Pileup rejection		& 0.8	&0--4		&0--4		\\ \hline
-Primary vertex		& 2.4	&1--12	&1--8		\\ \hline
+\multirow{2}{*}{Sources}  & \multicolumn{4}{c|}{Systematic uncertainty (\%)} \\\cline{2-5} 
+         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ & $Y^{\rm{jet}}$ \\ \hline \hline
+Pileup rejection		& 0.8	&0--4		&0--4	&0--2	\\ \hline
+Primary vertex		& 2.4	&1--12	&1--8	&1--8	\\ \hline
 
-Tracking			& 4.0 	&2		&2		\\ \hline
+Tracking			& 4.0 	&2		&2	&2--3	\\ \hline
 
-ZYAM			& 5.1	&2		&2		\\ \hline
-Jet contamination	& 4.5	&3--7		&3--9		\\ \hline
+ZYAM			& 5.1	&2		&2	&N.A.	\\ \hline
+Jet contamination	& 4.5	&3--7		&3--9	&N.A.	\\ \hline
 
-Event mixing			& 4.4	&2--8		&1--16	\\ \hline
+Event mixing			& 4.4	&2--8		&1--16	&1	\\ \hline
 
-Efficiency correction	& 2.5 	&1		&1		\\ \hline \hline
-Total(in quadrature)			& 9.7	&4--16	&4--22	\\ 
+Efficiency correction	& 2.5 	&1		&1	&3	\\ \hline \hline
+Total(in quadrature)			& 9.7	&4--16	&4--22	&4--10 \\ 
 \hline 
@@
 The variation is set by the minimum multiplicity of reconstructed vertices from 5 to 3.
+The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection.
+The uncertainty varies up to 4\% for event with the $\ptlead$ or $\ptjet$ selection.
+The uncertainty for $Y^{\rm{jet}}$ is estimated to be 0--2\$ with varying event-scale selections.
 %Pileup cut (multbins) -> (default pileup from the physics selection)
 %Pileup cut (multbins) -> PileupMV (?)
-The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection.
-The uncertainty varies up to 4\% for event with the $\ptlead$ or $\ptjet$ selection.
 The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
@@
 The estimated uncertainty is 1--12\% with the varying event-scale selections.
+The uncertainty for $Y^{\rm{jet}}$ is estimated to be 1--8\%.
 
@@
 The uncertainty is measured by averaging for various transverse momentum ranges regardless of event-scale selections.
+The uncertainty for $Y^{\rm{jet}}$ is estimated to be 2--3\%.
 
@@
 The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ tracks, which is not largely affected by the event-scale selection.
+The uncertainty for $Y^{\rm{jet}}$ is not considered due to negligible deviation compared with statistical fluctuation.
 The uncertainty from the jet contamination is estimated by varying the $\Delta\eta$ projection range to see how much the jet contamination varies, which is thought be small.
 The estimated uncertainty is 3--9\% with the varying event-scale selection.
+The uncertainty for $Y^{\rm{jet}}$ is not evaluated as the jet yield is measured.
 
@@
 The estimated uncertainty is 1--16\% with the varying event-scale selection.
+The uncertainty for $Y^{\rm{jet}}$ is estimated to be 1\%.
 The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
-The estimated uncertainty is 1-2.5\% regardless of the event-scale selection.
+The estimated uncertainty is 1--2.5\% regardless of the event-scale selection.
+The uncertainty for $Y^{\rm{jet}}$ is estimated to be 3\%.
 

### 2020-10-26 sec_results.tex
updates

@@
 	\centering
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.eps} }
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.eps} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.pdf} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
 	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high-multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right).
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.eps}
+	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
 	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for various transverse momentum intervals in each multiplicity class.
@@
 	\centering
-	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.eps}}
+	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.pdf}}
 	\caption{ Fully corrected near-side ridge yield as a function transverse momentum.
@@
 	\centering
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.eps} }
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.eps} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrlh.pdf} }
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
 	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection.
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.eps}
+	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
 	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$ in the 0--0.1\% multiplicity class.
@@
 The near-side yield increases as the threshold of $\ptjet$ increases compared to one measured in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
-\iffalse The event-scale measurement with $\ptlead$ favors harder jets as a leading particle carries a large fraction of the momentum.
-In contrast, soft jets are favored for reconstructed jets.
-\fi The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations.
+The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations.
 The near-side peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$, while underestimated by $\pythiashoving$ and overestimated by $\epos$.
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.eps}
+	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
 	\caption{The ridge yield spectra with respect to the leading particle and jet selections.
@@
 The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
+
+\begin{figure}[h!]
+	\centering
+	\includegraphics[width=0.99\linewidth]{./figures/Fig9_JetYieldESE.pdf}
+	\caption{The jet yield spectra with respect to the leading particle (left) and jet selections (right).
+The filled circles show measurement with ALICE.
+Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$.}
+	\label{fig:RidgeYield_ESE}
+\end{figure}
+
+Jet yield has been measured as a function of minimum $\ptlead$ and $\ptjet$ threshold to further discuss ridge yields and jet yields.
+%quantify the trend of the jet yield.
+$\epos$ provides comparable estimates for jet yields, while $\pythiam$ and $\pythiashoving$ overestimate jet yields for both selections.
+Increasing trend of jet yield as a function of minimum $\ptlead$ and saturating trend of jet yield as a function of minimum $\ptjet$ have been observed and estimated by models.
+Jet yield measured with $\ptlead>$20~GeV/$c$ is comparable with the one measured with $\ptjet>$10~GeV/$c$, where ridge yields with corresponding selections are also comparable.

### 2020-11-12 abstract.tex
after Alice's comments

@@
-The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
+Two-particle angular correlations have been measured in high-multiplicity $\sqrt{s} =13$ TeV proton-proton collisions by the ALICE collaboration.
+From the correlations, the yields of particle pairs at short-($\Delta\eta$ \approx 0) and long-range($1.6<\Delta\eta<1.8$) in rapidity have been extracted on the near side ($\Delta\varphi$ \approx 0).
+The correlations and yields are reported as a function of transverse momentum($p_{\rm T}$) in the range $1 < p_{\rm T} < 5$ GeV/$c$.
+Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 
+The results demonstrate that the long-range “ridge” yield, related to the collective behavior of the produced system, is present in events with high-$p_{\rm T}$ processes.
+The magnitudes of the short- and long-range yields are found to grow with the event scale.
+The results have been compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
+It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependences.
+
+%The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
 Many theoretical approaches to interpreting this effect have been developed.

### 2020-11-12 paper.tex
after Alice's comments

@@
 %%% Put your own title + short title here:
-\title{Long-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
+\title{Long- and short-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
 \ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
@@
 %\input{abstract.tex}
+We report on the studies of two-particle angular correlations measured in high-multiplicity proton-proton collisions at $\sqrt{s} =13$ TeV with ALICE. 
+The yields of two-particle angular correlations at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity are measured at the near side ($\Delta\varphi \sim 0$).
+The correlations and yields are reported as a function of charged-particle transverse momentum ($p_{\mathrm T}$) in $1 < p_{\mathrm T} < 5$ GeV/$c$.
+Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 
+The results demonstrate that the long-range ``ridge`` yield, related to the collective behavior of the produced system, is present in events with high-$p_{\mathrm T}$ processes.
+The magnitudes of the short- and long-range yields are found to grow with the event scale.
+The results have been compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
+It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependences.
 
-Long-range azimuthal correlations are measured in high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by ALICE at the LHC.
+%Long-range azimuthal correlations are measured in high-multiplicity pp collisions at center-of-mass energy $\sqrt{s} = 13$~TeV by the ALICE collaboration at the LHC.
 The measurement was carried out for trigger and associated particles having transverse momenta in the range $1 < p_{\mathrm T} < 5$~GeV/$c$.
 Trigger and associated particles were separated by a large pseudorapidity interval $1.6 < |\Delta \eta |<1.8$.
-%These results are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of  for the trigger and associated particles.
-In addition to the conventional long-range correlation studies, the results are further investigated in events with a high-pT leading track or jet.
+Measured ridge yield is consistent with the results from the CMS collaboration.
+%These resfults are obtained in a relative pseudorapidity range of $1.6 < |\eta| < 1.8$ and transverse momentum region of  for the trigger and associated particles.
+%In addition to the conventional long-range correlation studies, the results are further investigated in events with a high-$p_{\rm{T}}$ leading track or jet.
 %where jets with a harder fragmentation are present.
-The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
+%The jets are reconstructed by using the anti-$k_\mathrm{T}$ algorithm with resolution parameter $R=0.4$ in $|\eta_\mathrm{jet}|<0.4$. 
 %The magnitude of the correlation dubbed ridge yield, is consistent with the results from other LHC experiments for unbiased events.
-Measured ridge yield is consistent with the results from the CMS experiments for unbiased high-multiplicity events.
-These long-range correlations are also seen in the events containing jets.
-Furthermore, data show that the ridge yields tend to grow with transverse momentum of the jet or leading track.
+%These long-range correlations are also seen in the events containing high-$\pt$ jets for the first time.
+Furthermore, data show that the ridge yield tends to grow with transverse momentum of the jet or leading track.
 %increase in events holding $\ptjet > 10$~GeV/$c$.
-The results are compared to $\pythiashoving$ and $\epos$ calculations.  
-$\pythiashoving$ model can describe low $p_{\mathrm T}$ ridge yields up to 1.5 GeV/$c$ but can not give good description of $p_{\mathrm T}$ dependence both for the unbiased and jet-tagged events.
+%Event-scale selection is further studied by measuring the near-side jet-like peak.
+%The results are compared to $\pythiashoving$ and $\epos$ calculations.  
+%$\pythiashoving$ model can describe low $p_{\mathrm T}$ ridge yields up to 1.5 GeV/$c$ but can not give a good description of $p_{\mathrm T}$ dependence both for the unbiased and jet-tagged events.
 $\epos$ model can describe $\pt$ dependence of ridge yield while overestimating the yield at the low $\pt<$ 2 GeV/$c$.
-The results open new aspects of studying the small collision systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
+On the other hand, near-side jet-like correlations are overestimated by $\pythiashoving$ and quantitatively estimated by $\epos$, which is opposite description to the ridge yield.
 

### 2020-11-12 sec_ana.tex
after Alice's comments

--- 2020-08-27 sec_ana.tex
@@
 
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
-The V0 provides trigger and estimation of event multiplicity.
-A sample of events including higher numbers of produced particles is obtained with a high-multiplicity trigger, which is achieved by requiring 5 times of mean signal amplitudes of energy deposit by charged particles in the V0 detector.
+The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within the pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
+The V0 is used to assess event activity and it provides minimum bias (MB) and high-multiplicity (HM) trigger.
+The minimum bias trigger is obtained by a time coincidence of V0A and V0C signals.
+The high multiplicity trigger requires that amplitude of the combined V0A and V0C signal exceeds 5 times the mean value measured in minimum bias collisions, providing top 0.1\% events of MB events.
 
-Charged particles are reconstructed by the ITS and TPC, which are working in a constant solenoidal magnetic field of 0.5~T.
-The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD) and Silicon Strip Detector (SSD).
+Charged particles are reconstructed by the ITS and TPC, which are working in a uniform solenoidal magnetic field of 0.5~T.
+The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD), and Silicon Strip Detector (SSD).
+You can find more details about SPD in~\cite{Santoro2009:ALICESPD}.
 The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}| < 8$~cm.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
+The efficiency goes up to 80\% for intermediate transverse momentum, 1--5~GeV/$c$.
+The transverse momentum resolution is around 1\% for primary tracks with low $\pt<$1~GeV/$c$, and linearly degrades up to 6\% at $\pt \sim$ 40~GeV/$c$~\cite{Contin_2012:ITSPTRES}.
 %https://arxiv.org/pdf/1910.14400.pdf
-
-%The multiplicity class is classified by the signal amplitude of the V0 detector.
-The high-multiplicity events used in the present analysis have the top 0.1\% signal amplitude (the 0--0.1\% multiplicity class) by the V0 detector with respect to the set of minimum bias events at ALICE.
-Corresponding number of charged particles is reported as $\sim$31 in the mid-rapidity region ($|\eta|<0.5$) that is almost 5 times larger than the minimum-bias events.
-Statistics of the high-multiplicity event benefits from a dedicated high-multiplicity trigger that was recently implemented at ALICE  in the LHC Run 2 period.
+%https://arxiv.org/abs/1402.4476
 
@@
 
-The two-particle correlations function is measured as functions of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences($\Delta\varphi$) between the trigger and associated particles.
+The analyzed data samples of minimum-bias and high-multiplicity pp $\sqrt{s}=$13 TeV events correspond to integrated luminosities of 19 nb$^{-1}$ and 11.4 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
+
+The primary vertex position is reconstructed by combining observed signal clusters in the SPD.
+Reconstructed primary vertices of selected events are required to be located within 8 cm from the ALICE center.
+Probability of pileup events is about 0.6\%.
+Pileup events can be resolved and rejected if the longitudinal displacement of their primary vertices is larger than 0.8 cm.
+The probability of pileup is estimated to be 0.6\%.
+
+%Requirements for reconstruction of charged particles are optimized to have the flat angular distribution of charged particles that is called hybrid tracks to minimize the effect of inactive regions of the ITS and TPC detectors~\cite{hybridExplanation}.
+The hybrid tracks combine two different classes of tracks.
+The first class consists of tracks that have at least one hit in the SPD.
+The tracks from the second class do not have any SPD associated hit and mainly rely on the position information of the primary vertex when reconstructing the tracks.
+Charge particle selection criteria are optimized for a homogeneous response over the full TPC volume to mitigate the effect of small regions where some of ITS layers are inactive.
+The selected set of tracks consists of two track classes.
+Tracks from the first class are required to have at least one hit in the SPD.
+Tracks from the second class do not have any SPD associated hit and their initial point is instead constrained to the primary vertex.
+
+The two-particle correlations function is measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences ($\Delta\varphi$) between the trigger and associated particles,
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)} \lvert_{\pttrig,\ptassoc}  ,
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \lvert_{\pttrig,\ptassoc}   \quad.
 \label{eq:corrfunction}
@@
 where $\pttrig$ and $\ptassoc$ are transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles and $N_\mathrm{pair}$ is the number of trigger-associated particle pairs.
-$S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ is in mixed events.
-The mixed events distribution is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
-In mixed events, the primary vertices and multiplicity classes are required to be in the same range to avoid the acceptance effect with respect to the multiplicity class and primary vertex.
-The interval of primary vertex is 2 cm.
-The final per-trigger yield is constructed by averaging correlations function over the primary vertex intervals.
+$N_\mathrm{trig}$ and $N_\mathrm{pair}$ were corrected for track reconstruction efficiencies as $N_\mathrm{trig,cor} = N_\mathrm{trig}/ \epsilon_{\rm{trig}}$ and $N_\mathrm{pair,cor} = N_\mathrm{pair}/(\epsilon_{\rm{trig}}\epsilon_{\rm{assoc}})$ for a given $\pt$ and $\eta$, respectively.
+$S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ in mixed events.
+$B(\Delta\eta, \Delta\varphi)$ is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
+Primary vertices of events to be mixed are required to be within the same, 2 cm wide $z_{vtx}$ bin.
+The final per-trigger yield is constructed by averaging correlation functions over these primary vertex bins.
 
-The ridge yields at large $\Delta\eta$ are extracted in different multiplicity classes and transverse momentum intervals.
-The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$ where non-flow effects (mainly coming from jets) are negligible.
+Ridge yields at large $\Delta\eta$ are extracted for various multiplicity classes and transverse momentum intervals.
+The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$, where non-flow effects (mainly coming from jets) are negligible on the near-side.
 In this region, the $\Delta\varphi$ distribution, or the so called per-trigger yield is expressed as
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \rm{d} \Delta \eta \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \rm{d} \Delta \eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\eta} \quad.
 \end{eqnarray}
 
-The baseline of the correlations is subtracted by implementing Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
-The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi$=$\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ distribution is obtained from the function, which fits the $\Delta\varphi$ distribution with a Fourier series up to the third harmonic.
-Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ distribution makes the yield at $\Delta\varphi_{\rm{min}}$ zero.
-The ridge yield ($Y^{\rm{assoc}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ distribution over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure.
+The baseline of the correlations is subtracted by means of the Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
+The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi=\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ projection (Note that the value of $\Delta\varphi_{\rm{min}}$ can be different in data and in models.) is obtained from the function, which fits the data with a Fourier series up to the third harmonic.
+Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ projection makes the yield at $\Delta\varphi_{\rm{min}}$ zero.
+The ridge yield ($Y^{\rm{ridge}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ projection over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure,
 \begin{eqnarray}
-Y^{\rm{assoc}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \rm{d} \Delta\varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } \quad.
+Y^{\rm{ridge}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \rm{d} \Delta\varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } \quad.
 \end{eqnarray}
 
-The ridge yield is further studied in events having a hard jet or a high-pT leading particle in the ALICE central barrel.
+The ridge yield is further studied in events having a hard jet or a high-$\pt$ leading particle in the mid rapidity.
 Such requirement is expected to bias impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
@@
 On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
-The event-scale is set by requiring minimum transverse momentum of leading track or reconstructed jet in mid-rapidity since hard scattering produces leading tracks with a high $p_\mathrm{T}$ or jets.
+The event-scale is set by requiring a minimum transverse momentum of leading track or reconstructed jet in mid-rapidity.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.
-Jets are reconstructed with charged particles only (charged jets) with the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$.
+Jets are reconstructed with charged particles only (track-based jets) with the anti-$k_{\rm{T}}$ algorithm~\cite{Cacciari2008:FASTJET,Cacciari2012:FASTJET} and the resolution parameter $R=$~0.4.
+The recombination scheme used in this article is $\pt$ scheme.
 Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
-The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured for the $k_{\rm{T}}$ algorithm with $R = 0.2$.
+The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{ALICE2019:KTJETSub}.
 
-Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT3~\cite{Brun:1994aa} is used to correct the acceptance and the efficiency of the ALICE detectors.
+To quantify variation of near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $p_\mathrm{T,\,jet}$, neat-side jet-like peak is extracted from near-side $\Delta\eta$ correlations.
+The near-side is defined as $|\Delta\varphi|<$1.28, where the correlations function is projected along to $\Delta\varphi$ direction for 1$<\pttrig$, $\ptassoc<$2 GeV/$c$ in high-multiplicity events.
+The near-side $\Delta\eta$ correlations are constructed as
+\begin{eqnarray}
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } = \int_{|\Delta \varphi|<1.28} \rm{d} \Delta \varphi \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\varphi} \quad.
+\end{eqnarray}
+
+The baseline of the $\Delta\eta$ correlations is also subtracted by using the ZYAM procedure.
+The minimum yield $(C_{\rm{ZYAM}})$ of $\Delta\eta$ correlations is found within $|\Delta\eta|<$1.6 and used for subtraction from  $\Delta\eta$ correlations, which results in zero-yield at minimum.
+The near-side jet-like peak yield ($Y^{\mathrm{near}}$) is measured by integrating the $\Delta\eta$ correlations over $|\Delta\eta|<$1.6,
+\begin{eqnarray}
+Y^{\rm{near}} = \int_{|\Delta \eta|<1.6} \rm{d} \Delta\eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } - C_{\rm{ZYAM}} \right)\quad.
+\end{eqnarray}
+
+%Monte Carlo simulation with $\pythiam$ event generator and particle transport inside ALICE using GEANT3~\cite{Brun:1994aa} is used to correct the acceptance and the efficiency of the ALICE detectors.
 
@@
 
-Systematic uncertainties on $Y^{\rm{assoc}}$ were estimated by varying the analysis selection criteria and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}.
-The uncertainty on $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, which denotes the ridge yield as a function of $\pttrig$($\ptassoc$), was evaluated without any biases from even-scale selection.
-The uncertainties on $Y^{\rm{assoc}}(\ptlead)$ and $Y^{\rm{assoc}}(\ptjet)$, which denote the ridge yield as functions of $\ptlead$ and $\ptjet$, were evaluated only for the 1$<\pttrig, \ptassoc<$2 GeV/$c$ range.
+Systematic uncertainties on $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ were estimated by varying the analysis selection criteria and corrections and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}.
+$Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ denotes the ridge yield as a function of $\pttrig$($\ptassoc$) in event-scale unbiased events.
+Ridge yields measured in event-scaled biased events are denoted $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ and they were evaluated for 1$<\pttrig, \ptassoc<$2 GeV/$c$.
+The uncertainties on $Y^{\rm{near}}(\ptlead)$ and $Y^{\rm{near}}(\ptjet)$ were evaluated and reported in Tab.~\ref{tab:syst} together because the measured uncertainties are comparable to each other.
 
 \begin{table}[h!]
-\caption{The relative systematic uncertainty of the associated yield spectrum are estimated for $Y^{\rm{assoc}}(\pttrig,\,\ptassoc)$, $Y^{\rm{assoc}}(\ptlead)$, and $Y^{\rm{assoc}}(\ptjet)$, respectively.}
+\caption{The relative systematic uncertainty on the associated yield spectrum estimated for $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$, $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and, $Y^{\rm{near}}$, respectively.}
 \centering
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline 
-\multirow{2}{*}{Sources}  & \multicolumn{3}{c|}{Systematic uncertainty (\%)} \\\cline{2-4}
-         & $Y^{\rm{assoc}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{assoc}}(\it{p}_{\rm{T, Jet}})$ \\ \hline \hline
-Pileup rejection		& 0.8	&0--4		&0--4		\\ \hline
-Primary Vertex		& 2.4	&1--12	&1--8		\\ \hline
+\multirow{2}{*}{Sources}  & \multicolumn{4}{c|}{Systematic uncertainty (\%)} \\\cline{2-5} 
+         & $Y^{\rm{ridge}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{ridge}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{ridge}}(\it{p}_{\rm{T, Jet}})$ & $Y^{\rm{near}}$ \\ \hline \hline
+Pileup rejection		& 0.8	&0.1--3.7		&0.1--3.9	&0.2--2.2	\\ \hline
+Primary vertex		& 2.4	&0.5--12.2	&0.5--8.2	&1.1--7.8	\\ \hline
 
-Tracking			& 4.0 	&2		&2		\\ \hline
+Tracking			& 4.0 	&2.0		&2.0	&1.5--3.4	\\ \hline
 
-ZYAM			& 5.1	&2		&2		\\ \hline
-$\Delta\eta$ range	& 4.5	&3--7		&3--9		\\ \hline
+ZYAM			& 5.1	&2.1		&2.1	&N.A.	\\ \hline
+Jet contamination	& 4.5	&3.4--8.1		&3.4--9.4	&N.A.	\\ \hline
 
-Event mixing			& 4.4	&2--8		&1--16	\\ \hline
+Event mixing			& 4.4	&1.0--9.6		&1.0--16.4	&0.5-1.7	\\ \hline
 
-Efficiency correction	& 2.5 	&1		&1		\\ \hline \hline
-Total(in quadrature)			& 9.7	&4--16	&4--22	\\ 
+Efficiency correction	& 2.5 	&1.2		&1.2	&3.1	\\ \hline \hline
+Total(in quadrature)			& 9.7	&4.2--18.2	&4.2--22.0	&3.9--10.9 \\ 
 \hline 
@@
 The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
-The pileup rejection is achieved by reconstructing the multiple vertex in the individual event.
-The multiplicity of the reconstructed vertices determines whether the event is contaminated by pileup or not.
-The variation is set by the minimum multiplicity of reconstructed vertices from 5 to 3.
+The multiplicity of the track contributors to each vertex determines whether the event is contaminated by pileup or not.
+The variation is set by the minimum multiplicity of track contributors from 5 to 3.
+The estimated uncertainty is 0.8\% for events without event-scale bias.
+The uncertainty varies up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
+The corresponding uncertainty on $Y^{\rm{near}}$ is 0.2–-2.2\%.
 %Pileup cut (multbins) -> (default pileup from the physics selection)
 %Pileup cut (multbins) -> PileupMV (?)
-The estimated uncertainty is 1\% without $\ptlead$ or $\ptjet$ selection.
-The uncertainty is increased up to 4\% for event with the $\ptlead$ or $\ptjet$ selection.
+
 The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
 The narrower primary vertex selection allows one to test the acceptance effect on the measurement.
-The estimated uncertainty is increased up to 12\% from 1\%.
+The estimated uncertainty is 0.5--12.2\% with the varying event-scale selections.
+The uncertainty for $Y^{\rm{near}}$ is estimated to be 1.1--7.8\%.
 
-The uncertainty from the track selection is estimated by varying the track selection criteria from the one optimized for refining the angular track distribution to the other optimized for particle identification.
-The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
+The uncertainty from the track selection is estimated by varying from the hybrid tracks to the other one optimized for particle identification that is called the global tracks.
+The selection criteria of the global tracks are almost identical to the hybrid tracks.
+Each global track is required to have at least one SPD hit.
+%except for the requirement of at least one hit on the SPD.
+Due to the requirement, the quality of the global tracks is sensitive to the condition of the SPD, finally resulting in a non-flat azimuthal distribution of charged particles with the selection. 
+%The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The estimated uncertainty for track selection is 4\% by averaging the uncertainty for whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ particles.
+The uncertainty associated to the variation of the track selections is estimated to be 4.0\%.
+The uncertainty was obtained by averaging relative variations over different transverse momentum ranges.
+The corresponding uncertainty on $Y^{\rm{near}}$ is estimated to be 1.5--3.4\%.
 
-The ZYAM procedure is implemented by finding a minimum yield in a given finding range.
-The uncertainty from the ZYAM procedure is estimated by varying the range from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$.
-The estimated uncertainty for track selection is 5.1\% by averaging the uncertainty for the whole transverse momentum bins and 2\% for 1$<\it{p}_{\rm{T}}<$2 GeV/$c$ tracks, which is not largely affected by the event-scale selection.
-The uncertainty from the $\Delta\eta$ projection range is estimated by varying the $\Delta\eta$ range.
-The uncertainty reflects effects from longitudinal de-correlations and possible non-flow contamination, which is thought be small.
-The estimated uncertainty is 3--9\% with the varying event-scale selection, which is obtained by averaging the whole transverse momentum range.
+Systematic uncertainty resulting from the ZYAM procedure was estimated by varying the range of the fit, which is used to find the minimum, from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$.
+The estimated uncertainty is 5.1\% without event-scale bias.
+The uncertainty varies to 2\% for events with the $\ptlead$ or $\ptjet$ selection.
+The uncertainty for $Y^{\rm{near}}$ is not considered due to negligible deviation compared with statistical fluctuation.
+The uncertainty from the jet contamination is estimated by varying the $\Delta\eta$ projection range to see how much the jet contamination varies, which is thought be small.
+The estimated uncertainty is 3.4--9.4\% with the varying event-scale selection.
+The uncertainty for $Y^{\rm{near}}$ is not considered as the jet yield is observables.
 
-The uncertainty from the event mixing intervals of primary vertex is estimated by varying the bin size from 2 to 1 cm.
-The estimated uncertainty is 1--16\% with the varying event-scale selection.
-The estimated uncertainty is largely varied from the fact that the event mixing distribution is constructed without the event-scale selection.
+The uncertainty from the event mixing $z_{vtx}$ bin of primary vertex is estimated by varying the interval size from 2 to 1 cm.
+The estimated uncertainty is 1.0--16.4\% with the varying event-scale selection.
+The uncertainty for $Y^{\rm{near}}$ is estimated to be 0.5--1.7\%.
 The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
+The estimated uncertainty is 1.2--2.5\% regardless of the event-scale selection.
+The uncertainty for $Y^{\rm{near}}$ is estimated to be 3.1\%.
 
@@
 %*The M.C. closure test for efficiency correction results in $\sim$2.5\% discrepancy. The discrepancy is considered into systematic uncertainty.
-
-\iffalse
-
-\begin{table}[!h]
-\centering
-\caption{ Summary of the systematic uncertainties. See text for details.}
-\begin{tabular}{ c|c }
-%\begin{tabular}{c || c}
-\hline
-Source &  Uncertainty \\ \hline
-Event mixing & 6-10\% \\  \hline
-$\Delta\eta$ projection range & 10-15\% \\ \hline
-M.C. closure & 4\% \\ \hline
-Primary vertex & 4\% \\ \hline
-Pileup Cut & 4\% \\ \hline
-Track selection & 5\% \\ \hline
-Total & 14-20\% \\
-\hline
-\end{tabular}
-%\caption{ Definition of multiplicity class in this analysis.
-Reference definition of multiplicity coud be found in the following link; \url{https://twiki.cern.ch/twiki/bin/viewauth/ALICE/ReferenceMult}  }
-\end{table}
-\fi

### 2020-11-12 sec_intro.tex
after Alice's comments

--- 2020-08-10 sec_intro.tex
@@
 
-Strong collectivity observed in the azimuthal correlations of particles emitted over a wide pseudorapidity range, in high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, indicates the formation of a strongly interacting matter called the quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
-The recent efforts are focused on constraining the transport properties of the QGP in hydrodynamic models~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} along with few advanced experimental efforts~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj}.
-In recent years similar collective behaviors via long-range azimuthal correlations are also observed for small systems with high final-state particle multiplicity such as proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}, % strong indications for collective flow with hydrodynamic characteristics even in small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
-The observed long-range azimuthal correlations suggest flow with hydrodynamic characteristics even in these small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
+In high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, significant correlations are observed between particles emitted over a wide pseudorapidity range.
+These collective effects are indicative of the formation of a strongly interacting matter called the quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
+Recent theoretical~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} and experimental~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj} advancements have contributed significantly to understanding the transport properties of the QGP.
+Similar long-range correlations, typically interpreted as signatures of collectivity in heavy-ion collisions, are also observed in high-multiplicity proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}.
+Azimuthal correlations of particles separated by a large gap in pseudorapidity may suggest hydrodynamic behavior even in these small systems, although the volume and lifetime of the medium produced by such a colliding system are expected to be small, and there are other mechanisms which can produce similar flow-like signals~\cite{Busza:2018rrf,Nagle:2018nvi}.
+%The observed long-range azimuthal correlations suggest flow with hydrodynamic characteristics even in these small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
 
-Measurements of two-particle angular correlations are typically performed in terms of two dimensional $\Delta\eta$--$\Delta\varphi$ correlation functions, where $\Delta\eta$ is the relative pseudorapidity and $\Delta\varphi$ is the azimuthal angle separation between both particles.
-Long-range structure of two-particle correlation functions is of particular interest in studies of possible novel collective effects, where the effects of known sources such as resonance decays and fragmentation of high-momentum partons are known to be small.
-For most pp Monte Carlo (MC) event generators, the typical sources of such long-range correlations are momentum conservation.
+Measurements of two-particle angular correlations give information on many physical effects, including collectivity, hadronization, fragmentation, and femtoscopic effects~\cite{Lisa:2005dd}, and are typically quantified as a function of $\Delta\eta$, the relative pseudorapidity, and $\Delta\varphi$, the separation in azimuthal angle, of pairs of particles.
+The long-range structure of two-particle correlation functions is well suited to analyse collective effects, since it is not created by resonance decays and fragmentation of high-momentum partons.
+A typical source of long-range correlations in Monte Carlo pp generators is momentum conservation.
 %and away-side ($\Delta\varphi$ $\approx$ $\pi$) jet correlations.
-The enhancement in the associated yield of two-particle correlations at small relative azimuthal angle ($\Delta\varphi$) that extends over a long-range of relative pseudorapidity ($\Delta\eta$), is dubbed ``ridge'' due to its characteristic shape in the $\Delta\eta$--$\Delta\varphi$ plane.
+The enhancement in the associated yield of two-particle correlations at small $\Delta\varphi$ that extends over a large $\Delta\eta$, is dubbed ``ridge'' due to its characteristic shape in the $\Delta\eta$--$\Delta\varphi$ plane.
 The shape of these $\Delta\varphi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
 The second and third order terms are the dominant harmonic coefficients.
-In heavy-ion collisions harmonic coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
+In heavy-ion collisions, harmonic coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
 
@@
 The proton shape and its fluctuations are also important to model the small systems~\cite{Mantysaari:2017cni}.
-Nevertheless, the hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty}. 
-The influence and interplay of the initial state and final state effects have recently been studied carefully for the first time in ~\cite{Greif:2019ygb}, pointing out that the details of the initial state are crucially important for quantitative description of measurements in small systems~\cite{Schenke:2019pmk}.
-Attempts to describe the collective effects systematically from small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Greif:2019ygb}.
+%Nevertheless, the hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty,Schenke:2019pmk}. 
+The influence and interplay of the initial state and final state effects should be further studied carefully with the inclusion of  the details of the initial state for quantitative description of measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo}.
+Attempts to describe the collective effects systematically from small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Schenke:2020mbo}.
 However, a quantitative description of the full set of experimental data has not been achieved yet.
-A summary of various explanations for the observed correlations in these small systems is given in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
+A summary of various explanations for the observed correlations in small systems is given in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
+
+Besides the hybrid models mentioned above, alternative approaches have been developed to describe collectivity in small systems.
+String shoving implemented in PYTHIA 8 describes long-range correlations by generating color strings which interact and repel each other in transverse direction, which results in a microscopic transverse pressure~\cite{Bierlich:2017vhg}.
+The microscopic model for collectivity, based on interacting strings implemented in $\pythiae$ event generator the so-called ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
+This challenges the hydrodynamic picture and predicts modifications to jet fragmentation properties~\cite{Bierlich:2019ixq}.
+EPOS LHC describes collectivity in small systems with a parameterized hydrodynamic evolution of the high-energy density region, so called ``core'', formed by many color string fields~\cite{Pierog:2013ria}.
 
 Furthermore, if collectivity in small systems is due to final-state interactions, it is expected to have an effect on jets.
-Proving the presence of jet quenching will be another crucial milestone to demonstrate the existence of the QGP in high-multiplicity pp collisions.
-Most of the observables for the jet quenching in pp and p--Pb collisions do not show any clear evidence so far~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
-The difficulties are attributed to an ambiguous reference since the hard probes themselves are also enhanced by requiring high-multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}.
+Proving the presence of jet quenching would be another crucial milestone to demonstrate the existence of the QGP in high-multiplicity pp collisions.
+However, so far there has been no sign of jet quenching observed in high-multiplicity pp and p--Pb~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
+Since the presence of hard processes contributes to the number of produced particles, and thus the choice of high-multiplicity events results in an increased probability to select events containing jets, these measurements are complicated by the lack of an unambiguous minimally-biased reference system.
+Jet fragmentation can be studied in two-particle correlation functions by looking at short-range correlations around ($\Delta\eta$,$\Delta\varphi$)=(0,0)~\cite{Adam:2016tsv}.
+%The choice of a reference system can thus be ambiguous especially for pp since the hard probes themselves are enhanced by requiring high-multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}, also resulting in enhancement of probability to select events with high-$\pt$ jets.
 %Small system studies: A theory overview 1807.07191 Strickland:2018exs
 %find one more one this regard.
-The ATLAS experiment recently showed that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
-The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in~\cite{Frankfurt:2003td,Frankfurt:2010ea}.
-The microscopic model for collectivity, based on interacting string implemented in $\pythiae$ event generator as so-called the ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
-This challenges the hydrodynamic picture and predicts modifications to jet fragmentation
-properties~\cite{Bierlich:2019ixq}.
+%The ATLAS experiment recently showed that the ridge remains in events tagged with a Z-boson~\cite{Aaboud:2019mcw}, possibly with an accompanying jet.
+%The impact parameter dependence on dijet or multi-jet production in pp collisions was studied in~\cite{Frankfurt:2003td,Frankfurt:2010ea}.
 
@@
 
-To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high-multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high-multiplicity event trigger during the LHC Run 2 data taking period.
+To further investigate the interplay of jet production and collective effects in small systems, we simultaneously studied long- and short-range correlations in very high-multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high-multiplicity event trigger during the LHC Run 2 data taking period.
 In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.
-The results are compared to previous measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
-In addition, we report the ridge yield in events, where a hard scattering took place, to explore possible physical origins of the long-range correlations.
+The results are compared to the previous measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+%In addition, we report the ridge yield in events, where a hard scattering took place, to explore possible physical origins of the long-range correlations.
+In addition, we report the ridge yield and near-side jet-like correlations with event-scale selection.
+The event-scale selection is done by requiring a minimum transverse momentum of leading track or reconstructed jet in mid-rapidity, which is reported to bias the impact parameter of pp collisions to be smaller on average in ~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
 The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, respectively.
-The sources of systematic uncertainties are presented in Sec.~\ref{sec:uncertainties}.
-The results of the measurements and comparisons to model calculations are given in Sec.~\ref{sec:results}.
+The sources of systematic uncertainties are discussed in Sec.~\ref{sec:uncertainties}.
+The results of the measurements and comparisons to model calculations are presented in Sec.~\ref{sec:results}.
 Finally, Sec.~\ref{sec:summary} summarizes the obtained results.

### 2020-11-12 sec_results.tex
after Alice's comments

@@
 	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
-	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in the high-multiplicity (0--0.1\%, left) and the minimum-bias events (0--100\%, right).
-The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < 2$ GeV/$c$.
+	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in high-multiplicity (0--0.1\%, left) and minimum-bias events (0--100\%, right).
+The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < $2 GeV/$c$.
 }
@@
 Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as a function of the $\Delta \eta$ and $\Delta \varphi$ separation of trigger and associated particles.
-The per trigger yield iss measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < 2$ GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
+The per trigger yield is measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < $2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
 The left panel is for the high-multiplicity class.
 The right one is from the minimum bias events.
-The ridge structure is clearly observed in the high-multiplicity class while it is not seen in the minimum bias events.
+The ridge structure is clearly observed in the high-multiplicity class while it is less visible and conclusive in the minimum bias events.
 The away-side yield is populated mostly by correlation of jets which are back-to-back.
@@
 	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for various transverse momentum intervals in each multiplicity class.
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for three transverse momentum intervals in high-multiplicity and minimum bias events.
 The distributions in upper panels are measured with 0--100\% multiplicity class.
 The distribution in lower panels are measured with 0--0.1\% multiplicity class.
-Transverse momentum ranges of trigger particle and associated particle are $1<\pt<2$ (left), $2<\pt<3$ (middle) and $3<\pt<4$ GeV/$c$ (right), respectively.
-The model predictions are presented as colored lines.
-Blue line corresponds to $\pythiashoving$, orange line corresponds to $\pythiam$ and green line corresponds to $\epos$.}
+Transverse momentum ranges of trigger particle and associated particle are $1<\pt<$2 (left), 2$<\pt<$3 (middle) and 3$<\pt<$4 GeV/$c$ (right), respectively.
+The model predictions are presented using $\pythiashoving$, $\pythiam$, and $\epos$.}
 	\label{fig:PlotDeltaPhi}
@@
 
-Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class and the high-multiplicity class.
-The near-side ($\Delta\varphi\sim 0$) peak in high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
-The near-side peak is highest in the interval of $1<\it{p}_{\rm{T}}<2$ GeV/$c$ and gradually decreases with increasing $\it{p}_{\rm{T}}$ in the high-multiplicity class.
-The measurements in the high-multiplicity class are compared to the results measured by the CMS collaboration~\cite{Khachatryan:2015lva}.
-The particle multiplicity in the present analysis is estimated with the forward V0 subsystem, whereas whereas the analysis \cite{Khachatryan:2015lva}  used the mid-rapidity particles in $|\eta|<$2.4 and $\pt>0.4$ GeV/$c$.
-By interpolating the $\eta$ and $\pt{}$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
-The near-side peaks in all transverse momentum ranges are comparable to each other within the uncertainties.
-The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptances.
-The model predictions are presented for the measurements in high-multiplicity class with the identical charged track acceptance and the $\Delta\eta$ projection range to those used in this article.
-The high-multiplicity class for each model is determined by requiring the minimum number of charged particles larger than 105, which corresponds to the top 0--0.1\% multiplicity class based on $\pythiam$.
-The $\pythiashoving$ gives good estimates of the near-side peak and slightly overestimates the away-side yield for the interval of 1$<\it{p}_{\rm{T}}<$2 GeV/$c$.
-However the $\pythiashoving$ underestimates the near-side peak for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
+Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class and the high-multiplicity class down to 1 GeV/$c$ where non-flow contamination is negligible.
+The near-side ($\Delta\varphi\sim 0$) ridge in high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
+Within the range of analyzed particle $\pt$, yield in the near-side ridge decreases with increasing $\pt$ in the high-multiplicity class.
+The measurements in the high-multiplicity class are compared to the results published by the CMS collaboration~\cite{Khachatryan:2015lva}.
+In case of the CMS measurement, charged particle multiplicity was obtained by counting $\pt>0.4$ GeV/$c$ tracks in $|\eta|<$2.4.
+In our analysis, event multiplicity is determined from the forward V0 detectors.
+The difference of multiplicity definition between the ALICE and the CMS was studied based on Pythia8 event generator.
+The mid-rapidity particle distributions are extrapolated using 0--0.1\% event defined by V0M.
+CMS acceptance for counting multiplicity was applied to the extrapolated particle distribution.
+The multiplicity from the distribution is 96, which is about 20\% lower than the multiplicity the CMS used.
+%By interpolating the $\eta$ and $\pt$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
+Near-side ridges in all transverse momentum ranges are comparable to each other within the uncertainties.
+The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in jet acceptance in $\eta$.
+The ALICE data are compared with model predictions where we apply the comparable high-multiplicity selection and $\Delta\eta$ projection range.
+The high-multiplicity class for each model is determined by requiring the minimum number of charged particles larger than 105 in the V0M acceptance, which corresponds to the top 0--0.1\% multiplicity class based on $\pythiam$, where 110 and 108 are corresponding multiplicities for $\epos$ and $\pythiashoving$, respectively.
+The $\pythiashoving$ gives good estimates of the near-side ridge yield and slightly overestimates the away-side yield for the interval of 1$<\it{p}_{\rm{T}}<$2 GeV/$c$.
+However, the $\pythiashoving$ underestimates the near-side ridge yield for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
 $\pythiam$ does not show any peaks in the near-side as expected.
 It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<$2 GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
-On the other hand, $\epos$ describes better $\pt$ dependence quantitatively for the 1$<\it{p}_{\rm{T}}<$4 GeV/$c$ range, while overestimating the near-side peak for the $\it{p}_{\rm{T}}<$2 GeV/$c$ range.
+On the other hand, $\epos$ describes quantitatively better the $\pt$ dependence in the 1$<\it{p}_{\rm{T}}<$4 GeV/$c$ range, while overestimating the near-side ridge yield for the $\it{p}_{\rm{T}}<$2 GeV/$c$ range.
 
@@
 %The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high-multiplicity class and compared to \cite{Khachatryan:2015lva}.
-Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the measurements are comparable with each other.
+Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the slight disagreement between the two sets of results could be expected.
 The spectrum is also compared with model calculations.
 $\pythiam$ gives zero yields since it does not contain the ridge effect.
-$\pythiashoving$ describes the yield qualitatively however its yield decreases more rapidly than the measured data as $\pttrigassoc$ increases.
-$\epos$, unlike $\pythiashoving$, gives estimates for the $\pt$ dependence showing the ridge yield for the $\it{p}_{\rm{T}}>2$ GeV/$c$ range, while estimating larger yield for the $\it{p}_{\rm{T}}<2$ GeV/$c$.
+$\pythiashoving$ describes the yield qualitatively however the predicted yield decreases more rapidly than the measured one as $\pttrigassoc$ increases.
+$\epos$, unlike $\pythiashoving$, describes well the $\pt$ dependence of the ridge yield for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range, while predicting larger yield for $\it{p}_{\rm{T}}<$2 GeV/$c$.
 
@@
 	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
-	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class with the minimum $\ptlead$ (left) or $\ptjet$ (right) selection.
-The interval of $\pttrig$ and $\ptassoc$ is $1<\pt<2$ GeV/$c$.
-The minimum requirement for $\ptlead$ or $\ptjet$ is 9 or 10 GeV/$c$, respectively.
-}
+	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in thigh-multiplicity events where a selection on event-scale was required in addition.
+The interval of $\pttrig$ and $\ptassoc$ is 1$<\pt<$2 GeV/$c$.
+Left: selecting HM events with a $\ptlead>$ 9 GeV/$c$ leading track.
+Right: selecting HM events with a $\ptlead>$ 10 GeV/$c$}
 	\label{fig:PlotCorrHMTSel}
@@
 
-The ridge yield is further studied with respect to two different event-scales of the hard processes.
-Event-scale measurement by the largest $\pt$ of charged particles in each event is denoted as $\ptlead$ while the other is done by reconstructing jets and measuring their transverse momenta, represented as $\ptjet$.
-As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) or $\ptjet>10$~GeV/$c$ (right) .
+The ridge yield is further studied with respect to two different event-scales.
+In the first measurement, the event-scale is set by requiring a minimum $\pt$ cutoff on a leading track in event (denoted as $\ptlead$), while in the second measurement, we impose a minimum $\pt$ cutoff on a leading jet  (denoted as $\ptjet$).
+As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) and $\ptjet>10$~GeV/$c$ (right) .
 %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
-It is worth noting that the correlation function with the minimum $\ptjet$ selection has double peaks along the $\Delta\eta$ axis at $\Delta\varphi = \pi$ due to the jet tagging with the limited jet acceptance in the mid-rapidity as described in this article.
+It is worth noting that the correlation function with the minimum $\ptjet$ selection has a double peak structure which is oriented along $\Delta\eta$ axis at $\Delta\varphi=\pi$.
+This structure emerges due to jet tagging within the limited acceptance in mid-rapidity.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
-	\caption{ One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ with the minimum $\ptlead$(lower) or $\ptjet$(upper) selection for $1< \pttrig~\mathrm (\ptassoc) <2$ GeV/$c$ in the 0--0.1\% multiplicity class.
-The filled circles show the ALICE measurement.
-Model predictions are presented with a blue line for $\pythiam$, an orange line for $\pythiashoving$ and a green line for $\epos$.}
+	\caption{ $\Delta\varphi$ projections of the correlation function constrained to 1.6$<|\Delta\eta|<$1.8 in HM events with additional event-scale bias.
+Top: imposing a cut on leading jet,  bottom: imposing a cut on leading hadron.
+ALICE data are compared with prediction of models.}
 	\label{fig:PlotDeltaPhiESE}
@@
 Even with the event-scale selection, the ridge is still visible at the near-side.
-The near-side yield increases as the threshold of $\ptjet$ increases compared to one measured in unbiased events, while the ridge yields for an increasing threshold of $\ptlead$ increase less than those of $\ptjet$.
+The near-side ridge peak increases as the thresholds of $\ptlead$ and $\ptjet$ increase compared to the one measured in unbiased events.
 The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations.
-The near-side peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$, while underestimated by $\pythiashoving$ and overestimated by $\epos$.
-On the other hand, $\pythiam$ does not show the near-side peak with the event-scale selections, while giving similar estimates for away-side yield as $\pythiashoving$.
+Near-side ridge peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$.
+On the other hand, $\pythiam$ does not show the  near-side ridge peak for neither of the two event-scale selection, but it gives compatible results for the away-side yield as $\pythiashoving$.
 %Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
-	\caption{The ridge yield spectra with respect to the leading particle and jet selections.
+	\includegraphics[width=0.89\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
+	\caption{The ridge yield with respect to the leading particle(left) and jet selections(right).
 The filled circles show measurement with ALICE.
-Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$.
-Ratios of measured data to models are prepared for $\pythiashoving$ and $\epos$.}
+The measurements are compared with model descriptions from $\pythiam$, $\pythiashoving$, and $\epos$ for both selections.}
 	\label{fig:RidgeYield_ESE}
@@
 
-Finally, the ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-The ridge yields are increased for $\it{p}^{\rm{LP}}_{\rm{T,min}} >$ 7 and $\it{p}^{\rm{Jet}}_{\rm{T,min}} \ge$ 10~GeV/$c$ compared to one from the unbiased events.
-A moderate increase of the ridge yields toward higher $\ptlead$ or $\ptjet$ is observed and there is no difference between two event selections within the uncertainties.
+The ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+Events with imposed event-scale show  increased ridge yields when compared to unbiased HM events.
+A moderate increase of the ridge yields as a function of higher $\ptlead$ or $\ptjet$ is observed and there is no difference between the two event selections within the uncertainties.
 The results are compared with $\pythiashoving$, $\pythiam$ and $\epos$.
-$\pythiashoving$ describes comparable trend with data, underestimating the ridge yield.
-On the other hand, $\epos$ also describes comparable trend with data, overestimating the ridge yield.
+$\pythiashoving$ gives comparable trend with data, underestimating the ridge yield.
+On the other hand, $\epos$ also describes comparable trend with the data, but overestimates the ridge yield.
 The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
@@
 	\centering
-	\includegraphics[width=0.99\linewidth]{./figures/Fig9_JetYieldESE.pdf}
-	\caption{The jet yield spectra with respect to the leading particle (left) and jet selections (right).
+	\includegraphics[width=0.89\linewidth]{./figures/Fig9_JetYieldESE.pdf}
+	\caption{ Near-side jet-like peak yield with respect to the minimum leading particle(left) and jet selections(right).
 The filled circles show measurement with ALICE.
-Model predictions are compared to measurement as blue lines for $\pythiam$, orange lines for $\pythiashoving$ and green lines for $\epos$.}
-	\label{fig:RidgeYield_ESE}
+The measurements are compared with model descriptions from $\pythiam$, $\pythiashoving$, and $\epos$ for both selections.}
+	\label{fig:JetYield_ESE}
 \end{figure}
 
-Jet yield has been measured as a function of minimum $\ptlead$ and $\ptjet$ threshold to further discuss ridge yields and jet yields.
+Finally, Near-side jet-like peak yield was measured as a function of minimum $\ptlead$ and $\ptjet$ threshold in Fig.~\ref{fig:JetYield_ESE} to further test the models that aim to describe the near-side ridge.
 %quantify the trend of the jet yield.
-$\epos$ provides comparable estimates for jet yields, while $\pythiam$ and $\pythiashoving$ overestimate jet yields for both selections.
-Increasing trend of jet yield as a function of minimum $\ptlead$ and saturating trend of jet yield as a function of minimum $\ptjet$ have been observed and estimated by models.
-Jet yield measured with $\ptlead>$20~GeV/$c$ is comparable with the one measured with $\ptjet>$10~GeV/$c$, where ridge yields with corresponding selections are also comparable.
+$\epos$ provides comparable estimates for near-side yields, while $\pythiam$ and $\pythiashoving$ overestimate near-side yields for both selections.
+Increasing trend of near-side yield as a function of minimum $\ptlead$ and saturating trend of near-side yield as a function of minimum $\ptjet$ have been observed, which are also qualitatively explained by models.
+Near-side jet-like peak yield measured with $\ptlead>$20~GeV/$c$ is comparable with the one measured with $\ptjet>$10~GeV/$c$, where ridge yields with corresponding selections are also comparable.

### 2020-11-12 sec_summary.tex
after Alice's comments

@@
 \label{sec:summary}
-Long-range azimuthal correlations are studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV.
-These results are obtained in the relative pseudorapidity range $1.6 < |\Delta\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles.
-The results are compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+Long-range azimuthal correlations were studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV.
+These results were obtained in the relative pseudorapidity range $1.6 < |\Delta\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles.
+The results were compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
 %In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
-$\pythiashoving$ describes the yield qualitatively but its yield is decreased more rapidly than the data as $\pttrigassoc$ increases.
+$\pythiashoving$ describes the yield qualitatively but the predicted yield decreases more rapidly than the data as $\pttrigassoc$ increases.
 On the other hand, $\epos$ gives better description for $\pt$ dependence while overestimating the ridge yield in the low $\pt<$2 GeV/$c$.
-$\pythiam$ does not describe the ridge in the long-range, which gives closure of the results against non-flow contamination.
+$\pythiam$ does not describe the ridge in the long-range.
 %Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
@@
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
-Furthermore the ridge yields are studied with the event-scale selections through the minimum transverse momentum of jet or leading particle requirement, which are more prone of requiring harder processes in pp collisions.
+Furthermore the ridge yields were studied with the event-scale selections through the minimum transverse momentum of jet or leading particle requirement. 
 The ridge structure still persists with both selections.
 The ridge yields increase as $\ptlead$ and $\ptjet$ increase.
-The latter, however, is more significant than the former selection.
-The results are compared with $\pythiashoving$, $\epos$ and $\pythiam$ calculations, where $\pythiam$ also provides closure against non-flow contamination by estimate ridge yield to be zero with event-scale selections.
+The results are compared with $\pythiashoving$, $\epos$ and $\pythiam$ calculations.
 $\pythiashoving$ and $\epos$ estimate qualitative trends for event-scale selection.
-The former underestimates the ridge yield, unlike the latter overestimating the ridge yield.
+However, the former underestimates the ridge yield and the latter overestimates the ridge yield.
+Responses to event-scale selection are further studied by measuring near-side jet-like correlations.
+$\epos$ provides better description for near-side jet-like correlations with the event-scale selection, while $\pythiashoving$ overestimates near-side jet-like correlations, which results in opposite trends between the ridge yield and near-side jet-like correlations.
 The results might open new way of studying impact parameter dependence of the small systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-11-12 abstract.tex
also abstract file to be consistent

--- 2020-04-23 abstract.tex
@@
-The observed azimuthal modulations of long-range correlations in pseudorapidity in small systems like pp or p-Pb collisions show strikingly similar features to those seen in heavy ion collisions.
-Many theoretical approaches to interpreting this effect have been developed.
-However, it is still unclear whether these long-range correlations are due to final or initial state effects.
-To further investigate these effects, we studied long-range correlations as a function of transverse momentum in very high multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high multiplicity event trigger during 2016 and 2017 with ALICE.
-In this talk, we present the near-side per-trigger yield at large pseudorapidity separation (ridge yield) as a function of transverse momentum in pp collisions at $\sqrt{s} =13$ TeV.
-The results are compared to previous measurements from CMS experiments.
-In addition, we present the ridge yield in events where harder fragmentation processes are present, to explore possible physical origins of long-range correlations.
+We report on the studies of two-particle angular correlations measured in high-multiplicity proton-proton collisions at $\sqrt{s} =13$ TeV with ALICE. 
+The yields of two-particle angular correlations at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity are measured at the near side ($\Delta\varphi \sim 0$).
+The correlations and yields are reported as a function of charged-particle transverse momentum ($p_{\mathrm T}$) in $1 < p_{\mathrm T} < 5$ GeV/$c$.
+Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 
+The results demonstrate that the long-range ``ridge`` yield, related to the collective behavior of the produced system, is present in events with high-$p_{\mathrm T}$ processes.
+The magnitudes of the short- and long-range yields are found to grow with the event scale.
+The results have been compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
+It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependences.

### 2020-11-12 paper.tex
final after Alice

@@
 %%% Put your own title + short title here:
-\title{Long- and short-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
+\title{Long- and short-range correlations and their event scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
 \ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
@@
 %\input{abstract.tex}
-We report on the studies of two-particle angular correlations measured in high-multiplicity proton-proton collisions at $\sqrt{s} =13$ TeV with ALICE. 
-The yields of two-particle angular correlations at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity are measured at the near side ($\Delta\varphi \sim 0$).
-The correlations and yields are reported as a function of charged-particle transverse momentum ($p_{\mathrm T}$) in $1 < p_{\mathrm T} < 5$ GeV/$c$.
+Two-particle angular correlations have been measured in high-multiplicity $\sqrt{s} =13$ TeV proton-proton collisions by the ALICE collaboration.
+From the correlations, the yields of particle pairs at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity have been extracted on the near side ($\Delta\varphi$ $\sim$ 0).
+The correlations and yields are reported as a function of transverse momentum ($p_{\mathrm T}$) in the range 1$ < p_{\mathrm T} < $5 GeV/$c$.
 Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 

### 2020-11-17 paper.tex
Updates after Q3

@@
 From the correlations, the yields of particle pairs at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity have been extracted on the near side ($\Delta\varphi$ $\sim$ 0).
-The correlations and yields are reported as a function of transverse momentum ($p_{\mathrm T}$) in the range 1$ < p_{\mathrm T} < $5 GeV/$c$.
+The correlations and yields are reported as a function of transverse momentum ($p_{\mathrm T}$) in the range 1$ < p_{\mathrm T} < $4 GeV/$c$.
 Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 
@@
 The results have been compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
-It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependences.
+It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependencies.
 

### 2020-11-17 sec_ana.tex
Updates after Q3

@@
 The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within the pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
-The V0 is used to assess event activity and it provides minimum bias (MB) and high-multiplicity (HM) trigger.
+The V0 is used to assess event activity and it provides a minimum bias (MB) and a high-multiplicity (HM) trigger.
 The minimum bias trigger is obtained by a time coincidence of V0A and V0C signals.
-The high multiplicity trigger requires that amplitude of the combined V0A and V0C signal exceeds 5 times the mean value measured in minimum bias collisions, providing top 0.1\% events of MB events.
+The event activity selection is done on the sum of the V0A and V0C signals, which is denoted V0M.
+The high multiplicity trigger requires that the V0M signal exceeds 5 times the mean value measured in minimum bias collisions, selecting the top 0.1\% of MB events that have the largest V0 multiplicity.
 
 Charged particles are reconstructed by the ITS and TPC, which are working in a uniform solenoidal magnetic field of 0.5~T.
-The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD), and Silicon Strip Detector (SSD).
+The ITS is a silicon tracker with six layers of sensors.
+The two innermost layers are formed by the Silicon Pixel Detector (SPD)~\cite{Santoro2009:ALICESPD}.
+%The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD), and Silicon Strip Detector (SSD).
 You can find more details about SPD in~\cite{Santoro2009:ALICESPD}.
-The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles with a primary vertex in $|z_\mathrm{vtx}| < 8$~cm.
+The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles emitted from a primary vertex with $|z_\mathrm{vtx}| < 8$~cm.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
 The efficiency goes up to 80\% for intermediate transverse momentum, 1--5~GeV/$c$.
-The transverse momentum resolution is around 1\% for primary tracks with low $\pt<$1~GeV/$c$, and linearly degrades up to 6\% at $\pt \sim$ 40~GeV/$c$~\cite{Contin_2012:ITSPTRES}.
+The transverse momentum resolution is around 1\% for primary tracks with low $\pt<$1~GeV/$c$, and linearly increases up to 6\% at $\pt \sim$ 40~GeV/$c$~\cite{Contin_2012:ITSPTRES}.
 %https://arxiv.org/pdf/1910.14400.pdf
@@
 
-The analyzed data samples of minimum-bias and high-multiplicity pp $\sqrt{s}=$13 TeV events correspond to integrated luminosities of 19 nb$^{-1}$ and 11.4 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
+The analyzed data samples of minimum-bias and high-multiplicity pp $\sqrt{s}=$13 TeV events correspond to integrated luminosities of 19 nb$^{-1}$ and 11 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
 
@@
 Pileup events can be resolved and rejected if the longitudinal displacement of their primary vertices is larger than 0.8 cm.
-The probability of pileup is estimated to be 0.6\%.
 
+%The probability of pileup is estimated to be 0.6\%.
 %Requirements for reconstruction of charged particles are optimized to have the flat angular distribution of charged particles that is called hybrid tracks to minimize the effect of inactive regions of the ITS and TPC detectors~\cite{hybridExplanation}.
@@
 Tracks from the first class are required to have at least one hit in the SPD.
-Tracks from the second class do not have any SPD associated hit and their initial point is instead constrained to the primary vertex.
+Tracks from the second class do not have any SPD associated hit and their initial point is instead constrained to the primary vertex~\cite{20151:HybridTracks}.
 
-The two-particle correlations function is measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences ($\Delta\varphi$) between the trigger and associated particles,
+The two-particle correlation function is measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences ($\Delta\varphi$) between the trigger and associated particles,
 \begin{eqnarray}
@@
 where $\pttrig$ and $\ptassoc$ are transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles and $N_\mathrm{pair}$ is the number of trigger-associated particle pairs.
-$N_\mathrm{trig}$ and $N_\mathrm{pair}$ were corrected for track reconstruction efficiencies as $N_\mathrm{trig,cor} = N_\mathrm{trig}/ \epsilon_{\rm{trig}}$ and $N_\mathrm{pair,cor} = N_\mathrm{pair}/(\epsilon_{\rm{trig}}\epsilon_{\rm{assoc}})$ for a given $\pt$ and $\eta$, respectively.
-$S (\Delta\eta, \Delta\varphi)$ is constructed using two-particle correlations in the same event and $B(\Delta\eta, \Delta\varphi)$ in mixed events.
-$B(\Delta\eta, \Delta\varphi)$ is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
-Primary vertices of events to be mixed are required to be within the same, 2 cm wide $z_{vtx}$ bin.
+$S (\Delta\eta, \Delta\varphi)$ is the average number of pairs in the same event and $B(\Delta\eta, \Delta\varphi)$ in mixed events.
+$B(\Delta\eta, \Delta\varphi)$ is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$, so that it corrects for acceptance effects.
+The right-hand side of Eq.
+1 had been corrected for the track reconstruction efficiency, which is mainly relevant for the associated particles.
+Primary vertices of events to be mixed are required to be within the same, 2 cm wide $z_{\rm{vtx}}$ bin.
 The final per-trigger yield is constructed by averaging correlation functions over these primary vertex bins.
@@
 Ridge yields at large $\Delta\eta$ are extracted for various multiplicity classes and transverse momentum intervals.
-The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$, where non-flow effects (mainly coming from jets) are negligible on the near-side.
+The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$,  which is the maximum $\delta\eta$ range one can use for the ALICE measurements.
+At low $\pt$, the jet-like correlations extend into this region and for this reason the ridge yield is only reported for $\pt>$~1GeV/$c$.
+The $\delta\Delta\eta$ is the normalization factor to get per-trigger yield per unit pseudorapidity.
 In this region, the $\Delta\varphi$ distribution, or the so called per-trigger yield is expressed as
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \rm{d} \Delta \eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\eta} \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \rm{d} \Delta \eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\eta} - C_{\rm{ZYAM}} \quad.
 \end{eqnarray}
@@
 
-The ridge yield is further studied in events having a hard jet or a high-$\pt$ leading particle in the mid rapidity.
-Such requirement is expected to bias impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+The ridge yield is further studied in events having a hard jet or a high-$\pt$ leading particle in the mid-rapidity region.
+Such requirement is expected to bias the impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
 %The ridge yield is further studied by exploiting the largest momentum transfer among the initial partons in a given event, which results from the hard scattering.
@@
 Jets are reconstructed with charged particles only (track-based jets) with the anti-$k_{\rm{T}}$ algorithm~\cite{Cacciari2008:FASTJET,Cacciari2012:FASTJET} and the resolution parameter $R=$~0.4.
-The recombination scheme used in this article is $\pt$ scheme.
+The recombination scheme used in this article is the $\pt$ scheme.
 Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
@@
 
-To quantify variation of near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $p_\mathrm{T,\,jet}$, neat-side jet-like peak is extracted from near-side $\Delta\eta$ correlations.
-The near-side is defined as $|\Delta\varphi|<$1.28, where the correlations function is projected along to $\Delta\varphi$ direction for 1$<\pttrig$, $\ptassoc<$2 GeV/$c$ in high-multiplicity events.
+To quantify variation of near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $p_\mathrm{T,\,jet}$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
+The near-side is defined as $|\Delta\varphi|<$1.28, where the correlation function is projected on the $\Delta\eta$ axis.
+The $\delta\Delta\varphi$ is the normalization factor to get per-trigger yield per unit azimuthal angle.
 The near-side $\Delta\eta$ correlations are constructed as
@@
 
-The baseline of the $\Delta\eta$ correlations is also subtracted by using the ZYAM procedure.
+The baseline of the $\Delta\eta$ correlation is also subtracted by using the ZYAM procedure.
 The minimum yield $(C_{\rm{ZYAM}})$ of $\Delta\eta$ correlations is found within $|\Delta\eta|<$1.6 and used for subtraction from  $\Delta\eta$ correlations, which results in zero-yield at minimum.
@@
 
-Systematic uncertainties on $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ were estimated by varying the analysis selection criteria and corrections and evaluated as functions of $\pttrig$($\ptassoc$) and $\ptlead$ or $\ptjet$ as described in Tab.~\ref{tab:syst}.
+Systematic uncertainties on $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ were estimated by varying the analysis selection criteria and corrections, which will be explained in the following in more detail.
+Tab.~\ref{tab:syst} summarizes the obtained values.
 $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ denotes the ridge yield as a function of $\pttrig$($\ptassoc$) in event-scale unbiased events.
@@
 \begin{table}[h!]
-\caption{The relative systematic uncertainty on the associated yield spectrum estimated for $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$, $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and, $Y^{\rm{near}}$, respectively.}
+\caption{The relative systematic uncertainty on the associated yield spectrum estimated for $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$, $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and $Y^{\rm{near}}$, respectively.}
 \centering
@@
 
-The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
-The multiplicity of the track contributors to each vertex determines whether the event is contaminated by pileup or not.
-The variation is set by the minimum multiplicity of track contributors from 5 to 3.
+The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from The main variation concerned reduction of the minimal number of track contributors required for vertex reconstruction from 5 to 3.
 The estimated uncertainty is 0.8\% for events without event-scale bias.
 The uncertainty varies up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
-The corresponding uncertainty on $Y^{\rm{near}}$ is 0.2–-2.2\%.
+The corresponding uncertainty on $Y^{\rm{near}}$ is 0.2--2.2\%.
 %Pileup cut (multbins) -> (default pileup from the physics selection)
@@
 
-The uncertainty from the primary vertex selection along the beam axis is estimated by varying the selection range of primary vertex from $|z_\mathrm{vtx}|<$ 8 to 6 cm.
+Another source of systematic uncertainty is related to the selected range of primary vertex.
+The accepted range was varied from $|z_\mathrm{vtx}|<$ 8 cm to $|z_\mathrm{vtx}|<$ 6 cm.
 The narrower primary vertex selection allows one to test the acceptance effect on the measurement.
@@
 
-The uncertainty from the track selection is estimated by varying from the hybrid tracks to the other one optimized for particle identification that is called the global tracks.
+A Further source of systematic uncertainty is related to the imposed track selection criteria.
+The corresponding uncertainty was estimated by employing other track selection criteria, denoted global tracks, which are optimized for particle identification.
 The selection criteria of the global tracks are almost identical to the hybrid tracks.
@@
 %except for the requirement of at least one hit on the SPD.
-Due to the requirement, the quality of the global tracks is sensitive to the condition of the SPD, finally resulting in a non-flat azimuthal distribution of charged particles with the selection. 
+Due to inefficient parts of the SPD, azimuthal distribution of global tracks is not flat.
 %The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The uncertainty associated to the variation of the track selections is estimated to be 4.0\%.
+The uncertainty associated with the track selection criteria variation is estimated to be 4.0\%.
 The uncertainty was obtained by averaging relative variations over different transverse momentum ranges.
@@
 Systematic uncertainty resulting from the ZYAM procedure was estimated by varying the range of the fit, which is used to find the minimum, from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$.
-The estimated uncertainty is 5.1\% without event-scale bias.
-The uncertainty varies to 2\% for events with the $\ptlead$ or $\ptjet$ selection.
-The uncertainty for $Y^{\rm{near}}$ is not considered due to negligible deviation compared with statistical fluctuation.
-The uncertainty from the jet contamination is estimated by varying the $\Delta\eta$ projection range to see how much the jet contamination varies, which is thought be small.
-The estimated uncertainty is 3.4--9.4\% with the varying event-scale selection.
-The uncertainty for $Y^{\rm{near}}$ is not considered as the jet yield is observables.
+In case of the ridge yields that were measured in events where event-scale bias was not imposed, the estimated uncertainty is 5\%.
+On the other hands, this uncertainty is about 2\% for the ridge yields obtained in events with the $\ptlead$ or $\ptjet$ bias.
+The corresponding uncertainty on $Y^{\rm{near}}$ is not considered due to negligible deviation compared with statistical uncertainty.
+A similar source of systematic uncertainty represents the possible contamination of the ridge yield by jet fragments.
+The uncertainty was estimated by varying the $\Delta\eta$ projection range from 1.7$<\Delta\eta<$1.8 to 1.4$<\Delta\eta<$1.8 in order to see how much the jet contamination varies, which is thought be small.
+The estimated uncertainty is about 3.4--9.4\%.
+This uncertainty was considered only for the measured ridge yields.
 
-The uncertainty from the event mixing $z_{vtx}$ bin of primary vertex is estimated by varying the interval size from 2 to 1 cm.
-The estimated uncertainty is 1.0--16.4\% with the varying event-scale selection.
-The uncertainty for $Y^{\rm{near}}$ is estimated to be 0.5--1.7\%.
+The final source of systematic uncertainty is associated to the choice of the width of $z_{\rm vtx}$ bins that are used in event mixing.
+The default value 2\,cm was changed to 1\,cm.
+The resulting uncertainty on ridge yield was estimated to be 1--16.4\%.
+The corresponding uncertainty on $Y^{\rm{near}}$ is about 0.5--1.7\%.
 The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.

### 2020-11-17 sec_intro.tex
Updates after Q3

@@
 
-Furthermore, if collectivity in small systems is due to final-state interactions, it is expected to have an effect on jets.
-Proving the presence of jet quenching would be another crucial milestone to demonstrate the existence of the QGP in high-multiplicity pp collisions.
-However, so far there has been no sign of jet quenching observed in high-multiplicity pp and p--Pb~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
-Since the presence of hard processes contributes to the number of produced particles, and thus the choice of high-multiplicity events results in an increased probability to select events containing jets, these measurements are complicated by the lack of an unambiguous minimally-biased reference system.
-Jet fragmentation can be studied in two-particle correlation functions by looking at short-range correlations around ($\Delta\eta$,$\Delta\varphi$)=(0,0)~\cite{Adam:2016tsv}.
+If collectivity in small systems is due to final-state interactions, it is expected 
+that these final-state interactions will affect also produced jets.
+Proving the presence of jet quenching would be another crucial evidence of the existence of the QGP in high-multiplicity pp collisions.
+However, so far there has been no sign of jet quenching observed in high-multiplicity pp and p--Pb collisions~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
+Jet fragmentation can be studied in two-particle correlation functions by looking at short-range correlations around $(\Delta\eta$,$\Delta\varphi)=(0,0)$~\cite{Adam:2016tsv}.
 %The choice of a reference system can thus be ambiguous especially for pp since the hard probes themselves are enhanced by requiring high-multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}, also resulting in enhancement of probability to select events with high-$\pt$ jets.
@@
 In addition, we report the ridge yield and near-side jet-like correlations with event-scale selection.
-The event-scale selection is done by requiring a minimum transverse momentum of leading track or reconstructed jet in mid-rapidity, which is reported to bias the impact parameter of pp collisions to be smaller on average in ~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+The event-scale selection is done by requiring a minimum transverse momentum of leading track or reconstructed jet in mid-rapidity, which is expected to bias the impact parameter of pp collisions to be smaller on average ~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
 The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, respectively.

### 2020-11-17 sec_results.tex
Updates after Q3

@@
 
-Figure~\ref{fig:PlotCorrMBHMT} shows two-particle correlation functions as a function of the $\Delta \eta$ and $\Delta \varphi$ separation of trigger and associated particles.
-The per trigger yield is measured with Eq.~\ref{eq:corrfunction} for $1 < \pttrig~\mathrm (\ptassoc) < $2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV}.
-The left panel is for the high-multiplicity class.
-The right one is from the minimum bias events.
+Figure~\ref{fig:PlotCorrMBHMT} shows the per-trigger yield obtained from Eq.
+1 for $1 < \pttrig~\mathrm (\ptassoc) < $2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for high-multiplicity (left) and minimum bias events (right panel).
 The ridge structure is clearly observed in the high-multiplicity class while it is less visible and conclusive in the minimum bias events.
-The away-side yield is populated mostly by correlation of jets which are back-to-back.
+The away-side yield is populated mostly by back-to-back jet correlations.
 
@@
 	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for three transverse momentum intervals in high-multiplicity and minimum bias events.
-The distributions in upper panels are measured with 0--100\% multiplicity class.
-The distribution in lower panels are measured with 0--0.1\% multiplicity class.
-Transverse momentum ranges of trigger particle and associated particle are $1<\pt<$2 (left), 2$<\pt<$3 (middle) and 3$<\pt<$4 GeV/$c$ (right), respectively.
-The model predictions are presented using $\pythiashoving$, $\pythiam$, and $\epos$.}
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for three transverse momentum intervals in high-multiplicity (lower panels) and minimum bias (upper panels) events after ZYAM subtraction.
+Transverse momentum ranges of trigger particles and associated particles are $1<\pt<$2 (left), 2$<\pt<$3 (middle) and 3$<\pt<$4 GeV/$c$ (right), respectively.
+The presented model predictions were calculated using $\pythiashoving$, $\pythiam$, and $\epos$.}
 	\label{fig:PlotDeltaPhi}
@@
 
-Projected $\Delta\varphi$ distributions of the two-particle correlation functions in $1.6<|\Delta\eta|<1.8$ are shown in Fig.~\ref{fig:PlotDeltaPhi} for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class and the high-multiplicity class down to 1 GeV/$c$ where non-flow contamination is negligible.
-The near-side ($\Delta\varphi\sim 0$) ridge in high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
+Figure~\ref{fig:PlotDeltaPhi} shows Delta phi projections of the two-particle correlation functions obtained in the range 1.6$<|\Delta \eta |<$1.8 for several track $\pt$ intervals after ZYAM subtraction, see Eq.
+2.
+Results are shown for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (upper) and the high-multiplicity class (lower) down to 1 GeV/$c$ where non-flow contamination is negligible.
+The near-side ($\Delta\varphi\sim 0$) ridge in the high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
 Within the range of analyzed particle $\pt$, yield in the near-side ridge decreases with increasing $\pt$ in the high-multiplicity class.
@@
 In our analysis, event multiplicity is determined from the forward V0 detectors.
-The difference of multiplicity definition between the ALICE and the CMS was studied based on Pythia8 event generator.
-The mid-rapidity particle distributions are extrapolated using 0--0.1\% event defined by V0M.
-CMS acceptance for counting multiplicity was applied to the extrapolated particle distribution.
-The multiplicity from the distribution is 96, which is about 20\% lower than the multiplicity the CMS used.
-%By interpolating the $\eta$ and $\pt$ distributions based on PYTHIA, it is found that the multiplicity in \cite{Khachatryan:2015lva} is about 20\% higher than 0--0.1\% in this analysis, corresponding 0--0.03\%.
+The difference in multiplicity selection between ALICE (forward) and CMS (mid-rapidity) was studied using PYTHIA 8 simulations and it was found that the CMS multiplicity is ${\approx}20\,\%$ larger than the ALICE one when compared in the acceptance region of the measurements reported here, $|\eta|<$0.9.
 Near-side ridges in all transverse momentum ranges are comparable to each other within the uncertainties.
-The larger away yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in jet acceptance in $\eta$.
-The ALICE data are compared with model predictions where we apply the comparable high-multiplicity selection and $\Delta\eta$ projection range.
-The high-multiplicity class for each model is determined by requiring the minimum number of charged particles larger than 105 in the V0M acceptance, which corresponds to the top 0--0.1\% multiplicity class based on $\pythiam$, where 110 and 108 are corresponding multiplicities for $\epos$ and $\pythiashoving$, respectively.
+The larger away-side yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptance for the multiplicity selection, which overlaps somewhat with the $\eta$ region in Fig.~\ref{fig:PlotDeltaPhi} for CMS results.
+The ALICE data are compared with model predictions where we apply a comparable high-multiplicity selection and $\Delta\eta$ projection range.
+Selection of high-multiplicity events in models was done by requiring a minimal number of charged particles that pass the V0M acceptance.
+This threshold was set to 105, which was tuned to reach the top 0-0.1\% centrality selection using $\pythiam$.
+The threshold for $\epos$ or $\pythiashoving$ is 110 or 108, respectively.
 The $\pythiashoving$ gives good estimates of the near-side ridge yield and slightly overestimates the away-side yield for the interval of 1$<\it{p}_{\rm{T}}<$2 GeV/$c$.
-However, the $\pythiashoving$ underestimates the near-side ridge yield for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
-$\pythiam$ does not show any peaks in the near-side as expected.
-It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<$2 GeV/$c$ and gives good estimates for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range.
-On the other hand, $\epos$ describes quantitatively better the $\pt$ dependence in the 1$<\it{p}_{\rm{T}}<$4 GeV/$c$ range, while overestimating the near-side ridge yield for the $\it{p}_{\rm{T}}<$2 GeV/$c$ range.
+However, the $\pythiashoving$ underestimates the near-side ridge yield for $\it{p}_{\rm{T}}>$2 GeV/$c$.
+$\pythiam$ does not show any near-side ridge as expected.
+It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<$2 GeV/$c$ and gives good estimates for $\it{p}_{\rm{T}}>$2 GeV/$c$.
+On the other hand, $\epos$ describes quantitatively better the $\pt$ dependence in the 2$<\it{p}_{\rm{T}}<$4 GeV/$c$ range, while overestimating the near-side ridge yield for the $\it{p}_{\rm{T}}<$2 GeV/$c$ range.
 
@@
 The filled circles denote the measurement with ALICE.
-The CMS measurement~\cite{Khachatryan:2015lva} is represented by open blue box markers.
+The CMS measurement~\cite{Khachatryan:2015lva} is represented by open blue box markers and extends down to lower $\pt$ due to the larger $\Delta\eta$ acceptance.
 The three lines show model predictions from $\pythiam$ (blue line), $\pythiashoving$ (orange line) and $\epos$ (green line).}
@@
 
-Fig.~\ref{fig:PlotYSpect} shows the near-side ridge yield measured in high-multiplicity events as a function of transverse momentum. The ALICE data are compared to \cite{Khachatryan:2015lva}.
+Figure~\ref{fig:PlotYSpect} shows the near-side ridge yield measured in high-multiplicity events as a function of transverse momentum.
+The ALICE data are with results from CMS~\cite{Khachatryan:2015lva}.
 %The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high-multiplicity class and compared to \cite{Khachatryan:2015lva}.
-Taking into account the differences in acceptance of charged tracks and estimated multiplicity, the slight disagreement between the two sets of results could be expected.
-The spectrum is also compared with model calculations.
-$\pythiam$ gives zero yields since it does not contain the ridge effect.
-$\pythiashoving$ describes the yield qualitatively however the predicted yield decreases more rapidly than the measured one as $\pttrigassoc$ increases.
+Taking into account the differences in acceptance of both measurements and chosen multiplicity estimator, the slight disagreement between the two sets of results could be expected.
+The data is also compared with model calculations.
+$\pythiam$ gives zero ridge yields since it does not account for the ridge effect.
+$\pythiashoving$ describes the yield qualitatively.
+however the predicted yield decreases more rapidly than the measured one as $\pttrigassoc$ increases.
 $\epos$, unlike $\pythiashoving$, describes well the $\pt$ dependence of the ridge yield for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range, while predicting larger yield for $\it{p}_{\rm{T}}<$2 GeV/$c$.
@@
 	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
-	\caption{ Two-dimensional correlations function as a function of $\Delta\eta$ and $\Delta\varphi$ in thigh-multiplicity events where a selection on event-scale was required in addition.
+	\caption{ Two-dimensional correlation functions as a function of $\Delta\eta$ and $\Delta\varphi$ in high-multiplicity events where a selection on event-scale was required in addition.
 The interval of $\pttrig$ and $\ptassoc$ is 1$<\pt<$2 GeV/$c$.
-Left: selecting HM events with a $\ptlead>$ 9 GeV/$c$ leading track.
-Right: selecting HM events with a $\ptlead>$ 10 GeV/$c$}
+Left: HM events with a $\ptlead>$ 9 GeV/$c$ leading track.
+Right: HM events with a $\ptlead>$ 10 GeV/$c$.}
 	\label{fig:PlotCorrHMTSel}
@@
 In the first measurement, the event-scale is set by requiring a minimum $\pt$ cutoff on a leading track in event (denoted as $\ptlead$), while in the second measurement, we impose a minimum $\pt$ cutoff on a leading jet (denoted as $\ptjet$).
-As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) and $\ptjet>10$~GeV/$c$ (right) .
+As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) and $\ptjet>10$~GeV/$c$ (right).
 %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
-It is worth noting that the correlation function with the minimum $\ptjet$ selection has a double peak structure which is oriented along $\Delta\eta$ axis at $\Delta\varphi=\pi$.
-This structure emerges due to jet tagging within the limited acceptance in mid-rapidity.
+It is worth noting that the correlation function obtained with the minimum $\ptjet$ selection has a double peak structure which is oriented along the $\Delta\eta$ axis at $\Delta\varphi=\pi$.
+This structure emerges due to the restricted acceptance of jet tagging, $|\eta_{\rm{jet}}|<$0.4.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
-	\caption{ $\Delta\varphi$ projections of the correlation function constrained to 1.6$<|\Delta\eta|<$1.8 in HM events with additional event-scale bias.
-Top: imposing a cut on leading jet,  bottom: imposing a cut on leading hadron.
+	\caption{ $\Delta\varphi$ projections of the correlation functions constrained to 1.6$<|\Delta\eta|<$1.8 in HM events with an additional event-scale bias.
+Top: with an imposed cut on leading jet $\pt$,  bottom: with an imposed cut on leading hadron $\pt$.
 ALICE data are compared with prediction of models.}
@@
 Near-side ridge peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$.
-On the other hand, $\pythiam$ does not show the  near-side ridge peak for neither of the two event-scale selection, but it gives compatible results for the away-side yield as $\pythiashoving$.
+On the other hand, $\pythiam$ does not show the  near-side ridge peak for neither of the two event-scale selections, but it gives compatible results for the away-side yield as $\pythiashoving$.
 %Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
@@
 	\includegraphics[width=0.89\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
-	\caption{The ridge yield with respect to the leading particle(left) and jet selections(right).
-The filled circles show measurement with ALICE.
-The measurements are compared with model descriptions from $\pythiam$, $\pythiashoving$, and $\epos$ for both selections.}
+	\caption{Near-side ridge yield as a function of the $\ptlead$ (left) and $\ptjet$ (right) bias.
+Data points (filled circles) show the ALICE measurement.
+They are compared to predictions of models which are represented by color bands.
+The bottom panel shows a ratio of the models to the data.
+The uncertainty on the data is represented by the gray band centered around unity.}
 	\label{fig:RidgeYield_ESE}
@@
 The ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
-Events with imposed event-scale show  increased ridge yields when compared to unbiased HM events.
-A moderate increase of the ridge yields as a function of higher $\ptlead$ or $\ptjet$ is observed and there is no difference between the two event selections within the uncertainties.
-The results are compared with $\pythiashoving$, $\pythiam$ and $\epos$.
-$\pythiashoving$ gives comparable trend with data, underestimating the ridge yield.
-On the other hand, $\epos$ also describes comparable trend with the data, but overestimates the ridge yield.
+High-multiplicity events with imposed event-scale bias exhibit increased ridge yields when compared to unbiased HM events.
+A moderate increase of the ridge yields as a function of $\ptlead$ or $\ptjet$ is observed and there is no difference between the two event selections within the uncertainties.
+Comparison to model calculations suggests that $\pythiashoving$ gives comparable trend with data, but underestimates the ridge yield.
+On the other hand, $\epos$, which also provides a trend comparable with the data, overestimates the ridge yield.
 The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
@@
 	\includegraphics[width=0.89\linewidth]{./figures/Fig9_JetYieldESE.pdf}
-	\caption{ Near-side jet-like peak yield with respect to the minimum leading particle(left) and jet selections(right).
+	\caption{ Near-side jet-like peak yield with respect to the minimum leading particle (left) and jet selections (right).
 The filled circles show measurement with ALICE.
@@
 
-Finally, Near-side jet-like peak yield was measured as a function of minimum $\ptlead$ and $\ptjet$ threshold in Fig.~\ref{fig:JetYield_ESE} to further test the models that aim to describe the near-side ridge.
+Finally, near-side jet-like peak yield was measured as a function of minimum $\ptlead$ and $\ptjet$ threshold in Fig.~\ref{fig:JetYield_ESE} to further test the models that aim to describe the near-side ridge.
 %quantify the trend of the jet yield.
-$\epos$ provides comparable estimates for near-side yields, while $\pythiam$ and $\pythiashoving$ overestimate near-side yields for both selections.
-Increasing trend of near-side yield as a function of minimum $\ptlead$ and saturating trend of near-side yield as a function of minimum $\ptjet$ have been observed, which are also qualitatively explained by models.
-Near-side jet-like peak yield measured with $\ptlead>$20~GeV/$c$ is comparable with the one measured with $\ptjet>$10~GeV/$c$, where ridge yields with corresponding selections are also comparable.
+$\epos$ provides comparable estimates of the near-side jet-like peak yield, while $\pythiam$ and $\pythiashoving$ overestimate near-side yields for both selections.
+
+In all models where the ridge is due to final-state interactions, e.g., $\epos$ and $\pythiashoving$, one also expects the near side jet yield to be affected.
+This one can observe when comparing the measured near-side jet yields with PYTHIA 8 calculations with and without String Shoving.
+The new ALICE results therefore provide constraints beyond traditional ridge measurements that challenge existing models.

### 2020-11-17 sec_summary.tex
Updates after Q3

@@
 \label{sec:summary}
-Long-range azimuthal correlations were studied in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV.
-These results were obtained in the relative pseudorapidity range $1.6 < |\Delta\eta| < 1.8$ and transverse momentum interval $1 < \pt < 5$~GeV/$c$ for the trigger and associated particles.
-The results were compatible to the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+
+Long- and short-range correlations for pairs of charged particles with 1$ < \pt < $4~GeV/$c$ have been studied in pp collisions at $\sqrt{s} = 13$~TeV with a focus on high-multiplicity events.
+The ridge and near-side jet yields have been extracted and their event scale dependence have been studied.
+The obtained long-range ridge yields are compatible with the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
 %In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
 $\pythiashoving$ describes the yield qualitatively but the predicted yield decreases more rapidly than the data as $\pttrigassoc$ increases.
-On the other hand, $\epos$ gives better description for $\pt$ dependence while overestimating the ridge yield in the low $\pt<$2 GeV/$c$.
-$\pythiam$ does not describe the ridge in the long-range.
+On the other hand, $\epos$ gives better description for $\pt$ dependence while overestimating the ridge yield for $\pt<$2 GeV/$c$.
+Finally, no long-range ridge is formed in $\pythiam$.
 %Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
@@
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
-Furthermore the ridge yields were studied with the event-scale selections through the minimum transverse momentum of jet or leading particle requirement. 
+The ridge yields were further studied in high-multiplicity events biased with additional event scale selections, which imposed a minimum transverse momentum cutoff on a leading track or jet.
 The ridge structure still persists with both selections.
@@
 The results are compared with $\pythiashoving$, $\epos$ and $\pythiam$ calculations.
-$\pythiashoving$ and $\epos$ estimate qualitative trends for event-scale selection.
+$\pythiashoving$ and $\epos$ estimate qualitatively the trends for event-scale selection.
 However, the former underestimates the ridge yield and the latter overestimates the ridge yield.
-Responses to event-scale selection are further studied by measuring near-side jet-like correlations.
-$\epos$ provides better description for near-side jet-like correlations with the event-scale selection, while $\pythiashoving$ overestimates near-side jet-like correlations, which results in opposite trends between the ridge yield and near-side jet-like correlations.
+The models are further tested whether they reproduce the yield of the near-side jet-like correlation measured in the biased events.
+
+Evolution of the near-side jet yield as a function event-scale $\pt$ is better captured by $\epos$, while $\pythiashoving$ tends to overshoot the data. 
+%which results in opposite trends between the ridge yield and near-side jet-like correlations.
 The results might open new way of studying impact parameter dependence of the small systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.

### 2020-11-17 sec_ana.tex
updates

@@
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \lvert_{\pttrig,\ptassoc}  \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \lvert_{\pttrig,\,\ptassoc}  \quad.
 \label{eq:corrfunction}
@@
 Ridge yields at large $\Delta\eta$ are extracted for various multiplicity classes and transverse momentum intervals.
-The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$,  which is the maximum $\delta\eta$ range one can use for the ALICE measurements.
+The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$,  which is the maximum $\Delta\eta$ range one can use for the ALICE measurements.
 At low $\pt$, the jet-like correlations extend into this region and for this reason the ridge yield is only reported for $\pt>$~1GeV/$c$.
@@
 Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
-The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{ALICE2019:KTJETSub}.
+The transverse momentum of jets $\ptjet$ is corrected for underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{ALICE2019:KTJETSub}.
 
-To quantify variation of near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $p_\mathrm{T,\,jet}$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
+To quantify variation of near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $\ptjet$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
 The near-side is defined as $|\Delta\varphi|<$1.28, where the correlation function is projected on the $\Delta\eta$ axis.
@@
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } = \int_{|\Delta \varphi|<1.28} \rm{d} \Delta \varphi \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\varphi} \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } = \int_{|\Delta \varphi|<1.28} \rm{d} \Delta \varphi \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\varphi} - C_{\rm{ZYAM}} \quad.
 \end{eqnarray}
@@
 \begin{eqnarray}
-Y^{\rm{near}} = \int_{|\Delta \eta|<1.6} \rm{d} \Delta\eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } - C_{\rm{ZYAM}} \right)\quad.
+Y^{\rm{near}} = \int_{|\Delta \eta|<1.6} \rm{d} \Delta\eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } \right)\quad.
 \end{eqnarray}

### 2020-11-17 sec_results.tex
updates

@@
 Left: HM events with a $\ptlead>$ 9 GeV/$c$ leading track.
-Right: HM events with a $\ptlead>$ 10 GeV/$c$.}
+Right: HM events with a $\ptjet>$ 10 GeV/$c$.}
 	\label{fig:PlotCorrHMTSel}
@@
 
-In all models where the ridge is due to final-state interactions, e.g., $\epos$ and $\pythiashoving$, one also expects the near side jet yield to be affected.
-This one can observe when comparing the measured near-side jet yields with PYTHIA 8 calculations with and without String Shoving.
+In all models where the ridge is due to final-state interactions, e.g., $\epos$ and PYTHIA 8 String Shoving, one also expects the near-side jet-like peak yield to be affected.
+This can be observed when comparing the measured near-side jet yields with PYTHIA 8 calculations with and without String Shoving.
 The new ALICE results therefore provide constraints beyond traditional ridge measurements that challenge existing models.

### 2020-12-06 paper.tex
updates

@@
 \usepackage {array}
-\linenumbers
+%\linenumbers
 
@@
 \PHyear{}
-\PHnumber{2019-xxx}      % required, will be obtained from PH
+\PHnumber{2020-xxx}      % required, will be obtained from PH
 %\PHdate{Day Month}  % required, will be obtained from PH
@@
 %%% Put your own title + short title here:
-\title{Long- and short-range correlations and their event scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
+\title{Long- and short-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
 \ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
@@
 %\input{abstract.tex}
-Two-particle angular correlations have been measured in high-multiplicity $\sqrt{s} =13$ TeV proton-proton collisions by the ALICE collaboration.
-From the correlations, the yields of particle pairs at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity have been extracted on the near side ($\Delta\varphi$ $\sim$ 0).
+Two-particle angular correlations are measured in high-multiplicity $\sqrt{s} =13$ TeV proton-proton collisions by the ALICE collaboration.
+From the correlations, the yields of particle pairs at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity are extracted on the near side ($\Delta\varphi$ $\sim$ 0).
 The correlations and yields are reported as a function of transverse momentum ($p_{\mathrm T}$) in the range 1$ < p_{\mathrm T} < $4 GeV/$c$.
-Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 
-The results demonstrate that the long-range ``ridge`` yield, related to the collective behavior of the produced system, is present in events with high-$p_{\mathrm T}$ processes.
-The magnitudes of the short- and long-range yields are found to grow with the event scale.
-The results have been compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
-It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependencies.
+Furthermore, the event-scale dependence is for the first time studied by requiring the presence of high-$p_{\rm T}$ leading tracks and jets for varying $p_{\rm T}$ thresholds. 
+The results demonstrate that the long-range ``ridge`` yield, possibly related to the collective behavior of the produced system, is present in events with high-$p_{\mathrm T}$ processes.
+The magnitudes of the short- and long-range yields are found to grow with the event-scale.
+The results are compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
+It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event-scale dependencies.
 
@@
 \section*{Acknowledgements}
-\noindent The ALICE Collaboration would like to thank Christian Bierlich for providing the PYTHIA8 string shoving calculations.
+\noindent The ALICE Collaboration would like to thank Christian Bierlich for providing the PYTHIA8 String Shoving calculations.
 %{\it (TBI: The default acknowledgments will be done by EB centrally.)}

### 2020-12-06 sec_ana.tex
updates

@@
 You can find more details about SPD in~\cite{Santoro2009:ALICESPD}.
-The ITS and TPC covering the full azimuthal region have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles emitted from a primary vertex with $|z_\mathrm{vtx}| < 8$~cm.
+The ITS and TPC, covering the full azimuthal region, have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles emitted within 8 cm from the primary vertex ($z_\mathrm{vtx}$) along the beam direction.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
@@
 
-The analyzed data samples of minimum-bias and high-multiplicity pp $\sqrt{s}=$13 TeV events correspond to integrated luminosities of 19 nb$^{-1}$ and 11 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
+The analyzed data samples of minimum-bias and high-multiplicity pp events at $\sqrt{s}=$13 TeV correspond to integrated luminosities of 19 nb$^{-1}$ and 11 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
 
@@
 The tracks from the second class do not have any SPD associated hit and mainly rely on the position information of the primary vertex when reconstructing the tracks.
-Charge particle selection criteria are optimized for a homogeneous response over the full TPC volume to mitigate the effect of small regions where some of ITS layers are inactive.
+Charge particle selection criteria are optimized for a homogeneous response over the full TPC volume to mitigate the effect of small regions where some of the ITS layers are inactive.
 The selected set of tracks consists of two track classes.
@@
 
-The two-particle correlation function is measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle differences ($\Delta\varphi$) between the trigger and associated particles,
+The two-particle correlation function is measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle difference ($\Delta\varphi$) between the trigger and associated particles,
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \lvert_{\pttrig,\,\ptassoc}  \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \lvert_{\pttrig,\,\ptassoc}  \quad,
 \label{eq:corrfunction}
@@
 The right-hand side of Eq.
-1 had been corrected for the track reconstruction efficiency, which is mainly relevant for the associated particles.
-Primary vertices of events to be mixed are required to be within the same, 2 cm wide $z_{\rm{vtx}}$ bin.
+(1) has been corrected for the track reconstruction efficiency, which is mainly relevant for the associated particles.
+Primary vertices of events to be mixed are required to be within the same 2 cm wide $z_{\rm{vtx}}$ bin~\cite{KOPYLOV1974472:evtmixing}.
 The final per-trigger yield is constructed by averaging correlation functions over these primary vertex bins.
@@
 The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$,  which is the maximum $\Delta\eta$ range one can use for the ALICE measurements.
-At low $\pt$, the jet-like correlations extend into this region and for this reason the ridge yield is only reported for $\pt>$~1GeV/$c$.
-The $\delta\Delta\eta$ is the normalization factor to get per-trigger yield per unit pseudorapidity.
+At low $\pt$, the jet-like correlations extend into this region and for this reason the ridge yield is only reported for $\pt>$~1 GeV/$c$.
 In this region, the $\Delta\varphi$ distribution, or the so called per-trigger yield is expressed as
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \rm{d} \Delta \eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\eta} - C_{\rm{ZYAM}} \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta_{\Delta\eta}} \rm{d}\Delta \eta - C_{\rm{ZYAM}} \quad,
 \end{eqnarray}
+where $\delta_{\Delta\eta}$ is the normalization factor to get per-trigger yield per unit pseudorapidity.
 
-The baseline of the correlations is subtracted by means of the Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
-The minimum yield $(C_{\rm{ZYAM}})$ at the $\Delta\varphi=\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ projection (Note that the value of $\Delta\varphi_{\rm{min}}$ can be different in data and in models.) is obtained from the function, which fits the data with a Fourier series up to the third harmonic.
-Subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ projection makes the yield at $\Delta\varphi_{\rm{min}}$ zero.
+The baseline of the correlation is subtracted by means of the Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
+The minimum yield $(C_{\rm{ZYAM}})$ at $\Delta\varphi=\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ projection (Note that the value of $\Delta\varphi_{\rm{min}}$ can be different in data and in models.) is obtained from the function, which fits the data with a Fourier series up to the third harmonic.
+By construction, the yield at $\Delta\varphi_{min}$ is zero after subtracting $C_{ZYAM}$ from the $\Delta\varphi$ projection.
 The ridge yield ($Y^{\rm{ridge}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ projection over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure,
@@
 On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
-The event-scale is set by requiring a minimum transverse momentum of leading track or reconstructed jet in mid-rapidity.
+This event scale is set by requiring a minimum transverse momentum of the leading track or the reconstructed jet at mid-rapidity.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.
@@
 Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
-The transverse momentum of jets $\ptjet$ is corrected for underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{ALICE2019:KTJETSub}.
+The transverse momentum of jets $\ptjet$ is corrected for the underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{ALICE2019:KTJETSub}.
 
-To quantify variation of near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $\ptjet$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
+To quantify the variation of the near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $\ptjet$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
 The near-side is defined as $|\Delta\varphi|<$1.28, where the correlation function is projected on the $\Delta\eta$ axis.
-The $\delta\Delta\varphi$ is the normalization factor to get per-trigger yield per unit azimuthal angle.
 The near-side $\Delta\eta$ correlations are constructed as
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } = \int_{|\Delta \varphi|<1.28} \rm{d} \Delta \varphi \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta\Delta\varphi} - C_{\rm{ZYAM}} \quad.
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } = \int_{|\Delta \varphi|<1.28} \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta_{\Delta\varphi}} \rm{d} \Delta \varphi - \it{D}_{\rm{ZYAM}} \quad,
 \end{eqnarray}
+where $\delta_{\Delta\varphi}$ is the normalization factor to get per-trigger yield per unit azimuthal angle.
 
-The baseline of the $\Delta\eta$ correlation is also subtracted by using the ZYAM procedure.
-The minimum yield $(C_{\rm{ZYAM}})$ of $\Delta\eta$ correlations is found within $|\Delta\eta|<$1.6 and used for subtraction from  $\Delta\eta$ correlations, which results in zero-yield at minimum.
+The baseline of the $\Delta\eta$ correlation is also subtracted using the ZYAM procedure.
+The minimum yield $(D_{\rm{ZYAM}})$ of $\Delta\eta$ correlations is found within $|\Delta\eta|<$1.6 and used for subtraction from  $\Delta\eta$ correlations, which results in zero-yield at minimum.
 The near-side jet-like peak yield ($Y^{\mathrm{near}}$) is measured by integrating the $\Delta\eta$ correlations over $|\Delta\eta|<$1.6,
@@
 
-Systematic uncertainties on $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ were estimated by varying the analysis selection criteria and corrections, which will be explained in the following in more detail.
-Tab.~\ref{tab:syst} summarizes the obtained values.
-$Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ denotes the ridge yield as a function of $\pttrig$($\ptassoc$) in event-scale unbiased events.
-Ridge yields measured in event-scaled biased events are denoted $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ and they were evaluated for 1$<\pttrig, \ptassoc<$2 GeV/$c$.
-The uncertainties on $Y^{\rm{near}}(\ptlead)$ and $Y^{\rm{near}}(\ptjet)$ were evaluated and reported in Tab.~\ref{tab:syst} together because the measured uncertainties are comparable to each other.
+Systematic uncertainties on $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ are estimated by varying the analysis selection criteria and corrections, which will be explained in the following in more detail.
+Table~\ref{tab:syst} summarizes the obtained values.
+$Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ denotes the ridge yield as a function of $\pttrig$($\ptassoc$) in event-scale-unbiased events.
+Ridge yields measured in event-scale-biased events are denoted $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ and they are evaluated for 1$<\pttrig, \ptassoc<$2 GeV/$c$.
+The uncertainties on $Y^{\rm{near}}(\ptlead)$ and $Y^{\rm{near}}(\ptjet)$ are evaluated and reported in Tab.~\ref{tab:syst} together because the measured uncertainties are comparable to each other.
 
@@
 
-ZYAM			& 5.1	&2.1		&2.1	&N.A.	\\ \hline
+ZYAM			& 5.1	&2.1		&2.1	&---	\\ \hline
 Jet contamination	& 4.5	&3.4--8.1		&3.4--9.4	&N.A.	\\ \hline
@@
 
-The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from The main variation concerned reduction of the minimal number of track contributors required for vertex reconstruction from 5 to 3.
-The estimated uncertainty is 0.8\% for events without event-scale bias.
-The uncertainty varies up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
+The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
+The main variation concerns reduction of the minimal number of track contributors required for vertex reconstruction from 5 to 3.
+The estimated uncertainty on $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ is 0.8\% for events without event-scale bias.
+The uncertainties on $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ vary up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
 The corresponding uncertainty on $Y^{\rm{near}}$ is 0.2--2.2\%.
@@
 
-Another source of systematic uncertainty is related to the selected range of primary vertex.
-The accepted range was varied from $|z_\mathrm{vtx}|<$ 8 cm to $|z_\mathrm{vtx}|<$ 6 cm.
-The narrower primary vertex selection allows one to test the acceptance effect on the measurement.
+Another source of systematic uncertainty is related to the selected range of the primary vertex.
+The accepted range is changed from $|z_\mathrm{vtx}|<$ 8 cm to $|z_\mathrm{vtx}|<$ 6 cm.
+The narrower primary vertex selection allows one to test acceptance effects on the measurement.
 The estimated uncertainty is 0.5--12.2\% with the varying event-scale selections.
@@
 
-A Further source of systematic uncertainty is related to the imposed track selection criteria.
-The corresponding uncertainty was estimated by employing other track selection criteria, denoted global tracks, which are optimized for particle identification.
+A further source of systematic uncertainty is related to the imposed track selection criteria.
+The corresponding uncertainty is estimated by employing other track selection criteria, denoted global tracks, which are optimized for particle identification.
 The selection criteria of the global tracks are almost identical to the hybrid tracks.
@@
 %except for the requirement of at least one hit on the SPD.
-Due to inefficient parts of the SPD, azimuthal distribution of global tracks is not flat.
+Due to inefficient parts of the SPD, the azimuthal distribution of global tracks is not flat.
 %The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
@@
 The uncertainty associated with the track selection criteria variation is estimated to be 4.0\%.
-The uncertainty was obtained by averaging relative variations over different transverse momentum ranges.
+The uncertainty is obtained by averaging relative variations over different transverse momentum ranges.
 The corresponding uncertainty on $Y^{\rm{near}}$ is estimated to be 1.5--3.4\%.
 
-Systematic uncertainty resulting from the ZYAM procedure was estimated by varying the range of the fit, which is used to find the minimum, from the $|\Delta\varphi|<\pi/$2 up to $|\Delta\varphi|<1.2$.
-In case of the ridge yields that were measured in events where event-scale bias was not imposed, the estimated uncertainty is 5\%.
-On the other hands, this uncertainty is about 2\% for the ridge yields obtained in events with the $\ptlead$ or $\ptjet$ bias.
-The corresponding uncertainty on $Y^{\rm{near}}$ is not considered due to negligible deviation compared with statistical uncertainty.
+The systematic uncertainty resulting from the ZYAM procedure is estimated by varying the range of the fit, which is used to find the minimum, from $|\Delta\varphi|<\pi/$2 down to $|\Delta\varphi|<1.2$.
+The estimated uncertainty on the ridge yield is 2\% (5\%) in events with (without) the event-scale selection.
+The corresponding uncertainty on $Y^{\rm{near}}$ is negligible compared with statistical uncertainty.
 A similar source of systematic uncertainty represents the possible contamination of the ridge yield by jet fragments.
-The uncertainty was estimated by varying the $\Delta\eta$ projection range from 1.7$<\Delta\eta<$1.8 to 1.4$<\Delta\eta<$1.8 in order to see how much the jet contamination varies, which is thought be small.
+The uncertainty is estimated by varying the $\Delta\eta$ projection range from 1.7$<\Delta\eta<$1.8 to 1.4$<\Delta\eta<$1.8 in order to see how much the jet contamination varies, which is thought be small.
 The estimated uncertainty is about 3.4--9.4\%.
@@
 The final source of systematic uncertainty is associated to the choice of the width of $z_{\rm vtx}$ bins that are used in event mixing.
-The default value 2\,cm was changed to 1\,cm.
-The resulting uncertainty on ridge yield was estimated to be 1--16.4\%.
+The default value 2\,cm is changed to 1\,cm.
+The resulting uncertainty on the ridge yield is estimated to be 1--16.4\%.
 The corresponding uncertainty on $Y^{\rm{near}}$ is about 0.5--1.7\%.
-The uncertainty from the efficiency correction for charged track is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
+The uncertainty from the efficiency correction for charged tracks is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
 The estimated uncertainty is 1.2--2.5\% regardless of the event-scale selection.

### 2020-12-06 sec_intro.tex
updates

@@
 In high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, significant correlations are observed between particles emitted over a wide pseudorapidity range.
-These collective effects are indicative of the formation of a strongly interacting matter called the quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
+The origin of these observations are collective effects, which are related to the formation of a strongly interacting matter called the quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
 Recent theoretical~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} and experimental~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj} advancements have contributed significantly to understanding the transport properties of the QGP.
@@
 The ridge structures in high-multiplicity pp and p--Pb events have been attributed to initial-state effects or final-state effects.
-The initial-state effects are usually referred to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo}, which are formed along the longitudinal direction.
-The final-state effects may contribute via parton-induced interactions~\cite{Arbuzov:2011yr} or collective effects due to a hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+The initial-state effects usually referred to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo}, which are formed along the longitudinal direction.
+The final-state effects may contribute via parton-induced interactions~\cite{Arbuzov:2011yr} or collective effects due to hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
 Hybrid models implementing both effects are generally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}. 
-The proton shape and its fluctuations are also important to model the small systems~\cite{Mantysaari:2017cni}.
+The proton shape and its fluctuations are also important to model small systems~\cite{Mantysaari:2017cni}.
 %Nevertheless, the hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty,Schenke:2019pmk}. 
-The influence and interplay of the initial state and final state effects should be further studied carefully with the inclusion of  the details of the initial state for quantitative description of measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo}.
-Attempts to describe the collective effects systematically from small to large systems are being made experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Schenke:2020mbo}.
-However, a quantitative description of the full set of experimental data has not been achieved yet.
+To understand the influence of initial or final state effects, and possibly disentangle the two, a quantitative description of the measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo} needs to account for details of the initial state.
+Systematic studies of these correlation effects from small to large systems are being performed, both experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Schenke:2020mbo}.
+However, the quantitative description of the full set of experimental data has not been achieved yet.
 A summary of various explanations for the observed correlations in small systems is given in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
@@
 Besides the hybrid models mentioned above, alternative approaches have been developed to describe collectivity in small systems.
-String shoving implemented in PYTHIA 8 describes long-range correlations by generating color strings which interact and repel each other in transverse direction, which results in a microscopic transverse pressure~\cite{Bierlich:2017vhg}.
-The microscopic model for collectivity, based on interacting strings implemented in $\pythiae$ event generator the so-called ``String Shoving model''~\cite{Bierlich:2017vhg}, can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
+A microscopic model for collectivity has been implemented in the PYTHIA8 event generator, which is based on interacting strings and is called the “string shoving model”~\cite{Bierlich:2017vhg}.
+In this model, strings repel each other in the transverse direction, which results in microscopic transverse pressure and, consequently, in long-range correlations.
+PYTHIA with string shoving can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
 This challenges the hydrodynamic picture and predicts modifications to jet fragmentation properties~\cite{Bierlich:2019ixq}.
@@
 that these final-state interactions will affect also produced jets.
-Proving the presence of jet quenching would be another crucial evidence of the existence of the QGP in high-multiplicity pp collisions.
+Proving the presence of jet quenching would be another crucial evidence of the existence of a high-density strongly-interacting system, possibly a  QGP, in high-multiplicity pp collisions.
 However, so far there has been no sign of jet quenching observed in high-multiplicity pp and p--Pb collisions~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
@@
 
-To further investigate the interplay of jet production and collective effects in small systems, we simultaneously studied long- and short-range correlations in very high-multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high-multiplicity event trigger during the LHC Run 2 data taking period.
+To further investigate the interplay of jet production and collective effects in small systems, we simultaneously study long- and short-range correlations in very-high-multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high-multiplicity event trigger during the LHC Run 2 data taking period.
 In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.
@@
 In addition, we report the ridge yield and near-side jet-like correlations with event-scale selection.
-The event-scale selection is done by requiring a minimum transverse momentum of leading track or reconstructed jet in mid-rapidity, which is expected to bias the impact parameter of pp collisions to be smaller on average ~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+The event-scale selection is done by requiring a minimum transverse momentum of the leading track or the reconstructed jet at mid-rapidity, which is expected to bias the impact parameter of pp collisions to be smaller on average ~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
 The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, respectively.

### 2020-12-06 sec_results.tex
updates

@@
 Figure~\ref{fig:PlotCorrMBHMT} shows the per-trigger yield obtained from Eq.
-1 for $1 < \pttrig~\mathrm (\ptassoc) < $2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for high-multiplicity (left) and minimum bias events (right panel).
+(1) for $1 < \pttrig~\mathrm (\ptassoc) < $2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for high-multiplicity (left) and minimum bias events (right panel).
 The ridge structure is clearly observed in the high-multiplicity class while it is less visible and conclusive in the minimum bias events.
@@
 
-Figure~\ref{fig:PlotDeltaPhi} shows Delta phi projections of the two-particle correlation functions obtained in the range 1.6$<|\Delta \eta |<$1.8 for several track $\pt$ intervals after ZYAM subtraction, see Eq.
-2.
+Figure~\ref{fig:PlotDeltaPhi} shows $\Delta\varphi$ projections of the two-particle correlation functions obtained in the range 1.6$<|\Delta \eta |<$1.8 for several track $\pt$ intervals after ZYAM subtraction, see Eq.
+(2).
 Results are shown for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (upper) and the high-multiplicity class (lower) down to 1 GeV/$c$ where non-flow contamination is negligible.
-The near-side ($\Delta\varphi\sim 0$) ridge in the high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no hint of the signal in the minimum bias class.
-Within the range of analyzed particle $\pt$, yield in the near-side ridge decreases with increasing $\pt$ in the high-multiplicity class.
+The near-side ($\Delta\varphi\sim 0$) ridge in the high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no definitive signal in the minimum bias class.
+Within the range of analyzed particle $\pt$, the yield in the near-side ridge decreases with increasing $\pt$ in the high-multiplicity class.
 The measurements in the high-multiplicity class are compared to the results published by the CMS collaboration~\cite{Khachatryan:2015lva}.
-In case of the CMS measurement, charged particle multiplicity was obtained by counting $\pt>0.4$ GeV/$c$ tracks in $|\eta|<$2.4.
+In case of the CMS measurement, the charged particle multiplicity was obtained by counting $\pt>0.4$ GeV/$c$ tracks in $|\eta|<$2.4.
 In our analysis, event multiplicity is determined from the forward V0 detectors.
-The difference in multiplicity selection between ALICE (forward) and CMS (mid-rapidity) was studied using PYTHIA 8 simulations and it was found that the CMS multiplicity is ${\approx}20\,\%$ larger than the ALICE one when compared in the acceptance region of the measurements reported here, $|\eta|<$0.9.
+The difference in multiplicity selection between ALICE (forward) and CMS (mid-rapidity) is studied using PYTHIA 8 simulations and it is found that the CMS multiplicity is ${\approx}20\,\%$ larger than the ALICE one when compared in the acceptance region of the measurements reported here, $|\eta|<$0.9.
 Near-side ridges in all transverse momentum ranges are comparable to each other within the uncertainties.
-The larger away-side yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptance for the multiplicity selection, which overlaps somewhat with the $\eta$ region in Fig.~\ref{fig:PlotDeltaPhi} for CMS results.
+The larger away-side yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptance for the multiplicity selection, which overlaps somewhat with the $\eta$ region in Fig.~\ref{fig:PlotDeltaPhi} for the CMS results.
 The ALICE data are compared with model predictions where we apply a comparable high-multiplicity selection and $\Delta\eta$ projection range.
-Selection of high-multiplicity events in models was done by requiring a minimal number of charged particles that pass the V0M acceptance.
-This threshold was set to 105, which was tuned to reach the top 0-0.1\% centrality selection using $\pythiam$.
+Selection of high-multiplicity events in models is done by requiring a minimal number of charged particles that pass the V0M acceptance.
+This threshold is set to 105, which is tuned to reach the top 0--0.1\% centrality selection using $\pythiam$.
 The threshold for $\epos$ or $\pythiashoving$ is 110 or 108, respectively.
+The statistical uncertainties due to the limited number of events for model calculations are shown as band in each figure.
 The $\pythiashoving$ gives good estimates of the near-side ridge yield and slightly overestimates the away-side yield for the interval of 1$<\it{p}_{\rm{T}}<$2 GeV/$c$.
@@
 Figure~\ref{fig:PlotYSpect} shows the near-side ridge yield measured in high-multiplicity events as a function of transverse momentum.
-The ALICE data are with results from CMS~\cite{Khachatryan:2015lva}.
+The ALICE data are compared with results from CMS~\cite{Khachatryan:2015lva}.
 %The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high-multiplicity class and compared to \cite{Khachatryan:2015lva}.
-Taking into account the differences in acceptance of both measurements and chosen multiplicity estimator, the slight disagreement between the two sets of results could be expected.
+Taking into account the differences in acceptance of both measurements and in the chosen multiplicity estimator, a perfect agreement between the two sets of results is not expected.
 The data is also compared with model calculations.
 $\pythiam$ gives zero ridge yields since it does not account for the ridge effect.
-$\pythiashoving$ describes the yield qualitatively.
-however the predicted yield decreases more rapidly than the measured one as $\pttrigassoc$ increases.
+$\pythiashoving$ describes the yield qualitatively, however the predicted yield decreases more rapidly than the measured one as $\pttrigassoc$ increases.
 $\epos$, unlike $\pythiashoving$, describes well the $\pt$ dependence of the ridge yield for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range, while predicting larger yield for $\it{p}_{\rm{T}}<$2 GeV/$c$.
@@
 The ridge yield is further studied with respect to two different event-scales.
-In the first measurement, the event-scale is set by requiring a minimum $\pt$ cutoff on a leading track in event (denoted as $\ptlead$), while in the second measurement, we impose a minimum $\pt$ cutoff on a leading jet (denoted as $\ptjet$).
+In the first measurement, the event-scale is set by requiring a minimum $\pt$ cutoff on the leading track in event (denoted as $\ptlead$), while in the second measurement, we impose a minimum $\pt$ cutoff on the leading jet (denoted as $\ptjet$).
 As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) and $\ptjet>10$~GeV/$c$ (right).
@@
 The bottom panel shows a ratio of the models to the data.
-The uncertainty on the data is represented by the gray band centered around unity.}
+The total uncertainty on the data is represented by the gray band centered around unity.}
 	\label{fig:RidgeYield_ESE}
@@
 
-The ridge yields as functions of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The ridge yield as function of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
 High-multiplicity events with imposed event-scale bias exhibit increased ridge yields when compared to unbiased HM events.
@@
 On the other hand, $\epos$, which also provides a trend comparable with the data, overestimates the ridge yield.
-The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related with the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
+The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related to the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
 
@@
 The filled circles show measurement with ALICE.
-The measurements are compared with model descriptions from $\pythiam$, $\pythiashoving$, and $\epos$ for both selections.}
+The measurements are compared with model descriptions from $\pythiam$, $\pythiashoving$, and $\epos$ for both selections.
+The total uncertainty on the data is represented by the gray
+band centered around unity.}
 	\label{fig:JetYield_ESE}
@@
 
-Finally, near-side jet-like peak yield was measured as a function of minimum $\ptlead$ and $\ptjet$ threshold in Fig.~\ref{fig:JetYield_ESE} to further test the models that aim to describe the near-side ridge.
+Finally, the near-side jet-like peak yield is measured as a function of minimum $\ptlead$ and $\ptjet$ in Fig.~\ref{fig:JetYield_ESE} to further test the models that aim to describe the near-side ridge.
 %quantify the trend of the jet yield.

### 2020-12-06 sec_summary.tex
updates

@@
 
-Long- and short-range correlations for pairs of charged particles with 1$ < \pt < $4~GeV/$c$ have been studied in pp collisions at $\sqrt{s} = 13$~TeV with a focus on high-multiplicity events.
-The ridge and near-side jet yields have been extracted and their event scale dependence have been studied.
+Long- and short-range correlations for pairs of charged particles with 1$ < \pt < $4~GeV/$c$ are studied in pp collisions at $\sqrt{s} = 13$~TeV with a focus on high-multiplicity events.
+The ridge and near-side jet yields are extracted and their event scale dependence have been studied.
 The obtained long-range ridge yields are compatible with the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
@@
 $\pythiashoving$ describes the yield qualitatively but the predicted yield decreases more rapidly than the data as $\pttrigassoc$ increases.
-On the other hand, $\epos$ gives better description for $\pt$ dependence while overestimating the ridge yield for $\pt<$2 GeV/$c$.
+On the other hand, $\epos$ gives a better description for the $\pt$ dependence while overestimating the ridge yield for $\pt<$2 GeV/$c$.
 Finally, no long-range ridge is formed in $\pythiam$.
@@
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
-The ridge yields were further studied in high-multiplicity events biased with additional event scale selections, which imposed a minimum transverse momentum cutoff on a leading track or jet.
+The ridge yields are further studied in high-multiplicity events biased with additional event scale selections, which imposes a minimum transverse momentum cutoff on a leading track or jet.
 The ridge structure still persists with both selections.
@@
 However, the former underestimates the ridge yield and the latter overestimates the ridge yield.
-The models are further tested whether they reproduce the yield of the near-side jet-like correlation measured in the biased events.
-
+The model predictions are also compared with the yield of the near-side jet-like correlation measured in the biased events.
 Evolution of the near-side jet yield as a function event-scale $\pt$ is better captured by $\epos$, while $\pythiashoving$ tends to overshoot the data.
 %which results in opposite trends between the ridge yield and near-side jet-like correlations.
-The results might open new way of studying impact parameter dependence of the small systems with jet tagged events in the future and will help to explore possible physical origins of long-range correlations.
+The results might open new way of studying the impact parameter dependence of small systems with jet tagged events in the future and will help to constrain the physical origins of long-range correlations.

### 2020-12-17 paper.tex
update after CR1

--- 2020-11-12 paper.tex
@@
 %%% Put your own title + short title here:
-\title{Long- and short-range correlations and their event scale dependence in high-multiplicity pp collisions at $\sqrt{s} = 13$~TeV}
-\ShortTitle{Long-range correlations in pp collisions}   % appears on right page headers
+\title{Long- and short-range correlations and their event-scale dependence in high-multiplicity pp collisions at $\boldsymbol{\sqrt{{\textit s}}}=13$~TeV}
+\ShortTitle{Long-range correlations in pp collisions at $\sqrt{s} = 13$~TeV}   % appears on right page headers
 
@@
 %\input{abstract.tex}
-Two-particle angular correlations have been measured in high-multiplicity $\sqrt{s} =13$ TeV proton-proton collisions by the ALICE collaboration.
-From the correlations, the yields of particle pairs at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in rapidity have been extracted on the near side ($\Delta\varphi$ $\sim$ 0).
-The correlations and yields are reported as a function of transverse momentum ($p_{\mathrm T}$) in the range 1$ < p_{\mathrm T} < $5 GeV/$c$.
-Furthermore, the event-scale dependence has for the first time been studied by requiring the presence of high-$p_{\rm T}$ leading tracks and/or jets for varying $p_{\rm T}$ thresholds. 
-The results demonstrate that the long-range ``ridge`` yield, related to the collective behavior of the produced system, is present in events with high-$p_{\mathrm T}$ processes.
+Two-particle angular correlations are measured in high-multiplicity proton--proton collisions at $\sqrt{s} =13$~TeV by the ALICE Collaboration.
+The yields of particle pairs at short-($\Delta\eta$ $\sim$ 0) and long-range ($1.6 < |\Delta\eta| < 1.8$) in pseudorapidity are extracted on the near-side ($\Delta\varphi$ $\sim$ 0).
+They are reported as a function of transverse momentum ($p_{\mathrm T}$) in the range 1~$<p_{\mathrm T}<$~4 GeV/$c$.
+Furthermore, the event-scale dependence is studied for the first time by requiring the presence of high-$p_{\rm T}$ leading particles and jets for varying $p_{\rm T}$ thresholds. 
+The results demonstrate that the long-range ``ridge'' yield, possibly related to the collective behavior of the system, is present in events with high-$p_{\mathrm T}$ processes.
 The magnitudes of the short- and long-range yields are found to grow with the event scale.
-The results have been compared to calculations with EPOS LHC and PYTHIA 8, with and without string-shoving interactions.
-It is found that while both models describe the qualitative trends in the data, EPOS LHC shows a better quantitative agreement, in particular for the $p_{\rm T}$ and event scale dependences.
+The results are compared to EPOS~LHC and PYTHIA~8 calculations, with and without string-shoving interactions.
+It is found that while both models describe the qualitative trends in the data, calculations from EPOS~LHC show a better quantitative agreement, in particular for the $p_{\rm T}$ and event-scale dependencies.
 
@@
 \section*{Acknowledgements}
-\noindent The ALICE Collaboration would like to thank Christian Bierlich for providing the PYTHIA8 string shoving calculations.
+\noindent The ALICE Collaboration would like to thank Christian Bierlich for providing the PYTHIA8 String Shoving configurations.
 %{\it (TBI: The default acknowledgments will be done by EB centrally.)}

### 2020-12-17 sec_ana.tex
update after CR1

@@
 %Recent center-of-mass energy in pp collisions reaches up to $\sqrt{s} = 13$~TeV during the last LHC Run 2 period. 
-The analysis is based on the data sets of pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 during the LHC Run 2 period.
-The full description of the ALICE detector in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
-The present analysis mainly utilizes the V0~\cite{Abbas:2013taa}, ITS (Inner Tracking System)~\cite{aliceITS}, and TPC (Time Projection Chamber)~\cite{aliceTPC} detectors.
+The analysis is carried out with data samples of pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 during the LHC Run 2 period.
+The full description of the ALICE detector and its performance in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
+The present analysis utilizes the V0~\cite{Abbas:2013taa}, the Inner Tracking System (ITS)~\cite{aliceITS} and the Time Projection Chamber (TPC)~\cite{aliceTPC} detectors.
 
-The V0 detector consists of two rings, V0-A and V0-C, each made of 32 scintillator tiles, covering the full azimuthal angle within the pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
-The V0 is used to assess event activity and it provides a minimum bias (MB) and a high-multiplicity (HM) trigger.
+The V0 detector consists of stations placed on both sides of the interaction point, V0A and V0C, each made of 32 scintillator tiles, covering the full azimuthal angle within the pseudorapidity intervals $2.8 < \eta < 5.1$ and $-3.7 < \eta < -1.7$, respectively.
+The V0 is used to provide a minimum bias (MB) and a high-multiplicity (HM) trigger.
 The minimum bias trigger is obtained by a time coincidence of V0A and V0C signals.
-The event activity selection is done on the sum of the V0A and V0C signals, which is denoted V0M.
-The high multiplicity trigger requires that the V0M signal exceeds 5 times the mean value measured in minimum bias collisions, selecting the top 0.1\% of MB events that have the largest V0 multiplicity.
+The event activity selection is done on the sum of the V0A and V0C signals, which is denoted as V0M.
+The high multiplicity trigger requires that the V0M signal exceeds 5 times the mean value measured in minimum bias collisions, selecting the 0.1\% of MB events that have the largest V0 multiplicity.
+The analyzed data samples of minimum bias and high-multiplicity pp events at $\sqrt{s}=$~13 TeV correspond to integrated luminosities of 19 nb$^{-1}$ and 11 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
 
-Charged particles are reconstructed by the ITS and TPC, which are working in a uniform solenoidal magnetic field of 0.5~T.
-The ITS is a silicon tracker with six layers of sensors.
-The two innermost layers are formed by the Silicon Pixel Detector (SPD)~\cite{Santoro2009:ALICESPD}.
-%The ITS is composed of three sub-systems, Silicon Pixel Detector (SPD), Silicon Drift Detector (SDD), and Silicon Strip Detector (SSD).
-You can find more details about SPD in~\cite{Santoro2009:ALICESPD}.
+The primary vertex position is reconstructed from the measured signals in the Silicon Pixel Detector (SPD), which forms the innermost two layers of the ITS.
+Reconstructed primary vertices of selected events are required to be located within 8 cm from the center of the detector along the beam direction.
+The probability of pileup events is about 0.6\% in MB events.
+Pileup events can be resolved and are rejected if the longitudinal displacement of their primary vertices is larger than 0.8 cm.
+
+Charged-particle tracks are reconstructed by the ITS and TPC, which are operated in a uniform solenoidal magnetic field of 0.5~T along the beam direction.
+The ITS is a silicon tracker with six layers of silicon sensors where the two innermost ones are formed by the SPD~\cite{Santoro2009:ALICESPD}, the next two layers called the Silicon Drift Detector (SDD), and the outermost layers named the Silicon Strip Detector (SSD).
 The ITS and TPC, covering the full azimuthal region, have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles emitted within 8 cm from the primary vertex ($z_\mathrm{vtx}$) along the beam direction.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
-The efficiency goes up to 80\% for intermediate transverse momentum, 1--5~GeV/$c$.
-The transverse momentum resolution is around 1\% for primary tracks with low $\pt<$1~GeV/$c$, and linearly increases up to 6\% at $\pt \sim$ 40~GeV/$c$~\cite{Contin_2012:ITSPTRES}.
-%https://arxiv.org/pdf/1910.14400.pdf
-%https://arxiv.org/abs/1402.4476
+The efficiency reaches 80\% for intermediate transverse momentum, 1 to 5~GeV/$c$.
+The transverse momentum resolution is around 1\% for primary tracks with $\pt<$~1~GeV/$c$, and linearly increases up to 6\% at $\pt \sim$ 40~GeV/$c$~\cite{Contin_2012:ITSPTRES}.
+%https://arxiv.org/pdf/1910.14400.pdf %https://arxiv.org/abs/1402.4476
 
-\section{Analysis Procedure}
+The charged particle selection criteria are optimized to make the efficiency uniform over the full TPC volume to mitigate the effect of small regions where some of the ITS layers are inactive.
+The selection consists of two track classes.
+Those belonging to the first class are required to have at least one hit in the SPD.
+Tracks from the second class do not have any SPD associated hit and their initial point is instead constrained to the primary vertex~\cite{Adam:2015ewa}.
+
+\section{Analysis procedure}
 \label{sec:ana}
-
-The analyzed data samples of minimum-bias and high-multiplicity pp events at $\sqrt{s}=$13 TeV correspond to integrated luminosities of 19 nb$^{-1}$ and 11 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
-
-The primary vertex position is reconstructed by combining observed signal clusters in the SPD.
-Reconstructed primary vertices of selected events are required to be located within 8 cm from the ALICE center.
-Probability of pileup events is about 0.6\%.
-Pileup events can be resolved and rejected if the longitudinal displacement of their primary vertices is larger than 0.8 cm.
-
 %The probability of pileup is estimated to be 0.6\%.
@@
 The tracks from the second class do not have any SPD associated hit and mainly rely on the position information of the primary vertex when reconstructing the tracks.
-Charge particle selection criteria are optimized for a homogeneous response over the full TPC volume to mitigate the effect of small regions where some of the ITS layers are inactive.
-The selected set of tracks consists of two track classes.
-Tracks from the first class are required to have at least one hit in the SPD.
-Tracks from the second class do not have any SPD associated hit and their initial point is instead constrained to the primary vertex~\cite{20151:HybridTracks}.
-
-The two-particle correlation function is measured as a function of relative pseudorapidity ($\Delta\eta$) and azimuthal angle difference ($\Delta\varphi$) between the trigger and associated particles,
+The two-particle correlation function is measured as a function of the relative pseudorapidity ($\Delta\eta$) and the azimuthal angle difference ($\Delta\varphi$) between the trigger and the associated particles,
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \lvert_{\pttrig,\,\ptassoc}  \quad,
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d} \Delta\eta \rm{d}\Delta\varphi} = B(0, 0)\frac{S(\Delta\eta, \Delta\varphi)}{B(\Delta\eta, \Delta\varphi)}  \Big\lvert_{\pttrig,\,\ptassoc}\quad ,
 \label{eq:corrfunction}
 \end{eqnarray}
-where $\pttrig$ and $\ptassoc$ are transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles and $N_\mathrm{pair}$ is the number of trigger-associated particle pairs.
-$S (\Delta\eta, \Delta\varphi)$ is the average number of pairs in the same event and $B(\Delta\eta, \Delta\varphi)$ in mixed events.
-$B(\Delta\eta, \Delta\varphi)$ is normalized by its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$, so that it corrects for acceptance effects.
-The right-hand side of Eq.
-(1) has been corrected for the track reconstruction efficiency, which is mainly relevant for the associated particles.
-Primary vertices of events to be mixed are required to be within the same 2 cm wide $z_{\rm{vtx}}$ bin~\cite{KOPYLOV1974472:evtmixing}.
+where $\pttrig$ and $\ptassoc$ ($\pttrig>\ptassoc$) are the transverse momenta of the trigger and associated particles, respectively, $N_\mathrm{trig}$ is the number of trigger particles, and $N_\mathrm{pair}$ is the number of trigger-associated particle pairs.
+The average number of pairs in the same event and in mixed events are denoted as $S(\Delta\eta, \Delta\varphi)$ and $B(\Delta\eta, \Delta\varphi)$, respectively.
+Normalization of $B(\Delta\eta, \Delta\varphi)$ is done with its value at $\Delta\eta$ and $\Delta\varphi = 0$, represented as $B (0,0)$.
+Acceptance effects are corrected by dividing $S(\Delta\eta, \Delta\varphi)$ with $B(\Delta\eta, \Delta\varphi)/B (0,0)$.
+The right-hand side of Eq.~(1) is corrected for the track reconstruction efficiency, which is mainly relevant for the associated particles, as a function of transverse momentum and pseudorapidity.
+Primary vertices of events to be mixed are required to be within the same, 2 cm wide, $z_{\rm{vtx}}$ interval~\cite{KOPYLOV1974472:evtmixing,Adam:2016tsv} for each multiplicity class.
 The final per-trigger yield is constructed by averaging correlation functions over these primary vertex bins.
@@
 Ridge yields at large $\Delta\eta$ are extracted for various multiplicity classes and transverse momentum intervals.
-The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$,  which is the maximum $\Delta\eta$ range one can use for the ALICE measurements.
-At low $\pt$, the jet-like correlations extend into this region and for this reason the ridge yield is only reported for $\pt>$~1 GeV/$c$.
-In this region, the $\Delta\varphi$ distribution, or the so called per-trigger yield is expressed as
+The large $\Delta\eta$ range is selected as $1.6<|\Delta\eta|<1.8$, which is the range where the tracking quality -- efficiency and precision -- is the best.
+The ridge yield is only reported for $\pt>$~1~GeV/$c$.
+Below 1~GeV/$c$, the jet-like contribution to the correlation function extends into the region where the ridge yield is measured, 1.6~$<|\Delta\eta|<$~1.8.
+In this region, the $\Delta\varphi$ distribution, or the so-called per-trigger yield, is expressed as
 \begin{eqnarray}
-\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta_{\Delta\eta}} \rm{d}\Delta \eta - C_{\rm{ZYAM}} \quad,
+\frac{1}{N_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } = \int_{1.6<|\Delta \eta|<1.8} \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}^{2} N_{\rm{pair}} }{ \rm{d}\Delta\eta d\Delta\varphi} \right) \dfrac{1}{\delta_{\Delta\eta}} \rm{d}\Delta \eta - C_{\rm{ZYAM}}\quad ,
 \end{eqnarray}
-where $\delta_{\Delta\eta}$ is the normalization factor to get per-trigger yield per unit pseudorapidity.
+where $\delta_{\Delta\eta}=$~0.4 is the normalization factor to get the per-trigger yield per unit of pseudorapidity.
 
 The baseline of the correlation is subtracted by means of the Zero-Yield-At-Minimum (ZYAM) procedure~\cite{Ajitanand:2005jj}.
-The minimum yield $(C_{\rm{ZYAM}})$ at $\Delta\varphi=\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ projection (Note that the value of $\Delta\varphi_{\rm{min}}$ can be different in data and in models.) is obtained from the function, which fits the data with a Fourier series up to the third harmonic.
-By construction, the yield at $\Delta\varphi_{min}$ is zero after subtracting $C_{ZYAM}$ from the $\Delta\varphi$ projection.
+The minimum yield $(C_{\rm{ZYAM}})$ at $\Delta\varphi=\Delta\varphi_{\rm{min}}$ in the $\Delta\varphi$ projection (note that the value of $\Delta\varphi_{\rm{min}}$ can be different in data and in models) is obtained from a fit function, which fits the data with a Fourier series up to the third harmonic.
+By construction, the yield at $\Delta\varphi_{\rm{min}}$ is zero after subtracting $C_{\rm{ZYAM}}$ from the $\Delta\varphi$ projection.
 The ridge yield ($Y^{\rm{ridge}}$) is obtained by integrating the near-side peak of the $\Delta\varphi$ projection over $|\Delta\varphi|<|\Delta\varphi_{\rm{min}}|$ after the ZYAM procedure,
 \begin{eqnarray}
-Y^{\rm{ridge}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \rm{d} \Delta\varphi \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi } \quad.
+Y^{\rm{ridge}} = \int_{|\Delta \varphi| < |\Delta\varphi_{\rm{min}}| } \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\varphi }  \rm{d} \Delta\varphi .
 \end{eqnarray}
@@
 The ridge yield is further studied in events having a hard jet or a high-$\pt$ leading particle in the mid-rapidity region.
-Such requirement is expected to bias the impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+Such a requirement is expected to bias the impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
 %The ridge yield is further studied by exploiting the largest momentum transfer among the initial partons in a given event, which results from the hard scattering.
@@
 On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two proton ///original version
-This event scale is set by requiring a minimum transverse momentum of the leading track or the reconstructed jet at mid-rapidity.
+This event scale is set by requiring a minimum transverse momentum of the leading track ($\ptlead$) or the reconstructed jet ($\ptjet$) at midrapidity.
 The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle.
-Jets are reconstructed with charged particles only (track-based jets) with the anti-$k_{\rm{T}}$ algorithm~\cite{Cacciari2008:FASTJET,Cacciari2012:FASTJET} and the resolution parameter $R=$~0.4.
+Jets are reconstructed with charged particles only (track-based jets) with the anti-$k_{\rm{T}}$ algorithm~\cite{Cacciari:2008gp,Cacciari:2011ma} and the resolution parameter $R=$~0.4.
 The recombination scheme used in this article is the $\pt$ scheme.
-Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle.
-The transverse momentum of jets $\ptjet$ is corrected for the underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{ALICE2019:KTJETSub}.
+Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and in the full azimuthal angle.
+The transverse momentum of jets $\ptjet$ is corrected for the underlying event density that is measured using the $k_{\rm{T}}$ algorithm with $R=$~0.2~\cite{Acharya:2018eat}.
 
-To quantify the variation of the near-side jet-like peak with event-scale selections using minimum $p_\mathrm{T,\,LP}$ or $\ptjet$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
-The near-side is defined as $|\Delta\varphi|<$1.28, where the correlation function is projected on the $\Delta\eta$ axis.
-The near-side $\Delta\eta$ correlations are constructed as
+To quantify the variation of the near-side jet-like peak with event-scale selections with a minimum $p_\mathrm{T,\,LP}$ or $\ptjet$, the near-side jet-like peak yield is extracted from the near-side $\Delta\eta$ correlations.
+The near-side is defined as $|\Delta\varphi|<$~1.28, where the correlation function is projected on the $\Delta\eta$ axis.
+The projection range, 1.28, is chosen to fully cover $\Delta\varphi_{\rm{min}}$.
+The near-side $\Delta\eta$ correlations are then constructed as
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\delta_{\Delta\varphi}$ is the normalization factor to get per-trigger yield per unit azimuthal angle.
-
-The baseline of the $\Delta\eta$ correlation is also subtracted using the ZYAM procedure.
-The minimum yield $(D_{\rm{ZYAM}})$ of $\Delta\eta$ correlations is found within $|\Delta\eta|<$1.6 and used for subtraction from  $\Delta\eta$ correlations, which results in zero-yield at minimum.
-The near-side jet-like peak yield ($Y^{\mathrm{near}}$) is measured by integrating the $\Delta\eta$ correlations over $|\Delta\eta|<$1.6,
+where $\delta_{\Delta\varphi}=$~2.56 is the normalization factor to get per-trigger yield per unit of azimuthal angle.
+%The baseline of the $\Delta\eta$ correlation is also subtracted using the ZYAM procedure. 
+The minimum yield $(D_{\rm{ZYAM}})$ of the $\Delta\eta$ correlations is found within $|\Delta\eta|<$~1.6 and used for the subtraction from  the $\Delta\eta$ correlations, which results in zero-yield at the minimum.
+The near-side jet-like peak yield ($Y^{\mathrm{near}}$) is measured by integrating the $\Delta\eta$ correlations over $|\Delta\eta|<$~1.6,
 \begin{eqnarray}
-Y^{\rm{near}} = \int_{|\Delta \eta|<1.6} \rm{d} \Delta\eta \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } \right)\quad.
-\end{eqnarray}
+Y^{\rm{near}} = \int_{|\Delta \eta|<1.6} \left( \frac{1}{\it{N}_{\rm{trig}}} \frac{ \rm{d}\it{}N_{\rm{pair}} }{ \rm{d}\Delta\eta } \right) \rm{d} \Delta\eta
+\end{eqnarray} .
 
@@
 
-\section{Systematic Uncertainties of the Measured Yields}
+\section{Systematic uncertainties of the measured yields}
 \label{sec:uncertainties}
 
-Systematic uncertainties on $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ are estimated by varying the analysis selection criteria and corrections, which will be explained in the following in more detail.
-Table~\ref{tab:syst} summarizes the obtained values.
-$Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ denotes the ridge yield as a function of $\pttrig$($\ptassoc$) in event-scale-unbiased events.
-Ridge yields measured in event-scale-biased events are denoted $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ and they are evaluated for 1$<\pttrig, \ptassoc<$2 GeV/$c$.
-The uncertainties on $Y^{\rm{near}}(\ptlead)$ and $Y^{\rm{near}}(\ptjet)$ are evaluated and reported in Tab.~\ref{tab:syst} together because the measured uncertainties are comparable to each other.
+The systematic uncertainties of $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ are estimated by varying the analysis selection criteria and corrections.
+Table~\ref{tab:syst} summarizes the obtained values where $Y^{\rm{ridge}}(\pttrig, \ptassoc)$ denotes the ridge yield without event-scale selection.
+Ridge yields measured in event-scale-biased events by selecting high-$\pt$ leading particles and jets for 1~$<\ptassoc<\pttrig<$~2~GeV/$c$ are denoted as $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$, respectively.
+The uncertainties of $Y^{\rm{near}}(\ptlead)$ and $Y^{\rm{near}}(\ptjet)$ are reported in Table~\ref{tab:syst} in a single column because they are compatible to each other.
 
 \begin{table}[h!]
-\caption{The relative systematic uncertainty on the associated yield spectrum estimated for $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$, $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and $Y^{\rm{near}}$, respectively.}
+\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$, $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and $Y^{\rm{near}}$, respectively.
+The total uncertainty does not include the uncertainty from the upper limit of the jet contamination.
+}
 \centering
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{c|c|c|c|c}
 \hline 
-\multirow{2}{*}{Sources}  & \multicolumn{4}{c|}{Systematic uncertainty (\%)} \\\cline{2-5} 
-         & $Y^{\rm{ridge}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{ridge}}(\it{p}_{\rm{T, Lead}})$ & $Y^{\rm{ridge}}(\it{p}_{\rm{T, Jet}})$ & $Y^{\rm{near}}$ \\ \hline \hline
-Pileup rejection		& 0.8	&0.1--3.7		&0.1--3.9	&0.2--2.2	\\ \hline
-Primary vertex		& 2.4	&0.5--12.2	&0.5--8.2	&1.1--7.8	\\ \hline
+\multirow{2}{*}{Sources}  & \multicolumn{4}{c}{Systematic uncertainty (\%)} \\\cline{2-5} 
+         & $Y^{\rm{ridge}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{ridge}}(\ptlead)$ & $Y^{\rm{ridge}}(\ptjet)$ & $Y^{\rm{near}}$ \\ \hline 
+Pileup rejection		& 0.8	&0.1--3.7		&0.1--3.9	&0.2--2.2	\\ 
+Primary vertex		& 2.4	&0.5--12.2	&0.5--8.2	&1.1--7.8	\\
 
-Tracking			& 4.0 	&2.0		&2.0	&1.5--3.4	\\ \hline
+Tracking			& 4.0 	&2.0		&2.0	&1.5--3.4	\\
 
-ZYAM			& 5.1	&2.1		&2.1	&---	\\ \hline
-Jet contamination	& 4.5	&3.4--8.1		&3.4--9.4	&N.A.	\\ \hline
+ZYAM			& 5.1	&2.1		&2.1	&---	\\ 
+Event mixing			& 4.4	&1.0--9.6		&1.0--16.4	&0.5-1.7	\\
 
-Event mixing			& 4.4	&1.0--9.6		&1.0--16.4	&0.5-1.7	\\ \hline
-
-Efficiency correction	& 2.5 	&1.2		&1.2	&3.1	\\ \hline \hline
-Total(in quadrature)			& 9.7	&4.2--18.2	&4.2--22.0	&3.9--10.9 \\ 
+Efficiency correction	& 2.5 	&1.2		&1.2	&3.1	\\  
+Jet contamination	& 18.8--25.9 ($\pt<$~2~GeV/$c$)	& 18.9		&18.9	&N.A.	\\ \hline 
+Total (in quadrature)			& 7.6	&3.3--16.3	&3.3--19.0	&3.9--10.9 \\ 
 \hline 
@@
 
-The uncertainty from the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
-The main variation concerns reduction of the minimal number of track contributors required for vertex reconstruction from 5 to 3.
-The estimated uncertainty on $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ is 0.8\% for events without event-scale bias.
-The uncertainties on $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ vary up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
-The corresponding uncertainty on $Y^{\rm{near}}$ is 0.2--2.2\%.
+The uncertainty associated to the pileup rejection is estimated by measuring the changes of results with different rejection criteria from the default one.
+It is mainly estimated by varying the minimal number of track contributors required for reconstruction of pileup event vertices from 3 to 5.
+The estimated uncertainty of $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ is 0.8\% for events without event-scale bias.
+The uncertainties of $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ vary up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
+The corresponding uncertainty of $Y^{\rm{near}}$ is 0.2--2.2\%.
 %Pileup cut (multbins) -> (default pileup from the physics selection)
@@
 
-A further source of systematic uncertainty is related to the imposed track selection criteria.
+An additional source of systematic uncertainty is related to the track selection criteria.
 The corresponding uncertainty is estimated by employing other track selection criteria, denoted global tracks, which are optimized for particle identification.
@@
 %except for the requirement of at least one hit on the SPD.
-Due to inefficient parts of the SPD, the azimuthal distribution of global tracks is not flat.
+Due to inefficient parts of the SPD, the azimuthal distribution of global tracks is not uniform.
 %The variation is achieved by changing the mandatory SPD requirement and the maximal threshold for chi-square of the track fit.
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The uncertainty associated with the track selection criteria variation is estimated to be 4.0\%.
+The uncertainty associated with the track selection is estimated to be 4.0\%.
 The uncertainty is obtained by averaging relative variations over different transverse momentum ranges.
@@
 The systematic uncertainty resulting from the ZYAM procedure is estimated by varying the range of the fit, which is used to find the minimum, from $|\Delta\varphi|<\pi/$2 down to $|\Delta\varphi|<1.2$.
-The estimated uncertainty on the ridge yield is 2\% (5\%) in events with (without) the event-scale selection.
-The corresponding uncertainty on $Y^{\rm{near}}$ is negligible compared with statistical uncertainty.
-A similar source of systematic uncertainty represents the possible contamination of the ridge yield by jet fragments.
-The uncertainty is estimated by varying the $\Delta\eta$ projection range from 1.7$<\Delta\eta<$1.8 to 1.4$<\Delta\eta<$1.8 in order to see how much the jet contamination varies, which is thought be small.
-The estimated uncertainty is about 3.4--9.4\%.
-This uncertainty was considered only for the measured ridge yields.
+The estimated uncertainty is 2\% (5\%) for the ridge yield in events with (without) the event-scale selection.
+The corresponding uncertainty on $Y^{\rm{near}}$ is negligible compared to the statistical uncertainty.
 
-The final source of systematic uncertainty is associated to the choice of the width of $z_{\rm vtx}$ bins that are used in event mixing.
-The default value 2\,cm is changed to 1\,cm.
-The resulting uncertainty on the ridge yield is estimated to be 1--16.4\%.
-The corresponding uncertainty on $Y^{\rm{near}}$ is about 0.5--1.7\%.
-The uncertainty from the efficiency correction for charged tracks is estimated by comparing correlations functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
-The estimated uncertainty is 1.2--2.5\% regardless of the event-scale selection.
-The uncertainty for $Y^{\rm{near}}$ is estimated to be 3.1\%.
+The source of systematic uncertainty is associated to the choice of the width of $z_{\rm vtx}$ bins that are used in the event mixing method.
+The default value of 2\,cm is changed to 1\,cm.
+The resulting uncertainty of the ridge yield is 1.0--16.4\% for the different $\pttrig$ ($\ptassoc$) intervals.
+The uncertainty for $Y^{\rm{near}}$ is about 0.5--1.7\% as a function of $\ptlead$ ($\ptjet$).
+The uncertainty from the efficiency correction for charged particles is estimated by comparing correlation functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
+The estimated uncertainties are 2.5\%, 1.2\%, 1.2\%, and 3.1\% for $Y^{\rm{ridge}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$,  $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and $Y^{\rm{near}}$, respectively.
+
+In the limited $\eta$-acceptance of ALICE, the ridge structure is not flat in $\Delta \eta$ suggesting that jet-like correlations (non-flow) could contribute, implying that they would impact the ridge-yield extraction.
+We stress that the models used for comparisons also contain such a non-flow effect, but differences in jet-like correlations between data and MC models could influence the interpretation.
+To account for the related uncertainty, the variation of the yield with $\Delta\eta$ between 1.5 and 1.8, which should be an upper limit of the residual jet-like contamination, is used as a systematic uncertainty of the ridge yield.
+The estimated upper limit of the uncertainty is 25.9\% for the 1.0~$<\pt<$~1.5~GeV/$c$ range, 18.8\% for the 1.5~$<\pt<$~2.0 GeV/$c$ range, 18.9\% for the 1.0~$<\pt<$~2.0~GeV/$c$ range, and negligible for $\pt>$~2.0~GeV/$c$.
+This uncertainty is considered only for the measured ridge yields.
 

### 2020-12-17 sec_intro.tex
update after CR1

@@
 
-In high-energy nucleus-nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, significant correlations are observed between particles emitted over a wide pseudorapidity range.
-The origin of these observations are collective effects, which are related to the formation of a strongly interacting matter called the quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
-Recent theoretical~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard2019} and experimental~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj} advancements have contributed significantly to understanding the transport properties of the QGP.
-Similar long-range correlations, typically interpreted as signatures of collectivity in heavy-ion collisions, are also observed in high-multiplicity proton-proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton-nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and lighter nucleus-nucleus systems~\cite{PHENIX:2018lia,Aidala:2017ajz}.
-Azimuthal correlations of particles separated by a large gap in pseudorapidity may suggest hydrodynamic behavior even in these small systems, although the volume and lifetime of the medium produced by such a colliding system are expected to be small, and there are other mechanisms which can produce similar flow-like signals~\cite{Busza:2018rrf,Nagle:2018nvi}.
+In high-energy nucleus--nucleus collisions at RHIC~\cite{Adams:2005dq,Adcox:2004mh,Arsene:2004fa,Back:2004je} and LHC~\cite{Abelev:2012di, Abelev:2014pua, ATLAS:2011ah}, significant correlations are observed between particles emitted over a wide pseudorapidity range.
+The origin of these observations are collective effects, which are related to the formation of a strongly interacting quark-gluon plasma (QGP), which exhibits hydrodynamic behavior (see the reviews~\cite{Romatschke:2007mq,Jeon:2015dfa,Romatschke:2017ejr}).
+Recent theoretical~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard:2019bmu} and experimental~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj} advancements have contributed significantly to the understanding of the transport properties of the QGP.
+Similar long-range correlations are also observed in high-multiplicity proton--proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton--nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and light nucleus--nucleus collisions~\cite{PHENIX:2018lia,Aidala:2017ajz}.
+The fact that these correlations extend over a large range in pseudorapidity implies that they originate from early times in these collisions and thus suggest that hydrodynamic behavior is present even in these small systems, although the volume and lifetime of the medium produced in such a collision system are expected to be small, and there are other mechanisms which can produce similar flow-like signals~\cite{Busza:2018rrf,Nagle:2018nvi}.
 %The observed long-range azimuthal correlations suggest flow with hydrodynamic characteristics even in these small systems, though the volume and lifetime of the medium produced by such a system are expected to be small~\cite{Busza:2018rrf,Nagle:2018nvi}.
 
-Measurements of two-particle angular correlations give information on many physical effects, including collectivity, hadronization, fragmentation, and femtoscopic effects~\cite{Lisa:2005dd}, and are typically quantified as a function of $\Delta\eta$, the relative pseudorapidity, and $\Delta\varphi$, the separation in azimuthal angle, of pairs of particles.
-The long-range structure of two-particle correlation functions is well suited to analyse collective effects, since it is not created by resonance decays and fragmentation of high-momentum partons.
-A typical source of long-range correlations in Monte Carlo pp generators is momentum conservation.
+Measurements of two-particle angular correlations provide information on many physical effects, including collectivity, hadronization, fragmentation, and femtoscopic effects~\cite{Lisa:2005dd}, and are typically quantified as a function of $\Delta\eta$, the relative pseudorapidity, and $\Delta\varphi$, the separation in azimuthal angle, of particle pairs.
+The long-range structure of two-particle angular correlations is well suited to analyze collective effects, since it is not created by resonance decays nor fragmentation of high-momentum partons.
+A typical source of long-range correlations in Monte Carlo pp generators is the momentum conservation.
 %and away-side ($\Delta\varphi$ $\approx$ $\pi$) jet correlations.
-The enhancement in the associated yield of two-particle correlations at small $\Delta\varphi$ that extends over a large $\Delta\eta$, is dubbed ``ridge'' due to its characteristic shape in the $\Delta\eta$--$\Delta\varphi$ plane.
+The enhancement in the yield of two-particle correlations at small $\Delta\varphi$ that extends over a large $\Delta\eta$ is dubbed ``ridge'' due to its characteristic shape in the $\Delta\eta$--$\Delta\varphi$ plane.
 The shape of these $\Delta\varphi$ correlations can be studied via a Fourier decomposition~\cite{Poskanzer:1998yz,Voloshin:2008dg}.
 The second and third order terms are the dominant harmonic coefficients.
-In heavy-ion collisions, harmonic coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard2019}.
+In heavy-ion collisions, harmonic coefficients can be related to the collision geometry and density fluctuations of the colliding nuclei~\cite{Alver:2010gr,Alver:2010dn,ALICE:2011ab} and to transport properties of the QGP in relativistic viscous hydrodynamic models~\cite{Gale:2012rq,Niemi:2015qia,Shen:2014vra,Bernhard:2016tnd,Bernhard:2019bmu}.
 
 % TODO more pA measurements
-The ridge structures in high-multiplicity pp and p--Pb events have been attributed to initial-state effects or final-state effects.
-The initial-state effects usually referred to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma} and color reconnections~\cite{Ortiz:2013yxa,Sarma:2019teo}, which are formed along the longitudinal direction.
-The final-state effects may contribute via parton-induced interactions~\cite{Arbuzov:2011yr} or collective effects due to hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+The ridge structures in high-multiplicity pp and p--Pb events have been attributed to initial-state or final-state effects.
+Initial-state effects, usually attributed to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma}, can form along the longitudinal direction.
+The final-state effects might be parton-induced interactions~\cite{Arbuzov:2011yr} or collective phenomena due to hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
 Hybrid models implementing both effects are generally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}.
+EPOS LHC describes collectivity in small systems with a parameterized hydrodynamic evolution of the high-energy density region, so called ``core'', formed by many color string fields~\cite{Pierog:2013ria}.
 The proton shape and its fluctuations are also important to model small systems~\cite{Mantysaari:2017cni}.
 %Nevertheless, the hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty,Schenke:2019pmk}. 
-To understand the influence of initial or final state effects, and possibly disentangle the two, a quantitative description of the measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo} needs to account for details of the initial state.
+To understand the influence of initial or final state effects, and to possibly disentangle the two, a quantitative description of the measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo} needs to account for details of the initial state.
 Systematic studies of these correlation effects from small to large systems are being performed, both experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Schenke:2020mbo}.
 However, the quantitative description of the full set of experimental data has not been achieved yet.
-A summary of various explanations for the observed correlations in small systems is given in ~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi}.
+A summary of various explanations for the observed correlations in small systems is given in~\cite{Strickland:2018exs,Loizides:2016tew,Nagle:2018nvi,Loizides:2016tew}.
 
-Besides the hybrid models mentioned above, alternative approaches have been developed to describe collectivity in small systems.
-A microscopic model for collectivity has been implemented in the PYTHIA8 event generator, which is based on interacting strings and is called the “string shoving model”~\cite{Bierlich:2017vhg}.
+Besides the hybrid models mentioned above, alternative approaches were developed to describe collectivity in small systems.
+A microscopic model for collectivity was implemented in the PYTHIA~8 event generator, which is based on interacting strings (string shoving) and is called the “string shoving model”~\cite{Bierlich:2017vhg}.
 In this model, strings repel each other in the transverse direction, which results in microscopic transverse pressure and, consequently, in long-range correlations.
-PYTHIA with string shoving can qualitatively reproduce the CMS near-side ridge yield~\cite{Khachatryan:2016txc}.
-This challenges the hydrodynamic picture and predicts modifications to jet fragmentation properties~\cite{Bierlich:2019ixq}.
-EPOS LHC describes collectivity in small systems with a parameterized hydrodynamic evolution of the high-energy density region, so called ``core'', formed by many color string fields~\cite{Pierog:2013ria}.
+PYTHIA~8 with string shoving can qualitatively reproduce the near-side ($\Delta\varphi\sim0$) ridge yield measured by the CMS Collaboration~\cite{Khachatryan:2016txc}.
+This challenges the hydrodynamic picture and predicts modifications of the jet fragmentation properties~\cite{Bierlich:2019ixq}.
 
-If collectivity in small systems is due to final-state interactions, it is expected 
-that these final-state interactions will affect also produced jets.
-Proving the presence of jet quenching would be another crucial evidence of the existence of a high-density strongly-interacting system, possibly a  QGP, in high-multiplicity pp collisions.
-However, so far there has been no sign of jet quenching observed in high-multiplicity pp and p--Pb collisions~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
-Jet fragmentation can be studied in two-particle correlation functions by looking at short-range correlations around $(\Delta\eta$,$\Delta\varphi)=(0,0)$~\cite{Adam:2016tsv}.
-%The choice of a reference system can thus be ambiguous especially for pp since the hard probes themselves are enhanced by requiring high-multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}, also resulting in enhancement of probability to select events with high-$\pt$ jets.
+It is expected that final-state interactions affect also produced jets if they are the source of collectivity in small systems.
+Proving the presence of jet quenching~\cite{Gyulassy:1990ye,Wang:1991xy} would be another crucial evidence of the existence of a high-density strongly-interacting system, possibly a QGP, in high-multiplicity pp collisions.
+However, there is no evidence observed so far for the jet quenching effect in high-multiplicity pp and p--Pb collisions~\cite{Khachatryan:2016odn,Adam:2016jfp,Adam:2016dau,Acharya:2017okq}.
+Jet fragmentation can be studied in two-particle angular correlations in short-range correlations around $(\Delta\eta$, $\Delta\varphi)=(0,0)$~\cite{Adam:2016tsv}.
+
+%The choice of a reference system can thus be ambiguous especially forBernhard2019 pp since the hard probes themselves are enhanced by requiring high-multiplicity event~\cite{Adam:2016jfp,Acharya:2018egz}, also resulting in enhancement of probability to select events with high-$\pt$ jets.
 %Small system studies: A theory overview 1807.07191 Strickland:2018exs
@@
 
-To further investigate the interplay of jet production and collective effects in small systems, we simultaneously study long- and short-range correlations in very-high-multiplicity pp collisions at $\sqrt{s} =13$ TeV, collected with the high-multiplicity event trigger during the LHC Run 2 data taking period.
-In this article, we present the near-side per-trigger yield at large pseudorapidity separation as a function of transverse momentum.
-The results are compared to the previous measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+To further investigate the interplay of jet production and collective effects in small systems, long- and short-range correlations are studied simultaneously in high-multiplicity pp collisions at $\sqrt{s} =13$ TeV using the ALICE LHC Run 2 data collected with the high-multiplicity event trigger in 2016--2018.
+In this article, the near-side per-trigger yield at large pseudorapidity separation is presented as a function of transverse momentum.
+The results are compared with previous measurements by the CMS Collaboration~\cite{Khachatryan:2015lva}.
 %In addition, we report the ridge yield in events, where a hard scattering took place, to explore possible physical origins of the long-range correlations.
-In addition, we report the ridge yield and near-side jet-like correlations with event-scale selection.
-The event-scale selection is done by requiring a minimum transverse momentum of the leading track or the reconstructed jet at mid-rapidity, which is expected to bias the impact parameter of pp collisions to be smaller on average ~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+In addition, the ridge yield and near-side jet-like correlations with the event-scale selection are reported.
+The event-scale selection is done by requiring a minimum transverse momentum of the leading particle or the reconstructed jet at midrapidity, which is expected to bias the impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+
 The experimental setup and analysis method are described in Sec.~\ref{sec:experiment} and \ref{sec:ana}, respectively.
 The sources of systematic uncertainties are discussed in Sec.~\ref{sec:uncertainties}.
-The results of the measurements and comparisons to model calculations are presented in Sec.~\ref{sec:results}.
-Finally, Sec.~\ref{sec:summary} summarizes the obtained results.
+The results and comparisons with model calculations of the measurements are presented in Sec.~\ref{sec:results}.
+Finally, results are summarized in~Sec.~\ref{sec:summary}.
 

### 2020-12-17 sec_results.tex
update after CR1

@@
 \subsection{Ridge yield}
-
-\begin{figure}[h!]
+\label{sec:resultunbiased}
+\begin{figure}[b!]
 	\centering
+	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
 	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corr1.pdf} }
-	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrmb.pdf} }
-	\caption{ Dihadron correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in high-multiplicity (0--0.1\%, left) and minimum-bias events (0--100\%, right).
-The intervals of $\pttrig$ and $\ptassoc$ are equally $1 < \it{p}_{\rm{T}} < $2 GeV/$c$.
-}
+	\caption{ Two-particle correlation functions as functions of $\Delta\eta$ and $\Delta\varphi$ in minimum-bias events (0--100\%, left) and high-multiplicity (0--0.1\%, right).
+Note that the near-side jet peaks exceed the chosen range of the $z$-axis.
+The intervals of $\pttrig$ and $\ptassoc$ are 1~$<\it{p}_{\rm{T}}<$~2~GeV/$c$ in both cases.}
 	\label{fig:PlotCorrMBHMT}
@@
 
-Figure~\ref{fig:PlotCorrMBHMT} shows the per-trigger yield obtained from Eq.
-(1) for $1 < \pttrig~\mathrm (\ptassoc) < $2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for high-multiplicity (left) and minimum bias events (right panel).
-The ridge structure is clearly observed in the high-multiplicity class while it is less visible and conclusive in the minimum bias events.
+Figure~\ref{fig:PlotCorrMBHMT} shows the per-trigger yield obtained from Eq.~(1) for 1~$<\pttrig~\mathrm (\ptassoc)<$~2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for minimum bias events (left) and high-multiplicity (right).
+It is worth noting that the $z$-axes for the yield of the correlations is properly scaled in order to zoom in the ridge yield, as a result, the jet peaks are sheared off in both figures.
+The ridge structure is clearly observed in the high-multiplicity class while it is less significant in the minimum bias events.
 The away-side yield is populated mostly by back-to-back jet correlations.
@@
 	\includegraphics[width=0.9\linewidth]{./figures/Fig2_PlotDeltaPhi.pdf}
-	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for three transverse momentum intervals in high-multiplicity (lower panels) and minimum bias (upper panels) events after ZYAM subtraction.
-Transverse momentum ranges of trigger particles and associated particles are $1<\pt<$2 (left), 2$<\pt<$3 (middle) and 3$<\pt<$4 GeV/$c$ (right), respectively.
+	\caption{One-dimensional $\Delta\varphi$ distribution in the large $\Delta\eta$ projection for three transverse momentum intervals in minimum bias (upper panels) and high-multiplicity (lower panels) events after ZYAM subtraction.
+Transverse momentum intervals of the trigger particles and associated particles are 1~$<\pt<$~2 (left), 2~$<\pt<$~3 (middle) and, 3~$<\pt<$~4 GeV/$c$ (right), respectively.
 The presented model predictions were calculated using $\pythiashoving$, $\pythiam$, and $\epos$.}
@@
 
-Figure~\ref{fig:PlotDeltaPhi} shows $\Delta\varphi$ projections of the two-particle correlation functions obtained in the range 1.6$<|\Delta \eta |<$1.8 for several track $\pt$ intervals after ZYAM subtraction, see Eq.
-(2).
-Results are shown for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (upper) and the high-multiplicity class (lower) down to 1 GeV/$c$ where non-flow contamination is negligible.
-The near-side ($\Delta\varphi\sim 0$) ridge in the high-multiplicity class is clearly observed in all transverse momentum ranges studied while there is no definitive signal in the minimum bias class.
+Figure~\ref{fig:PlotDeltaPhi} shows $\Delta\varphi$ projections of the two-particle correlation functions obtained in the range 1.6~$<|\Delta \eta |<$~1.8 for several track $\pt$ intervals after the ZYAM subtraction (see Eq.~(2)).
+The results are shown for various $\it{p}_{\rm{T}}$ intervals in the minimum bias class (upper) and the high-multiplicity class (lower) down to 1~GeV/$c$ where the non-flow contamination is negligible.
+The near-side ($\Delta\varphi\sim 0$) ridge in the high-multiplicity class is clearly observed for $\pt<$~3~GeV/$c$ while there is no definitive signal in the minimum bias class.
 Within the range of analyzed particle $\pt$, the yield in the near-side ridge decreases with increasing $\pt$ in the high-multiplicity class.
-The measurements in the high-multiplicity class are compared to the results published by the CMS collaboration~\cite{Khachatryan:2015lva}.
-In case of the CMS measurement, the charged particle multiplicity was obtained by counting $\pt>0.4$ GeV/$c$ tracks in $|\eta|<$2.4.
+
+The measurements in the high-multiplicity class are compared with the results published by the CMS Collaboration~\cite{Khachatryan:2015lva}.
+In case of the CMS measurement, the charged particle multiplicity was obtained by counting the number of particles satisfying $\pt>0.4$~GeV/$c$ in $|\eta|<$~2.4.
 In our analysis, event multiplicity is determined from the forward V0 detectors.
-The difference in multiplicity selection between ALICE (forward) and CMS (mid-rapidity) is studied using PYTHIA 8 simulations and it is found that the CMS multiplicity is ${\approx}20\,\%$ larger than the ALICE one when compared in the acceptance region of the measurements reported here, $|\eta|<$0.9.
-Near-side ridges in all transverse momentum ranges are comparable to each other within the uncertainties.
+The difference in multiplicity selection between ALICE (forward) and CMS (midrapidity) is studied using PYTHIA~8 simulations and it is found that the calculated multiplicity using the CMS procedure is about 20\% larger than the one from ALICE when compared in the acceptance region of the measurements reported in this article, $|\eta|<$~0.9.
+Near-side ridges in all transverse momentum ranges are comparable.
 The larger away-side yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptance for the multiplicity selection, which overlaps somewhat with the $\eta$ region in Fig.~\ref{fig:PlotDeltaPhi} for the CMS results.
-The ALICE data are compared with model predictions where we apply a comparable high-multiplicity selection and $\Delta\eta$ projection range.
-Selection of high-multiplicity events in models is done by requiring a minimal number of charged particles that pass the V0M acceptance.
-This threshold is set to 105, which is tuned to reach the top 0--0.1\% centrality selection using $\pythiam$.
-The threshold for $\epos$ or $\pythiashoving$ is 110 or 108, respectively.
-The statistical uncertainties due to the limited number of events for model calculations are shown as band in each figure.
-The $\pythiashoving$ gives good estimates of the near-side ridge yield and slightly overestimates the away-side yield for the interval of 1$<\it{p}_{\rm{T}}<$2 GeV/$c$.
-However, the $\pythiashoving$ underestimates the near-side ridge yield for $\it{p}_{\rm{T}}>$2 GeV/$c$.
-$\pythiam$ does not show any near-side ridge as expected.
-It slightly underestimates the away-side peak for $1<\it{p}_{\rm{T}}<$2 GeV/$c$ and gives good estimates for $\it{p}_{\rm{T}}>$2 GeV/$c$.
-On the other hand, $\epos$ describes quantitatively better the $\pt$ dependence in the 2$<\it{p}_{\rm{T}}<$4 GeV/$c$ range, while overestimating the near-side ridge yield for the $\it{p}_{\rm{T}}<$2 GeV/$c$ range.
+
+In Fig.~\ref{fig:PlotDeltaPhi}, the ALICE measurements are also compared with model predictions where a comparable high-multiplicity selection and $\Delta\eta$ projection range are applied.
+The selection of high-multiplicity events in the models is done by requiring a minimal number of charged particles emitted within the V0M detector acceptance.
+In case of $\pythiam$, the 0--0.1\% centrality threshold is 105 charged particles.
+The threshold for $\epos$ and $\pythiashoving$ are 110 and 108, respectively.
+The magnitude of string shoving ($g$) is set to 3.0 in this study.
+The statistical uncertainties due to the limited number of events for the model calculations are shown as bands in each figure.
+The $\pythiashoving$ provides good estimates of the near-side ridge yield and slightly overestimates the away-side yield for the interval 1~$<\it{p}_{\rm{T}}<$~2~GeV/$c$.
+However, the $\pythiashoving$ model underestimates the near-side ridge yield for $\it{p}_{\rm{T}}>$~2~GeV/$c$.
+The $\pythiam$ model does not show any near-side ridge as expected.
+It slightly underestimates the away-side peak for 1~$<\it{p}_{\rm{T}}<$~2~GeV/$c$ and provides good estimates for $\it{p}_{\rm{T}}>$~2~GeV/$c$.
+On the other hand, $\epos$ describes the shape of the ridge yield quantitatively better in the 2~$<\pttrigassoc<$~4~GeV/$c$ range, while overestimating the near-side ridge yield for $\pttrigassoc<$~2~GeV/$c$ range.
 
@@
 	\centering
-	\subfigure{\includegraphics[width=0.99\textwidth]{./figures/Fig3_PlotRidgeYield.pdf}}
+	\subfigure{\includegraphics[width=0.89\textwidth]{./figures/Fig3_PlotRidgeYield.pdf}}
 	\caption{ Fully corrected near-side ridge yield as a function transverse momentum.
-The filled circles denote the measurement with ALICE.
-The CMS measurement~\cite{Khachatryan:2015lva} is represented by open blue box markers and extends down to lower $\pt$ due to the larger $\Delta\eta$ acceptance.
-The three lines show model predictions from $\pythiam$ (blue line), $\pythiashoving$ (orange line) and $\epos$ (green line).}
+The open blue boxes denote the measurement by ALICE.
+The statistical and systematic uncertainties are shows as vertical bars and boxes, respectively.
+The CMS measurement~\cite{Khachatryan:2015lva} is represented by filled circles and extends down to lower $\pt$ due to the larger $\Delta\eta$ acceptance.
+The three lines show model predictions from $\pythiam$ (blue dotted line), $\pythiashoving$ (orange line) and, $\epos$ (green dashed line).}
 	\label{fig:PlotYSpect}
@@
 
-Figure~\ref{fig:PlotYSpect} shows the near-side ridge yield measured in high-multiplicity events as a function of transverse momentum.
-The ALICE data are compared with results from CMS~\cite{Khachatryan:2015lva}.
+Figure~\ref{fig:PlotYSpect} shows the near-side ridge yield measured in high-multiplicity events as a function of $\pttrigassoc$.
+The measurement is compared with the result from CMS~\cite{Khachatryan:2015lva}.
 %The ridge yields as a function of the transverse momentum are shown in Fig.~\ref{fig:PlotYSpect} in the high-multiplicity class and compared to \cite{Khachatryan:2015lva}.
-Taking into account the differences in acceptance of both measurements and in the chosen multiplicity estimator, a perfect agreement between the two sets of results is not expected.
-The data is also compared with model calculations.
-$\pythiam$ gives zero ridge yields since it does not account for the ridge effect.
-$\pythiashoving$ describes the yield qualitatively, however the predicted yield decreases more rapidly than the measured one as $\pttrigassoc$ increases.
-$\epos$, unlike $\pythiashoving$, describes well the $\pt$ dependence of the ridge yield for the $\it{p}_{\rm{T}}>$2 GeV/$c$ range, while predicting larger yield for $\it{p}_{\rm{T}}<$2 GeV/$c$.
+Considering the differences in acceptance and the chosen multiplicity estimator of both measurements, perfect agreement between the two sets of results is not expected.
+The measurement is also compared with model calculations.
+As expected, the PYTHIA~8 model with Tune 4C does not produce a near-side ridge because it is not designed to account for this effect.
+The $\pythiashoving$ model describes the yield qualitatively, however the predicted yield decreases more rapidly than the measured one for increasing $\pttrigassoc$.
+The $\epos$ model, unlike the $\pythiashoving$ model, describes well the $\pt$ dependence of the ridge yield for the range $\it{p}_{\rm{T}}>$~2~GeV/$c$ , while predicting larger yields for $\it{p}_{\rm{T}}<$~2 GeV/$c$.
 
@@
 	\subfigure{ \includegraphics[width=0.47 \textwidth]{./figures/corrjet.pdf} }
-	\caption{ Two-dimensional correlation functions as a function of $\Delta\eta$ and $\Delta\varphi$ in high-multiplicity events where a selection on event-scale was required in addition.
-The interval of $\pttrig$ and $\ptassoc$ is 1$<\pt<$2 GeV/$c$.
-Left: HM events with a $\ptlead>$ 9 GeV/$c$ leading track.
-Right: HM events with a $\ptjet>$ 10 GeV/$c$.}
+	\caption{ Two-dimensional correlation functions as a function of $\Delta\eta$ and $\Delta\varphi$ in high-multiplicity events including a selection on the event-scale.
+The interval of $\pttrig$ and $\ptassoc$ is 1~$<\pttrigassoc<$~2~GeV/$c$.
+Left: HM events with a $\ptlead>$~9~GeV/$c$ leading track.
+Right: HM events with a $\ptjet>$~10~GeV/$c$.}
 	\label{fig:PlotCorrHMTSel}
@@
 The ridge yield is further studied with respect to two different event-scales.
-In the first measurement, the event-scale is set by requiring a minimum $\pt$ cutoff on the leading track in event (denoted as $\ptlead$), while in the second measurement, we impose a minimum $\pt$ cutoff on the leading jet (denoted as $\ptjet$).
-As shown in Fig.~\ref{fig:PlotCorrHMTSel}, the ridge structure for $1< \pttrig\,(\ptassoc) <2$ GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>9$~GeV/$c$ (left) and $\ptjet>10$~GeV/$c$ (right).
+In the first measurement, the event-scale is set by requiring a minimum $\pt$ cutoff on the leading particle in each event (denoted as $\ptlead$), while in the second measurement, a minimum $\pt$ cutoff is imposed on the leading jet (denoted as $\ptjet$).
+
+Figure~\ref{fig:PlotCorrHMTSel} shows that the ridge structure for 1~$< \pttrig\,(\ptassoc) <$~2 GeV/$c$ still persists in high-multiplicity pp collisions with $\ptlead>$~9~GeV/$c$ (left) and $\ptjet>$~10~GeV/$c$ (right).
 %The interval is the same to the measured ridge yield is maximum without the event-scale selection.
 It is worth noting that the correlation function obtained with the minimum $\ptjet$ selection has a double peak structure which is oriented along the $\Delta\eta$ axis at $\Delta\varphi=\pi$.
-This structure emerges due to the restricted acceptance of jet tagging, $|\eta_{\rm{jet}}|<$0.4.
+This structure emerges due to the restricted acceptance of the jet tagging, $|\eta_{\rm{jet}}|<$~0.4.
 
@@
 	\includegraphics[width=0.99\linewidth]{./figures/Fig5_PlotDeltaPhiESE.pdf}
-	\caption{ $\Delta\varphi$ projections of the correlation functions constrained to 1.6$<|\Delta\eta|<$1.8 in HM events with an additional event-scale bias.
-Top: with an imposed cut on leading jet $\pt$,  bottom: with an imposed cut on leading hadron $\pt$.
+	\caption{ One-dimensional $\Delta\varphi$ projections of the correlation functions constrained to 1.6~$<|\Delta\eta|<$~1.8 in HM events with an additional event-scale bias.
+Top: with an imposed selection on the leading jet $\pt$,  bottom: with an imposed selection on the leading particle $\pt$.
 ALICE data are compared with prediction of models.}
@@
 
-Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in $1.6<|\Delta\eta|<1.8$ with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement.
-Even with the event-scale selection, the ridge is still visible at the near-side.
-The near-side ridge peak increases as the thresholds of $\ptlead$ and $\ptjet$ increase compared to the one measured in unbiased events.
+Figure~\ref{fig:PlotDeltaPhiESE} shows projected $\Delta\varphi$ distributions of the correlation functions in 1.6~$<|\Delta\eta|<$~1.8 with the minimum $\ptlead$ (lower) and $\ptjet$ (upper) requirement.
+Even with the event-scale selection, the ridge is still visible on the near-side.
+The near-side ridge peak increases as the thresholds of $\ptlead$ and $\ptjet$ increase compared to the one measured in unbiased events in Sec.~\ref{sec:resultunbiased}.
 The results are compared with $\pythiashoving$, $\pythiam$, and $\epos$ calculations.
-Near-side ridge peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$.
-On the other hand, $\pythiam$ does not show the  near-side ridge peak for neither of the two event-scale selections, but it gives compatible results for the away-side yield as $\pythiashoving$.
+The near-side ridge peaks are qualitatively reproduced by $\pythiashoving$ and $\epos$ models.
+On the other hand, the $\pythiam$ does not show the  near-side ridge peak for neither of the two event-scale selections, but it gives compatible results for the away-side yield just like the $\pythiashoving$ model.
+
 %Both models describe the away-side yield with the $\ptjet$ selection and overestimate away-side yield with the $\ptlead$ selection.
@@
 	\includegraphics[width=0.89\linewidth]{./figures/Fig6_RidgeYieldESE.pdf}
-	\caption{Near-side ridge yield as a function of the $\ptlead$ (left) and $\ptjet$ (right) bias.
+	\caption{Near-side ridge yield as a function of the $\it{p}^{\rm{LP}}_{\rm{T,min}}$ (left) and $\it{p}^{\rm{Jet}}_{\rm{T,min}}$ (right).
 Data points (filled circles) show the ALICE measurement.
-They are compared to predictions of models which are represented by color bands.
+The statistical and systematic uncertainties are shows as vertical bars and boxes, respectively.
+The upper limit of the jet contamination is not included in the  systematic uncertainty, which is 18.9\%.
+They are compared with predictions of models which are represented by colored bands.
 The bottom panel shows a ratio of the models to the data.
-The total uncertainty on the data is represented by the gray band centered around unity.}
+The uncertainty of the data is represented by the gray band centered around unity.}
 	\label{fig:RidgeYield_ESE}
@@
 
-The ridge yield as function of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{Jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
+The ridge yields as function of the minimum $\ptlead$ ($\it{p}^{\rm{LP}}_{\rm{T,min}}$) and $\ptjet$ ($\it{p}^{\rm{jet}}_{\rm{T,min}}$) selections are shown in Fig.~\ref{fig:RidgeYield_ESE}.
 High-multiplicity events with imposed event-scale bias exhibit increased ridge yields when compared to unbiased HM events.
-A moderate increase of the ridge yields as a function of $\ptlead$ or $\ptjet$ is observed and there is no difference between the two event selections within the uncertainties.
-Comparison to model calculations suggests that $\pythiashoving$ gives comparable trend with data, but underestimates the ridge yield.
-On the other hand, $\epos$, which also provides a trend comparable with the data, overestimates the ridge yield.
-The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related to the expected shorter impact parameters for dijet or multi-jet production events studied in~\cite{Frankfurt:2010ea}.
+A small increase of the ridge yields as a function of $\ptlead$ or $\ptjet$ is observed and there is no difference between the two event-scale selections within the uncertainties.
+Comparisons to model calculations show that $\pythiashoving$ provides a comparable trend with data, but underestimates the ridge yield.
+On the other hand, $\epos$ overestimates the ridge yield while providing a trend comparable with the data.
+The origin of the enhanced ridge yields for higher momentum jet-tagged events is not clear to date but it might be related to the expected smaller impact parameters for dijet or multi-jet production events as studied in~\cite{Frankfurt:2010ea}.
 
@@
 	\includegraphics[width=0.89\linewidth]{./figures/Fig9_JetYieldESE.pdf}
-	\caption{ Near-side jet-like peak yield with respect to the minimum leading particle (left) and jet selections (right).
+	\caption{ Near-side jet-like peak yield as a function of the $\it{p}^{\rm{LP}}_{\rm{T,min}}$ (left) and $\it{p}^{\rm{jet}}_{\rm{T,min}}$ (right).
 The filled circles show measurement with ALICE.
+The statistical and systematic uncertainties are shown as vertical bars and boxes, respectively.
 The measurements are compared with model descriptions from $\pythiam$, $\pythiashoving$, and $\epos$ for both selections.
-The total uncertainty on the data is represented by the gray
-band centered around unity.}
+The total uncertainty of the ratio is represented by the gray band centered around unity.}
 	\label{fig:JetYield_ESE}
@@
 Finally, the near-side jet-like peak yield is measured as a function of minimum $\ptlead$ and $\ptjet$ in Fig.~\ref{fig:JetYield_ESE} to further test the models that aim to describe the near-side ridge.
-%quantify the trend of the jet yield.
-$\epos$ provides comparable estimates of the near-side jet-like peak yield, while $\pythiam$ and $\pythiashoving$ overestimate near-side yields for both selections.
+$\epos$ provides comparable estimates of the near-side jet-like peak yield, while $\pythiam$ and $\pythiashoving$ overestimate the near-side yields for both event selections.
 
-In all models where the ridge is due to final-state interactions, e.g., $\epos$ and PYTHIA 8 String Shoving, one also expects the near-side jet-like peak yield to be affected.
-This can be observed when comparing the measured near-side jet yields with PYTHIA 8 calculations with and without String Shoving.
+In all models if the ridge is due to final-state interactions, e.g., $\epos$ and PYTHIA~8 String Shoving, one also expects the near-side jet-like peak yield to be affected.
+This can be observed when comparing the measured near-side jet yields with PYTHIA~8 calculations with and without String Shoving.
 The new ALICE results therefore provide constraints beyond traditional ridge measurements that challenge existing models.

### 2020-12-17 sec_summary.tex
update after CR1

@@
 
-Long- and short-range correlations for pairs of charged particles with 1$ < \pt < $4~GeV/$c$ are studied in pp collisions at $\sqrt{s} = 13$~TeV with a focus on high-multiplicity events.
+Long- and short-range correlations for pairs of charged particles with 1~$ < \pt < $~4~GeV/$c$ are studied in pp collisions at $\sqrt{s} = 13$~TeV with a focus on high-multiplicity events.
 The ridge and near-side jet yields are extracted and their event scale dependence have been studied.
-The obtained long-range ridge yields are compatible with the measurements by the CMS collaboration~\cite{Khachatryan:2015lva}.
+The obtained long-range ridge yields are compatible to those observed by the CMS collaboration~\cite{Khachatryan:2015lva}.
 %In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
-$\pythiashoving$ describes the yield qualitatively but the predicted yield decreases more rapidly than the data as $\pttrigassoc$ increases.
-On the other hand, $\epos$ gives a better description for the $\pt$ dependence while overestimating the ridge yield for $\pt<$2 GeV/$c$.
-Finally, no long-range ridge is formed in $\pythiam$.
+The $\pythiashoving$ model describes the observed yields qualitatively but the yields it predicts decrease more rapidly with increasing $\pttrigassoc$ than those measured.
+On the other hand, the $\epos$ model gives a better description for the $\pttrigassoc$ dependence while overestimating the ridge yield for $\pttrigassoc<$~2 GeV/$c$.
+Finally, no long-range ridge is formed in The $\pythiam$ model.
 %Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
@@
 The results are compared with $\pythiashoving$ calculations, showing the enhancement while underestimating the absolute ridge yield.
-The ridge yields are further studied in high-multiplicity events biased with additional event scale selections, which imposes a minimum transverse momentum cutoff on a leading track or jet.
-The ridge structure still persists with both selections.
-The ridge yields increase as $\ptlead$ and $\ptjet$ increase.
-The results are compared with $\pythiashoving$, $\epos$ and $\pythiam$ calculations.
-$\pythiashoving$ and $\epos$ estimate qualitatively the trends for event-scale selection.
-However, the former underestimates the ridge yield and the latter overestimates the ridge yield.
+
+The ridge yields are further studied in high-multiplicity events biased with additional event-scale selections, which impose a minimum transverse momentum cutoff on a leading track or jet.
+The ridge structure still persists with both selection criteria.
+The ridge yields increases as $\ptlead$ and $\ptjet$ increase.
+$\pythiashoving$ and $\epos$ estimate qualitatively the trends for the event-scale selections.
+However, the former underestimates and the latter overestimates it.
 The model predictions are also compared with the yield of the near-side jet-like correlation measured in the biased events.
-Evolution of the near-side jet yield as a function event-scale $\pt$ is better captured by $\epos$, while $\pythiashoving$ tends to overshoot the data.
+The evolution of the near-side jet yield as a function of event-scale $\pt$ is better captured by $\epos$, while the $\pythiashoving$ calculation tends to overshoot the data.
 %which results in opposite trends between the ridge yield and near-side jet-like correlations.
-The results might open new way of studying the impact parameter dependence of small systems with jet tagged events in the future and will help to constrain the physical origins of long-range correlations.
+The results might open a new way of studying the impact parameter dependence of small systems with jet tagged events in the future and will help to constrain the physical origins of long-range correlations.

### 2021-01-06 sec_ana.tex
updates after CR2

@@
 The analysis is carried out with data samples of pp collisions at $\sqrt{s} = 13$~TeV collected from 2016 to 2018 during the LHC Run 2 period.
-The full description of the ALICE detector and its performance in the LHC Run 2 can be found in Refs.~\cite{Aamodt:2008zz,Abelev:2014ffa}.
-The present analysis utilizes the V0~\cite{Abbas:2013taa}, the Inner Tracking System (ITS)~\cite{aliceITS} and the Time Projection Chamber (TPC)~\cite{aliceTPC} detectors.
+The full description of the ALICE detector and its performance in the LHC Run 2 can be found in~\cite{Aamodt:2008zz,Abelev:2014ffa}.
+The present analysis utilizes the V0~\cite{Abbas:2013taa}, the Inner Tracking System (ITS)~\cite{aliceITS}, and the Time Projection Chamber (TPC)~\cite{aliceTPC} detectors.
 
@@
 The event activity selection is done on the sum of the V0A and V0C signals, which is denoted as V0M.
-The high multiplicity trigger requires that the V0M signal exceeds 5 times the mean value measured in minimum bias collisions, selecting the 0.1\% of MB events that have the largest V0 multiplicity.
+The high-multiplicity trigger requires that the V0M signal exceeds 5 times the mean value measured in minimum bias collisions, selecting the 0.1\% of MB events that have the largest V0 multiplicity.
 The analyzed data samples of minimum bias and high-multiplicity pp events at $\sqrt{s}=$~13 TeV correspond to integrated luminosities of 19 nb$^{-1}$ and 11 pb$^{-1}$, respectively~\cite{ALICE-PUBLIC-2016-002}.
@@
 The ITS is a silicon tracker with six layers of silicon sensors where the two innermost ones are formed by the SPD~\cite{Santoro2009:ALICESPD}, the next two layers called the Silicon Drift Detector (SDD), and the outermost layers named the Silicon Strip Detector (SSD).
-The ITS and TPC, covering the full azimuthal region, have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles emitted within 8 cm from the primary vertex ($z_\mathrm{vtx}$) along the beam direction.
+The ITS and TPC, covering the full azimuthal region, have acceptances up to $|\eta| < 1.4$ and 0.9, respectively, for detection of charged particles emitted within 8 cm from the primary vertex position ($z_\mathrm{vtx}$) along the beam direction.
 The tracking of charged particles is done with the combined information of the ITS and TPC that enables the reconstruction of tracks down to 0.15~GeV/$c$ with about 65\% efficiency.
@@
 
-The systematic uncertainties of $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ are estimated by varying the analysis selection criteria and corrections.
-Table~\ref{tab:syst} summarizes the obtained values where $Y^{\rm{ridge}}(\pttrig, \ptassoc)$ denotes the ridge yield without event-scale selection.
-Ridge yields measured in event-scale-biased events by selecting high-$\pt$ leading particles and jets for 1~$<\ptassoc<\pttrig<$~2~GeV/$c$ are denoted as $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$, respectively.
-The uncertainties of $Y^{\rm{near}}(\ptlead)$ and $Y^{\rm{near}}(\ptjet)$ are reported in Table~\ref{tab:syst} in a single column because they are compatible to each other.
+The systematic uncertainties of $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$ are estimated by varying the analysis selection criteria and corrections and are summarized in Tab.~\ref{tab:syst}.
 
 \begin{table}[h!]
-\caption{The relative systematic uncertainty of the associated yield spectrum estimated for $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$, $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and $Y^{\rm{near}}$, respectively.
-The total uncertainty does not include the uncertainty from the upper limit of the jet contamination.
-}
+\caption{The relative systematic uncertainty of $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$. }
 \centering
-\begin{tabular}{c|c|c|c|c}
+\begin{tabular}{c|cc}
 \hline 
-\multirow{2}{*}{Sources}  & \multicolumn{4}{c}{Systematic uncertainty (\%)} \\\cline{2-5} 
-         & $Y^{\rm{ridge}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$ & $Y^{\rm{ridge}}(\ptlead)$ & $Y^{\rm{ridge}}(\ptjet)$ & $Y^{\rm{near}}$ \\ \hline 
-Pileup rejection		& 0.8	&0.1--3.7		&0.1--3.9	&0.2--2.2	\\ 
-Primary vertex		& 2.4	&0.5--12.2	&0.5--8.2	&1.1--7.8	\\
-
-Tracking			& 4.0 	&2.0		&2.0	&1.5--3.4	\\
-
-ZYAM			& 5.1	&2.1		&2.1	&---	\\ 
-Event mixing			& 4.4	&1.0--9.6		&1.0--16.4	&0.5-1.7	\\
-
-Efficiency correction	& 2.5 	&1.2		&1.2	&3.1	\\  
-Jet contamination	& 18.8--25.9 ($\pt<$~2~GeV/$c$)	& 18.9		&18.9	&N.A.	\\ \hline 
-Total (in quadrature)			& 7.6	&3.3--16.3	&3.3--19.0	&3.9--10.9 \\ 
+\multirow{2}{*}{Sources}  & \multicolumn{2}{c}{Systematic uncertainty (\%)} \\\cline{2-3} 
+         & $Y^{\rm{ridge}}$ & $Y^{\rm{near}}$ \\ \hline 
+Pileup rejection    	& $\pm$0.8--3.9    &$\pm$0.2--2.2	\\ 
+Primary vertex	        & $\pm$0.5--2.4	   &$\pm$1.1	\\ 
+Tracking		        & $\pm$2.0--4.0    &$\pm$1.5--3.4	\\ 
+ZYAM		        	& $\pm$2.1--5.1	   &$\pm$2.2	\\ 
+Event mixing	    	& $\pm$1.0--4.4	   &$\pm$0.5-1.7	\\ 
+Efficiency correction	& $\pm$2.5 	    &$\pm$3.1	\\  
+Jet contamination   	& $-$18.8--25.9 ($\pt<$~2~GeV/$c$)	&N.A.	\\ \hline 
+Total (in quadrature)			& $^{+\rm{4.9}\textrm{--}\rm{9.4}}_{-\rm{19.4}\textrm{--}\rm{21.0}}$ & $\pm$3.9--5.9 \\ 
 \hline 
@@
 It is mainly estimated by varying the minimal number of track contributors required for reconstruction of pileup event vertices from 3 to 5.
-The estimated uncertainty of $Y^{\rm{ridge}}(\pttrig,\,\ptassoc)$ is 0.8\% for events without event-scale bias.
-The uncertainties of $Y^{\rm{ridge}}(\ptlead)$ and $Y^{\rm{ridge}}(\ptjet)$ vary up to 3.9\% for events with the $\ptlead$ or $\ptjet$ selection.
-The corresponding uncertainty of $Y^{\rm{near}}$ is 0.2--2.2\%.
+The estimated uncertainty of $Y^{\rm{ridge}}$ is 0.8-3.9\%.
+The corresponding uncertainty of $Y^{\rm{near}}$ is estimated to be 0.2--2.2\%.
 %Pileup cut (multbins) -> (default pileup from the physics selection)
@@
 The narrower primary vertex selection allows one to test acceptance effects on the measurement.
-The estimated uncertainty is 0.5--12.2\% with the varying event-scale selections.
-The uncertainty for $Y^{\rm{near}}$ is estimated to be 1.1--7.8\%.
+The estimated uncertainty of $Y^{\rm{ridge}}$ is 0.5--2.4\%.
+The uncertainty for $Y^{\rm{near}}$ is estimated to be 1.1\%.
 
@@
 %https://github.com/alisw/AliRoot/blob/master/ANALYSIS/ESDfilter/macros/AddTaskESDFilter.C
-The uncertainty associated with the track selection is estimated to be 4.0\%.
-The uncertainty is obtained by averaging relative variations over different transverse momentum ranges.
-The corresponding uncertainty on $Y^{\rm{near}}$ is estimated to be 1.5--3.4\%.
+The uncertainties associated with the track selection are estimated to be 2.0--4.0\% and 1.5--3.4\% for $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$, respectively.
 
-The systematic uncertainty resulting from the ZYAM procedure is estimated by varying the range of the fit, which is used to find the minimum, from $|\Delta\varphi|<\pi/$2 down to $|\Delta\varphi|<1.2$.
-The estimated uncertainty is 2\% (5\%) for the ridge yield in events with (without) the event-scale selection.
-The corresponding uncertainty on $Y^{\rm{near}}$ is negligible compared to the statistical uncertainty.
+The systematic uncertainty of $Y^{\rm{ridge}}$ resulting from the ZYAM procedure is estimated by varying the range of the fit, which is used to find the minimum, from $|\Delta\varphi|<\pi/$2 down to $|\Delta\varphi|<1.2$.
+The estimated uncertainty of $Y^{\rm{ridge}}$ is 2.1--5.1\%.
+The corresponding uncertainty on $Y^{\rm{near}}$ is estimated by varying the range from $|\Delta\eta|<$~1.6 to $|\Delta\eta|<$~1.5 and 1.7.
+The estimated uncertainty of $Y^{\rm{near}}$ is 2.2\%.
 
@@
 The default value of 2\,cm is changed to 1\,cm.
-The resulting uncertainty of the ridge yield is 1.0--16.4\% for the different $\pttrig$ ($\ptassoc$) intervals.
-The uncertainty for $Y^{\rm{near}}$ is about 0.5--1.7\% as a function of $\ptlead$ ($\ptjet$).
+The resulting uncertainty of $Y^{\rm{ridge}}$ is 1.0--4.4\%.
+The uncertainty for $Y^{\rm{near}}$ is about 0.5--1.7\%.
 The uncertainty from the efficiency correction for charged particles is estimated by comparing correlation functions of true particles with correlations functions of reconstructed tracks with the efficiency correction in simulation.
-The estimated uncertainties are 2.5\%, 1.2\%, 1.2\%, and 3.1\% for $Y^{\rm{ridge}}(\it{p}_{\rm{T, trig}},\,\it{p}_{\rm{T, assoc}})$,  $Y^{\rm{ridge}}(\ptlead)$, $Y^{\rm{ridge}}(\ptjet)$, and $Y^{\rm{near}}$, respectively.
+The estimated uncertainties are 2.5\% and 3.1\% for $Y^{\rm{ridge}}$ and $Y^{\rm{near}}$, respectively.
 
@@
 To account for the related uncertainty, the variation of the yield with $\Delta\eta$ between 1.5 and 1.8, which should be an upper limit of the residual jet-like contamination, is used as a systematic uncertainty of the ridge yield.
-The estimated upper limit of the uncertainty is 25.9\% for the 1.0~$<\pt<$~1.5~GeV/$c$ range, 18.8\% for the 1.5~$<\pt<$~2.0 GeV/$c$ range, 18.9\% for the 1.0~$<\pt<$~2.0~GeV/$c$ range, and negligible for $\pt>$~2.0~GeV/$c$.
+The estimated upper limit of the uncertainty is $-$25.9\% for the 1.0~$<\pt<$~1.5~GeV/$c$ range,  $-$18.8\% for the 1.5~$<\pt<$~2.0 GeV/$c$ range,  $-$18.9\% for the 1.0~$<\pt<$~2.0~GeV/$c$ range, and negligible for $\pt>$~2.0~GeV/$c$.
 This uncertainty is considered only for the measured ridge yields.

### 2021-01-06 sec_intro.tex
updates after CR2

@@
 Recent theoretical~\cite{Niemi:2015qia,Bernhard:2016tnd,Bernhard:2019bmu} and experimental~\cite{ALICE:2016kpq,Acharya:2017gsw,Acharya:2017zfg,Acharya:2020taj} advancements have contributed significantly to the understanding of the transport properties of the QGP.
-Similar long-range correlations are also observed in high-multiplicity proton--proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton--nucleus (pA)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and light nucleus--nucleus collisions~\cite{PHENIX:2018lia,Aidala:2017ajz}.
+Similar long-range correlations are also observed in high-multiplicity proton--proton (pp)~\cite{Aad:2015gqa,Khachatryan:2015lva,Khachatryan:2016txc,Acharya:2019vdf}, proton--nucleus (p--A)~\cite{Abelev:2012ola,Aad:2014lta,Aaboud:2016yar,Khachatryan:2016ibd}, and light nucleus--nucleus collisions~\cite{PHENIX:2018lia,Aidala:2017ajz}.
 The fact that these correlations extend over a large range in pseudorapidity implies that they originate from early times in these collisions and thus suggest that hydrodynamic behavior is present even in these small systems, although the volume and lifetime of the medium produced in such a collision system are expected to be small, and there are other mechanisms which can produce similar flow-like signals~\cite{Busza:2018rrf,Nagle:2018nvi}.
@@
 The ridge structures in high-multiplicity pp and p--Pb events have been attributed to initial-state or final-state effects.
-Initial-state effects, usually attributed to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma}, can form along the longitudinal direction.
-The final-state effects might be parton-induced interactions~\cite{Arbuzov:2011yr} or collective phenomena due to hydrodynamic behavior of the produced particles arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
+Initial-state effects, usually attributed to gluon saturation~\cite{Dusling:2012cg,Bzdak:2013zma}, can form long-range
+correlations along the longitudinal direction.
+The final-state effects might be parton-induced interactions~\cite{Arbuzov:2011yr} or collective phenomena due to hydrodynamic behavior of the produced matter arising in a high-density system possibly formed in these collisions~\cite{Weller:2017tsr,Zhao:2017rgg}.
 Hybrid models implementing both effects are generally used in hydrodynamic simulations~\cite{Greif:2017bnr,Mantysaari:2017cni}.
@@
 %Nevertheless, the hydrodynamics itself might not be the only mechanism of the observed collectivity~\cite{Zhao:2020pty,Schenke:2019pmk}. 
-To understand the influence of initial or final state effects, and to possibly disentangle the two, a quantitative description of the measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo} needs to account for details of the initial state.
+To understand the influence of initial- or final-state effects, and to possibly disentangle the two, a quantitative description of the measurements in small systems~\cite{Schenke:2019pmk,Schenke:2020mbo} needs to account for details of the initial state.
 Systematic studies of these correlation effects from small to large systems are being performed, both experimentally~\cite{Acharya:2019vdf} and theoretically~\cite{Schenke:2020mbo}.
@@
 The event-scale selection is done by requiring a minimum transverse momentum of the leading particle or the reconstructed jet at midrapidity, which is expected to bias the impact parameter of pp collisions to be smaller on average~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
+At the same time, the transverse momentum of the leading particle or the reconstructed jet is a measure of the momentum transfer in the hard parton scattering~\cite{Chatrchyan:2012tt,Chatrchyan:2011id}.
 

### 2021-01-06 sec_results.tex
updates after CR2

@@
 
-Figure~\ref{fig:PlotCorrMBHMT} shows the per-trigger yield obtained from Eq.~(1) for 1~$<\pttrig~\mathrm (\ptassoc)<$~2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for minimum bias events (left) and high-multiplicity (right).
+Figure~\ref{fig:PlotCorrMBHMT} shows the per-trigger yield obtained from Eq.~(1) for 1~$<\pttrig~\mathrm (\ptassoc)<$~2 GeV/$c$ in pp collisions at $\sqrt{\it{s}} = $\unit{13} {\rm{}TeV} for minimum bias events (left) and high-multiplicity events (right).
 It is worth noting that the $z$-axes for the yield of the correlations is properly scaled in order to zoom in the ridge yield, as a result, the jet peaks are sheared off in both figures.
@@
 Near-side ridges in all transverse momentum ranges are comparable.
-The larger away-side yields observed in \cite{Khachatryan:2015lva} can be attributed to the difference in $\eta$ acceptance for the multiplicity selection, which overlaps somewhat with the $\eta$ region in Fig.~\ref{fig:PlotDeltaPhi} for the CMS results.
+The larger away-side yields observed in Fig.~\ref{fig:PlotDeltaPhi} for the CMS results can be attributed to the overlap in $\eta$ acceptance between the multiplicity selection and the correlation function measurement.
 
@@
 The open blue boxes denote the measurement by ALICE.
-The statistical and systematic uncertainties are shows as vertical bars and boxes, respectively.
+The statistical and systematic uncertainties are shown as vertical bars and boxes, respectively.
 The CMS measurement~\cite{Khachatryan:2015lva} is represented by filled circles and extends down to lower $\pt$ due to the larger $\Delta\eta$ acceptance.
-The three lines show model predictions from $\pythiam$ (blue dotted line), $\pythiashoving$ (orange line) and, $\epos$ (green dashed line).}
+The three lines show model predictions from $\pythiam$ (blue dotted line), $\pythiashoving$ (orange line), and $\epos$ (green dashed line).}
 	\label{fig:PlotYSpect}
@@
 Data points (filled circles) show the ALICE measurement.
-The statistical and systematic uncertainties are shows as vertical bars and boxes, respectively.
-The upper limit of the jet contamination is not included in the  systematic uncertainty, which is 18.9\%.
-They are compared with predictions of models which are represented by colored bands.
+The statistical and systematic uncertainties are shown as vertical bars and boxes, respectively.
+As the ridge yield is obtained in the same operational way for data and models, the upper limit of the systematic uncertainty due to jet contamination, which is 18.9\%, is not included in the figure.
+The data are compared with predictions of models which are represented by colored bands.
 The bottom panel shows a ratio of the models to the data.

### 2021-01-06 sec_summary.tex
updates after CR2

@@
 The ridge and near-side jet yields are extracted and their event scale dependence have been studied.
-The obtained long-range ridge yields are compatible to those observed by the CMS collaboration~\cite{Khachatryan:2015lva}.
+The obtained long-range ridge yields are compatible to those observed by the CMS Collaboration~\cite{Khachatryan:2015lva}.
 %In addition, the $\pt$ and the $\it{p}_{\rm{T,Lead}}$ or $\it{p}_{\rm{T,Jet}}$ selection dependence of the long-range azimuthal correlations are measured.
@@
 On the other hand, the $\epos$ model gives a better description for the $\pttrigassoc$ dependence while overestimating the ridge yield for $\pttrigassoc<$~2 GeV/$c$.
-Finally, no long-range ridge is formed in The $\pythiam$ model.
+Finally, no long-range ridge is formed in the $\pythiam$ model.
 %Furthermore the ridge yields are studied in events, where jets with a harder fragmentation are preferred by requiring the minimum value of the transverse momentum of leading particles in each event $\ptlead$ or the one of reconstructed jets $\ptjet$.
@@
 The ridge structure still persists with both selection criteria.
-The ridge yields increases as $\ptlead$ and $\ptjet$ increase.
+The ridge yield increases as $\ptlead$ and $\ptjet$ increase.
 $\pythiashoving$ and $\epos$ estimate qualitatively the trends for the event-scale selections.
